### 2019-08-28 analysis/data_simulations.Rmd
add data simulation and advance experiments

---
title: "Data simulations"
author: "M. Bohn"
date: "27 8 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tmvnsim)
library(corrr)
library(corrplot)
library(Hmisc)
library(ggthemes)

```

```{r}
sim <- function(seed,trials,sig) {

set.seed(seed)

low <- rep(0, 5)
high <- rep(1, 5)
sig <- matrix(sig, 5, 5)
diag(sig) <- 1
res <- tmvnsim(nsamp=100, k=5, lower=low, upper=high, imod=rep(F, 5)
		, means=rep(0, 5), sigma=sig)%>%
  as_tibble()

cuts = trials +1
breaks = seq(0,1,length.out = cuts+1)
labels = seq(0,1,length.out = trials+1)

x <- res$samp %>% 
  as_tibble()

mean_con <- correlate(x) %>%
  gather(key, value)%>%
  filter(key !="rowname")%>%
  na.omit()%>%
  summarise(mean_con = mean(as.numeric(value)))

x_2 <- res$samp %>% 
  as_tibble()%>%
  mutate(V1 = as.numeric(as.character(cut(V1, breaks = breaks, labels = labels))),
         V2 = as.numeric(as.character(cut(V2, breaks = breaks, labels = labels))),
         V3 = as.numeric(as.character(cut(V3, breaks = breaks, labels = labels))),
         V4 = as.numeric(as.character(cut(V4, breaks = breaks, labels = labels))),
         V5 = as.numeric(as.character(cut(V5, breaks = breaks, labels = labels))))

mean_bin <- correlate(x_2) %>%
  gather(key, value)%>%
  filter(key !="rowname")%>%
  na.omit()%>%
  summarise(mean_bin = mean(as.numeric(value)))

bind_cols(mean_con, mean_bin)

}
```

```{r}
n_sim = 1000

sim_6 <-
  tibble(seed = 1:n_sim) %>% 
  mutate(tidy = map(seed, sim, sig = .95, trials = 6))%>%
  unnest(tidy)%>%
  gather(type, corr, -seed)%>%
  mutate(trials = "6")

sim_5 <-
  tibble(seed = 1:n_sim) %>% 
  mutate(tidy = map(seed, sim, sig = .95, trials = 5))%>%
  unnest(tidy)%>%
  gather(type, corr, -seed)%>%
  mutate(trials = "5")

sim_4 <-
  tibble(seed = 1:n_sim) %>% 
  mutate(tidy = map(seed, sim, sig = .95, trials = 4))%>%
  unnest(tidy)%>%
  gather(type, corr, -seed)%>%
  mutate(trials = "4")

sim_3 <-
  tibble(seed = 1:n_sim) %>% 
  mutate(tidy = map(seed, sim, sig = .95, trials = 3))%>%
  unnest(tidy)%>%
  gather(type, corr, -seed)%>%
  mutate(trials = "3")

sim_2 <-
  tibble(seed = 1:n_sim) %>% 
  mutate(tidy = map(seed, sim, sig = .95, trials = 2))%>%
  unnest(tidy)%>%
  gather(type, corr, -seed)%>%
  mutate(trials = "2")

sim_1 <-
  tibble(seed = 1:n_sim) %>% 
  mutate(tidy = map(seed, sim, sig = .95, trials = 1))%>%
  unnest(tidy)%>%
  gather(type, corr, -seed)%>%
  mutate(trials = "1")

sim_plot = bind_rows(
  sim_6,
  sim_5,
  sim_4,
  sim_3,
  sim_2,
  sim_1
)

ggplot(sim_plot, aes(x = corr, fill = type))+
  geom_density(alpha = .5)+
  xlim(0,1)+
  facet_grid(trials~.)+
  theme_few()+
  scale_fill_ptol()

```

```{r}

n_sim = 1000

sim_4_r05 <-
  tibble(seed = 1:n_sim) %>% 
  mutate(tidy = map(seed, sim, sig = .95, trials = 5))%>%
  unnest(tidy)%>%
  gather(type, corr, -seed)%>%
  mutate(trials = "2", 
         cor = ".5")

sim_4_r03 <-
  tibble(seed = 1:n_sim) %>% 
  mutate(tidy = map(seed, sim, sig = .90, trials = 5))%>%
  unnest(tidy)%>%
  gather(type, corr, -seed)%>%
  mutate(trials = "1", 
         cor = ".3")

sim_plot_cor = bind_rows(
  sim_4_r05,
  sim_4_r03
)

ggplot(sim_plot_cor, aes(x = corr, fill = type))+
  geom_density(alpha = .5)+
  xlim(0,1)+
  facet_grid(cor~.)+
  theme_few()+
  scale_fill_ptol()
```

### 2019-08-28 experiments/pragBat.js

@@ -16,6 +16,14 @@ for (i = 0; i < preSounds.length; i++) {
 	sound[i].src = "sound/" + preSounds[i];
 }
 
+
+// change button color on click 
+
+function submitButtonStyle(_this) {
+  _this.style.backgroundColor = "green";
+}
+
+
 // ## Helper functions
 
 
@@ -455,11 +463,11 @@ var train = {
     checkInput: function() {
 		//subject ID
 		if (document.getElementById("subjectID").value.length < 1) {
-			$("#checkMessage").html('<font color="red">Bitte subject ID eintragen</font>');
+			$("#checkMessage").html('<font color="red">Bitte Kind ID eintragen</font>');
 			return;
 		}
         if (document.getElementById("subjectAge").value.length < 1) {
-			$("#checkMessage").html('<font color="red">Bitte subject age eingeben</font>');
+			$("#checkMessage").html('<font color="red">Bitte Alter des Kindes eingeben</font>');
 			return;
 		}
 		train.subid = document.getElementById("subjectID").value

### 2019-08-28 analysis/data_processing.Rmd
update experiments

---
title: "Data Processing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)

```

```{r}
# importing data

files <- dir("~/Work/PragBat/raw_data/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/PragBat/raw_data/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,33,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date, 
                                               trial = as.character(trial))
  raw_data <- bind_rows(raw_data, id)
}

```

### 2019-08-28 experiments/discourse_continuity.js

@@ -1,4 +1,4 @@
-var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt", "bread", "tv", "pencil"];
+var preloadItems = ["car", "truck", "train", "bus", "airplane", "boat", "motorbike", "strawberry", "apple", "banana", "cherry", "orange", "melon", "pineapple", "dog", "cat", "horse", "bear", "cow", "monkey", "elephant", "shoe", "sock", "hat", "shirt", "jacket", "dress", "skirt","drum", "flute", "guitar", "xylophone", "piano", "trumpet", "violin"];
 
 var images = new Array();
 for (i = 0; i < preloadItems.length; i++) {
@@ -9,7 +9,7 @@ for (i = 0; i < preloadItems.length; i++) {
 //only preload relevant audios (no speaker change)
 var preloadAudios = ["hi", "lets", "intro", "thank", "it"];
 
-var posAgents = ["Bunny", "Frog", "Mouse", "Sheep", "Tiger"]
+var posAgents = ["Tiger","Bunny","Frog","Mouse","Pig"]
 
 var audios = new Array();
 for (i = 0; i < posAgents.length; i++) {
@@ -129,7 +129,7 @@ showSlide("instructions");
 
 var slides = [1, 2, 3, 4, 5, 6, "choice"]
 
-var trials = [0, 1, 2, 3]
+var trials = [0, 1, 2, 3, 4]
 
 var backgrounds = [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12];
 
@@ -137,12 +137,14 @@ var vehiclesF = ["train", "car", "boat", "motorbike", "truck", "airplane", "bus"
 var fruitsF = ["orange", "apple", "pineapple", "cherry", "banana", "melon", "strawberry"]
 var mammalsF = ["elephant", "bear", "monkey", "cow", "horse", "cat", "dog"]
 var clothesF = ["sock", "shoe", "hat", "shirt", "skirt", "jacket", "dress"]
+var instrumentsF = ["drum", "flute", "guitar", "xylophone", "piano", "trumpet", "violin"]
 
 var allFamiliar = {
[…]

### 2019-08-28 experiments/informativeness.js

@@ -291,7 +291,7 @@ if (informativeness.targetSwitch[0] == "stay") {
       data = {
         subid: train.subid,
         subage: train.subage,
-        experiment: "informativeness",
+        task: "informativeness",
         trial: informativeness.trial[0],
         agent: informativeness.agents[0],
         leftObject: informativeness.leftFruit[0],

### 2019-08-28 experiments/mutual_exclusivity.js

@@ -9,7 +9,7 @@ var me = {
           ["straight","down"],
           ["straight","down"],
           ["straight","down"]],
-  novels: ["t21","t22","t23","t24","t25"],
+  novels: ["t21","t22","t10","t12","t15"],
   familiars: ["carrot","bread","apple_me","duck","eggplant"],
   back: [6,7,8,9,10],
   novelPos: ["left", "right", "right", "left", "right"],

### 2019-08-28 analysis/data_simulations.Rmd
add second simulation

@@
 ```
+
+```{r}
+library(bindata)
+
+# Parameters of joint distribution
+size <- 1
+p1 <- 0.7
+p2 <- 0.6
+rho<- 0.3
+
+# Create one pair of correlated binomial values
+trials <- rmvbin(size, c(p1,p2), bincorr=(1-rho)*diag(2)+rho)
+colSums(trials)
+
+# A function to create n correlated pairs
+rmvBinomial <- function(id, n, size, p1, p2, rho) {
+    X <- replicate(n, {
+             colSums(rmvbin(size, c(p1,p2), bincorr=(1-rho)*diag(2)+rho))
+         })
+    t(X)%>%
+  as_tibble()%>%
+      mutate(trial = 1:n, 
+             id = id)%>%
+      gather(task, score, -trial, -id)
+}
+# Try it out, creating 1000 pairs
+
+sim2 <- function (seed, n_trials) {
+
+n_sub = 100
+
+set.seed(seed)
+
+tibble(id = 1:n_sub) %>% 
+  mutate(tidy = map(id, rmvBinomial, n =n_trials, size=size, p1=p1, p2=p2, rho=rho))%>%
+  unnest(tidy)%>%
+  group_by(id, task)%>%
+  summarise(mean= mean(score))%>%
+  spread(task, mean)%>%
+  ungroup()%>%
+  summarise(cor = cor(V1,V2))
+
+}
+
+n_sim = 1000
+
+cor_sim_5 <- tibble(seed = 1:n_sim) %>% 
+  mutate(tidy = map(seed, sim2, n_trials = 5))%>%
+  unnest(tidy)%>%
+  mutate(trials = "5")
+
+cor_sim_4 <- tibble(seed = 1:n_sim) %>% 
+  mutate(tidy = map(seed, sim2, n_trials = 4))%>%
+  unnest(tidy)%>%
+  mutate(trials = "4")
+
+cor_sim_3 <- tibble(seed = 1:n_sim) %>% 
+  mutate(tidy = map(seed, sim2, n_trials = 3))%>%
+  unnest(tidy)%>%
+  mutate(trials = "3")
+
+cor_sim_2 <- tibble(seed = 1:n_sim) %>% 
+  mutate(tidy = map(seed, sim2, n_trials = 2))%>%
+  unnest(tidy)%>%
+  mutate(trials = "2")
+
+sim_plot_cor = bind_rows(
+  cor_sim_5,
+  cor_sim_4,
+  cor_sim_3,
+  cor_sim_2
+)
+
+ggplot(sim_plot_cor, aes(x = cor, fill = trials))+
+  geom_density(alpha = .5)+
+  geom_vline(xintercept = .3)+
+  xlim(0,1)+
+  theme_few()+
+  scale_fill_ptol()
+```

### 2019-08-28 experiments/discourse_continuity.js

@@ -360,8 +360,8 @@ var discon = {
 
     introAll: function () {
         showSlide("introAll");
-        document.getElementById("text_introAll").innerHTML = "In this game, you're going to meet the little animals. They each live in a house and they have many different kinds of things at home. Each animal will tell you about some of things they have in their house.";
-        document.getElementById("text_introAll_2").innerHTML = "Your job is to touch the thing the animal is talking about. So, listen carefully and find out which one you have to touch.";
+        document.getElementById("text_introAll").innerHTML = "In diesem Spiel nehmen Dich die Tiere mit zu sich nach Hause. Jedes der Tiere wohnt in einem Haus und jedes hat viele verschiedene Dinge zu hause. Jedes Tier erzählt Dir von den Dingen die es zu Hasue hat.";
+        document.getElementById("text_introAll_2").innerHTML = "Deine Aufageb ist es, das Ding zu berühren, über das das Tier spricht. Pass also gut auf und finde heraus welches Du berühren musst.";
     },
 
     intro: function () {

### 2019-08-28 experiments/informativeness.js

@@ -342,7 +342,7 @@ if (informativeness.targetSwitch[0] == "stay") {
       data = {
         subid: train.subid,
         subage: train.subage,
-        experiment: "informativeness",
+        task: "informativeness",
         trial: informativeness.trial[0],
         agent: informativeness.agents[0],
         leftObject: informativeness.leftFruit[0],

### 2019-08-28 analysis/data_simulations.Rmd
add some more simulations

@@
 
-n_sub = 100
+n_sub = 50
 
@@
   ungroup()%>%
-  summarise(cor = cor(V1,V2))
+  summarise(correl = cor(V1,V2))
 
@@
 
-n_sim = 1000
+n_sim = 100
 
@@
 
-ggplot(sim_plot_cor, aes(x = cor, fill = trials))+
+ggplot(sim_plot_cor, aes(x = correl, fill = trials))+
   geom_density(alpha = .5)+
@@
 ```
+
+```{r}
+ggsave("../graphs/n100_rho03.pdf", width = 5, height = 4, scale = 1.5)
+```

### 2019-09-19 experiments/card_sorting.js
add card sorting study

@@ -1,0 +1,207 @@
+
+function showSample(a) {
+    $(".sample").show();
+    document.getElementById("sample").src = a;
+};
+
+
+// the actual experiment
+var sort = {
+  trial: ["train","train2",1,2,3,4,5,6,"switch",1,2,3,4,5,6],
+  sample: ["red_rabbit", "blue_boat", "red_rabbit", "blue_boat", "blue_boat", "red_rabbit", "red_rabbit", "blue_boat", "red_rabbit", "blue_boat","blue_boat", "red_rabbit","blue_boat","red_rabbit"],
+  phase: ["color","shape"],   
+  data: [],
+    
+
+    
+// end of the experiment
+  end: function() {
+    // Show the finish slide.
+    showSlide("select");
+    setTimeout(function() { turk.submit(sort) }, 200);
+  },
+    
+  
+// what happens between trials - display agent from previous trial and click on it to move on to the next trial    
+   chooseLeft: function(event) {
+    
+    event.target.style.border = '5px solid orange';
+    
+    $("#sample").animate({bottom: "300px", left: "100px", opacity: 0},{duration: 1500})
+          
+    pause("next", 1500)
+    
+    setTimeout(function() {sort.newtrial() }, 1500);
+    
+   
+    // Code correct: does name of chosen object contain the name of the correct object
+    if (sort.phase[0] == "color"){
+        
+        if (sort.sample[0] == "blue_boat"){
+           var correct = 1 
+        } else {
+            var correct = 0    
+        }
+        
+        
+        } else {
+        if (sort.sample[0] == "blue_boat"){
+           var correct = 0
+        } else {
+            var correct = 1    
+        }
+        };   
+    
+
+    // data collected  
+      data = {
+        subid: train.subid,
+        subage: train.subage,
+        phase: sort.phase[0],
+        task: "card_sorting",
+        sample: sort.sample[0],
+        trial: sort.trial[0],
+        target: "blue_rabbit",
+        correct: correct
+            };
+      sort.data.push(data);
+             
+  },
+    
+    
+   chooseRight: function(event) {
+    
+    event.target.style.border = '5px solid orange';
+    
+    $("#sample").animate({bottom: "300px", left: "700px", opacity: 0},{duration: 1500})
+          
+    pause("next", 1500)
+    
+    setTimeout(function() {sort.newtrial() }, 1500);
+    
+   
+    // Code correct: does name of chosen object contain the name of the correct object
[…]

### 2019-09-19 experiments/card_sorting.js
update card sorting

@@ -18,7 +18,7 @@ var sort = {
   end: function() {
     // Show the finish slide.
     showSlide("select");
-    setTimeout(function() { turk.submit(sort) }, 200);
+    setTimeout(function() { turk.submit(sort) }, 500);
   },
     
   

### 2019-11-06 experiments/card_sorting.js
update timing inf

@@ -138,16 +138,20 @@ var sort = {
 
                 if (sort.sample[0] == "blue_boat") {
                     var correct = 1
+                    var correct_location = "left"
                 } else {
                     var correct = 0
+                    var correct_location = "right"
                 }
 
 
             } else {
                 if (sort.sample[0] == "blue_boat") {
                     var correct = 0
+                    var correct_location = "right"
                 } else {
                     var correct = 1
+                    var correct_location = "left"
                 }
             };
 
@@ -160,7 +164,10 @@ var sort = {
                 task: "card_sorting",
                 sample: sort.sample[0],
                 trial: sort.trial[0],
-                target: "blue_rabbit",
+                leftObject: "blue_rabbit",
+                leftObject: "red_boat",
+                correct_location: correct_location,
+                pick: "blue_rabbit",
                 correct: correct
             };
             sort.data.push(data);
@@ -193,16 +200,20 @@ var sort = {
 
                 if (sort.sample[0] == "blue_boat") {
                     var correct = 0
+                    var correct_location = "left"
                 } else {
                     var correct = 1
+                    var correct_location = "right"
                 }
 
 
             } else {
                 if (sort.sample[0] == "blue_boat") {
                     var correct = 1
+                    var correct_location = "right"
                 } else {
                     var correct = 0
+                    var correct_location = "left"
                 }
             };
 
@@ -215,7 +226,10 @@ var sort = {
                 task: "card_sorting",
                 sample: sort.sample[0],
                 trial: sort.trial[0],
-                target: "red_boat",
+                leftObject: "blue_rabbit",
+                leftObject: "red_boat",
+                correct_location: correct_location,
+                pick: "red_boat",
                 correct: correct
             };
             sort.data.push(data);

### 2019-11-06 experiments/informativeness.js

@@ -128,7 +128,7 @@ targetSwitch: ["stay","switch","switch","stay","switch","stay","stay"],
       setTimeout(function() {
       sourceSound("sound/" + informativeness.agents[0] + "_which.mp3");
       playSound();
-      }, 2500) 
+      }, 2750) 
 
  
       choiceInfRightFruit("images/empty.png") 

### 2019-11-06 experiments/pragBat.js

@@ -10,6 +10,10 @@ for (i = 0; i < preFruits.length; i++) {
 
 var preSounds = [
          "Monkey_hello.mp3",
+    "Monkey_filler_inf_intro.mp3",
+"Monkey_filler_label.mp3",
+"Monkey_filler_more.mp3",
+"Monkey_filler_which.mp3",
          "Monkey_inf_intro.mp3",
          "Monkey_label.mp3",
          "Monkey_me_choice.mp3",
@@ -35,6 +39,10 @@ var preSounds = [
          "Bunny_pref_choice.mp3",
          "Bunny_which.mp3",
         "Frog_hello.mp3",
+   "Frog_filler_inf_intro.mp3",
+"Frog_filler_label.mp3",
+"Frog_filler_more.mp3",
+"Frog_filler_which.mp3",
          "Frog_inf_intro.mp3",
          "Frog_label.mp3",
          "Frog_me_choice.mp3",

### 2019-11-08 analysis/data_processing.Rmd
add second simulation
fix minor bugs before start testing

@@
 library(readxl)
+library(corrr)
+library(corrplot)
 
@@
 
+data <- raw_data %>%
+  filter(trial != "training", 
+         trial != "filler1", 
+         trial != "filler2",
+         trial != "train",
+         trial != "train2")%>%
+  filter(phase == "shape" | is.na(phase))%>%
+  select(subid, subage, test_date, task, trial, correct)%>%
+  mutate(subid = str_replace(subid,"-","_"))%>%
+  separate(subid, into = c("id","test_day"), sep="_")
+
+raw_data %>%
+  filter(
+         trial == "filler1" | 
+         trial == "filler2")
+
 ```
+
+```{r}
+data%>%
+  group_by(task)%>%
+  summarise(n= length(unique(id)))
+```
+
+```{r}
+p1 <- data%>%
+  group_by(id,subage,task)%>%
+  summarise(mean = mean(correct))
+
+p2 <- p1 %>%
+  group_by(subage,task)%>%
+  multi_boot_standard(col = "mean")
+
+ggplot()+
+  geom_hline(yintercept = .5, lty = 2)+
+  geom_line(data = p2,aes(x = subage, y = mean, group = task), alpha = .5)+
+  geom_jitter(data = p1, aes(x = subage, y = mean, col = subage), alpha = .5, width = .2, height = .01)+
+  geom_pointrange(data = p2, aes(x = subage, y = mean, ymin = ci_lower, ymax = ci_upper, col = subage))+
+  facet_wrap(~task)+
+  labs(x = "Age Group", y = "Proportion Correct")+
+  scale_color_ptol()+
+  theme_few()
+
+```

### 2019-11-08 experiments/informativeness.js

@@ -13,7 +13,7 @@ var informativeness = {
     ["straight","point","down"],
     ["straight","point","down"],
     ["straight","point","down"]],
-  leftFruit: ["t11","t12","t13","t14","t15","t16","t17"],
+  leftFruit: ["t11","t12","t13","t44","t15","t16","t17"],
   rightFruit: ["t18","t19","t20","t36","t37","t38","t39"],
   inf: ["left","right","left","left","right","left","right"],
   data: [],

### 2019-11-08 experiments/pragBat.js

@@ -1,5 +1,5 @@
 // preload
-var preFruits = ["duck.png","car.png","car_me.png","bear.png","ball.png","t01.png", "t02.png", "t03.png", "t04.png", "t05.png", "t06.png", "t07.png", "t08.png", "t09.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t17.png", "carrot.png","bread.png","apple_me.png","kite.png", "t18.png","t19.png","t20.png","t21.png","t22.png","t23.png","t24.png","t25.png","t26.png","t27.png","t28.png","t29.png","t30.png","t31.png","t32.png","t33.png","t34.png","t35.png",  "back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png", "bear_me.png"];
+var preFruits = ["duck.png","car.png","car_me.png","bear.png","ball.png","t01.png", "t02.png", "t03.png", "t04.png", "t05.png", "t06.png", "t07.png", "t08.png", "t09.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t17.png", "carrot.png","bread.png","apple_me.png","kite.png", "t18.png","t19.png","t20.png","t21.png","t22.png","t23.png","t24.png","t25.png","t26.png","t27.png","t28.png","t29.png","t30.png","t31.png","t32.png","t33.png","t34.png","t35.png", "t36.png","t37.png","t38.png","t39.png","t44.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png", "bear_me.png"];
 //for critical trials and fillers
 var images = new Array();
 for (i = 0; i < preFruits.length; i++) {

### 2019-11-14 experiments/novelty.js
remove ring

@@ -323,7 +323,6 @@ eat2: function(event) {
            
         if (novelty.agentOrient[0][0] == "disappear") {
             showAgent(novelty.agents[0], "straight")
-            sourceSound("sound/ring.mp3")
             playSound();
             setTimeout(function () {
                 showAgent(novelty.agents[0], "disappear")

### 2019-11-15 analysis/data_processing.Rmd
fix bug

@@
   select(subid, subage, test_date, task, trial, correct)%>%
-  mutate(subid = str_replace(subid,"-","_"))%>%
-  separate(subid, into = c("id","test_day"), sep="_")
+  separate(subid, into = c("id","test_day"), sep="\\.")
 

### 2019-11-15 experiments/novelty.js

@@ -323,7 +323,6 @@ eat2: function(event) {
            
         if (novelty.agentOrient[0][0] == "disappear") {
             showAgent(novelty.agents[0], "straight")
-            playSound();
             setTimeout(function () {
                 showAgent(novelty.agents[0], "disappear")
             }, 1000);

### 2019-11-29 analysis/data_processing.Rmd
add heatmap

@@
 library(corrplot)
+library(ggcorrplot)
+library(reshape2)
 
@@
 
+unique(raw_data$subid)
+
 data <- raw_data %>%
@@
   filter(phase == "shape" | is.na(phase))%>%
+  mutate(subid = recode(subid, `13.2` = "Vp13.2",
+                        `13.2` = "Vp13.2",
+                        `14.2` = "Vp14.2",
+                        `16.2` = "Vp16.2",
+                        `19.1` = "Vp19.1",
+                        `12.1` = "Vp12.1"
+                        ))%>%
   select(subid, subage, test_date, task, trial, correct)%>%
-  separate(subid, into = c("id","test_day"), sep="\\.")
+  separate(subid, into = c("id","test_day"), sep="\\.")%>%
+  mutate(test_day = ifelse(id == "Vp12" & test_date =="2019-11-26", 2, test_day))
 
-raw_data %>%
-  filter(
-         trial == "filler1" | 
-         trial == "filler2")
+data %>%
+  group_by(id, test_day, test_date)%>%
+  summarise(n())%>%
+  arrange(id,test_date)
 
@@
 data%>%
-  group_by(task)%>%
+  group_by(subage)%>%
+  summarise(n= length(unique(id)))
+```
+
+```{r}
+data%>%
+  group_by(test_day,task)%>%
   summarise(n= length(unique(id)))
@@
 ```
+
+```{r}
+p3 <- data%>%
+  filter(task != "training")%>%
+  group_by(id,task, test_day)%>%
+  summarise(mean = mean(correct))%>%
+  spread(test_day, mean)%>%
+  rename("Day1" = `1`,
+         "Day2" = `2`)%>%
+  na.omit()
+
+ggplot(p3, aes(x = Day1, y = Day2))+
+  geom_jitter(width = .05, height = .05, alpha = .5)+
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
+  geom_smooth(method = "lm", col = "#af6300")+
+  facet_grid(~task)+
+  coord_fixed()+
+  xlim(-.1,1.1)+
+  ylim(-.1,1.1)+
+  theme_few()
+
+```
+
+```{r}
+reli <- data%>%
+  filter(task != "training")%>%
+  group_by(id,task, test_day)%>%
+  summarise(mean = mean(correct))%>%
+  spread(test_day, mean)%>%
+  na.omit()%>%
+  rename("Day1" = `1`,
+         "Day2" = `2`)%>%
+  group_by(task)%>%
+  summarize(reli = cor.test(Day1,Day2)$estimate,
+            lci = cor.test(Day1,Day2)$conf.int[1],
+            uci = cor.test(Day1,Day2)$conf.int[2],
+            p = cor.test(Day1,Day2)$p.value)%>%
+  mutate_if(is.numeric, round, digits = 2)
+
+reli
+```
+
+```{r}
+cor <- data%>%
+  filter(task != "training")%>%
+  group_by(id,task)%>%
+  summarise(mean = mean(correct))%>%
+  spread(task, mean)%>%
+  ungroup()%>%
+  select(-id)%>%
+  corrr::correlate(diagonal = reli$reli)%>%
+  gather(task, cor, -rowname)%>%
+  mutate_if(is.numeric, round, digits = 2)%>%
+  mutate(cor = replace(cor, duplicated(cor), NA))%>%
+  na.omit()
+
+ggplot(cor, aes(x = rowname, y = task, fill = cor))+
+  geom_tile(color = "white")+
+  labs(x = "", y = "")+
+  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white", 
+   midpoint = 0, limit = c(-1,1), space = "Lab", 
+   name="Correlation") +
+   coord_fixed()+
+  theme_few(base_size = 12)+
+  geom_text(aes(label = cor), color = "black", size = 3) +
+  theme(legend.justification = c(1, 0),
+        legend.position = c(0.55, 0.7),
+        legend.direction = "horizontal",
+        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
+  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
+                title.position = "top", title.hjust = 0.5))
+```

### 2019-11-29 analysis/data_processing.Rmd
add data file

@@
 
+write.csv(data, file = "../data/data.csv")
+
 data %>%
@@
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
-  geom_smooth(method = "lm", col = "#af6300")+
+  geom_smooth(method = "lm", col = "#af6300", se = F)+
   facet_grid(~task)+

### 2020-01-21 analysis/data_processing.Rmd
push data for Clara to explore

--- 2019-11-29 analysis/data_processing.Rmd
@@
 library(reshape2)
+library(psych)
+library(readODS)
 
@@
 # importing data
-
+### die flogenden Zeilen kannst du überspringen. Weiter gehts in Zeile 68
 files <- dir("~/Work/PragBat/raw_data/")
@@
 
-data <- raw_data %>%
+task_data <- raw_data %>%
   filter(trial != "training", 
@@
                         `19.1` = "Vp19.1",
-                        `12.1` = "Vp12.1"
+                        `12.1` = "Vp12.1",
+                        `29.2` = "Vp29.2",
+                        `26.1` = "Vp26.2",
+                        `37.1` = "Vp37.1",
+                        `38.1` = "Vp38.1"
                         ))%>%
@@
 
-data %>%
-  group_by(id, test_day, test_date)%>%
-  summarise(n())%>%
-  arrange(id,test_date)
+#write_csv(task_data, "../data/data.csv")
+
+task_data <- read_csv("../data/data.csv")
+
+# damit du das daten file mit dem log file (deine Liste) mergen kannst (brauchen wir für das numerische alter) legst du deine liste in den gleichen ordner in dem auch ader repository ordner liegt.
+Dann sollte es klappen.
+
+log <- read_ods("../../VP Liste.ods", sheet = 2)%>%
+  mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
+         id = paste("Vp",`ID `, sep = ""))%>%
+  select(id, age, status)
+
+data <- task_data %>%
+  left_join(log)%>%
+  mutate(check_age = ifelse(subage == substr(age,1,1),T,F))
 
@@
   summarise(n= length(unique(id)))
+
+```
+
+```{r}
+data %>%
+  group_by(subage,id)%>%
+  summarise(testdays = length(unique(test_day)))%>%
+  filter(testdays == 2)%>%
+  summarise(complete_retest_data = length(id))
+```
+
+```{r}
+data %>%
+  group_by(id,test_day)%>%
+  summarise(n())%>%
+  arrange(id,test_day)
+
 ```
@@
   group_by(id,subage,task)%>%
+  filter(subage != "5",
+         task != "training")%>%
   summarise(mean = mean(correct))
@@
   labs(x = "Age Group", y = "Proportion Correct")+
-  scale_color_ptol()+
-  theme_few()
+  scale_color_ptol(name = "Age")+
+  theme_few()+
+  theme(legend.position = c(.85,.2))
+```
 
+```{r}
+p12 <- data%>%
+  group_by(id,age,task)%>%
+  filter(task != "training")%>%
+  summarise(mean = mean(correct))
+
+ggplot(data = p12, aes(x = age, y = mean))+
+  geom_hline(yintercept = .5, lty = 2)+
+  geom_jitter(alpha = .5, width = .2, height = .01)+
+  geom_smooth(method = "glm")+
+  facet_wrap(~task)+
+  labs(x = "Age", y = "Proportion Correct")+
+  scale_color_ptol(name = "Age")+
+  theme_few()+
+  theme(legend.position = c(.85,.2))
 ```
@@
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
-  geom_smooth(method = "lm", col = "#af6300")+
+  geom_smooth(method = "lm", col = "#af6300", se = T)+
   facet_grid(~task)+
@@
 ```{r}
+reli_age <- data%>%
+  filter(task != "training")%>%
+  group_by(subage, id,task, test_day)%>%
+  summarise(mean = mean(correct))%>%
+  spread(test_day, mean)%>%
+  na.omit()%>%
+  rename("Day1" = `1`,
+         "Day2" = `2`)%>%
+  group_by(subage,task)%>%
+  summarize(reli = cor.test(Day1,Day2)$estimate,
+            lci = cor.test(Day1,Day2)$conf.int[1],
+            uci = cor.test(Day1,Day2)$conf.int[2],
+            p = cor.test(Day1,Day2)$p.value)%>%
+  mutate_if(is.numeric, round, digits = 2)
+
+reli_age
+```
+
+```{r}
 cor <- data%>%
@@
   gather(task, cor, -rowname)%>%
+  mutate(cor = replace(cor, duplicated(cor), NA))%>%
   mutate_if(is.numeric, round, digits = 2)%>%
-  mutate(cor = replace(cor, duplicated(cor), NA))%>%
   na.omit()
@@
 ```
+
+```{r}
+library(psy)
+
+fa_data <- p1 %>%
+  spread(task, mean)%>%
+  ungroup()%>%
+  select(-id, -subage)%>%
+  na.omit()
+
+pca <- principal(fa_data,nfactors=2, rotate="varimax")
+
+fit <- factanal(fa_data, 2, rotation="varimax")
+
+scree.plot(fit$correlation)
+
+fit$loadings
+
+pca$loadings
+
+plot(pca)
+
+```

### 2020-01-24 analysis/data_processing.Rmd
add first model for age

@@
 library(readODS)
+library(brms)
 
@@
 ### die flogenden Zeilen kannst du überspringen. Weiter gehts in Zeile 68
-files <- dir("~/Work/PragBat/raw_data/")
-
-raw_data <- data_frame()
-for (f in files) {
-  jf <- paste("~/Work/PragBat/raw_data/",f,sep="")
-  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-  date <- str_sub(jf,33,str_length(jf)-11)
-  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date, 
-                                               trial = as.character(trial))
-  raw_data <- bind_rows(raw_data, id)
-}
-
-unique(raw_data$subid)
-
-task_data <- raw_data %>%
-  filter(trial != "training", 
-         trial != "filler1", 
-         trial != "filler2",
-         trial != "train",
-         trial != "train2")%>%
-  filter(phase == "shape" | is.na(phase))%>%
-  mutate(subid = recode(subid, `13.2` = "Vp13.2",
-                        `13.2` = "Vp13.2",
-                        `14.2` = "Vp14.2",
-                        `16.2` = "Vp16.2",
-                        `19.1` = "Vp19.1",
-                        `12.1` = "Vp12.1",
-                        `29.2` = "Vp29.2",
-                        `26.1` = "Vp26.2",
-                        `37.1` = "Vp37.1",
-                        `38.1` = "Vp38.1"
-                        ))%>%
-  select(subid, subage, test_date, task, trial, correct)%>%
-  separate(subid, into = c("id","test_day"), sep="\\.")%>%
-  mutate(test_day = ifelse(id == "Vp12" & test_date =="2019-11-26", 2, test_day))
+# files <- dir("~/Work/PragBat/raw_data/")
+# 
+# raw_data <- data_frame()
+# for (f in files) {
+#   jf <- paste("~/Work/PragBat/raw_data/",f,sep="")
+#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+#   date <- str_sub(jf,33,str_length(jf)-11)
+#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date, 
+#                                                trial = as.character(trial))
+#   raw_data <- bind_rows(raw_data, id)
+# }
+# 
+# unique(raw_data$subid)
+# 
+# 
+# task_data <- raw_data %>%
+#   filter(trial != "training", 
+#          trial != "filler1", 
+#          trial != "filler2",
+#          trial != "train",
+#          trial != "train2")%>%
+#   filter(phase == "shape" | is.na(phase))%>%
+#   mutate(subid = recode(subid, `13.2` = "Vp13.2",
+#                         `13.2` = "Vp13.2",
+#                         `14.2` = "Vp14.2",
+#                         `16.2` = "Vp16.2",
+#                         `19.1` = "Vp19.1",
+#                         `12.1` = "Vp12.1",
+#                         `29.2` = "Vp29.2",
+#                         `26.1` = "Vp26.2",
+#                         `37.1` = "Vp37.1",
+#                         `38.1` = "Vp38.1"
+#                         ))%>%
+#   select(subid, subage, test_date, task, trial, correct)%>%
+#   separate(subid, into = c("id","test_day"), sep="\\.")%>%
+#   mutate(test_day = ifelse(id == "Vp12" & test_date =="2019-11-26", 2, test_day))
 
@@
 
-task_data <- read_csv("../data/data.csv")
+#task_data <- read_csv("../data/data.csv")
 
@@
 
-log <- read_ods("../../VP Liste.ods", sheet = 2)%>%
-  mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
-         id = paste("Vp",`ID `, sep = ""))%>%
-  select(id, age, status)
+# log <- read_ods("../../VP Liste.ods", sheet = 2)%>%
+#   mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
+#          id = paste("Vp",`ID `, sep = ""))%>%
+#   select(id, age, status)
+#   
+# 
+# data <- task_data %>%
+#   left_join(log)%>%
+#   mutate(check_age = ifelse(subage == substr(age,1,1),T,F))
 
-data <- task_data %>%
-  left_join(log)%>%
-  mutate(check_age = ifelse(subage == substr(age,1,1),T,F))
+data <- read_csv("../data/data.csv")%>%
+  mutate(subage = factor(subage),
+         trial = ifelse(test_day == "2", trial + 4, trial))%>%
+  select(-X)
 
@@
   group_by(id,subage,task)%>%
-  filter(subage != "5",
-         task != "training")%>%
+  filter(task != "training")%>%
   summarise(mean = mean(correct))
@@
   geom_smooth(method = "glm")+
-  facet_wrap(~task)+
+  facet_grid(~task)+
   labs(x = "Age", y = "Proportion Correct")+
@@
   theme_few()+
-  theme(legend.position = c(.85,.2))
+  theme(legend.position = c(.85,.2))+
+  coord_fixed(ratio = 2)
+```
+# Card Sorting model
+
+```{r}
+# card sorting
+
+card_sorting_data <- data %>%
+  filter(task == "card_sorting")
+
+card_sorting_model_data <- card_sorting_data %>%
+  mutate(age = age - mean(age),
+         trial = trial - mean(trial))
+
+# card_sorting_model1 <- brm(correct ~ age + trial + (trial|id),
+#                     data = card_sorting_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4, 
+#           cores = 4,
+#           save_all_pars = TRUE,
+#           iter = 10000)%>%
+#   add_criterion("waic")%>%
+#   saveRDS(., "../saves/card_sorting_model1.rds")
+# 
+# card_sorting_model2 <- brm(correct ~ trial + (trial|id),
+#                     data = card_sorting_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4, 
+#           cores = 4,
+#           save_all_pars = TRUE,
+#           iter = 10000)%>%
+#   add_criterion("waic")%>%
+#   saveRDS(., "../saves/card_sorting_model2.rds")
+
+card_sorting_model1 <-readRDS("../saves/card_sorting_model1.rds")
+
+card_sorting_model2 <-readRDS("../saves/card_sorting_model2.rds")
+
+ts <- loo_compare(card_sorting_model1, card_sorting_model2, criterion = "waic")%>%
+  as.data.frame() %>%
+  tibble::rownames_to_column("Model")%>%
+  mutate(
+    Model = recode(Model, card_sorting_model1 = "correct ~ age + trial + RE", 
+                   card_sorting_model2 = "correct ~ trial + RE"),
+    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
+    weight = round(weight, 3),
+    WAIC = round(waic, 2),
+    SE = round(se_waic,2))%>%
+  select(Model, WAIC, SE, weight)
+
+ts
+
+summary(card_sorting_model1)
+
+```
+
+```{r}
+p_sum_cs1 <- card_sorting_data %>%
+  mutate(subage = as.numeric(as.character(subage)))%>%
+  group_by(age,subage,id) %>%
+  summarise(correct = mean(correct))
+
+p_sum_cs2 <- p_sum_cs1 %>%
+  group_by(subage) %>%
+  multi_boot_standard(col = "correct")
+
+samples_cs_1 <- posterior_samples(card_sorting_model1, "^b")%>%
+  mutate(sample = 1:length(b_age))
+
+samples_cs_2 <- expand_grid(samples_cs_1,card_sorting_model_data$age)%>%
+  mutate(y = plogis(b_Intercept + b_age * `card_sorting_model_data$age`),
+         age = `card_sorting_model_data$age` + mean(card_sorting_data$age),
+         experiment = "card_sorting")%>%
+  filter(sample < 1000)
+
+map_cs <- tibble(
+  age = card_sorting_model_data$age,
+  int = fixef(card_sorting_model1)[1,1],
+  slope = fixef(card_sorting_model1)[2,1]
+)%>%
+  mutate(y = plogis(int + slope * age),
+         age = age + mean(card_sorting_data$age_num))
+
+p_cs <- ggplot() +
+  geom_hline(yintercept = .5, lty=2, size = 1)+
+  geom_line(data = samples_cs_2, aes(x = age, y = y, group = sample), size = .025, col = "grey")+
+  geom_line(data = map_cs, aes(x = age, y = y), size = 1)+
+  geom_jitter(data = p_sum_cs1,aes(x = age, y= correct), width = .00, height = .01, alpha = .5)+
+  geom_pointrange(data = p_sum_cs2, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper),size = .8, position = position_dodge(width = .2), pch = 4)+
+  labs(x="Age",y="Proportion correct")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(3,5)+
+  guides(alpha = F, col = F)+
+  scale_color_manual(values = "#CC6677")
 ```
@@
   filter(task != "training")%>%
+  droplevels()%>%
   group_by(id,task, test_day)%>%
@@
   filter(task != "training")%>%
+  droplevels()%>%
   group_by(subage, id,task, test_day)%>%
@@
   filter(task != "training")%>%
+  droplevels()%>%
   group_by(id,task)%>%

### 2020-01-24 analysis/data_processing.Rmd
update visualizations

@@
   mutate(subage = factor(subage),
-         trial = ifelse(test_day == "2", trial + 4, trial))%>%
+         trial = ifelse(test_day == "2", trial + 4, trial),
+         z_age = age - mean(age))%>%
   select(-X)
@@
 ```
-# Card Sorting model
+# Models
+
+## Card Sorting
 
@@
 card_sorting_model_data <- card_sorting_data %>%
-  mutate(age = age - mean(age),
-         trial = trial - mean(trial))
+  mutate(trial = trial - mean(trial))
 
-# card_sorting_model1 <- brm(correct ~ age + trial + (trial|id),
+# card_sorting_model1 <- brm(correct ~ z_age + trial + (trial|id),
 #                     data = card_sorting_model_data, family = bernoulli(),
@@
 
-ts <- loo_compare(card_sorting_model1, card_sorting_model2, criterion = "waic")%>%
+cs_ts <- loo_compare(card_sorting_model1, card_sorting_model2, criterion = "waic")%>%
   as.data.frame() %>%
@@
 
-ts
+cs_ts
 
@@
 
+## Inforamtiveness
+
 ```{r}
-p_sum_cs1 <- card_sorting_data %>%
+
+inf_data <- data %>%
+  filter(task == "informativeness")
+
+inf_model_data <- inf_data %>%
+  mutate(trial = trial - mean(trial))
+
+inf_model1 <- brm(correct ~ z_age + trial + (trial|id),
+                    data = inf_model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/inf_model1.rds")
+
+inf_model2 <- brm(correct ~ trial + (trial|id),
+                    data = inf_model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/inf_model2.rds")
+
+inf_model1 <-readRDS("../saves/inf_model1.rds")
+
+inf_model2 <-readRDS("../saves/inf_model2.rds")
+
+inf_ts <- loo_compare(inf_model1, inf_model2, criterion = "waic")%>%
+  as.data.frame() %>%
+  tibble::rownames_to_column("Model")%>%
+  mutate(
+    Model = recode(Model, inf_model1 = "correct ~ age + trial + RE", 
+                   inf_model2 = "correct ~ trial + RE"),
+    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
+    weight = round(weight, 3),
+    WAIC = round(waic, 2),
+    SE = round(se_waic,2))%>%
+  select(Model, WAIC, SE, weight)
+
+inf_ts
+
+summary(inf_data_model1)
+
+```
+
+## Mutual Exclusivity
+
+```{r}
+
+me_data <- data %>%
+  filter(task == "mutual_exclusivity")
+
+me_model_data <- me_data %>%
+  mutate(trial = trial - mean(trial))
+
+me_model1 <- brm(correct ~ z_age + trial + (trial|id),
+                    data = me_model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/me_model1.rds")
+
+me_model2 <- brm(correct ~ trial + (trial|id),
+                    data = me_model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/me_model2.rds")
+
+me_model1 <-readRDS("../saves/me_model1.rds")
+
+me_model2 <-readRDS("../saves/me_model2.rds")
+
+me_ts <- loo_compare(me_model1, me_model2, criterion = "waic")%>%
+  as.data.frame() %>%
+  tibble::rownames_to_column("Model")%>%
+  mutate(
+    Model = recode(Model, me_model1 = "correct ~ age + trial + RE", 
+                   me_model2 = "correct ~ trial + RE"),
+    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
+    weight = round(weight, 3),
+    WAIC = round(waic, 2),
+    SE = round(se_waic,2))%>%
+  select(Model, WAIC, SE, weight)
+
+me_ts
+
+summary(me_model1)
+
+```
+## Novelty
+
+```{r}
+
+nov_data <- data %>%
+  filter(task == "novelty")
+
+nov_model_data <- nov_data %>%
+  mutate(trial = trial - mean(trial))
+
+nov_model1 <- brm(correct ~ z_age + trial + (trial|id),
+                    data = nov_model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/nov_model1.rds")
+
+nov_model2 <- brm(correct ~ trial + (trial|id),
+                    data = nov_model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/nov_model2.rds")
+
+nov_model1 <-readRDS("../saves/nov_model1.rds")
+
+nov_model2 <-readRDS("../saves/nov_model2.rds")
+
+nov_ts <- loo_compare(nov_model1, nov_model2, criterion = "waic")%>%
+  as.data.frame() %>%
+  tibble::rownames_to_column("Model")%>%
+  mutate(
+    Model = recode(Model, nov_model1 = "correct ~ age + trial + RE", 
+                   nov_model2 = "correct ~ trial + RE"),
+    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
+    weight = round(weight, 3),
+    WAIC = round(waic, 2),
+    SE = round(se_waic,2))%>%
+  select(Model, WAIC, SE, weight)
+
+nov_ts
+
+summary(nov_model1)
+
+```
+# Visualizing individual tasks
+
+```{r}
+# Files to plot data means
+p_data <- data %>%
+  filter(task != "training")%>%
   mutate(subage = as.numeric(as.character(subage)))%>%
-  group_by(age,subage,id) %>%
+  group_by(task, age,subage,id) %>%
   summarise(correct = mean(correct))
 
-p_sum_cs2 <- p_sum_cs1 %>%
-  group_by(subage) %>%
+p_data2 <- p_data %>%
+  group_by(task, subage) %>%
   multi_boot_standard(col = "correct")
 
-samples_cs_1 <- posterior_samples(card_sorting_model1, "^b")%>%
-  mutate(sample = 1:length(b_age))
+# Files to plot individual samples from each task
+samples_to_draw <- sample(1:20000, 500)
 
-samples_cs_2 <- expand_grid(samples_cs_1,card_sorting_model_data$age)%>%
-  mutate(y = plogis(b_Intercept + b_age * `card_sorting_model_data$age`),
-         age = `card_sorting_model_data$age` + mean(card_sorting_data$age),
-         experiment = "card_sorting")%>%
-  filter(sample < 1000)
+## card sorting
+samples_cs <- posterior_samples(card_sorting_model1, "^b")%>%
+  mutate(sample = 1:length(b_age))%>%
+  filter(sample %in% samples_to_draw)%>%
+  expand_grid(data$z_age)%>%
+  mutate(y = plogis(b_Intercept + b_age * `data$z_age`),
+         age = `data$z_age` + mean(data$age),
+         task = "card_sorting")
 
+## informativeness
+samples_inf <- posterior_samples(inf_model1, "^b")%>%
+  mutate(sample = 1:length(b_age))%>%
+  filter(sample %in% samples_to_draw)%>%
+  expand_grid(data$z_age)%>%
+  mutate(y = plogis(b_Intercept + b_age * `data$z_age`),
+         age = `data$z_age` + mean(data$age),
+         task = "informativeness")
+
+## mutual exclusivity
+samples_me <- posterior_samples(me_model1, "^b")%>%
+  mutate(sample = 1:length(b_z_age))%>%
+  filter(sample %in% samples_to_draw)%>%
+  expand_grid(data$z_age)%>%
+  mutate(y = plogis(b_Intercept + b_z_age * `data$z_age`),
+         age = `data$z_age` + mean(data$age),
+         task = "mutual_exclusivity")
+## novelty
+
+samples_nov <- posterior_samples(nov_model1, "^b")%>%
+  mutate(sample = 1:length(b_z_age))%>%
+  filter(sample %in% samples_to_draw)%>%
+  expand_grid(data$z_age)%>%
+  mutate(y = plogis(b_Intercept + b_z_age * `data$z_age`),
+         age = `data$z_age` + mean(data$age),
+         task = "novelty")
+
+## combine files
+samples <- bind_rows(
+  samples_cs,
+  samples_inf,
+  samples_me,
+  samples_nov
+)
+
+# File to plot means of distributions for each task
+
+## card sorting
 map_cs <- tibble(
-  age = card_sorting_model_data$age,
+  age = data$z_age,
   int = fixef(card_sorting_model1)[1,1],
@@
   mutate(y = plogis(int + slope * age),
-         age = age + mean(card_sorting_data$age_num))
+         age = age + mean(data$age),
+         task = "card_sorting")
 
-p_cs <- ggplot() +
+## informativeness
+map_inf <- tibble(
+  age = data$z_age,
+  int = fixef(inf_model1)[1,1],
+  slope = fixef(inf_model1)[2,1]
+)%>%
+  mutate(y = plogis(int + slope * age),
+         age = age + mean(data$age),
+         task = "informativeness")
+
+## mutual exclusivity
+map_me <- tibble(
+  age = data$z_age,
+  int = fixef(me_model1)[1,1],
+  slope = fixef(me_model1)[2,1]
+)%>%
+  mutate(y = plogis(int + slope * age),
+         age = age + mean(data$age),
+         task = "mutual_exclusivity")
+
+## novelty
+map_nov <- tibble(
+  age = data$z_age,
+  int = fixef(nov_model1)[1,1],
+  slope = fixef(nov_model1)[2,1]
+)%>%
+  mutate(y = plogis(int + slope * age),
+         age = age + mean(data$age),
+         task = "novelty")
+
+maps <- bind_rows(
+  map_cs,
+  map_inf,
+  map_me,
+  map_nov
+)
+
+ggplot() +
   geom_hline(yintercept = .5, lty=2, size = 1)+
-  geom_line(data = samples_cs_2, aes(x = age, y = y, group = sample), size = .025, col = "grey")+
-  geom_line(data = map_cs, aes(x = age, y = y), size = 1)+
-  geom_jitter(data = p_sum_cs1,aes(x = age, y= correct), width = .00, height = .01, alpha = .5)+
-  geom_pointrange(data = p_sum_cs2, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper),size = .8, position = position_dodge(width = .2), pch = 4)+
+  geom_line(data = samples, aes(x = age, y = y, group = sample), size = .025, col = "grey")+
+  geom_line(data = maps, aes(x = age, y = y), size = 1)+
+  geom_jitter(data = p_data,aes(x = age, y= correct), width = .00, height = .01, alpha = .2)+
+  geom_pointrange(data = p_data2, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper),size = .5, position = position_dodge(width = .2), pch = 5, col = "#6866cc")+
   labs(x="Age",y="Proportion correct")+
+  facet_wrap(~task, nrow = 2)+
   theme_few() +
@@
   guides(alpha = F, col = F)+
-  scale_color_manual(values = "#CC6677")
+  coord_fixed(ratio = 2)
 ```

### 2020-01-24 analysis/data_processing.Rmd
update visualizations

@@
   guides(alpha = F, col = F)+
-  coord_fixed(ratio = 2)
+  coord_fixed(ratio = 2)+
+  ggsave("../graphs/task_results.png")
 ```

### 2020-01-25 analysis/data_processing.Rmd
update visualizations

--- 2020-01-24 analysis/data_processing.Rmd
@@
   labs(x="Age",y="Proportion correct")+
-  facet_wrap(~task, nrow = 2)+
+  facet_wrap(~task, nrow = 1)+
   theme_few() +
@@
   guides(alpha = F, col = F)+
-  coord_fixed(ratio = 2)
+  coord_fixed(ratio = 2)+
+  ggsave("../graphs/task_results.png", width = 10, height = 2.5, scale = 1.2)
+```
+
+# Visualizing predictor for age
+
+```{r}
+
+library(ggridges)
+
+x <- bind_rows(
+  posterior_samples(card_sorting_model1, "^b")%>%
+  select(b_age)%>%
+  mutate(task = "1 card_sorting",
+         ci = ifelse(b_age < fixef(card_sorting_model1)[2,3] | b_age > fixef(card_sorting_model1)[2,4], 1,2)),
+  posterior_samples(inf_model1, "^b")%>%
+  select(b_age)%>%
+  mutate(task = "4 informativeness",
+         ci = ifelse(b_age < fixef(inf_model1)[2,3] | b_age > fixef(inf_model1)[2,4], 1,2)),
+  posterior_samples(nov_model1, "^b")%>%
+  select(b_z_age)%>%
+  rename(b_age = b_z_age)%>%
+  mutate(task = "2 novelty",
+         ci = ifelse(b_age < fixef(nov_model1)[2,3] | b_age > fixef(nov_model1)[2,4], 1,2)),
+  posterior_samples(me_model1, "^b")%>%
+  select(b_z_age)%>%
+  rename(b_age = b_z_age)%>%
+  mutate(task = "3 mutual_exclusivity",
+         ci = ifelse(b_age < fixef(me_model1)[2,3] | b_age > fixef(me_model1)[2,4], 1,2))
+)
+
+ggplot(x, aes(x = b_age, y = task, fill = factor(stat(quantile))))+
+  geom_vline(xintercept = 0, col = "grey", lty = 2)+
+  stat_density_ridges(
+    geom = "density_ridges_gradient",
+    calc_ecdf = TRUE,
+    quantiles = c(0.025, 0.975)
+  ) +
+  scale_fill_manual(values = c("white", "lightblue", "white"))+ 
+  guides(fill = F)+
+  xlim(-10,20)+
+  theme_few()
+
 ```

### 2020-02-11 analysis/data_processing.Rmd
first draft second round

--- 2020-01-24 analysis/data_processing.Rmd
@@
 ---
-title: "Data Processing"
+title: "Prag Bat"
 output: html_document
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = F, warning = F, message = F)
 
@@
 library(brms)
+library(psy)
 
@@
 
+# Total sample size
+
 ```{r}
@@
   group_by(subage)%>%
-  summarise(n= length(unique(id)))
+  summarise(n= length(unique(id)))%>%
+  kable()
 
 ```
+
+# Sample size with two test days
 
@@
   filter(testdays == 2)%>%
-  summarise(complete_retest_data = length(id))
+  summarise(complete_retest_data = length(id))%>%
+  kable()
 ```
@@
 ```{r}
-data %>%
-  group_by(id,test_day)%>%
-  summarise(n())%>%
-  arrange(id,test_day)
+# data %>%
+#   group_by(id,test_day)%>%
+#   summarise(n())%>%
+#   arrange(id,test_day)
 
@@
 ```{r}
-data%>%
-  group_by(test_day,task)%>%
-  summarise(n= length(unique(id)))
+# data%>%
+#   group_by(test_day,task)%>%
+#   summarise(n= length(unique(id)))
 ```
+
+# Results by task binned by year
 
@@
   theme(legend.position = c(.85,.2))
-```
-
-```{r}
-p12 <- data%>%
-  group_by(id,age,task)%>%
-  filter(task != "training")%>%
-  summarise(mean = mean(correct))
-
-ggplot(data = p12, aes(x = age, y = mean))+
-  geom_hline(yintercept = .5, lty = 2)+
-  geom_jitter(alpha = .5, width = .2, height = .01)+
-  geom_smooth(method = "glm")+
-  facet_grid(~task)+
-  labs(x = "Age", y = "Proportion Correct")+
-  scale_color_ptol(name = "Age")+
-  theme_few()+
-  theme(legend.position = c(.85,.2))+
-  coord_fixed(ratio = 2)
 ```
@@
 
-cs_ts
+cs_ts%>%
+  kable()
 
-summary(card_sorting_model1)
+#summary(card_sorting_model1)
 
@@
 
-inf_model1 <- brm(correct ~ z_age + trial + (trial|id),
-                    data = inf_model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.99),
-          sample_prior = F,
-          chains = 4,
-          cores = 4,
-          save_all_pars = TRUE,
-          iter = 10000)%>%
-  add_criterion("waic")%>%
-  saveRDS(., "../saves/inf_model1.rds")
-
-inf_model2 <- brm(correct ~ trial + (trial|id),
-                    data = inf_model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.99),
-          sample_prior = F,
-          chains = 4,
-          cores = 4,
-          save_all_pars = TRUE,
-          iter = 10000)%>%
-  add_criterion("waic")%>%
-  saveRDS(., "../saves/inf_model2.rds")
+# inf_model1 <- brm(correct ~ z_age + trial + (trial|id),
+#                     data = inf_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           save_all_pars = TRUE,
+#           iter = 10000)%>%
+#   add_criterion("waic")%>%
+#   saveRDS(., "../saves/inf_model1.rds")
+# 
+# inf_model2 <- brm(correct ~ trial + (trial|id),
+#                     data = inf_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           save_all_pars = TRUE,
+#           iter = 10000)%>%
+#   add_criterion("waic")%>%
+#   saveRDS(., "../saves/inf_model2.rds")
 
@@
 
-inf_ts
+inf_ts%>%
+  kable()
 
-summary(inf_data_model1)
+#summary(inf_data_model1)
 
@@
 
-me_model1 <- brm(correct ~ z_age + trial + (trial|id),
-                    data = me_model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.99),
-          sample_prior = F,
-          chains = 4,
-          cores = 4,
-          save_all_pars = TRUE,
-          iter = 10000)%>%
-  add_criterion("waic")%>%
-  saveRDS(., "../saves/me_model1.rds")
-
-me_model2 <- brm(correct ~ trial + (trial|id),
-                    data = me_model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.99),
-          sample_prior = F,
-          chains = 4,
-          cores = 4,
-          save_all_pars = TRUE,
-          iter = 10000)%>%
-  add_criterion("waic")%>%
-  saveRDS(., "../saves/me_model2.rds")
+# me_model1 <- brm(correct ~ z_age + trial + (trial|id),
+#                     data = me_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           save_all_pars = TRUE,
+#           iter = 10000)%>%
+#   add_criterion("waic")%>%
+#   saveRDS(., "../saves/me_model1.rds")
+# 
+# me_model2 <- brm(correct ~ trial + (trial|id),
+#                     data = me_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           save_all_pars = TRUE,
+#           iter = 10000)%>%
+#   add_criterion("waic")%>%
+#   saveRDS(., "../saves/me_model2.rds")
 
@@
 
-me_ts
+me_ts%>%
+  kable()
 
-summary(me_model1)
+#summary(me_model1)
 
 ```
+
 ## Novelty
@@
 
-nov_model1 <- brm(correct ~ z_age + trial + (trial|id),
-                    data = nov_model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.99),
-          sample_prior = F,
-          chains = 4,
-          cores = 4,
-          save_all_pars = TRUE,
-          iter = 10000)%>%
-  add_criterion("waic")%>%
-  saveRDS(., "../saves/nov_model1.rds")
-
-nov_model2 <- brm(correct ~ trial + (trial|id),
-                    data = nov_model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.99),
-          sample_prior = F,
-          chains = 4,
-          cores = 4,
-          save_all_pars = TRUE,
-          iter = 10000)%>%
-  add_criterion("waic")%>%
-  saveRDS(., "../saves/nov_model2.rds")
+# nov_model1 <- brm(correct ~ z_age + trial + (trial|id),
+#                     data = nov_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           save_all_pars = TRUE,
+#           iter = 10000)%>%
+#   add_criterion("waic")%>%
+#   saveRDS(., "../saves/nov_model1.rds")
+# 
+# nov_model2 <- brm(correct ~ trial + (trial|id),
+#                     data = nov_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           save_all_pars = TRUE,
+#           iter = 10000)%>%
+#   add_criterion("waic")%>%
+#   saveRDS(., "../saves/nov_model2.rds")
 
@@
 
-nov_ts
+nov_ts%>%
+  kable()
 
-summary(nov_model1)
+#summary(nov_model1)
 
 ```
-# Visualizing individual tasks
+
+## Preference
 
 ```{r}
+
+pref_data <- data %>%
+  filter(task == "preference")
+
+pref_model_data <- pref_data %>%
+  mutate(trial = trial - mean(trial))
+
+# pref_model1 <- brm(correct ~ z_age + trial + (trial|id),
+#                     data = pref_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           save_all_pars = TRUE,
+#           iter = 10000)%>%
+#   add_criterion("waic")%>%
+#   saveRDS(., "../saves/pref_model1.rds")
+# 
+# pref_model2 <- brm(correct ~ trial + (trial|id),
+#                     data = pref_model_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           save_all_pars = TRUE,
+#           iter = 10000)%>%
+#   add_criterion("waic")%>%
+#   saveRDS(., "../saves/pref_model2.rds")
+
+pref_model1 <-readRDS("../saves/pref_model1.rds")
+
+pref_model2 <-readRDS("../saves/pref_model2.rds")
+
+pref_ts <- loo_compare(pref_model1, pref_model2, criterion = "waic")%>%
+  as.data.frame() %>%
+  tibble::rownames_to_column("Model")%>%
+  mutate(
+    Model = recode(Model, pref_model1 = "correct ~ age + trial + RE", 
+                   pref_model2 = "correct ~ trial + RE"),
+    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
+    weight = round(weight, 3),
+    WAIC = round(waic, 2),
+    SE = round(se_waic,2))%>%
+  select(Model, WAIC, SE, weight)
+
+pref_ts%>%
+  kable()
+
+#summary(pref_model1)
+
+```
+
+# Visualizing predictor for age and trial
+
+```{r}
+
+library(ggridges)
+
+x <- bind_rows(
+  posterior_samples(card_sorting_model1, "^b")%>%
+  select(-b_Intercept)%>%
+  mutate(task = "1 card_sorting"),
+  posterior_samples(inf_model1, "^b")%>%
+  select(-b_Intercept)%>%
+  mutate(task = "4 informativeness"),
+  posterior_samples(nov_model1, "^b")%>%
+  select(-b_Intercept)%>%
+  rename(b_age = b_z_age)%>%
+  mutate(task = "2 novelty"),
+  posterior_samples(me_model1, "^b")%>%
+  select(-b_Intercept)%>%
+  rename(b_age = b_z_age)%>%
+  mutate(task = "3 mutual_exclusivity"),
+  posterior_samples(pref_model1, "^b")%>%
+  select(-b_Intercept)%>%
+  rename(b_age = b_z_age)%>%
+  mutate(task = "0 preference")
+)%>%
+  gather(estimate, value, -task)
+
+ggplot(x, aes(y = task, x = value, fill = factor(stat(quantile))))+
+  stat_density_ridges(
+    geom = "density_ridges_gradient",
+    calc_ecdf = TRUE,
+    quantiles = c(0.025, 0.975)
+  ) +
+  facet_grid(~estimate, scales = "free_x")+
+  geom_vline(xintercept = 0, col = "grey", lty = 2)+
+  scale_fill_manual(values = c("white", "lightblue", "white"))+ 
+  guides(fill = F)+
+  theme_few()
+
+```
+
+# Results by task continous
+
+```{r, cache = T}
 # Files to plot data means
@@
 
+## preference
+
+samples_pref <- posterior_samples(pref_model1, "^b")%>%
+  mutate(sample = 1:length(b_z_age))%>%
+  filter(sample %in% samples_to_draw)%>%
+  expand_grid(data$z_age)%>%
+  mutate(y = plogis(b_Intercept + b_z_age * `data$z_age`),
+         age = `data$z_age` + mean(data$age),
+         task = "preference")
+
 ## combine files
@@
   samples_me,
-  samples_nov
+  samples_nov,
+  samples_pref
 )
@@
 
+## preference
+map_pref <- tibble(
+  age = data$z_age,
+  int = fixef(pref_model1)[1,1],
+  slope = fixef(pref_model1)[2,1]
+)%>%
+  mutate(y = plogis(int + slope * age),
+         age = age + mean(data$age),
+         task = "preference")
+
 maps <- bind_rows(
@@
   map_me,
-  map_nov
+  map_nov,
+  map_pref
 )
@@
   guides(alpha = F, col = F)+
-  coord_fixed(ratio = 2)
+  coord_fixed(ratio = 2)#+
+  #ggsave("../graphs/task_results.png", width = 10, height = 2.5, scale = 1.2)
 ```
 
+# Reliability
+
+## Plot
 ```{r}
@@
 
+## Table
 ```{r}
@@
 
-reli
+reli%>%
+  kable()
 ```
@@
 ```{r}
-reli_age <- data%>%
-  filter(task != "training")%>%
-  droplevels()%>%
-  group_by(subage, id,task, test_day)%>%
-  summarise(mean = mean(correct))%>%
-  spread(test_day, mean)%>%
-  na.omit()%>%
-  rename("Day1" = `1`,
-         "Day2" = `2`)%>%
-  group_by(subage,task)%>%
-  summarize(reli = cor.test(Day1,Day2)$estimate,
-            lci = cor.test(Day1,Day2)$conf.int[1],
-            uci = cor.test(Day1,Day2)$conf.int[2],
-            p = cor.test(Day1,Day2)$p.value)%>%
-  mutate_if(is.numeric, round, digits = 2)
+# reli_age <- data%>%
+#   filter(task != "training")%>%
+#   droplevels()%>%
+#   group_by(subage, id,task, test_day)%>%
+#   summarise(mean = mean(correct))%>%
+#   spread(test_day, mean)%>%
+#   na.omit()%>%
+#   rename("Day1" = `1`,
+#          "Day2" = `2`)%>%
+#   group_by(subage,task)%>%
+#   summarize(reli = cor.test(Day1,Day2)$estimate,
+#             lci = cor.test(Day1,Day2)$conf.int[1],
+#             uci = cor.test(Day1,Day2)$conf.int[2],
+#             p = cor.test(Day1,Day2)$p.value)%>%
+#   mutate_if(is.numeric, round, digits = 2)
+# 
+# 
+# reli_age
+```
 
-reli_age
-```
+# Overview: reliability and bi-variat correlations
 
@@
 
+# Factor analysis
+
 ```{r}
-library(psy)
-
 fa_data <- p1 %>%
@@
 
-fit <- factanal(fa_data, 2, rotation="varimax")
+#fit <- factanal(fa_data, 2, rotation="varimax")
 
-scree.plot(fit$correlation)
+#scree.plot(fit$correlation)
 
-fit$loadings
+#fit$loadings
 
@@
 
-plot(pca)
+#plot(pca)
 

### 2020-02-11 analysis/data_round2.Rmd
first draft second round

---
title: "Prag Bat Round 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)

library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
library(psych)
library(readODS)
library(brms)
library(psy)

```

```{r}
## die flogenden Zeilen kannst du überspringen. Weiter gehts in Zeile 68
files <- dir("~/Work/PragBat/raw_data2/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/PragBat/raw_data2/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,34,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date,
                                               trial = as.character(trial))
  raw_data <- bind_rows(raw_data, id)
}

raw_data

```

### 2020-02-11 experiments/ad_hoc.js

@@ -1,0 +1,161 @@
+
+// the actual experiment
+var adhoc = {
+  trial: ["train1","train2",1,2,3,4,5],
+  agents: ["Sheep"],
+  agentOrient: [
+          ["straight","down"],
+          ["straight","down"],
+          ["straight","down"],
+          ["straight","down"],
+          ["straight","down"],
+        ["straight","down"],
+      ["straight","down"]],
+  stimulus: ["house_train","friend_train","box","chair","table","plate","house"],
+  infPos: ["left", "right","left", "right", "right", "left", "right"],
+  data: [],
+
+
+
+// end of the experiment
+  end: function() {
+    // Show the finish slide.
+    showSlide("select");
+    setTimeout(function() { turk.submit(adhoc) }, 500);
+  },
+
+
+// what happens between trials - display agent from previous trial and click on it to move on to the next trial
+   eat: function(event) {
+
+    setTimeout(function() {adhoc.eat2() }, 1500);
+
+    showSlide("adhoc");
+
+    event.target.style.border = '5px solid blue';
+
+    sourceSound("sound/end.mp3");
+    playSound();
+
+
+    $(".object_r").unbind("click");
+    $(".object_l").unbind("click");
+
+      var pick = event.target.src;
+
+    // Code correct: does name of chosen object contain the name of the correct object
+    if (pick.includes("inf")){
+        var correct = 1
+        } else {
+        var correct = 0
+        };
+
+       if (adhoc.infPos[0] == "left"){
+        var LeftFruit = adhoc.stimulus[0]+"_inf";
+        var RightFruit = adhoc.stimulus[0]+"_dis";
+
+    } else  {
+
+        var LeftFruit = adhoc.stimulus[0]+"_dis";
+        var RightFruit = adhoc.stimulus[0]+"_inf";
+    }
+
+
+
+    // data collected
+      data = {
+        subid: train.subid,
+        subage: train.subage,
+        task: "ad_hoc_implicature",
+        trial: adhoc.trial[0],
+        agent: adhoc.agents[0],
+        leftObject: LeftFruit,
+        rightObject: RightFruit,
+        correct_location: adhoc.infPos[0],
+        pick: pick,
+        correct: correct
+            };
+      adhoc.data.push(data);
+
+  },
+
+eat2: function(event) {
+
+    showSlide("eat");
+
[…]

### 2020-02-11 experiments/discourse_continuity.js

@@ -1,0 +1,673 @@
+
+var backgroundImages = new Array();
+for (i = 1; i <= 12; i++) {
+    backgroundImages[i] = new Image();
+    backgroundImages[i].src = "images/backgrounds/back_int" + i + ".jpg";
+}
+
+function showSlide(id) {
+    // Hide all slides
+    $(".slide").hide();
+    // Show just the slide we want to show
+    $("#" + id).show();
+}
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+function showDisconAgent(id, orient) {
+    $(".discon_agent").hide();
+    $(".agent").hide();
+    $(".agent_transition").hide();
+    $("#" + id + "_" + orient).show();
+}
+
+function sourceRightItem(a) {
+    document.getElementById("item_r").src = a;
+}
+
+function showRightItem() {
+    document.getElementById('item_r').style.visibility = 'visible';
+}
+
+function hideRightItem() {
+    document.getElementById('item_r').style.visibility = 'hidden';
+}
+
+function sourceMiddleItem(a) {
+    document.getElementById("item_m").src = a;
+}
+
+function showMiddleItem() {
+    document.getElementById('item_m').style.visibility = 'visible';
+}
+
+function hideMiddleItem() {
+    document.getElementById('item_m').style.visibility = 'hidden';
+}
+
+function sourceLeftItem(a) {
+    document.getElementById("item_l").src = a;
+}
+
+function showLeftItem() {
+    document.getElementById('item_l').style.visibility = 'visible';
+}
+
+function hideLeftItem() {
+    document.getElementById('item_l').style.visibility = 'hidden';
+}
+
+function sourceSound(c) {
+    document.getElementById("sound").src = c;
+}
+
+function playSound() {
+    document.getElementById("sound").play();
+}
+
+function backgroundDis(x) {
+    document.getElementById("background_dis").src = x;
+}
+
+function backgroundDis2(x) {
+    document.getElementById("background2_dis").src = x;
+}
+
+function shuffleProperties(obj) {
+    var new_obj = {};
+    var keys = getKeys(obj);
+    keys;
[…]

### 2020-02-11 experiments/pragBat2.js

@@ -1,0 +1,696 @@
+// preload
+var preFruits = ["duck.png","car.png","car_me.png","bear.png","ball.png","t01.png", "t02.png", "t03.png", "t04.png", "t05.png", "t06.png", "t07.png", "t08.png", "t09.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t17.png", "carrot.png","bread.png","apple_me.png","kite.png", "t18.png","t19.png","t20.png","t21.png","t22.png","t23.png","t24.png","t25.png","t26.png","t27.png","t28.png","t29.png","t30.png","t31.png","t32.png","t33.png","t34.png","t35.png", "t36.png","t37.png","t38.png","t39.png","t44.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png", "bear_me.png"];
+//for critical trials and fillers
+var images = new Array();
+for (i = 0; i < preFruits.length; i++) {
+	images[i] = new Image();
+	images[i].src = "images/" + preFruits[i];
+}
+
+
+var preSounds = [
+         "Monkey_hello.mp3",
+    		 "Monkey_filler_inf_intro.mp3",
+"Monkey_filler_label.mp3",
+"Monkey_filler_more.mp3",
+"Monkey_filler_which.mp3",
+         "Monkey_inf_intro.mp3",
+         "Monkey_label.mp3",
+         "Monkey_me_choice.mp3",
+         "Monkey_pref_choice.mp3",
+         "Monkey_nov_choice.mp3",
+         "Monkey_npoint.mp3",
+         "Monkey_point_nothing.mp3",
+         "Monkey_point_old.mp3",
+         "Monkey_ppoint.mp3",
+         "Monkey_pref_choice.mp3",
+         "Monkey_train.mp3",
+         "Monkey_which.mp3",
+         "Bunny_hello.mp3",
+         "Bunny_inf_intro.mp3",
+         "Bunny_label.mp3",
+         "Bunny_me_choice.mp3",
+         "Bunny_pref_choice.mp3",
+         "Bunny_nov_choice.mp3",
+         "Bunny_npoint.mp3",
+         "Bunny_point_nothing.mp3",
+         "Bunny_point_old.mp3",
+         "Bunny_ppoint.mp3",
[…]

### 2020-02-11 experiments/simple_inf.js

@@ -1,0 +1,414 @@
+// the actual experiment
+var simple_inf = {
+  // Parameters for this sequence.
+  trial: ["filler1","filler2",1,2,3,4,5],
+  agents: ["Tiger"],
+  agentOrient:    [
+    ["straight","point","down"],
+    ["straight","point","down"],
+    ["straight","point","down"],
+    ["straight","point","down"],
+    ["straight","point","down"],
+    ["straight","point","down"],
+    ["straight","point","down"]],
+  object: ["tree","pig","bear","robot","rocket","truck","dino"],
+  inf: ["right","right","left","left","right","left","right"],
+  data: [],
+  targetSwitch: ["stay","switch","stay","switch","switch","stay","stay"],
+
+
+
+// end of the experiment
+  end: function() {
+    // Show the finish slide.
+    showSlide("select");
+      $(".table_l").show();
+    	$(".table_r").show();
+    setTimeout(function() { turk.submit(simple_inf) }, 500);
+  },
+
+
+// what happens between trials - display agent from previous trial and click on it to move on to the next trial
+   eat: function(event) {
+
+
+    showSlide("eat");
+
+    showEat(simple_inf.agents[0])
+
+    $(".agent_eat").click(simple_inf.newtrial);
+
+
+       sourceSound("sound/end.mp3");
+       playSound();
+
+       $("#inf_ob_l").css({opacity: '1'})
+       $("#inf_ob_r").css({opacity: '1'})
+
+  },
+
+
+// unbind and shif variables between trials
+ newtrial: function() {
+
+     $(".selector_l").css("border","none")
+
+     $(".selector_r").css("border","none")
+
+    $(".agent_eat").unbind("click");
+
+     $(".selector_r").unbind("click");
+     $(".selector_l").unbind("click");
+
+    leftInfObject("images/empty.png");
+    rightInfObject("images/empty.png");
+
+
+
+
+    simple_inf.agentOrient.shift();
+    simple_inf.inf.shift();
+    simple_inf.object.shift();
+     simple_inf.targetSwitch.shift();
+     simple_inf.trial.shift();
+
+
+   simple_inf.next();
+  },
+
+
+// recording the choice
+  choice: function() {
+
+    showSlide("inf_choice");
+
+    choiceInfAgent(simple_inf.agents[0],"choice")
+
+    $(".selector_l").show();
+
+    $(".selector_r").show();
+
+
[…]

### 2020-02-11 experiments/mutual_exclusivity.js
exchnage one item in ME to avoid oveerlap

@@ -9,43 +9,43 @@ var me = {
           ["straight","down"],
           ["straight","down"],
           ["straight","down"]],
-  novels: ["t22","t21","t23","t24","t25"],
+  novels: ["t22","t21","t23","t37","t25"],
   familiars: ["carrot","garlic","eggplant","duck","horseshoe"],
   back: [6,7,8,9,10],
   novelPos: ["left", "right", "right", "left", "right"],
   data: [],
-    
 
-    
+
+
 // end of the experiment
   end: function() {
     // Show the finish slide.
     showSlide("select");
     setTimeout(function() { turk.submit(me) }, 500);
   },
-    
-  
-// what happens between trials - display agent from previous trial and click on it to move on to the next trial    
+
+
+// what happens between trials - display agent from previous trial and click on it to move on to the next trial
    eat: function(event) {
-    
+
     setTimeout(function() {me.eat2() }, 1500);
-       
-    showSlide("choice");  
-       
+
+    showSlide("choice");
+
     event.target.style.border = '5px solid blue';
-    
+
     sourceSound("sound/end.mp3");
     playSound();
-    
-       
+
+
     $(".fruit_r").unbind("click");
     $(".fruit_l").unbind("click");
 
-      var pick_src = event.target.src;   
+      var pick_src = event.target.src;
     // get time for reaction time
 
-      
-       
+
+
     // Code correct: does name of chosen object contain the name of the correct object
     if (pick_src.indexOf(me.novels[0]) > -1) {
         var correct =1
@@ -54,20 +54,20 @@ var me = {
         var correct = 0
         var pick = me.familiars[0]
         };
-       
+
        if (me.novelPos[0] == "left"){
         var LeftFruit = me.novels[0];
         var RightFruit = me.familiars[0];
 
     } else  {
-        
+
         var LeftFruit = me.familiars[0];
         var RightFruit = me.novels[0];
-    }    
-       
-       
+    }
 
-    // data collected  
+
+
+    // data collected
       data = {
         subid: train.subid,
         subage: train.subage,
@@ -81,93 +81,93 @@ var me = {
         correct: correct
             };
       me.data.push(data);
-             
+
   },
- 
+
 eat2: function(event) {
-    
+
     showSlide("eat");
-    
+
    background("images/back"+me.back[0]+".jpg");
-    
+
[…]

### 2020-02-13 experiments/ad_hoc.js
First pass pragBat2

@@ -126,13 +126,25 @@ eat2: function(event) {
     };
 
 
-     // sourceSound("sound/adhoc/"+adhoc.agents[0]+"_"+adhoc.stimulus[0]+".mp3");
-     // playSound();
-
-
     showSlide("adhoc");
 
     showAgent(adhoc.agents[0],"straight");
+
+    if (adhoc.trial[0] == "train1"){
+
+      sourceSound("sound/adhoc/sheep_hello_adhoc.mp3");
+      playSound();
+
+setTimeout(function() {
+      sourceSound("sound/adhoc/"+adhoc.agents[0]+"_"+adhoc.stimulus[0]+".mp3");
+      playSound();
+}, 3000);
+
+    } else {
+
+     sourceSound("sound/adhoc/"+adhoc.agents[0]+"_"+adhoc.stimulus[0]+".mp3");
+     playSound();
+    }
 
     // specify what is shown on the objects depending on training and test condition
     if (adhoc.infPos[0] == "left"){
@@ -149,7 +161,7 @@ eat2: function(event) {
 
         }
 
-  
+
     // choice can be made by clicking the objects after - possible after 5s
     setTimeout(function() {
         $(".object_l").click(adhoc.eat);

### 2020-02-13 experiments/simple_inf.js

@@ -11,404 +11,411 @@ var simple_inf = {
     ["straight","point","down"],
     ["straight","point","down"],
     ["straight","point","down"]],
-  object: ["tree","pig","bear","robot","rocket","truck","dino"],
-  inf: ["right","right","left","left","right","left","right"],
-  data: [],
-  targetSwitch: ["stay","switch","stay","switch","switch","stay","stay"],
+    object: ["tree","pig","bear","robot","rocket","truck","dino"],
+    inf: ["right","right","left","left","right","left","right"],
+    data: [],
+    targetSwitch: ["stay","switch","stay","switch","switch","stay","stay"],
 
 
 
-// end of the experiment
-  end: function() {
-    // Show the finish slide.
-    showSlide("select");
+    // end of the experiment
+    end: function() {
+      // Show the finish slide.
+      showSlide("select");
       $(".table_l").show();
-    	$(".table_r").show();
-    setTimeout(function() { turk.submit(simple_inf) }, 500);
-  },
+      $(".table_r").show();
+      setTimeout(function() { turk.submit(simple_inf) }, 500);
+    },
 
 
-// what happens between trials - display agent from previous trial and click on it to move on to the next trial
-   eat: function(event) {
+    // what happens between trials - display agent from previous trial and click on it to move on to the next trial
+    eat: function(event) {
 
 
-    showSlide("eat");
+      showSlide("eat");
 
-    showEat(simple_inf.agents[0])
+      showEat(simple_inf.agents[0])
 
-    $(".agent_eat").click(simple_inf.newtrial);
-
-
-       sourceSound("sound/end.mp3");
-       playSound();
-
-       $("#inf_ob_l").css({opacity: '1'})
-       $("#inf_ob_r").css({opacity: '1'})
-
-  },
+      $(".agent_eat").click(simple_inf.newtrial);
 
 
-// unbind and shif variables between trials
- newtrial: function() {
+      sourceSound("sound/end.mp3");
+      playSound();
 
-     $(".selector_l").css("border","none")
+      $("#inf_ob_l").css({opacity: '1'})
+      $("#inf_ob_r").css({opacity: '1'})
 
-     $(".selector_r").css("border","none")
-
-    $(".agent_eat").unbind("click");
-
-     $(".selector_r").unbind("click");
-     $(".selector_l").unbind("click");
-
-    leftInfObject("images/empty.png");
-    rightInfObject("images/empty.png");
+    },
 
 
+    // unbind and shif variables between trials
[…]

### 2020-02-13 experiments/simple_inf.js
update simple inf timing

@@ -359,7 +359,7 @@ var simple_inf = {
 
             $("#inf_ob_l").animate({bottom: '100', queue:  true},300)
 
-          }, 4300)
+          }, 3700)
 
           setTimeout(function() {
             showInfAgent(simple_inf.agents[0],"look_l")
@@ -388,7 +388,7 @@ var simple_inf = {
 
             $("#inf_ob_r").animate({bottom: '100', queue:    true},300)
 
-          }, 4300)
+          }, 3700)
 
           setTimeout(function() {
             showInfAgent(simple_inf.agents[0],"look_r")

### 2020-02-13 experiments/ad_hoc.js
remove model saves

@@ -132,17 +132,17 @@ eat2: function(event) {
 
     if (adhoc.trial[0] == "train1"){
 
-      sourceSound("sound/adhoc/sheep_hello_adhoc.mp3");
+      sourceSound("sound/sheep_hello_adhoc.mp3");
       playSound();
 
 setTimeout(function() {
-      sourceSound("sound/adhoc/"+adhoc.agents[0]+"_"+adhoc.stimulus[0]+".mp3");
+      sourceSound("sound/"+adhoc.agents[0]+"_"+adhoc.stimulus[0]+".mp3");
       playSound();
 }, 3000);
 
     } else {
 
-     sourceSound("sound/adhoc/"+adhoc.agents[0]+"_"+adhoc.stimulus[0]+".mp3");
+     sourceSound("sound/"+adhoc.agents[0]+"_"+adhoc.stimulus[0]+".mp3");
      playSound();
     }
 

### 2020-02-21 analysis/data_processing.Rmd
fix timing ad hoc

@@
 ```{r}
-# importing data
-### die flogenden Zeilen kannst du überspringen. Weiter gehts in Zeile 68
-# files <- dir("~/Work/PragBat/raw_data/")
-# 
-# raw_data <- data_frame()
-# for (f in files) {
-#   jf <- paste("~/Work/PragBat/raw_data/",f,sep="")
-#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-#   date <- str_sub(jf,33,str_length(jf)-11)
-#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date, 
-#                                                trial = as.character(trial))
-#   raw_data <- bind_rows(raw_data, id)
-# }
-# 
-# unique(raw_data$subid)
-# 
-# 
-# task_data <- raw_data %>%
-#   filter(trial != "training", 
-#          trial != "filler1", 
-#          trial != "filler2",
-#          trial != "train",
-#          trial != "train2")%>%
-#   filter(phase == "shape" | is.na(phase))%>%
-#   mutate(subid = recode(subid, `13.2` = "Vp13.2",
-#                         `13.2` = "Vp13.2",
-#                         `14.2` = "Vp14.2",
-#                         `16.2` = "Vp16.2",
-#                         `19.1` = "Vp19.1",
-#                         `12.1` = "Vp12.1",
-#                         `29.2` = "Vp29.2",
-#                         `26.1` = "Vp26.2",
-#                         `37.1` = "Vp37.1",
-#                         `38.1` = "Vp38.1"
-#                         ))%>%
-#   select(subid, subage, test_date, task, trial, correct)%>%
-#   separate(subid, into = c("id","test_day"), sep="\\.")%>%
-#   mutate(test_day = ifelse(id == "Vp12" & test_date =="2019-11-26", 2, test_day))
+#importing data
+## die flogenden Zeilen kannst du überspringen. Weiter gehts in Zeile 68
+files <- dir("~/Work/PragBat/raw_data/")
 
-#write_csv(task_data, "../data/data.csv")
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/PragBat/raw_data/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  date <- str_sub(jf,33,str_length(jf)-11)
+  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date,
+                                               trial = as.character(trial))
+  raw_data <- bind_rows(raw_data, id)
+}
+
+unique(raw_data$subid)
+
+task_data <- raw_data %>%
+  filter(trial != "training",
+         trial != "filler1",
+         trial != "filler2",
+         trial != "train",
+         trial != "train2")%>%
+  filter(phase == "shape" | is.na(phase))%>%
+  mutate(subid = recode(subid, `13.2` = "Vp13.2",
+                        `13.2` = "Vp13.2",
+                        `14.2` = "Vp14.2",
+                        `16.2` = "Vp16.2",
+                        `19.1` = "Vp19.1",
+                        `12.1` = "Vp12.1",
+                        `29.2` = "Vp29.2",
+                        `26.1` = "Vp26.2",
+                        `37.1` = "Vp37.1",
+                        `38.1` = "Vp38.1"
+                        ),
+         item = ifelse(task == "card_sorting", sample,leftObject))%>%
+  select(subid, subage, test_date, task,item, trial, correct)%>%
+  separate(subid, into = c("id","test_day"), sep="\\.")%>%
+  mutate(test_day = ifelse(id == "Vp12" & test_date =="2019-11-26", 2, test_day))
 
@@
 
-# log <- read_ods("../../VP Liste.ods", sheet = 2)%>%
-#   mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
-#          id = paste("Vp",`ID `, sep = ""))%>%
-#   select(id, age, status)
-#   
-# 
-# data <- task_data %>%
-#   left_join(log)%>%
-#   mutate(check_age = ifelse(subage == substr(age,1,1),T,F))
+log <- read_ods("../../VP Liste.ods", sheet = 2)%>%
+  mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
+         id = paste("Vp",`ID `, sep = ""))%>%
+  select(id, age, status)
 
-data <- read_csv("../data/data.csv")%>%
-  mutate(subage = factor(subage),
-         trial = ifelse(test_day == "2", trial + 4, trial),
-         z_age = age - mean(age))%>%
-  select(-X)
+data <- task_data %>%
+  left_join(log)%>%
+  mutate(check_age = ifelse(subage == substr(age,1,1),T,F),
+         subage = as.numeric(substr(age,1,1)),
+         trial = as.numeric(trial))%>%
+  select(-test_date, - status, -check_age)%>%
+  mutate(trial = ifelse(test_day == "2", 
+                        ifelse(task == "card_sorting", trial + 6, trial +5),
+                        trial),
+         z_age = age - mean(age),
+         z_trial = trial - mean(trial))
+
+write_csv(data, "../data/data.csv")
+
+data <- read_csv("../data/data.csv")
 
@@
 
-# card_sorting_model1 <- brm(correct ~ z_age + trial + (trial|id),
-#                     data = card_sorting_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
-#           sample_prior = F,
-#           chains = 4, 
-#           cores = 4,
-#           save_all_pars = TRUE,
-#           iter = 10000)%>%
-#   add_criterion("waic")%>%
-#   saveRDS(., "../saves/card_sorting_model1.rds")
-# 
-# card_sorting_model2 <- brm(correct ~ trial + (trial|id),
-#                     data = card_sorting_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
-#           sample_prior = F,
-#           chains = 4, 
-#           cores = 4,
-#           save_all_pars = TRUE,
-#           iter = 10000)%>%
-#   add_criterion("waic")%>%
-#   saveRDS(., "../saves/card_sorting_model2.rds")
+card_sorting_model1 <- brm(correct ~ z_age + trial + (trial|id),
+                    data = card_sorting_model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/card_sorting_model1.rds")
+
+card_sorting_model2 <- brm(correct ~ trial + (trial|id),
+                    data = card_sorting_model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/card_sorting_model2.rds")
 

### 2020-02-21 experiments/ad_hoc.js

@@ -138,7 +138,7 @@ eat2: function(event) {
 setTimeout(function() {
      sourceSound("sound/adhoc/"+adhoc.stimulus[0]+".mp3");
       playSound();
-}, 3000);
+}, 4000);
 
     } else {
 

### 2020-02-21 analysis/data_processing.Rmd
update models

@@
 
-log <- read_ods("../../VP Liste.ods", sheet = 2)%>%
+log <- read_ods("../../VP Liste_Manuel.ods", sheet = 2)%>%
   mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
@@
   left_join(log)%>%
+  filter(status == "keep")%>%
   mutate(check_age = ifelse(subage == substr(age,1,1),T,F),
-         subage = as.numeric(substr(age,1,1)),
+         subage = factor(as.numeric(substr(age,1,1))),
          trial = as.numeric(trial))%>%
@@
 
-card_sorting_model_data <- card_sorting_data %>%
-  mutate(trial = trial - mean(trial))
-
-card_sorting_model1 <- brm(correct ~ z_age + trial + (trial|id),
-                    data = card_sorting_model_data, family = bernoulli(),
+card_sorting_model1 <- brm(correct ~ z_age + z_trial + (z_trial|id) + (z_age|item),
+                    data = card_sorting_data, family = bernoulli(),
           control = list(adapt_delta = 0.99),
@@
 
-card_sorting_model2 <- brm(correct ~ trial + (trial|id),
-                    data = card_sorting_model_data, family = bernoulli(),
+card_sorting_model2 <- brm(correct ~ z_trial + (z_trial|id) + (z_age|item),
+                    data = card_sorting_data, family = bernoulli(),
           control = list(adapt_delta = 0.99),
@@
 
-inf_model_data <- inf_data %>%
-  mutate(trial = trial - mean(trial))
+inf_model1 <- brm(correct ~ z_age + z_trial + (z_trial|id) + (z_age|item),
+                    data = inf_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/inf_model1.rds")
 
-# inf_model1 <- brm(correct ~ z_age + trial + (trial|id),
-#                     data = inf_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
-#           sample_prior = F,
-#           chains = 4,
-#           cores = 4,
-#           save_all_pars = TRUE,
-#           iter = 10000)%>%
-#   add_criterion("waic")%>%
-#   saveRDS(., "../saves/inf_model1.rds")
-# 
-# inf_model2 <- brm(correct ~ trial + (trial|id),
-#                     data = inf_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
-#           sample_prior = F,
-#           chains = 4,
-#           cores = 4,
-#           save_all_pars = TRUE,
-#           iter = 10000)%>%
-#   add_criterion("waic")%>%
-#   saveRDS(., "../saves/inf_model2.rds")
+inf_model2 <- brm(correct ~ z_trial + (z_trial|id) + (z_age|item),
+                    data = inf_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/inf_model2.rds")
 
@@
 
-me_model_data <- me_data %>%
-  mutate(trial = trial - mean(trial))
+me_model1 <- brm(correct ~ z_age + z_trial + (z_trial|id) + (z_age|item),
+                    data = me_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/me_model1.rds")
 
-# me_model1 <- brm(correct ~ z_age + trial + (trial|id),
-#                     data = me_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
-#           sample_prior = F,
-#           chains = 4,
-#           cores = 4,
-#           save_all_pars = TRUE,
-#           iter = 10000)%>%
-#   add_criterion("waic")%>%
-#   saveRDS(., "../saves/me_model1.rds")
-# 
-# me_model2 <- brm(correct ~ trial + (trial|id),
-#                     data = me_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
-#           sample_prior = F,
-#           chains = 4,
-#           cores = 4,
-#           save_all_pars = TRUE,
-#           iter = 10000)%>%
-#   add_criterion("waic")%>%
-#   saveRDS(., "../saves/me_model2.rds")
+me_model2 <- brm(correct ~ z_trial + (z_trial|id) + (z_age|item),
+                    data = me_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/me_model2.rds")
 
@@
 
-nov_model_data <- nov_data %>%
-  mutate(trial = trial - mean(trial))
+nov_model1 <- brm(correct ~ z_age + z_trial + (z_trial|id) + (z_age|item),
+                    data = nov_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/nov_model1.rds")
 
-# nov_model1 <- brm(correct ~ z_age + trial + (trial|id),
-#                     data = nov_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
-#           sample_prior = F,
-#           chains = 4,
-#           cores = 4,
-#           save_all_pars = TRUE,
-#           iter = 10000)%>%
-#   add_criterion("waic")%>%
-#   saveRDS(., "../saves/nov_model1.rds")
-# 
-# nov_model2 <- brm(correct ~ trial + (trial|id),
-#                     data = nov_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
-#           sample_prior = F,
-#           chains = 4,
-#           cores = 4,
-#           save_all_pars = TRUE,
-#           iter = 10000)%>%
-#   add_criterion("waic")%>%
-#   saveRDS(., "../saves/nov_model2.rds")
+nov_model2 <- brm(correct ~ z_trial + (z_trial|id) + (z_age|item),
+                    data = nov_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/nov_model2.rds")
 
@@
 
-pref_model_data <- pref_data %>%
-  mutate(trial = trial - mean(trial))
+pref_model1 <- brm(correct ~ z_age + z_trial + (z_trial|id) + (z_age|item),
+                    data = pref_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/pref_model1.rds")
 
-# pref_model1 <- brm(correct ~ z_age + trial + (trial|id),
-#                     data = pref_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
-#           sample_prior = F,
-#           chains = 4,
-#           cores = 4,
-#           save_all_pars = TRUE,
-#           iter = 10000)%>%
-#   add_criterion("waic")%>%
-#   saveRDS(., "../saves/pref_model1.rds")
-# 
-# pref_model2 <- brm(correct ~ trial + (trial|id),
-#                     data = pref_model_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99),
-#           sample_prior = F,
-#           chains = 4,
-#           cores = 4,
-#           save_all_pars = TRUE,
-#           iter = 10000)%>%
-#   add_criterion("waic")%>%
-#   saveRDS(., "../saves/pref_model2.rds")
+pref_model2 <- brm(correct ~ z_trial + (z_trial|id) + (z_age|item),
+                    data = pref_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = TRUE,
+          iter = 10000)%>%
+  add_criterion("waic")%>%
+  saveRDS(., "../saves/pref_model2.rds")
 
@@
   select(-b_Intercept)%>%
-  rename(b_age = b_z_age)%>%
   mutate(task = "2 novelty"),
@@
   select(-b_Intercept)%>%
-  rename(b_age = b_z_age)%>%
   mutate(task = "3 mutual_exclusivity"),
@@
   select(-b_Intercept)%>%
-  rename(b_age = b_z_age)%>%
   mutate(task = "0 preference")
@@
 samples_cs <- posterior_samples(card_sorting_model1, "^b")%>%
-  mutate(sample = 1:length(b_age))%>%
+  mutate(sample = 1:length(b_z_age))%>%
   filter(sample %in% samples_to_draw)%>%
   expand_grid(data$z_age)%>%
-  mutate(y = plogis(b_Intercept + b_age * `data$z_age`),
+  mutate(y = plogis(b_Intercept + b_z_age * `data$z_age`),
          age = `data$z_age` + mean(data$age),
@@
 samples_inf <- posterior_samples(inf_model1, "^b")%>%
-  mutate(sample = 1:length(b_age))%>%
+  mutate(sample = 1:length(b_z_age))%>%
   filter(sample %in% samples_to_draw)%>%
   expand_grid(data$z_age)%>%
-  mutate(y = plogis(b_Intercept + b_age * `data$z_age`),
+  mutate(y = plogis(b_Intercept + b_z_age * `data$z_age`),
          age = `data$z_age` + mean(data$age),

### 2020-03-26 analysis/data_processing.Rmd
prep bayesian correlation for running on cluster

@@
 library(psy)
+library(BayesianFirstAid)
+
+#devtools::install_github("rasmusab/bayesian_first_aid")
 
@@
 ```
+
+```{r}
+ggplot(p1, aes(x = mean))+
+  geom_density()+
+  facet_grid(~task)
+```
+
 # Models
@@
   rename("Day1" = `1`,
-         "Day2" = `2`)%>%
+         "Day2" = `2`)
+
+card_sorting_data <- reli %>%
+  filter(task == "card_sorting")
+
+f2 <- 
+  brm(data = reli, 
+      family = student,
+      mvbind(Day1, Day2) ~ 1,
+      prior = c(prior(gamma(2, .1), class = nu),
+                prior(normal(0, 100), class = Intercept),
+                prior(normal(0, 100), class = sigma, resp = Day1),
+                prior(normal(0, 100), class = sigma, resp = Day2),
+                prior(lkj(1), class = rescor)),
+      iter = 2000, warmup = 500, chains = 4, cores = 4)
+
+y <- reli%>%
   group_by(task)%>%
-  summarize(reli = cor.test(Day1,Day2)$estimate,
-            lci = cor.test(Day1,Day2)$conf.int[1],
-            uci = cor.test(Day1,Day2)$conf.int[2],
-            p = cor.test(Day1,Day2)$p.value)%>%
-  mutate_if(is.numeric, round, digits = 2)
+  bayes.cor.test( ~Day1 + Day2, data= .)
+
+xx <- bayes.cor.test( ~Day1 + Day2, data= card_sorting_data, method = "spearman")
+
+$stats%>%
+  as_data_frame(.,rownames = "par")%>%
+  filter(par == "rho")%>%
+  mutate(task = "card_sorting")%>%
+  select(task,mean,HDIlo,HDIup)
+
+x <- bayes.cor.test(reli$Day1, reli$Day2)
+
+plot(x)
+
+y <- x$stats
+
+y <- summary(x)
+
+as_data_frame(y,rownames = "par")%>%filter(par == "rho")%>%pull(mean)
+
+rownames(y)
 

### 2020-03-26 analysis/data_round2.Rmd
fix timing ad hoc
prep bayesian correlation for running on cluster

@@
 
-raw_data
+task_data <- raw_data%>%
+  filter(trial != "training",
+         trial != "filler1",
+         trial != "filler2",
+         trial != "train",
+         trial != "train1",
+         trial != "train2",
+         task != "training")%>%
+  filter(phase == "shape" | is.na(phase))%>%
+  separate(subid, into = c("id","test_day"), sep="_")
+
+log <- read_xlsx("../../pragBat2_vp_list.xlsx", sheet = 1)%>%
+  mutate(age = as.numeric(difftime(test_day_1, birthday, units = "days"))/365.25,
+         id = paste("VP",ID, sep = ""))%>%
+  select(id, age, status)
+
+data <- task_data %>%
+  left_join(log)%>%
+  filter(status == "keep")%>%
+  mutate(check_age = ifelse(subage == substr(age,1,1),T,F),
+         subage = factor(as.numeric(substr(age,1,1))),
+         trial = as.numeric(trial))%>%
+  mutate(trial = ifelse(test_day == "2", 
+                        ifelse(task == "card_sorting", trial + 6, trial +5),
+                        trial),
+         z_age = age - mean(age),
+         z_trial = trial - mean(trial))%>%
+    select(id, test_day, subage,age, task, trial, agent, correct, z_age, z_trial)
+
+write_csv(data, "../data/data_tom.csv")
+
+data <- read_csv("../data/data_tom.csv")
 
 ```
+
+```{r}
+data%>%
+  group_by(subage)%>%
+  summarise(n= length(unique(id)))
+```
+
+```{r}
+unique(data$id)
+```
+
+```{r}
+data %>%
+  group_by(subage,id)%>%
+  summarise(testdays = length(unique(test_day)))%>%
+  filter(testdays == 2)%>%
+  summarise(complete_retest_data = length(id))
+```
+
+```{r}
+raw_data%>%
+  filter(task == "simple_inf")%>%
+  separate(subid, into = c("id","test_day"), sep="_")%>%
+  filter(trial == "filler1" | trial == "filler2")%>%
+  group_by(id)%>%
+  summarise(mean = mean(correct))
+```
+
+```{r}
+p1 <- data%>%
+  group_by(id,age, subage,task)%>%
+  filter(task != "training")%>%
+  summarise(mean = mean(correct))
+
+p2 <- p1 %>%
+  group_by(subage,task)%>%
+  multi_boot_standard(col = "mean")%>%
+  mutate(chance = ifelse(task == "discourse_continuity", 1/3, 1/2))
+
+ggplot()+
+  geom_hline(data = p2, aes(yintercept = chance), lty = 2)+
+  geom_smooth(data = p1, aes(x = age, y = mean), method = "lm", col = "black", size = 1)+
+  geom_jitter(data = p1, aes(x = age, y = mean), alpha = .5, width = .05, height = .01)+
+  geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = subage))+
+  facet_wrap(~task)+
+  labs(x = "Age Group", y = "Proportion Correct")+
+  scale_color_ptol(name = "Age")+
+  ylim(-0.05, 1.05)+
+  theme_few()+
+  theme(legend.position = c(.85,.2))
+```
+
+```{r}
+p3 <- data%>%
+  filter(task != "training")%>%
+  group_by(id,task, test_day)%>%
+  summarise(mean = mean(correct))%>%
+  spread(test_day, mean)%>%
+  rename("Day1" = `1`,
+         "Day2" = `2`)%>%
+  na.omit()
+
+ggplot(p3, aes(x = Day1, y = Day2))+
+  geom_jitter(width = .05, height = .05, alpha = .5)+
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
+  geom_smooth(method = "lm", col = "#af6300", se = T)+
+  facet_grid(~task)+
+  coord_fixed()+
+  xlim(-.1,1.1)+
+  ylim(-.1,1.1)+
+  theme_few()
+
+```
+
+```{r}
+reli <- data%>%
+  filter(task != "training")%>%
+  droplevels()%>%
+  group_by(id,task, test_day)%>%
+  summarise(mean = mean(correct))%>%
+  spread(test_day, mean)%>%
+  na.omit()%>%
+  rename("Day1" = `1`,
+         "Day2" = `2`)%>%
+  group_by(task)%>%
+  summarize(reli = cor.test(Day1,Day2)$estimate,
+            lci = cor.test(Day1,Day2)$conf.int[1],
+            uci = cor.test(Day1,Day2)$conf.int[2],
+            p = cor.test(Day1,Day2)$p.value)%>%
+  mutate_if(is.numeric, round, digits = 2)
+```
+
+```{r}
+cor <- data%>%
+  filter(task != "training")%>%
+  droplevels()%>%
+  group_by(id,task)%>%
+  summarise(mean = mean(correct))%>%
+  spread(task, mean)%>%
+  ungroup()%>%
+  select(-id)%>%
+  corrr::correlate(diagonal = reli$reli)%>%
+  gather(task, cor, -rowname)%>%
+  mutate(cor = replace(cor, duplicated(cor), NA))%>%
+  mutate_if(is.numeric, round, digits = 2)%>%
+  na.omit()
+
+ggplot(cor, aes(x = rowname, y = task, fill = cor))+
+  geom_tile(color = "white")+
+  labs(x = "", y = "")+
+  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white", 
+   midpoint = 0, limit = c(-1,1), space = "Lab", 
+   name="Correlation") +
+   coord_fixed()+
+  theme_few(base_size = 12)+
+  geom_text(aes(label = cor), color = "black", size = 3) +
+  theme(legend.justification = c(1, 0),
+        legend.position = c(0.55, 0.7),
+        legend.direction = "horizontal",
+        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
+  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
+                title.position = "top", title.hjust = 0.5))
+```

### 2020-03-26 analysis/data_processing.Rmd
switch to Bayesian correlations

@@
 library(brms)
+library(broom)
 library(psy)
-library(BayesianFirstAid)
+library(ggridges)
 
 #devtools::install_github("rasmusab/bayesian_first_aid")
-
+#library(BayesianFirstAid)
 ```
@@
 ## die flogenden Zeilen kannst du überspringen. Weiter gehts in Zeile 68
-files <- dir("~/Work/PragBat/raw_data/")
-
-raw_data <- data_frame()
-for (f in files) {
-  jf <- paste("~/Work/PragBat/raw_data/",f,sep="")
-  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-  date <- str_sub(jf,33,str_length(jf)-11)
-  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date,
-                                               trial = as.character(trial))
-  raw_data <- bind_rows(raw_data, id)
-}
-
-unique(raw_data$subid)
-
-task_data <- raw_data %>%
-  filter(trial != "training",
-         trial != "filler1",
-         trial != "filler2",
-         trial != "train",
-         trial != "train2")%>%
-  filter(phase == "shape" | is.na(phase))%>%
-  mutate(subid = recode(subid, `13.2` = "Vp13.2",
-                        `13.2` = "Vp13.2",
-                        `14.2` = "Vp14.2",
-                        `16.2` = "Vp16.2",
-                        `19.1` = "Vp19.1",
-                        `12.1` = "Vp12.1",
-                        `29.2` = "Vp29.2",
-                        `26.1` = "Vp26.2",
-                        `37.1` = "Vp37.1",
-                        `38.1` = "Vp38.1"
-                        ),
-         item = ifelse(task == "card_sorting", sample,leftObject))%>%
-  select(subid, subage, test_date, task,item, trial, correct)%>%
-  separate(subid, into = c("id","test_day"), sep="\\.")%>%
-  mutate(test_day = ifelse(id == "Vp12" & test_date =="2019-11-26", 2, test_day))
-
-#task_data <- read_csv("../data/data.csv")
-
-# damit du das daten file mit dem log file (deine Liste) mergen kannst (brauchen wir für das numerische alter) legst du deine liste in den gleichen ordner in dem auch ader repository ordner liegt.
+# files <- dir("~/Work/PragBat/raw_data/")
+# 
+# raw_data <- data_frame()
+# for (f in files) {
+#   jf <- paste("~/Work/PragBat/raw_data/",f,sep="")
+#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+#   date <- str_sub(jf,33,str_length(jf)-11)
+#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date,
+#                                                trial = as.character(trial))
+#   raw_data <- bind_rows(raw_data, id)
+# }
+# 
+# unique(raw_data$subid)
+# 
+# 
+# task_data <- raw_data %>%
+#   filter(trial != "training",
+#          trial != "filler1",
+#          trial != "filler2",
+#          trial != "train",
+#          trial != "train2")%>%
+#   filter(phase == "shape" | is.na(phase))%>%
+#   mutate(subid = recode(subid, `13.2` = "Vp13.2",
+#                         `13.2` = "Vp13.2",
+#                         `14.2` = "Vp14.2",
+#                         `16.2` = "Vp16.2",
+#                         `19.1` = "Vp19.1",
+#                         `12.1` = "Vp12.1",
+#                         `29.2` = "Vp29.2",
+#                         `26.1` = "Vp26.2",
+#                         `37.1` = "Vp37.1",
+#                         `38.1` = "Vp38.1"
+#                         ),
+#          item = ifelse(task == "card_sorting", sample,leftObject))%>%
+#   select(subid, subage, test_date, task,item, trial, correct)%>%
+#   separate(subid, into = c("id","test_day"), sep="\\.")%>%
+#   mutate(test_day = ifelse(id == "Vp12" & test_date =="2019-11-26", 2, test_day))
+# 
+# 
+# #task_data <- read_csv("../data/data.csv")
+# 
+# # damit du das daten file mit dem log file (deine Liste) mergen kannst (brauchen wir für das numerische alter) legst du deine liste in den gleichen ordner in dem auch ader repository ordner liegt.
 Dann sollte es klappen.
-
-log <- read_ods("../../VP Liste_Manuel.ods", sheet = 2)%>%
-  mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
-         id = paste("Vp",`ID `, sep = ""))%>%
-  select(id, age, status)
-
-data <- task_data %>%
-  left_join(log)%>%
-  filter(status == "keep")%>%
-  mutate(check_age = ifelse(subage == substr(age,1,1),T,F),
-         subage = factor(as.numeric(substr(age,1,1))),
-         trial = as.numeric(trial))%>%
-  select(-test_date, - status, -check_age)%>%
-  mutate(trial = ifelse(test_day == "2", 
-                        ifelse(task == "card_sorting", trial + 6, trial +5),
-                        trial),
-         z_age = age - mean(age),
-         z_trial = trial - mean(trial))
-
-write_csv(data, "../data/data.csv")
+# 
+# log <- read_ods("../../VP Liste_Manuel.ods", sheet = 2)%>%
+#   mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
+#          id = paste("Vp",`ID `, sep = ""))%>%
+#   select(id, age, status)
+# 
+# 
+# data <- task_data %>%
+#   left_join(log)%>%
+#   filter(status == "keep")%>%
+#   mutate(check_age = ifelse(subage == substr(age,1,1),T,F),
+#          subage = factor(as.numeric(substr(age,1,1))),
+#          trial = as.numeric(trial))%>%
+#   select(-test_date, - status, -check_age)%>%
+#   mutate(trial = ifelse(test_day == "2", 
+#                         ifelse(task == "card_sorting", trial + 6, trial +5),
+#                         trial),
+#          z_age = age - mean(age),
+#          z_trial = trial - mean(trial))
+# 
+# write_csv(data, "../data/data.csv")
 
@@
   theme(legend.position = c(.85,.2))
-```
-
-```{r}
-ggplot(p1, aes(x = mean))+
-  geom_density()+
-  facet_grid(~task)
 ```
@@
 
-library(ggridges)
-
 x <- bind_rows(
@@
 ```{r}
-reli <- data%>%
+reli_data <- data%>%
   filter(task != "training")%>%
@@
 
-card_sorting_data <- reli %>%
-  filter(task == "card_sorting")
+# reli_card_sorting <- reli_data %>%
+#   filter(task == "card_sorting")%>%
+#   bayes.cor.test( ~Day1 + Day2, data =. )
+# 
+# reli_informativeness <- reli_data %>%
+#   filter(task == "informativeness")%>%
+#   bayes.cor.test( ~Day1 + Day2, data =. )
+# 
+# reli_novelty <- reli_data %>%
+#   filter(task == "novelty")%>%
+#   bayes.cor.test( ~Day1 + Day2, data =. )
+# 
+# reli_mutual_exclusivity <- reli_data %>%
+#   filter(task == "mutual_exclusivity")%>%
+#   bayes.cor.test( ~Day1 + Day2, data =. )
+# 
+# reli_preference <- reli_data %>%
+#   filter(task == "preference")%>%
+#   bayes.cor.test( ~Day1 + Day2, data =. )
+# 
+# 
+# reli_table <- bind_rows(
+# 
+#   reli_card_sorting%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task = "card_sorting")%>%
+#   select(task,mean,HDIlo,HDIup),
+# 
+#   reli_informativeness%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task = "informativeness")%>%
+#   select(task,mean,HDIlo,HDIup),
+# 
+#   reli_novelty%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task = "novelty")%>%
+#   select(task,mean,HDIlo,HDIup),
+# 
+#   reli_mutual_exclusivity%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task = "mutual_exclusivity")%>%
+#   select(task,mean,HDIlo,HDIup),
+# 
+#   reli_preference%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task = "preference")%>%
+#   select(task,mean,HDIlo,HDIup)
+# )
 
-f2 <- 
-  brm(data = reli, 
-      family = student,
-      mvbind(Day1, Day2) ~ 1,
-      prior = c(prior(gamma(2, .1), class = nu),
-                prior(normal(0, 100), class = Intercept),
-                prior(normal(0, 100), class = sigma, resp = Day1),
-                prior(normal(0, 100), class = sigma, resp = Day2),
-                prior(lkj(1), class = rescor)),
-      iter = 2000, warmup = 500, chains = 4, cores = 4)
+#write_csv(reli_table, "../data/reli_table.csv")
 
-y <- reli%>%
-  group_by(task)%>%
-  bayes.cor.test( ~Day1 + Day2, data= .)
+reli_table <- read_csv("../data/reli_table.csv")
 
-xx <- bayes.cor.test( ~Day1 + Day2, data= card_sorting_data, method = "spearman")
-
-$stats%>%
-  as_data_frame(.,rownames = "par")%>%
-  filter(par == "rho")%>%
-  mutate(task = "card_sorting")%>%
-  select(task,mean,HDIlo,HDIup)
-
-x <- bayes.cor.test(reli$Day1, reli$Day2)
-
-plot(x)
-
-y <- x$stats
-
-y <- summary(x)
-
-as_data_frame(y,rownames = "par")%>%filter(par == "rho")%>%pull(mean)
-
-rownames(y)
-
-reli%>%
-  kable()
+reli_table
 ```
@@
 ```{r}
-# reli_age <- data%>%
-#   filter(task != "training")%>%
-#   droplevels()%>%
-#   group_by(subage, id,task, test_day)%>%
-#   summarise(mean = mean(correct))%>%
-#   spread(test_day, mean)%>%
-#   na.omit()%>%
-#   rename("Day1" = `1`,
-#          "Day2" = `2`)%>%
-#   group_by(subage,task)%>%
-#   summarize(reli = cor.test(Day1,Day2)$estimate,
-#             lci = cor.test(Day1,Day2)$conf.int[1],
-#             uci = cor.test(Day1,Day2)$conf.int[2],
-#             p = cor.test(Day1,Day2)$p.value)%>%
-#   mutate_if(is.numeric, round, digits = 2)
+# reli_plot <- bind_rows(
+#   reli_card_sorting%>%
+#     as_tibble()%>%
+#     mutate(task = "card_sorting"),
 # 
+#   reli_informativeness%>%
+#     as_tibble()%>%
+#     mutate(task = "informativeness"),
 # 
-# reli_age
+#   reli_novelty%>%
+#     as_tibble()%>%
+#     mutate(task = "novelty"),
+# 
+#   reli_mutual_exclusivity%>%
+#     as_tibble()%>%
+#     mutate(task = "mutual_exclusivity"),
+# 
+#   reli_preference%>%
+#     as_tibble()%>%
+#     mutate(task = "preference")
+# )
+# 
+# write_csv(reli_plot, "../data/reli_plot.csv")
+
+reli_plot <- read_csv("../data/reli_plot.csv")
+
+ggplot(reli_plot, aes(y = task, x = rho, fill = factor(stat(quantile))))+
+  stat_density_ridges(
+    geom = "density_ridges_gradient",
+    calc_ecdf = TRUE,
+    quantiles = c(0.025,0.5, 0.975)
+  ) +
+  xlim(-1,1)+
+  geom_vline(xintercept = 0, col = "grey", lty = 2)+
+  xlab("test - retest correlation")+
+  scale_fill_manual(values = c("white", "lightblue", "lightblue", "white"))+ 
+  guides(fill = F)+
+  theme_few()
+
 ```
@@
 ```{r}
-cor <- data%>%
+cor_data <- data%>%
   filter(task != "training")%>%
@@
   ungroup()%>%
-  select(-id)%>%
-  corrr::correlate(diagonal = reli$reli)%>%
-  gather(task, cor, -rowname)%>%
-  mutate(cor = replace(cor, duplicated(cor), NA))%>%
-  mutate_if(is.numeric, round, digits = 2)%>%
-  na.omit()
+  select(-id)
 
-ggplot(cor, aes(x = rowname, y = task, fill = cor))+
+# cor_ci <- cor_data %>%
+#   bayes.cor.test(~card_sorting + informativeness, data =. )%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task1 = "card_sorting",
+#          task2 = "informativeness")%>%
+#   select(task1, task2 ,mean,HDIlo,HDIup)%>%
+#   mutate_if(is.numeric,round, digits = 2)
+# 
+# cor_cm <- cor_data %>%
+#   bayes.cor.test(~card_sorting + mutual_exclusivity, data =. )%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task1 = "card_sorting",
+#          task2 = "mutual_exclusivity")%>%
+#   select(task1, task2 ,mean,HDIlo,HDIup)%>%
+#   mutate_if(is.numeric,round, digits = 2)
+# 
+# cor_cn <- cor_data %>%
+#   bayes.cor.test(~card_sorting + novelty, data =. )%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task1 = "card_sorting",
+#          task2 = "novelty")%>%
+#   select(task1, task2 ,mean,HDIlo,HDIup)%>%
+#   mutate_if(is.numeric,round, digits = 2)
+# 
+# cor_cp <- cor_data %>%
+#   bayes.cor.test(~card_sorting + preference, data =. )%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task1 = "card_sorting",
+#          task2 = "preference")%>%
+#   select(task1, task2 ,mean,HDIlo,HDIup)%>%
+#   mutate_if(is.numeric,round, digits = 2)
+# 
+# cor_im <- cor_data %>%
+#   bayes.cor.test(~informativeness + mutual_exclusivity, data =. )%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task1 = "informativeness",
+#          task2 = "mutual_exclusivity")%>%
+#   select(task1, task2 ,mean,HDIlo,HDIup)%>%
+#   mutate_if(is.numeric,round, digits = 2)
+# 
+# cor_in <- cor_data %>%
+#   bayes.cor.test(~informativeness + novelty, data =. )%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task1 = "informativeness",
+#          task2 = "novelty")%>%
+#   select(task1, task2 ,mean,HDIlo,HDIup)%>%
+#   mutate_if(is.numeric,round, digits = 2)
+# 
+# cor_ip <- cor_data %>%
+#   bayes.cor.test(~informativeness + preference, data =. )%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task1 = "informativeness",
+#          task2 = "preference")%>%
+#   select(task1, task2 ,mean,HDIlo,HDIup)%>%
+#   mutate_if(is.numeric,round, digits = 2)
+# 
+# cor_mn <- cor_data %>%
+#   bayes.cor.test(~mutual_exclusivity + novelty, data =. )%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task1 = "mutual_exclusivity",
+#          task2 = "novelty")%>%
+#   select(task1, task2 ,mean,HDIlo,HDIup)%>%
+#   mutate_if(is.numeric,round, digits = 2)
+# 
+# cor_mp <- cor_data %>%
+#   bayes.cor.test(~mutual_exclusivity + preference, data =. )%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task1 = "mutual_exclusivity",
+#          task2 = "preference")%>%
+#   select(task1, task2 ,mean,HDIlo,HDIup)%>%
+#   mutate_if(is.numeric,round, digits = 2)
+# 
+# cor_np <- cor_data %>%
+#   bayes.cor.test(~novelty + preference, data =. )%>%
+#   summary()%>%
+#   tidy()%>%
+#   as_tibble()%>%
+#   filter(.rownames == "rho")%>%
+#   mutate(task1 = "novelty",
+#          task2 = "preference")%>%
+#   select(task1, task2 ,mean,HDIlo,HDIup)%>%
+#   mutate_if(is.numeric,round, digits = 2)
+# 
+# 
+# 
+# cor <- bind_rows(
+# cor_ci,
+# cor_cm,
+# cor_cn,
+# cor_cp,
+# cor_im,
+# cor_in,
+# cor_ip,
+# cor_mn,
+# cor_mp,
+# cor_np
+# )
+# 
+# write_csv(cor, "../data/bivariate_correlations.csv")
+
+cor <- read_csv("../data/bivariate_correlations.csv")
+```
+
+```{r}
+cor_plot <- bind_rows(
+  cor,  
+  reli_table%>%
+    mutate(task1 = task,
+          task2 = task)%>%
+    select(task1, task2, mean, HDIlo,HDIup)%>%
+    mutate_if(is.numeric,round, digits = 2)
+)
+```
+
+```{r}
+ggplot(cor_plot, aes(x = task2, y = task1, fill = mean))+
   geom_tile(color = "white")+
@@
   theme_few(base_size = 12)+
-  geom_text(aes(label = cor), color = "black", size = 3) +
+  geom_text(aes(label = mean), color = "black", size = 3) +
   theme(legend.justification = c(1, 0),
@@
 
-#fit <- factanal(fa_data, 2, rotation="varimax")
-
-#scree.plot(fit$correlation)
-
-#fit$loadings
-
-pca$loadings
-
-#plot(pca)
+pca
 

### 2020-10-27 analysis/data_processing.Rmd
add summary

@@
 library(reshape2)
-library(psych)
+#library(psych)
 library(readODS)
@@
 
-data <- read_csv("../data/data.csv")
+data <- read_csv("../data/data_r1.csv")
 
@@
 
+```{r}
+plot(reli_mutual_exclusivity)
+```
+
 # Overview: reliability and bi-variat correlations

### 2020-10-27 analysis/data_round2.Rmd
add summary

--- 2020-02-11 analysis/data_round2.Rmd
@@
 output: html_document
+
 ---
@@
 library(knitr)
-library(langcog)
 library(ggthemes)
@@
 library(psy)
+library(tidyboot)
+library(lubridate)
 
@@
 ```{r}
-## die flogenden Zeilen kannst du überspringen. Weiter gehts in Zeile 68
-files <- dir("~/Work/PragBat/raw_data2/")
+files <- dir("~/Work/Local/PragBat/raw_data2/")
 
@@
 for (f in files) {
-  jf <- paste("~/Work/PragBat/raw_data2/",f,sep="")
+  jf <- paste("~/Work/Local/PragBat/raw_data2/",f,sep="")
   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
@@
 
-raw_data
+task_data <- raw_data%>%
+  filter(trial != "training",
+         trial != "filler1",
+         trial != "filler2",
+         trial != "train",
+         trial != "train1",
+         trial != "train2",
+         task != "training")%>%
+  filter(phase == "shape" | is.na(phase))%>%
+  separate(subid, into = c("id","test_day"), sep="_")
+
+log <- read_xlsx("../../../../Cloud/PragBat/vpl_pragBat2.xlsx", sheet = 1)%>%
+  mutate(age = as.numeric(difftime(as.Date(as.character(test_day_1),format="%Y%m%d"), as.Date(as.character(birthday),format="%Y%m%d"), units = "days"))/365.25,
+         age_num_month = lubridate::time_length(difftime(as.Date(as.character(test_day_1),format="%Y%m%d"), as.Date(as.character(birthday),format="%Y%m%d")), "month"),
+          age_month = round(age_num_month)/12,
+         id = paste("VP",ID, sep = ""))%>%
+  select(id, age, age_month, status)
+
+data <- task_data %>%
+  left_join(log)%>%
+  filter(status == "keep")%>%
+  mutate(check_age = ifelse(subage == substr(age,1,1),T,F),
+         subage = factor(as.numeric(substr(age,1,1))),
+         trial = as.numeric(trial))%>%
+  mutate(trial = ifelse(test_day == "2", 
+                        ifelse(task == "card_sorting", trial + 6, trial +5),
+                        trial),
+         z_age = age - mean(age),
+         z_trial = trial - mean(trial),
+         item = ifelse(task == "card_sorting", sample,leftObject) )%>%
+    select(id, test_day, subage,age, task,item, trial, correct, z_age, z_trial)
+
+ # write_csv(data, "../data/data_r2.csv")
+```
+
+```{r}
+data%>%
+  group_by(subage)%>%
+  summarise(n= length(unique(id)))
+```
+
+```{r}
+unique(data$id)
 
 ```
+
+```{r}
+data %>%
+  group_by(subage,id)%>%
+  summarise(testdays = length(unique(test_day)))%>%
+  filter(testdays == 2)%>%
+  summarise(complete_retest_data = length(id))
+
+data %>%
+  group_by(subage)%>%
+  filter(test_day == 2)%>%
+  summarise(complete_retest_data = length(unique(id)))
+```
+
+```{r}
+p1 <- data%>%
+  group_by(id,age, subage,task)%>%
+  filter(task != "training")%>%
+  summarise(mean = mean(correct))
+
+p2 <- p1 %>%
+  group_by(subage,task)%>%
+  tidyboot_mean(column = mean)%>%
+  mutate(chance = ifelse(task == "discourse_continuity", 1/3, 1/2))
+
+ggplot()+
+  geom_hline(data = p2, aes(yintercept = chance), lty = 2)+
+  geom_smooth(data = p1, aes(x = age, y = mean), method = "lm", col = "black", size = 1)+
+  geom_jitter(data = p1, aes(x = age, y = mean), alpha = .5, width = .05, height = .01)+
+  geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = subage))+
+  facet_wrap(~task)+
+  labs(x = "Age Group", y = "Proportion Correct")+
+  scale_color_ptol(name = "Age")+
+  ylim(-0.05, 1.05)+
+  theme_few()+
+  theme(legend.position = c(.85,.2))
+
+```
+
+```{r}
+p3 <- data%>%
+  filter(task != "training")%>%
+  group_by(id,task, test_day)%>%
+  summarise(mean = mean(correct))%>%
+  spread(test_day, mean)%>%
+  rename("Day1" = `1`,
+         "Day2" = `2`)%>%
+  na.omit()
+
+ggplot(p3, aes(x = Day1, y = Day2))+
+  geom_jitter(width = .05, height = .05, alpha = .5)+
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
+  geom_smooth(method = "lm", col = "#af6300", se = T, size = 0.5)+
+  facet_grid(~task)+
+  coord_fixed()+
+  xlim(-.1,1.1)+
+  ylim(-.1,1.1)+
+  theme_few()
+
+```
+
+```{r}
+reli <- data%>%
+  filter(task != "training")%>%
+  droplevels()%>%
+  group_by(id,task, test_day)%>%
+  summarise(mean = mean(correct))%>%
+  spread(test_day, mean)%>%
+  na.omit()%>%
+  rename("Day1" = `1`,
+         "Day2" = `2`)%>%
+  group_by(task)%>%
+  summarize(reli = cor.test(Day1,Day2)$estimate,
+            lci = cor.test(Day1,Day2)$conf.int[1],
+            uci = cor.test(Day1,Day2)$conf.int[2],
+            p = cor.test(Day1,Day2)$p.value)%>%
+  mutate_if(is.numeric, round, digits = 2)
+```
+
+```{r}
+cor <- data%>%
+  filter(task != "training")%>%
+  droplevels()%>%
+  group_by(id,task)%>%
+  summarise(mean = mean(correct))%>%
+  spread(task, mean)%>%
+  ungroup()%>%
+  select(-id)%>%
+  corrr::correlate(diagonal = reli$reli)%>%
+  gather(task, cor, -rowname)%>%
+  mutate(cor = replace(cor, duplicated(cor), NA))%>%
+  mutate_if(is.numeric, round, digits = 2)%>%
+  na.omit()
+
+ggplot(cor, aes(x = rowname, y = task, fill = cor))+
+  geom_tile(color = "white")+
+  labs(x = "", y = "")+
+  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white", 
+   midpoint = 0, limit = c(-1,1), space = "Lab", 
+   name="Correlation") +
+   coord_fixed()+
+  theme_few(base_size = 12)+
+  geom_text(aes(label = cor), color = "black", size = 3) +
+  theme(legend.justification = c(1, 0),
+        legend.position = c(0.55, 0.7),
+        legend.direction = "horizontal",
+        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
+  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
+                title.position = "top", title.hjust = 0.5))
+```
+
+# Discourse continuity by category
+
+```{r}
+
+con_data <- task_data%>%
+  filter(task == "discourse_continuity")%>%
+  filter(!is.na(correct))
+
+pc1 <- con_data%>%
+  group_by(target1,subage, id) %>%
+  summarise(correct = mean(correct))
+
+pc2 <- pc1 %>%
+  group_by(target1,subage) %>%
+  tidyboot_mean(column = correct)
+
+ggplot()+
+  geom_hline(yintercept = 1/3, lty=2)+
+  geom_jitter( data = pc1, aes(x = subage, y = correct, col = target1), position = position_jitterdodge(jitter.width = .1,jitter.height = .025, dodge.width = .75 ), alpha = .3)+
+  geom_pointrange(data = pc2, aes(x = subage, y = mean, ymin = ci_lower, ymax = ci_upper, col = target1), position = position_dodge(width = .75), pch = 4)+
+  #facet_grid(~experiment)+
+  labs(x="Age",y="Proportion correct")+
+  theme_few()+
+  scale_color_colorblind(name = "Category")
+```
+
+# Data file Spin-off
+
+```{r}
+item_info <- data_frame(
+  task = c(rep("mutual_exclusivity",10),rep("simple_inf",10),rep("ad_hoc_implicature",10)),
+  trial = c(rep(1:10,3)), 
+  item = c(rep(c("carrot","garlic","eggplant","duck","horseshoe"),2),rep(c("bear","robot","rocket","truck","dino"),2), rep(c("box","chair","table","plate","house"),2))
+)
+
+retest_ids <- data %>%
+  filter(test_day == 2)%>%
+  group_by(id)%>%
+  summarise(n())%>%
+  pull(id)
+
+data %>%
+  filter(task == "mutual_exclusivity" |
+         task == "simple_inf" |
+         task == "ad_hoc_implicature",
+         id %in% retest_ids)%>%
+  select(-agent, -z_age, -z_trial)%>%
+  left_join(item_info)%>%
+  select(id, test_day, subage, age, age_month, task, trial, item, correct )%>%
+  mutate(c_age_month = age_month - min(age_month),
+         c_age = age - min(age))%>%
+  write_csv("../../../Spin-off/spin-off/data/data.csv")
+```

### 2020-10-27 analysis/reliability.Rmd
add summary

---
title: "Prag Bat"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)

library(tidyverse)
library(brms)
```

```{r}

data <- read_csv("../data/data.csv")

```

# Total sample size

```{r}
data%>%
  group_by(subage)%>%
  summarise(n= length(unique(id)))%>%
  kable()

```

# Sample size with two test days

```{r}
data %>%
  group_by(subage,id)%>%
  summarise(testdays = length(unique(test_day)))%>%
  filter(testdays == 2)%>%
  summarise(complete_retest_data = length(id))%>%
  kable()
```

```{r}
# data %>%
#   group_by(id,test_day)%>%
#   summarise(n())%>%
#   arrange(id,test_day)

```

```{r}
# data%>%
#   group_by(test_day,task)%>%
#   summarise(n= length(unique(id)))
```

# Models

## correlations

```{r}
# card sorting

complete_data <- reli_data %>%
  group_by(subage,id)%>%
  summarise(testdays = length(unique(test_day)))%>%
  filter(testdays == 2)%>%
  pull(id)

reli_data <- data%>%
  filter(task != "training", 
         id %in% complete_data)%>%
  mutate(test_day = ifelse(test_day == 1, "day1", "day2"))

rel_model <- brm(correct ~ (test_day|task/id),
                 data = reli_data, 
                 family = bernoulli(),
                 control = list(adapt_delta = 0.9),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = F,
          iter = 2000)

summary(rel_model)

task <- as_tibble(ranef(rel_model)$task, rownames = "task")%>%
  select(task,Estimate.Intercept, Estimate.test_dayday2)%>%
  rename("Day1_int" = Estimate.Intercept,
         "Day2_int" = Estimate.test_dayday2)%>%
  mutate(task = str_replace(task, "card_sorting", "cardsorting"),
         task = str_replace(task, "mutual_exclusivity", "mutualexclusivity"))

id <- as_tibble(ranef(rel_model)$`task:id`, rownames = "id")%>%
  select(id,Estimate.Intercept, Estimate.test_dayday2)%>%
  rename("Day1" = Estimate.Intercept,
         "Day2" = Estimate.test_dayday2)%>%
  mutate(id = str_replace(id, "card_sorting", "cardsorting"),
         id = str_replace(id, "mutual_exclusivity", "mutualexclusivity"),
         Day1 = plogis(Day1),
         Day2 = plogis(Day2))%>%
  separate(id, c("task", "id"), sep = "_")

left_join(id, task)%>%
  mutate(est_1 = plogis(Day1_int + Day1),
         est_2 = plogis(Day2_int + Day2))%>%
  group_by(task)%>%
  summarise(cor = cor(est_1, est_2))

```

## reliability

```{r}
# card sorting

cor_model <- brm(correct ~ 1 + (task|id) + (task|item),
                    data = data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 2000)

summary(cor_model)

```

### 2020-10-27 analysis/summary.Rmd
add summary

---
title: "Prag Bat Summary"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)

library(tidyverse)
library(knitr)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
#library(psych)
library(readODS)
library(brms)
library(psy)
library(tidyboot)
library(lubridate)
library(ggpubr)

```

```{r, include=FALSE}
data <- bind_rows(
  read_csv("../data/data_r1.csv")%>%filter(task != "training")%>%mutate(round = "R1"),
  read_csv("../data/data_r2.csv")%>%mutate(round = "R2")
  )%>%
  mutate(round = factor(round),
         id = paste(round, id, sep = "_"))

```

```{r, include=FALSE}
data%>%
  group_by(subage)%>%
  summarise(n= length(unique(id)))
```
# Objective

Assess reliability of and relations between different pragmatic inference tasks which we have developed over the years.

# Sample size

Our goal was to test at least 20 children per age group and round twice. Children were tested in a kindergarten in Leipzig.

```{r}
data %>%
  group_by(subage,id,round)%>%
  summarise(testdays = length(unique(test_day)))%>%
  group_by(round,subage)%>%
  summarise(n = length(unique(id)),
            complete_retest_data = sum(testdays == 2))%>%
  kable()
```

# Results by Task

All tasks had 5 trials, except for card sorting, which had 6. All subjects got the tasks in the same order and the same version of each task.

Round 1 included the following tasks:

* Informativeness (same setup and stimuli as in MCC)
* Preference (as in MCC)
* Novelty (as in SPIN)
* Mutual exclusivity (as in SPIN, with fewer items)
* Card sorting (DCCS sensu Zelazo, 2006)

Round 1 included the following tasks:

* Simple informativeness (same setup and stimuli as in Frank & Goodman, 2014)
* Ad-hoc implicature (same stimuli as Yoon & Frank, 2019)
* Discourse continuity (as in DISCON)
* Mutual exclusivity (as in SPIN, with fewer items, same as R1)
* Card sorting (DCCS sensu Zelazo, 2006, same as R1)

For mutual exclusivity and card sorting we have a direct replication. The plot below shows all data, including data from children who were tested only once.

```{r}
p1 <- data%>%
  group_by(round, id,age, subage,task)%>%
  filter(task != "training")%>%
  summarise(mean = mean(correct))

p2 <- p1 %>%
  group_by(round,subage,task)%>%
  tidyboot_mean(column = mean)%>%
  mutate(chance = ifelse(task == "discourse_continuity", 1/3, 1/2))

ggplot()+
  geom_hline(data = p2, aes(yintercept = chance), lty = 2)+
  geom_smooth(data = p1, aes(x = age, y = mean, lty = round), method = "lm", col = "black", size = 1)+
  geom_jitter(data = p1, aes(x = age, y = mean, pch = round), alpha = .5, width = .05, height = .01)+
  geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = factor(subage), pch = round), position = position_dodge(width = .5))+
  facet_wrap(~task)+
  labs(x = "Age Group", y = "Proportion Correct")+
  scale_color_ptol(name = "Age")+
  ylim(-0.05, 1.05)+
  theme_few()+
  theme(legend.position = c(.85,.1), legend.direction = "horizontal")

```

# Reliability

Based on simple Pearson correlations on the data aggregated by subject, task and test day.

```{r}
reli <- data%>%
  filter(task != "training")%>%
  droplevels()%>%
  group_by(round,id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  na.omit()%>%
  rename("Day1" = `1`,
         "Day2" = `2`)%>%
  group_by(round,task)%>%
  summarize(reli = cor.test(Day1,Day2)$estimate,
            lci = cor.test(Day1,Day2)$conf.int[1],
            uci = cor.test(Day1,Day2)$conf.int[2],
            p = cor.test(Day1,Day2)$p.value)%>%
  mutate_if(is.numeric, round, digits = 2)

reli%>%
  kable()
```

# Correlations between tasks

Based on simple Pearson correlations on the data aggregated by subject and task.

```{r, fig.align="center"}
cor_r1 <- data%>%
  filter(round == "R1")%>%
  droplevels()%>%
  group_by(id,task)%>%
  summarise(mean = mean(correct))%>%
  spread(task, mean)%>%
  ungroup()%>%
  select(-id)%>%
  corrr::correlate(diagonal = reli%>%filter(round == "R1")%>%pull(reli))%>%
  gather(task, cor, -rowname)%>%
  mutate(cor = replace(cor, duplicated(cor), NA))%>%
  mutate_if(is.numeric, round, digits = 2)%>%
  na.omit()%>%
  mutate(round = "R1")

cor_r2 <- data%>%
  filter(round == "R2")%>%
  droplevels()%>%
  group_by(id,task)%>%
  summarise(mean = mean(correct))%>%
  spread(task, mean)%>%
  ungroup()%>%
  select(-id)%>%
  corrr::correlate(diagonal = reli%>%filter(round == "R2")%>%pull(reli))%>%
  gather(task, cor, -rowname)%>%
  mutate(cor = replace(cor, duplicated(cor), NA))%>%
  mutate_if(is.numeric, round, digits = 2)%>%
  na.omit()%>%
  mutate(round = "R2")

cor <- bind_rows(
  cor_r1,
  cor_r2
)

ggarrange(
ggplot(cor_r1, aes(x = rowname, y = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Correlation") +
   coord_fixed()+
  theme_few()+
  geom_text(aes(label = cor), color = "black", size = 3) +
  ggtitle("Round 1")+
  theme(
        legend.position = "right",
        legend.direction = "horizontal",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)),

ggplot(cor_r2, aes(x = rowname, y = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Correlation") +
   coord_fixed()+
  theme_few()+
  geom_text(aes(label = cor), color = "black", size = 3) +
  ggtitle("Round 2")+
  theme(
        legend.position = "right",
        legend.direction = "horizontal",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)),
common.legend = T, legend = "top"

)
```

### 2020-10-27 experiments/data_submission.js

@@ -1,0 +1,254 @@
+// Bundle in Crockford's JSON2.js
+var JSON;JSON||(JSON={});
+(function(){function k(a){return a<10?"0"+a:a}function o(a){p.lastIndex=0;return p.test(a)?'"'+a.replace(p,function(a){var c=r[a];return typeof c==="string"?c:"\\u"+("0000"+a.charCodeAt(0).toString(16)).slice(-4)})+'"':'"'+a+'"'}function l(a,j){var c,d,h,m,g=e,f,b=j[a];b&&typeof b==="object"&&typeof b.toJSON==="function"&&(b=b.toJSON(a));typeof i==="function"&&(b=i.call(j,a,b));switch(typeof b){case "string":return o(b);case "number":return isFinite(b)?String(b):"null";case "boolean":case "null":return String(b);case "object":if(!b)return"null";
+e+=n;f=[];if(Object.prototype.toString.apply(b)==="[object Array]"){m=b.length;for(c=0;c<m;c+=1)f[c]=l(c,b)||"null";h=f.length===0?"[]":e?"[\n"+e+f.join(",\n"+e)+"\n"+g+"]":"["+f.join(",")+"]";e=g;return h}if(i&&typeof i==="object"){m=i.length;for(c=0;c<m;c+=1)typeof i[c]==="string"&&(d=i[c],(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h))}else for(d in b)Object.prototype.hasOwnProperty.call(b,d)&&(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h);h=f.length===0?"{}":e?"{\n"+e+f.join(",\n"+e)+"\n"+g+"}":"{"+f.join(",")+
+"}";e=g;return h}}if(typeof Date.prototype.toJSON!=="function")Date.prototype.toJSON=function(){return isFinite(this.valueOf())?this.getUTCFullYear()+"-"+k(this.getUTCMonth()+1)+"-"+k(this.getUTCDate())+"T"+k(this.getUTCHours())+":"+k(this.getUTCMinutes())+":"+k(this.getUTCSeconds())+"Z":null},String.prototype.toJSON=Number.prototype.toJSON=Boolean.prototype.toJSON=function(){return this.valueOf()};var q=/[\u0000\u00ad\u0600-\u0604\u070f\u17b4\u17b5\u200c-\u200f\u2028-\u202f\u2060-\u206f\ufeff\ufff0-\uffff]/g,
[…]

### 2020-10-27 experiments/mmturkey_pragBat.js

@@ -26,10 +26,10 @@ turk = turk || {};
     };
   }
 
-  
+
   var hopUndefined = !Object.prototype.hasOwnProperty,
       showPreviewWarning = true;
-  
+
   // We can disable the previewWarning by including this script with "nowarn" in the script url
   // (i.e. mmturkey.js?nowarn). This doesn't work in FF 1.5, which doesn't define document.scripts
   if (document.scripts) {
@@ -41,7 +41,7 @@ turk = turk || {};
       }
     }
   }
-  
+
   var param = function(url, name ) {
     name = name.replace(/[\[]/,"\\\[").replace(/[\]]/,"\\\]");
     var regexS = "[\\?&]"+name+"=([^&#]*)";
@@ -49,7 +49,7 @@ turk = turk || {};
     var results = regex.exec( url );
     return ( results == null ) ? "" : results[1];
   }
-  
+
   function getKeys(obj) {
     var a = [];
     for(var key in obj) {
@@ -59,13 +59,13 @@ turk = turk || {};
     }
     return a;
   }
-  
+
   // warning: Object.keys() is no good in older browsers
   function isTable(array,equality) {
   	if (!(array instanceof Array)) {
   		return false;
   	}
-  	
+
   	// if the array contains a non-Object, bail
   	if (array.reduce(function(acc,x) { return !(x instanceof Object) || acc },false)) {
   	  return false;
@@ -76,7 +76,7 @@ turk = turk || {};
   			return a && typeof x == "object"
   		},true);
   	}
-  	
+
     var arraysEqual = function(a,b) {
     	var i = a.length;
     	if (b.length != i) {
@@ -87,8 +87,8 @@ turk = turk || {};
     			return false;
     		}
     	}
-    	return true;	
-    }    
+    	return true;
+    }
 
   	var keys = getKeys(array[0]);
 
@@ -96,7 +96,7 @@ turk = turk || {};
   		return a && arraysEqual(keys,getKeys(x));
   	},true);
   }
-  
+
   var htmlifyTable = function(array) {
     var getRow = function(obj) {
       var str = "";
@@ -105,9 +105,9 @@ turk = turk || {};
       str += "</tr>";
       return str;
     }
-    
+
     var keys = getKeys(array[0]);
-    
+
     var str = "";
     str += "<span title='tabular representation of array of objects with the same set of keys'>";
     str += "<table border='1' style='border-collapse: collapse' cellpadding='3'>"
@@ -116,10 +116,10 @@ turk = turk || {};
     str += "</tr>";
[…]

### 2020-10-28 analysis/summary.Rmd
playing around with factor analysis

@@
 library(readODS)
-library(brms)
+#library(brms)
 library(psy)
@@
 library(ggpubr)
-
+library(lavaan)
 ```
@@
 data <- bind_rows(
-  read_csv("../data/data_r1.csv")%>%filter(task != "training")%>%mutate(round = "R1"),
-  read_csv("../data/data_r2.csv")%>%mutate(round = "R2")
-  )%>%
+  read_csv("../data/data_r1.csv") %>%filter(task != "training") %>%mutate(round = "R1"),
+  read_csv("../data/data_r2.csv") %>%mutate(round = "R2")
+  ) %>%
   mutate(round = factor(round),
@@
 ```{r, include=FALSE}
-data%>%
-  group_by(subage)%>%
+data %>%
+  group_by(subage) %>%
   summarise(n= length(unique(id)))
@@
 data %>%
-  group_by(subage,id,round)%>%
-  summarise(testdays = length(unique(test_day)))%>%
-  group_by(round,subage)%>%
+  group_by(subage,id,round) %>%
+  summarise(testdays = length(unique(test_day))) %>%
+  group_by(round,subage) %>%
   summarise(n = length(unique(id)),
-            complete_retest_data = sum(testdays == 2))%>%
+            complete_retest_data = sum(testdays == 2)) %>%
   kable()
@@
 
-Round 1 included the following tasks:
+Round 2 included the following tasks:
 
@@
 ```{r}
-p1 <- data%>%
-  group_by(round, id,age, subage,task)%>%
-  filter(task != "training")%>%
+p1 <- data %>%
+  group_by(round, id,age, subage,task) %>%
+  filter(task != "training") %>%
   summarise(mean = mean(correct))
@@
 p2 <- p1 %>%
-  group_by(round,subage,task)%>%
-  tidyboot_mean(column = mean)%>%
+  group_by(round,subage,task) %>%
+  tidyboot_mean(column = mean) %>%
   mutate(chance = ifelse(task == "discourse_continuity", 1/3, 1/2))
@@
   facet_wrap(~task)+
-  labs(x = "Age Group", y = "Proportion Correct")+
-  scale_color_ptol(name = "Age")+
+  labs(x = "Age Group", y = "Proportion Correct") +
+  scale_color_ptol(name = "Age") +
   ylim(-0.05, 1.05)+
@@
 ```{r}
-reli <- data%>%
-  filter(task != "training")%>%
-  droplevels()%>%
-  group_by(round,id,task, test_day)%>%
-  summarise(mean = mean(correct))%>%
-  spread(test_day, mean)%>%
-  na.omit()%>%
+wide_data <- data %>%
+  filter(task != "training") %>%
+  droplevels() %>%
+  group_by(round,id,task, test_day) %>%
+  summarise(mean = mean(correct)) %>%
+  spread(test_day, mean) %>%
+  na.omit() %>%
   rename("Day1" = `1`,
-         "Day2" = `2`)%>%
-  group_by(round,task)%>%
+         "Day2" = `2`)
+
+reli <- wide_data %>%
+  group_by(round, task) %>%
   summarize(reli = cor.test(Day1,Day2)$estimate,
@@
             uci = cor.test(Day1,Day2)$conf.int[2],
-            p = cor.test(Day1,Day2)$p.value)%>%
+            p = cor.test(Day1,Day2)$p.value, 
+            n = n()) %>%
   mutate_if(is.numeric, round, digits = 2)
 
-reli%>%
+reli %>%
+  kable()
+```
+Explore consolidating across rounds.
+
+```{r}
+reli_task <- wide_data %>%
+  group_by(task) %>%
+  summarize(reli = cor.test(Day1,Day2)$estimate,
+            lci = cor.test(Day1,Day2)$conf.int[1],
+            uci = cor.test(Day1,Day2)$conf.int[2],
+            p = cor.test(Day1,Day2)$p.value, 
+            n = n()) %>%
+  mutate_if(is.numeric, round, digits = 2)
+
+reli_task %>%
+  arrange(desc(reli)) %>%
   kable()
@@
 ```{r, fig.align="center"}
-cor_r1 <- data%>%
-  filter(round == "R1")%>%
-  droplevels()%>%
-  group_by(id,task)%>%
-  summarise(mean = mean(correct))%>%
-  spread(task, mean)%>%
-  ungroup()%>%
-  select(-id)%>%
-  corrr::correlate(diagonal = reli%>%filter(round == "R1")%>%pull(reli))%>%
-  gather(task, cor, -rowname)%>%
-  mutate(cor = replace(cor, duplicated(cor), NA))%>%
-  mutate_if(is.numeric, round, digits = 2)%>%
-  na.omit()%>%
+cor_r1 <- data %>%
+  filter(round == "R1") %>%
+  droplevels() %>%
+  group_by(id,task) %>%
+  summarise(mean = mean(correct)) %>%
+  spread(task, mean) %>%
+  ungroup() %>%
+  select(-id) %>%
+  corrr::correlate(diagonal = reli %>%
+                     filter(round == "R1") %>%
+                     pull(reli)) %>%
+  gather(task, cor, -rowname) %>%
+  mutate(cor = replace(cor, duplicated(cor), NA)) %>%
+  mutate_if(is.numeric, round, digits = 2) %>%
+  na.omit() %>%
   mutate(round = "R1")
@@
 cor_r2 <- data%>%
-  filter(round == "R2")%>%
-  droplevels()%>%
-  group_by(id,task)%>%
-  summarise(mean = mean(correct))%>%
-  spread(task, mean)%>%
-  ungroup()%>%
-  select(-id)%>%
-  corrr::correlate(diagonal = reli%>%filter(round == "R2")%>%pull(reli))%>%
-  gather(task, cor, -rowname)%>%
-  mutate(cor = replace(cor, duplicated(cor), NA))%>%
-  mutate_if(is.numeric, round, digits = 2)%>%
-  na.omit()%>%
+  filter(round == "R2") %>%
+  droplevels() %>%
+  group_by(id,task) %>%
+  summarise(mean = mean(correct)) %>%
+  spread(task, mean) %>%
+  ungroup() %>%
+  select(-id) %>%
+  corrr::correlate(diagonal = reli%>%filter(round == "R2") %>%pull(reli)) %>%
+  gather(task, cor, -rowname) %>%
+  mutate(cor = replace(cor, duplicated(cor), NA)) %>%
+  mutate_if(is.numeric, round, digits = 2) %>%
+  na.omit() %>%
   mutate(round = "R2")
@@
 ```
+
+# Factor analysis
+
+## EFA
+
+Average across task days.
+
+```{r}
+efa_data <- filter(data, round == "R1") %>%
+  group_by(id, task) %>% 
+  summarise(correct = mean(correct)) %>%
+  pivot_wider(names_from = task, values_from = correct)
+```
+
+```{r}
+fa_data <- as.matrix(dplyr::select(ungroup(efa_data), -1))
+f1 <- factanal(fa_data, 1)
+f1
+```
+
+```{r}
+f2 <- factanal(fa_data, 2)
+f2
+```
+`
+
+## CFA
+[https://lavaan.ugent.be/tutorial/cfa.html]()
+
+Data
+
+```{r}
+lavaan_data <- filter(data, round == "R1", test_day == 1) %>%
+  group_by(id, task) %>%
+  summarise(correct = mean(correct)) %>%
+  pivot_wider(names_from = task, values_from = correct)
+```
+
+```{r}
+model1 <- 'pragmatic  =~ informativeness + novelty + preference + mutual_exclusivity 
+          ef =~ card_sorting'
+
+fit <- cfa(model1, data=lavaan_data)
+summary(fit)
+```

### 2020-10-28 analysis/summary.Rmd
add cfa reli

@@
 library(lavaan)
+library(blavaan)
+library(semPlot)
 ```
@@
 ```{r}
-lavaan_data <- filter(data, round == "R1", test_day == 1) %>%
+lavaan_data_1 <- filter(data, round == "R1") %>%
   group_by(id, task) %>%
@@
   pivot_wider(names_from = task, values_from = correct)
+
+lavaan_data_2 <- filter(data, round == "R2") %>%
+  group_by(id, task) %>%
+  summarise(correct = mean(correct)) %>%
+  pivot_wider(names_from = task, values_from = correct)
+
+lavaan_data_r1 <- filter(data, round == "R1") %>%
+  group_by(test_day,id, task) %>%
+  summarise(correct = mean(correct)) %>%
+  pivot_wider(names_from = c(task,test_day), values_from = correct)%>%
+  na.omit()
+
+lavaan_data_r2 <- filter(data, round == "R2") %>%
+  group_by(test_day, id, task) %>%
+  summarise(correct = mean(correct)) %>%
+  pivot_wider(names_from = c(task,test_day), values_from = correct)%>%
+  na.omit()
+```
+### Reliability
+
+```{r}
+model_rel_1 <- '
+pragmatic_1  =~ informativeness_1  + mutual_exclusivity_1 + novelty_1 + preference_1
+pragmatic_2  =~ informativeness_2  + mutual_exclusivity_2 + novelty_2 + preference_2
+
+pragmatic_1 ~~ pragmatic_2
+
+informativeness_1 ~~ informativeness_2
+mutual_exclusivity_1 ~~ mutual_exclusivity_2
+novelty_1 ~~ novelty_2
+preference_1 ~~ preference_2
+'
+
+fit_rel_1 <- cfa(model_rel_1, data=lavaan_data_r1, std.lv = TRUE)
+
+summary(fit_rel_1,  ci = T)
+
 ```
@@
 ```{r}
-model1 <- 'pragmatic  =~ informativeness + novelty + preference + mutual_exclusivity 
-          ef =~ card_sorting'
+model_rel_2 <- '
+pragmatic_1  =~ ad_hoc_implicature_1  + mutual_exclusivity_1 + simple_inf_1 + discourse_continuity_1
+pragmatic_2  =~ ad_hoc_implicature_2  + mutual_exclusivity_2 + simple_inf_2 + discourse_continuity_2
 
-fit <- cfa(model1, data=lavaan_data)
-summary(fit)
+pragmatic_1 ~~ pragmatic_2
+
+ad_hoc_implicature_1 ~~ ad_hoc_implicature_2
+mutual_exclusivity_1 ~~ mutual_exclusivity_2
+simple_inf_1 ~~ simple_inf_2
+discourse_continuity_1 ~~ discourse_continuity_2
+
+'
+
+fit_rel_2 <- cfa(model_rel_2, data=lavaan_data_r2, std.lv = TRUE)
+
+summary(fit_rel_2, ci = T)
+
+semPaths(fit_rel_2, "std")
+
+fitmeasures(fit_rel_2)
+
 ```
+
+### Relations between constructs
+
+```{r}
+model_1 <- '
+pragmatic  =~ informativeness  + mutual_exclusivity + novelty + preference
+ef  =~ card_sorting
+'
+
+fit_1 <- cfa(model_1, data=lavaan_data_1, std.lv = TRUE)
+
+summary(fit_1, ci = T)
+
+semPaths(fit_1, "std")
+
+fitmeasures(fit_1)
+```
+
+```{r}
+model_2 <- '
+pragmatic  =~ ad_hoc_implicature  + mutual_exclusivity + simple_inf + discourse_continuity
+ef  =~ card_sorting
+'
+
+fit_2 <- cfa(model_2, data=lavaan_data_2, std.lv = TRUE)
+
+summary(fit_2, ci = T)
+
+semPaths(fit_2, "std")
+
+fitmeasures(fit_2)
+```
+
+### Bayesian estimation
+
+#### Reliability
+```{r}
+bfit_rel_1<- bcfa(model_rel_1, 
+                   data=lavaan_data_r1, 
+                   std.lv = TRUE,
+                   n.chains = 4,
+                   burnin = 2000,
+                   sample = 4000)
+
+summary(bfit_rel_1, ci = T)
+```
+
+```{r}
+
+bfit_rel_2 <- bcfa(model_rel_2, 
+                   data=lavaan_data_r2, 
+                   std.lv = TRUE,
+                   n.chains = 4,
+                   burnin = 2000,
+                   sample = 4000)
+
+summary(bfit_rel_2, ci = T)
+
+semPaths(bfit_rel_2, "std")
+```
+
+#### Relations between constructs
+
+```{r}
+bfit_1 <- bcfa(model_1, 
+                   data=lavaan_data_1, 
+                   std.lv = TRUE,
+                   n.chains = 4,
+                   burnin = 2000,
+                   sample = 4000)
+
+summary(bfit_1, ci = T)
+
+```
+
+```{r}
+bfit_2 <- bcfa(model_2, 
+                   data=lavaan_data_2, 
+                   std.lv = TRUE,
+                   n.chains = 4,
+                   burnin = 2000,
+                   sample = 4000
+               )
+
+summary(bfit_2, ci = T)
+
+semPaths(bfit_2, "std")
+```

### 2020-10-30 analysis/summary.Rmd
add cfa reli
add local save and blueprint for RMTS

@@
 
-fit_2 <- cfa(model_2, data=lavaan_data_2, std.lv = TRUE)
+fit_2 <- sem(model_2, data=lavaan_data_2)
 
-summary(fit_2, ci = T)
+summary(fit_2,  standardized = T)
 
-semPaths(fit_2, "std")
+fitmeasures(fit_2, c("cfi", "rmsea"))
 
-fitmeasures(fit_2)
+semPaths(fit_2, what = "paths", whatLabels= "stand", rotation = 1)
+
+### compare models
+
+model_2_2 <- '
+pragmatic  =~ ad_hoc_implicature  + mutual_exclusivity + simple_inf + discourse_continuity + card_sorting
+'
+
+fit_2_2 <- sem(model_2_2, data=lavaan_data_2)
+
+summary(fit_2_2,  standardized = T)
+
+fitmeasures(fit_2_2, c("cfi", "rmsea"))
+
+anova(fit_2,fit_2_2)
+
 ```
@@
 summary(bfit_rel_1, ci = T)
+
+semPaths(bfit_rel_1, "std")
 ```

### 2020-10-30 experiments/ad_hoc.js

@@ -21,7 +21,7 @@ var adhoc = {
   end: function() {
     // Show the finish slide.
     showSlide("select");
-    setTimeout(function() { turk.submit(adhoc) }, 500);
+    setTimeout(function() { downloadData(adhoc.data) }, 500);
   },
 
 

### 2020-10-30 experiments/card_sorting.js

@@ -18,12 +18,12 @@ var sort = {
         // Show the finish slide.
         showSlide("select");
         setTimeout(function () {
-            turk.submit(sort)
+            downloadData(sort.data)
         }, 500);
     },
 
 
-    // unbind and shift variables between trials      
+    // unbind and shift variables between trials
     newtrial: function () {
 
         $(".target_l").css("border", "none")
@@ -113,7 +113,7 @@ var sort = {
         }
 
         $(".target_l").click(function () {
-            
+
             event.target.style.border = '5px solid orange';
 
             $(".selector").show();
@@ -156,7 +156,7 @@ var sort = {
             };
 
 
-            // data collected  
+            // data collected
             data = {
                 subid: train.subid,
                 subage: train.subage,
@@ -173,7 +173,7 @@ var sort = {
             sort.data.push(data);
         });
 
-        
+
         $(".target_r").click(function () {
 
             $(".selector").show();
@@ -218,7 +218,7 @@ var sort = {
             };
 
 
-            // data collected  
+            // data collected
             data = {
                 subid: train.subid,
                 subage: train.subage,

### 2020-10-30 experiments/mutual_exclusivity.js

@@ -21,7 +21,7 @@ var me = {
   end: function() {
     // Show the finish slide.
     showSlide("select");
-    setTimeout(function() { turk.submit(me) }, 500);
+    setTimeout(function() { downloadData(me.data) }, 500);
   },
 
 

### 2020-10-30 experiments/pragBat3.js

@@ -1,0 +1,715 @@
+// preload
+var preFruits = ["duck.png","car.png","car_me.png","bear.png","ball.png","t01.png", "t02.png", "t03.png", "t04.png", "t05.png", "t06.png", "t07.png", "t08.png", "t09.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t17.png", "carrot.png","bread.png","apple_me.png","kite.png", "t18.png","t19.png","t20.png","t21.png","t22.png","t23.png","t24.png","t25.png","t26.png","t27.png","t28.png","t29.png","t30.png","t31.png","t32.png","t33.png","t34.png","t35.png", "t36.png","t37.png","t38.png","t39.png","t44.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png", "bear_me.png"];
+//for critical trials and fillers
+var images = new Array();
+for (i = 0; i < preFruits.length; i++) {
+	images[i] = new Image();
+	images[i].src = "images/" + preFruits[i];
+}
+
+
+var preSounds = [
+         "Monkey_hello.mp3",
+    		 "Monkey_filler_inf_intro.mp3",
+"Monkey_filler_label.mp3",
+"Monkey_filler_more.mp3",
+"Monkey_filler_which.mp3",
+         "Monkey_inf_intro.mp3",
+         "Monkey_label.mp3",
+         "Monkey_me_choice.mp3",
+         "Monkey_pref_choice.mp3",
+         "Monkey_nov_choice.mp3",
+         "Monkey_npoint.mp3",
+         "Monkey_point_nothing.mp3",
+         "Monkey_point_old.mp3",
+         "Monkey_ppoint.mp3",
+         "Monkey_pref_choice.mp3",
+         "Monkey_train.mp3",
+         "Monkey_which.mp3",
+         "Bunny_hello.mp3",
+         "Bunny_inf_intro.mp3",
+         "Bunny_label.mp3",
+         "Bunny_me_choice.mp3",
+         "Bunny_pref_choice.mp3",
+         "Bunny_nov_choice.mp3",
+         "Bunny_npoint.mp3",
+         "Bunny_point_nothing.mp3",
+         "Bunny_point_old.mp3",
+         "Bunny_ppoint.mp3",
[…]

### 2020-10-30 experiments/rmts.js

@@ -1,0 +1,218 @@
+function showRmtsSample(a) {
+    $(".rmts_sample").show();
+    document.getElementById("rmts_sample").src = a;
+};
+
+function showMatchL(a) {
+    $(".match_l").show();
+    document.getElementById("match_l").src = a;
+};
+
+function showMatchR(a) {
+    $(".match_r").show();
+    document.getElementById("match_r").src = a;
+};
+
+
+// the actual experiment
+var rmts = {
+    trial: ["train", "train2", 1, 2, 3, 4, 5, 6],
+    sample: ["A","B","C","D"],
+    matchPos: ["left", "right", "right", "left", "right"],
+    data: [],
+
+
+
+    // end of the experiment
+    end: function () {
+        // Show the finish slide.
+        showSlide("select");
+        setTimeout(function () {
+            downloadData(rmts.data)
+        }, 500);
+    },
+
+
+    // unbind and shift variables between trials
+    newtrial: function () {
+
+        $(".match_l").css("border", "none")
+        $(".match_r").css("border", "none")
+        $(".rmts_sample").css("border", "none")
+
+        $(".match_l").unbind("click");
+        $(".match_r").unbind("click");
+        $(".rmts_sample").unbind("click");
+
+        showRmtsSample("images/empty.png");
+        showMatchL("images/empty.png");
+        showMatchR("images/empty.png");
+
+
+
+
+        $("#rmts_text").text("");
+
+
+        rmts.trial.shift();
+        rmts.sample.shift();
+
+        setTimeout(function () {
+            rmts.next()
+        }, 1100);
+
+    },
+
+    next: function () {
+
+        $(".selector").hide();
+
+        if (rmts.trial.length == 0) {
+            setTimeout(function () {
+                rmts.end()
+            }, 0);
+            return;
+        };
+
+        showSlide("rmts")
+
+        $("#rmts_sample").css({
+            top: "100px",
+            left: "400px",
+            opacity: 1
+        })
+
+        showRmtsSample("images/rmts/sample_" + rmts.sample[0] + ".png")
+
+        if (rmts.matchPos[0] == "left") {
+          showMatchL("images/rmts/match_" + rmts.sample[0] + ".png");
+          showMatchR("images/rmts/dis_" + rmts.sample[0] + ".png");
+        } else {
+          showMatchR("images/rmts/match_" + rmts.sample[0] + ".png");
+          showMatchL("images/rmts/dis_" + rmts.sample[0] + ".png")
[…]

### 2020-10-30 experiments/simple_inf.js

@@ -24,7 +24,7 @@ var simple_inf = {
       showSlide("select");
       $(".table_l").show();
       $(".table_r").show();
-      setTimeout(function() { turk.submit(simple_inf) }, 500);
+      setTimeout(function() { downloadData(simple_inf.data) }, 500);
     },
 
 
@@ -348,7 +348,7 @@ showInfAgent(simple_inf.agents[0],"straight")
           $("#inf_ob_l").animate({bottom: '140', queue:  true},300)
 
           $("#inf_ob_l").animate({bottom: '100', queue:  true},300)
-        }, 1500)
+        }, 00)
 
 
 
@@ -379,7 +379,7 @@ showInfAgent(simple_inf.agents[0],"straight")
 
           $("#inf_ob_r").animate({bottom: '100', queue:    true},300)
 
-        }, 1500)
+        }, 00)
 
 
           setTimeout(function() {

### 2020-11-01 experiments/card_sorting.js
first pass round 3 with rmts

@@ -87,7 +87,7 @@ var sort = {
 
         $("#sample").css({
             bottom: "100px",
-            left: "400px",
+            left: "50%",
             opacity: 1
         })
 
@@ -120,7 +120,7 @@ var sort = {
 
             $("#sample").animate({
                 bottom: "300px",
-                left: "100px",
+                left: "25%",
                 opacity: 0
             }, {
                 duration: 1000
@@ -182,7 +182,7 @@ var sort = {
 
             $("#sample").animate({
                 bottom: "300px",
-                left: "700px",
+                left: "75%",
                 opacity: 0
             }, {
                 duration: 1000

### 2020-11-01 experiments/rmts.js

@@ -17,8 +17,8 @@ function showMatchR(a) {
 // the actual experiment
 var rmts = {
     trial: ["train", "train2", 1, 2, 3, 4, 5, 6],
-    sample: ["A","B","C","D"],
-    matchPos: ["left", "right", "right", "left", "right"],
+    sample: ["train_1","train_2","A","B","C","D","E","F"],
+    matchPos: ["left", "right", "right", "left", "right","right", "left", "left"],
     data: [],
 
 
@@ -56,6 +56,7 @@ var rmts = {
 
         rmts.trial.shift();
         rmts.sample.shift();
+        rmts.matchPos.shift();
 
         setTimeout(function () {
             rmts.next()
@@ -78,7 +79,7 @@ var rmts = {
 
         $("#rmts_sample").css({
             top: "100px",
-            left: "400px",
+            left:"50%",
             opacity: 1
         })
 
@@ -92,7 +93,7 @@ var rmts = {
           showMatchL("images/rmts/dis_" + rmts.sample[0] + ".png")
         }
 
-        $("#rmts_text").text("Welches von den Bildern passt besser zu diesem hier [auf oberes Bild zeigen]");
+        $("#rmts_text").text("Welches von den Bildern passt besser zu diesem hier? Welches Bild is ähnlicher zu diesem hier?");
 
 
         $(".match_l").click(function () {
@@ -103,7 +104,7 @@ var rmts = {
 
             $("#rmts_sample").animate({
                 top: "300px",
-                left: "200px",
+                left:"35%",
                 opacity: 0
             }, {
                 duration: 1000
@@ -162,7 +163,7 @@ var rmts = {
 
             $("#rmts_sample").animate({
                 top: "300px",
-                left: "600px",
+                left: "65%",
                 opacity: 0
             }, {
                 duration: 1000

### 2020-11-01 experiments/ad_hoc.js
fix timing inf

@@ -138,7 +138,7 @@ eat2: function(event) {
 setTimeout(function() {
      sourceSound("sound/adhoc/"+adhoc.stimulus[0]+".mp3");
       playSound();
-}, 4000);
+}, 3000);
 
     } else {
 

### 2020-11-01 experiments/simple_inf.js

@@ -96,7 +96,7 @@ var simple_inf = {
         sourceSound("sound/simpinf/"+simple_inf.object[0]+"_which.mp3");
         playSound();
 
-      }, 3000)
+      }, 2000)
 
       choiceLeftInfObject("images/empty.png")
       choiceRightInfObject("images/empty.png")
@@ -335,7 +335,7 @@ var simple_inf = {
         sourceSound("sound/simpinf/"+simple_inf.object[0]+"_label.mp3");
         playSound();
 
-        pause("moveButton2",7000);
+        pause("moveButton2",5000);
 
         if (simple_inf.inf[0] == "left"){
 
@@ -345,60 +345,61 @@ showInfAgent(simple_inf.agents[0],"straight")
         setTimeout(function() {
           showInfAgent(simple_inf.agents[0],"point_l")
 
-          $("#inf_ob_l").animate({bottom: '140', queue:  true},300)
+          $("#inf_ob_l").animate({bottom: '20%', queue:  true},300)
 
-          $("#inf_ob_l").animate({bottom: '100', queue:  true},300)
-        }, 00)
+          $("#inf_ob_l").animate({bottom: '15%', queue:  true},300)
+        }, 000)
 
 
 
           setTimeout(function() {
             showInfAgent(simple_inf.agents[0],"look_l")
-          }, 4300)
+          },2000)
 
           setTimeout(function() {
             showInfAgent(simple_inf.agents[0],"point_l")
 
-            $("#inf_ob_l").animate({bottom: '140', queue:  false},300)
+            $("#inf_ob_l").animate({bottom: '20%', queue:  false},300)
 
-            $("#inf_ob_l").animate({bottom: '100', queue:  true},300)
+            $("#inf_ob_l").animate({bottom: '15%', queue:  true},300)
 
-          }, 5400)
+          }, 3500)
 
           setTimeout(function() {
             showInfAgent(simple_inf.agents[0],"look_l")
-          }, 7700)
+          }, 5500)
 
         } else {
 showInfAgent(simple_inf.agents[0],"straight")
-                  setTimeout(function() {
+
+        setTimeout(function() {
 
           showInfAgent(simple_inf.agents[0],"point_r")
 
-          $("#inf_ob_r").animate({bottom: '140', queue:  false},300)
+          $("#inf_ob_r").animate({bottom: '20%', queue:  true},300)
 
-          $("#inf_ob_r").animate({bottom: '100', queue:    true},300)
[…]

### 2020-11-02 analysis/data_round3.Rmd
add new stimuli for rmts and change timing

--- 2020-10-27 analysis/data_round2.Rmd
@@
 ```{r}
-files <- dir("~/Work/Local/PragBat/raw_data2/")
+files <- dir("~/Work/Local/PragBat/raw_data3/")
 
@@
 for (f in files) {
-  jf <- paste("~/Work/Local/PragBat/raw_data2/",f,sep="")
+  jf <- paste("~/Work/Local/PragBat/raw_data3/",f,sep="")
   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-  date <- str_sub(jf,34,str_length(jf)-11)
-  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date,
+  date <- str_sub(jf,-22,str_length(jf)-14)
+  id <- as_data_frame(jd) %>% mutate(test_date = date,
                                               trial = as.character(trial))
@@
 
-log <- read_xlsx("../../../../Cloud/PragBat/vpl_pragBat2.xlsx", sheet = 1)%>%
+log <- read_xlsx("../../../../Cloud/PragBat/vpl_pragBat3.xlsx", sheet = 1)%>%
   mutate(age = as.numeric(difftime(as.Date(as.character(test_day_1),format="%Y%m%d"), as.Date(as.character(birthday),format="%Y%m%d"), units = "days"))/365.25,
@@
 ```
-
-# Discourse continuity by category
-
-```{r}
-
-con_data <- task_data%>%
-  filter(task == "discourse_continuity")%>%
-  filter(!is.na(correct))
-
-pc1 <- con_data%>%
-  group_by(target1,subage, id) %>%
-  summarise(correct = mean(correct))
-
-pc2 <- pc1 %>%
-  group_by(target1,subage) %>%
-  tidyboot_mean(column = correct)
-
-ggplot()+
-  geom_hline(yintercept = 1/3, lty=2)+
-  geom_jitter( data = pc1, aes(x = subage, y = correct, col = target1), position = position_jitterdodge(jitter.width = .1,jitter.height = .025, dodge.width = .75 ), alpha = .3)+
-  geom_pointrange(data = pc2, aes(x = subage, y = mean, ymin = ci_lower, ymax = ci_upper, col = target1), position = position_dodge(width = .75), pch = 4)+
-  #facet_grid(~experiment)+
-  labs(x="Age",y="Proportion correct")+
-  theme_few()+
-  scale_color_colorblind(name = "Category")
-```
-
-# Data file Spin-off
-
-```{r}
-item_info <- data_frame(
-  task = c(rep("mutual_exclusivity",10),rep("simple_inf",10),rep("ad_hoc_implicature",10)),
-  trial = c(rep(1:10,3)), 
-  item = c(rep(c("carrot","garlic","eggplant","duck","horseshoe"),2),rep(c("bear","robot","rocket","truck","dino"),2), rep(c("box","chair","table","plate","house"),2))
-)
-
-retest_ids <- data %>%
-  filter(test_day == 2)%>%
-  group_by(id)%>%
-  summarise(n())%>%
-  pull(id)
-
-data %>%
-  filter(task == "mutual_exclusivity" |
-         task == "simple_inf" |
-         task == "ad_hoc_implicature",
-         id %in% retest_ids)%>%
-  select(-agent, -z_age, -z_trial)%>%
-  left_join(item_info)%>%
-  select(id, test_day, subage, age, age_month, task, trial, item, correct )%>%
-  mutate(c_age_month = age_month - min(age_month),
-         c_age = age - min(age))%>%
-  write_csv("../../../Spin-off/spin-off/data/data.csv")
-```

### 2020-11-02 experiments/ad_hoc.js

@@ -51,13 +51,13 @@ var adhoc = {
         };
 
        if (adhoc.infPos[0] == "left"){
-        var LeftFruit = adhoc.stimulus[0]+"_inf";
-        var RightFruit = adhoc.stimulus[0]+"_dis";
+        var leftFruit = adhoc.stimulus[0]+"_inf";
+        var rightFruit = adhoc.stimulus[0]+"_dis";
 
     } else  {
 
-        var LeftFruit = adhoc.stimulus[0]+"_dis";
-        var RightFruit = adhoc.stimulus[0]+"_inf";
+        var leftFruit = adhoc.stimulus[0]+"_dis";
+        var rightFruit = adhoc.stimulus[0]+"_inf";
     }
 
 
@@ -68,9 +68,9 @@ var adhoc = {
         subage: train.subage,
         task: "ad_hoc_implicature",
         trial: adhoc.trial[0],
-        agent: adhoc.agents[0],
-        leftObject: LeftFruit,
-        rightObject: RightFruit,
+        item: adhoc.stimulus[0],
+        leftObject: leftFruit,
+        rightObject: rightFruit,
         correct_location: adhoc.infPos[0],
         pick: pick,
         correct: correct

### 2020-11-02 experiments/card_sorting.js

@@ -162,7 +162,7 @@ var sort = {
                 subage: train.subage,
                 phase: sort.phase[0],
                 task: "card_sorting",
-                sample: sort.sample[0],
+                item: sort.sample[0],
                 trial: sort.trial[0],
                 leftObject: "blue_rabbit",
                 leftObject: "red_boat",
@@ -224,7 +224,7 @@ var sort = {
                 subage: train.subage,
                 phase: sort.phase[0],
                 task: "card_sorting",
-                sample: sort.sample[0],
+                item: sort.sample[0],
                 trial: sort.trial[0],
                 leftObject: "blue_rabbit",
                 leftObject: "red_boat",

### 2020-11-02 experiments/mutual_exclusivity.js

@@ -73,7 +73,7 @@ var me = {
         subage: train.subage,
         task: "mutual_exclusivity",
         trial: me.trial[0],
-        agent: me.agents[0],
+        item: me.agents[0],
         leftObject: LeftFruit,
         rightObject: RightFruit,
         correct_location: me.novelPos[0],

### 2020-11-02 experiments/pragBat3.js

@@ -109,17 +109,14 @@ var posAgents = ["Bunny","Monkey","Dog","Frog","Cat"]
 function downloadData(safe) {
 					var toSave = JSON.stringify(safe)
 
-					var date = new Date()
-					var day = date.getUTCDate()
-					var month = date.getUTCMonth()+1
-					var year = date.getUTCFullYear()
-					var hour = date.getHours()
-					var minute = date.getMinutes()
+				  var date = new Date().toISOString()
+					var day = date.substr(0, 10)
+					var time = date.substr(11, 8)
 
 					var hiddenElement = document.createElement('a');
 					hiddenElement.href = 'data:text/json;charset=utf-8,' + encodeURI(toSave);
 					hiddenElement.target = '_blank';
-					hiddenElement.download = year + '-' + month + '-' + day + '-' + hour + '-' + minute + '-' +  me.subid+'_'+data.task+'.json';
+					hiddenElement.download = train.subid + '-' + data.task  + '-' + day + '-' + time + '.json';
 					hiddenElement.click();
 		}
 

### 2020-11-02 experiments/rmts.js

@@ -48,11 +48,8 @@ var rmts = {
         showMatchL("images/empty.png");
         showMatchR("images/empty.png");
 
-
-
-
-        $("#rmts_text").text("");
-
+                $("#rmts_text").text("");
+                $("#rmts_text_bottom").text("");
 
         rmts.trial.shift();
         rmts.sample.shift();
@@ -60,7 +57,7 @@ var rmts = {
 
         setTimeout(function () {
             rmts.next()
-        }, 1100);
+        }, 500);
 
     },
 
@@ -85,6 +82,12 @@ var rmts = {
 
         showRmtsSample("images/rmts/sample_" + rmts.sample[0] + ".png")
 
+
+  showMatchL("images/empty.png");
+  showMatchR("images/empty.png");
+
+  setTimeout(function () {
+
         if (rmts.matchPos[0] == "left") {
           showMatchL("images/rmts/match_" + rmts.sample[0] + ".png");
           showMatchR("images/rmts/dis_" + rmts.sample[0] + ".png");
@@ -92,9 +95,15 @@ var rmts = {
           showMatchR("images/rmts/match_" + rmts.sample[0] + ".png");
           showMatchL("images/rmts/dis_" + rmts.sample[0] + ".png")
         }
+      }, 2000)
 
-        $("#rmts_text").text("Welches von den Bildern passt besser zu diesem hier? Welches Bild is ähnlicher zu diesem hier?");
 
+  $("#rmts_text").text("Schau mal, hier ist eine Karte?");
+  $("#rmts_text_bottom").text("");
+
+setTimeout(function () {
+    $("#rmts_text_bottom").text("Hier sind noch zwei Karten. Welche von den Karten passt besser zur Ersten? Welches Karte ist ähnlicher zur ersten Karte?");
+  }, 2000)
 
         $(".match_l").click(function () {
 
@@ -112,6 +121,7 @@ var rmts = {
 
             pause("moveButton", 1100)
 
+
             setTimeout(function () {
                 rmts.newtrial()
             }, 1100);
@@ -122,13 +132,11 @@ var rmts = {
 
               if (rmts.matchPos[0] == "left") {
                     var correct = 1
-                    var choice_location = "left"
                     var pick = "match_" + rmts.sample[0]
                     var leftObject = "match_" + rmts.sample[0];
                     var rightObject = "dis_" + rmts.sample[0];
                 } else {
                   var correct = 0
-                  var choice_location = "left"
[…]

### 2020-11-02 experiments/simple_inf.js

@@ -182,7 +182,7 @@ var simple_inf = {
             subage: train.subage,
             task: "simple_inf",
             trial: simple_inf.trial[0],
-            agent: simple_inf.agents[0],
+            item: simple_inf.object[0],
             leftObject: leftObject,
             rightObject: rightObject,
             switch: simple_inf.targetSwitch[0],
@@ -246,7 +246,7 @@ var simple_inf = {
             subage: train.subage,
             task: "simple_inf",
             trial: simple_inf.trial[0],
-            agent: simple_inf.agents[0],
+            item: simple_inf.object[0],
             leftObject: leftObject,
             rightObject: rightObject,
             switch: simple_inf.targetSwitch[0],

### 2020-11-02 experiments/rmts.js
adjust timing rmts

@@ -124,7 +124,7 @@ setTimeout(function () {
 
             setTimeout(function () {
                 rmts.newtrial()
-            }, 1100);
+            }, 1000);
 
 
             // Code correct: does name of chosen object contain the name of the correct object
@@ -180,7 +180,7 @@ setTimeout(function () {
 
             setTimeout(function () {
                 rmts.newtrial()
-            }, 1100);
+            }, 1000);
 
 
 

### 2020-11-25 analysis/data_round2.Rmd
add file for reli sensu rouder and haaf

@@
          z_trial = trial - mean(trial),
-         item = ifelse(task == "card_sorting", sample,leftObject) )%>%
-    select(id, test_day, subage,age, task,item, trial, correct, z_age, z_trial)
+         item = ifelse(task == "card_sorting", sample, ifelse(task == "discourse_continuity", target1, leftObject)))%>%
+    select(id, test_day, subage,age,age_month, task,item, trial, correct, z_age, z_trial)
 
@@
 item_info <- data_frame(
-  task = c(rep("mutual_exclusivity",10),rep("simple_inf",10),rep("ad_hoc_implicature",10)),
-  trial = c(rep(1:10,3)), 
-  item = c(rep(c("carrot","garlic","eggplant","duck","horseshoe"),2),rep(c("bear","robot","rocket","truck","dino"),2), rep(c("box","chair","table","plate","house"),2))
+  task = c(rep("mutual_exclusivity",10),rep("simple_inf",10),rep("ad_hoc_implicature",10),rep("discourse_continuity",10),rep("card_sorting",12)),
+  trial = c(rep(1:10,4),1:12), 
+  item2 = c(rep(c("carrot","garlic","eggplant","duck","horseshoe"),2),rep(c("bear","robot","rocket","truck","dino"),2), rep(c("box","chair","table","plate","house"),2),rep(NA,22))
 )
@@
 data %>%
-  filter(task == "mutual_exclusivity" |
-         task == "simple_inf" |
-         task == "ad_hoc_implicature",
-         id %in% retest_ids)%>%
-  select(-agent, -z_age, -z_trial)%>%
+  filter(id %in% retest_ids)%>%
+  select(-z_age, -z_trial)%>%
   left_join(item_info)%>%
+  mutate(item = ifelse(task == "mutual_exclusivity" | task == "simple_inf" | task == "ad_hoc_implicature", item2,item))%>%
   select(id, test_day, subage, age, age_month, task, trial, item, correct )%>%

### 2020-11-25 analysis/reliability.Rmd
add both data files from r1 and r2 to reliability analysis
add file for reli sensu rouder and haaf

@@
 library(brms)
+library(tidybayes)
+library(ggpubr)
 ```
@@
 
-data <- read_csv("../data/data.csv")
+data <- bind_rows(
+data_r1 <- read_csv("../data/data_r1.csv")%>%mutate(id = paste(id,"r1",sep = "_")) ,
+data_r2 <- read_csv("../data/data_r2.csv")%>%mutate(id = paste(id,"r2",sep = "_"))
+)%>%
+  filter(task !="training")
 
@@
 
-```{r}
-data%>%
-  group_by(subage)%>%
-  summarise(n= length(unique(id)))%>%
-  kable()
-
-```
-
 # Sample size with two test days
@@
 data %>%
-  group_by(subage,id)%>%
+  group_by(task,id)%>%
   summarise(testdays = length(unique(test_day)))%>%
   filter(testdays == 2)%>%
-  summarise(complete_retest_data = length(id))%>%
-  kable()
+  summarise(complete_retest_data = length(id))
+```
+
+# Simple correaltions
+
+```{r}
+reli <- data%>%
+  filter(task != "training")%>%
+  droplevels()%>%
+  group_by(id,task, test_day)%>%
+  summarise(mean = mean(correct))%>%
+  spread(test_day, mean)%>%
+  na.omit()%>%
+  rename("Day1" = `1`,
+         "Day2" = `2`)%>%
+  group_by(task)%>%
+  summarize(reli = cor.test(Day1,Day2)$estimate,
+            lci = cor.test(Day1,Day2)$conf.int[1],
+            uci = cor.test(Day1,Day2)$conf.int[2],
+            p = cor.test(Day1,Day2)$p.value)%>%
+  mutate_if(is.numeric, round, digits = 2)
+
+reli
 ```
@@
 ```{r}
-# data %>%
-#   group_by(id,test_day)%>%
-#   summarise(n())%>%
-#   arrange(id,test_day)
+p_rel_data <- data%>%
+  filter(task != "training")%>%
+  droplevels()%>%
+  group_by(id,task, test_day)%>%
+  summarise(mean = mean(correct))%>%
+  spread(test_day, mean)%>%
+  na.omit()%>%
+  rename("day1" = `1`,
+         "day2" = `2`)
 
-```
-
-```{r}
-# data%>%
-#   group_by(test_day,task)%>%
-#   summarise(n= length(unique(id)))
+ggplot(p_rel_data, aes(x = day1, y = day2))+
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(alpha = .5)+
+  facet_wrap( ~ task)+
+  stat_cor(method = "pearson",  aes(x = day1, y = day2), size = 2)+
+  theme_minimal()+
+  theme(aspect.ratio = 1)
 ```
@@
 
-## correlations
+## Combined model
 
 ```{r}
-# card sorting
-
-complete_data <- reli_data %>%
+complete_data <- data %>%
   group_by(subage,id)%>%
@@
          id %in% complete_data)%>%
-  mutate(test_day = ifelse(test_day == 1, "day1", "day2"))
+  mutate(test_day = ifelse(test_day == 1, "day1", "day2"),
+         z_trial = scale(trial))
 
-rel_model <- brm(correct ~ (test_day|task/id),
+rel_model <- brm(correct ~ (1|test_day) + (1| task) + (1|id),
                  data = reli_data, 
@@
           save_all_pars = F,
-          iter = 2000)
+          iter = 5000)
 
@@
 
-task <- as_tibble(ranef(rel_model)$task, rownames = "task")%>%
-  select(task,Estimate.Intercept, Estimate.test_dayday2)%>%
-  rename("Day1_int" = Estimate.Intercept,
-         "Day2_int" = Estimate.test_dayday2)%>%
-  mutate(task = str_replace(task, "card_sorting", "cardsorting"),
-         task = str_replace(task, "mutual_exclusivity", "mutualexclusivity"))
+draws1 <- rel_model %>%
+  spread_draws(b_Intercept, day[test_day,], task[`test_day:test_day`,],id[`test_day:test_day:id`,])
+#   separate(id, c("id","round"), sep = "_", extra = "merge")
+# 
+# draws2 <- rel_model %>%
+#   spread_draws(b_Intercept,`r_id:test_day`[`id:test_day`,])%>%
+#   separate(`id:test_day`, c("id","go"), sep = "_", extra = "merge")%>%
+#   separate(go, c("round","day"), sep = "_", extra = "merge")
+# 
+# draws3 <- rel_model %>%
+#   spread_draws(b_Intercept,`r_id:test_day:task`[`id:test_day:task`,])%>%
+#   separate(`id:test_day:task`, c("id","go"), sep = "_", extra = "merge")%>%
+#   separate(go, c("round","go"), sep = "_", extra = "merge")%>%
+#   separate(go, c("day","task"), sep = "_", extra = "merge")
+# 
+# draws <- draws1 %>%
+#   left_join(draws2) %>%
+#   left_join(draws3)
 
-id <- as_tibble(ranef(rel_model)$`task:id`, rownames = "id")%>%
-  select(id,Estimate.Intercept, Estimate.test_dayday2)%>%
-  rename("Day1" = Estimate.Intercept,
-         "Day2" = Estimate.test_dayday2)%>%
-  mutate(id = str_replace(id, "card_sorting", "cardsorting"),
-         id = str_replace(id, "mutual_exclusivity", "mutualexclusivity"),
-         Day1 = plogis(Day1),
-         Day2 = plogis(Day2))%>%
-  separate(id, c("task", "id"), sep = "_")
+p_re_est <- draws1%>%
+  mutate(perf = b_Intercept + r_id + r_test_day + r_task)%>%
+  group_by(id, test_day,task )%>%
+  median_qi(perf)%>%
+  mutate(perf = plogis(perf))
 
-left_join(id, task)%>%
-  mutate(est_1 = plogis(Day1_int + Day1),
-         est_2 = plogis(Day2_int + Day2))%>%
+saveRDS(p_re_est,"../saves/p_re_est.rds")
+
+p_data <- data %>%
+  filter(id %in% complete_data)%>%
+  group_by(task, test_day,id)%>%
+  summarise(mean = mean(correct))%>%
+  mutate(day = paste("day",test_day,sep = ""))
+
+ggplot()+
+  geom_point(data = p_re_est, aes (x = id, y = perf), alpha = .5)+
+  geom_point(data = p_data, aes (x = id, y = mean), alpha = .5, col = "firebrick")+
+  facet_grid(day~task)+
+  theme_minimal()
+
+p_cor <- p_re_est %>%
+  select(task, id, test_day,perf)%>%
+  spread(test_day, perf)%>%
   group_by(task)%>%
-  summarise(cor = cor(est_1, est_2))
+  summarise(cor = cor(day1, day2))%>%
+  left_join(reli)
+
+p_re_est %>%
+  select(task, id, test_day,perf)%>%
+  spread(test_day, perf)%>%
+  ggplot(aes(x = day1, y = day2))+
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(alpha = .5)+
+  geom_point(data = p_rel_data, aes(x = day1, y = day2), alpha = .5, col = "firebrick")+
+  facet_wrap( ~ task)+
+  stat_cor(method = "pearson",  aes(x = day1, y = day2), size = 2)+
+  theme_minimal()+
+  theme(aspect.ratio = 1)
+
+```
+# Ignore below 
+## Separate models
+
+```{r}
+reli_data_1 <- reli_data%>%
+  filter(test_day == "day1")
+
+rel_model_1 <- brm(correct ~ (z_trial|id/task),
+                 data = reli_data_1, 
+                 family = bernoulli(),
+                 control = list(adapt_delta = 0.9),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          save_all_pars = F,
+          iter = 5000)
+
+summary(rel_model_1)
+
+draws_rel1_1 <- rel_model_1 %>%
+  spread_draws(b_Intercept,r_id[id,])%>%
+  separate(id, c("id","round"), sep = "_", extra = "merge")
+
+draws_rel1_2 <- rel_model_1 %>%
+  spread_draws(b_Intercept,`r_id:task`[`id:task`,])%>%
+  separate(`id:task`, c("id","go"), sep = "_", extra = "merge")%>%
+  separate(go, c("round","task"), sep = "_", extra = "merge")
+
+draws_rel1 <- draws_rel1_1 %>%
+  left_join(draws_rel1_2)%>%
+  mutate(perf = b_Intercept + r_id + `r_id:task`)%>%
+  group_by(id,task )%>%
+  median_qi(plogis(perf))%>%
+  mutate(day1 = `plogis(perf)`)
 
@@
 
-## reliability
+```{r}
+reli_data_2 <- reli_data%>%
+  filter(test_day == "day2")
 
-```{r}
-# card sorting
-
-cor_model <- brm(correct ~ 1 + (task|id) + (task|item),
-                    data = data, family = bernoulli(),
-          control = list(adapt_delta = 0.99),
+rel_model_2 <- brm(correct ~ (z_trial|id/task),
+                 data = reli_data_2, 
+                 family = bernoulli(),
+                 control = list(adapt_delta = 0.9),
           sample_prior = F,
@@
           cores = 4,
-          save_all_pars = TRUE,
-          iter = 2000)
+          save_all_pars = F,
+          iter = 5000)
 
-summary(cor_model)
+summary(rel_model_2)
+
+draws_rel2_1 <- rel_model_2 %>%
+  spread_draws(b_Intercept,r_id[id,])%>%
+  separate(id, c("id","round"), sep = "_", extra = "merge")
+
+draws_rel2_2 <- rel_model_2 %>%
+  spread_draws(b_Intercept,`r_id:task`[`id:task`,])%>%
+  separate(`id:task`, c("id","go"), sep = "_", extra = "merge")%>%
+  separate(go, c("round","task"), sep = "_", extra = "merge")
+
+draws_rel2 <- draws_rel2_1 %>%
+  left_join(draws_rel2_2)%>%
+  mutate(perf = b_Intercept + r_id + `r_id:task`)%>%
+  group_by(id,task )%>%
+  median_qi(plogis(perf))%>%
+  mutate(day2 = `plogis(perf)`)
 
 ```
+
+```{r}
+p_cor %>%left_join(
+  draws_rel1 %>%
+  select(id, task, day1)%>%
+  left_join(draws_rel2%>%
+  select(id, task, day2))%>%
+    group_by(task)%>%
+    summarise(cor_2_models = cor(day1, day2))
+    )
+
+```
+
+```{r}
+draws_rel1 %>%
+  select(id, task, day1)%>%
+  left_join(draws_rel2%>%
+  select(id, task, day2))%>%
+  ggplot(aes(x = day1, y = day2))+
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(alpha = .5)+
+  geom_point(data = p_rel_data, aes(x = day1, y = day2), alpha = .5, col = "firebrick")+
+  facet_wrap( ~ task)+
+  stat_cor(method = "pearson",  aes(x = day1, y = day2), size = 2)+
+  theme_minimal()+
+  theme(aspect.ratio = 1)
+```

### 2020-11-25 analysis/reliability_rouder_haaf.Rmd
add file for reli sensu rouder and haaf

---
title: "Prag Bat reliability"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)

library(tidyverse)
library(brms)
library(tidybayes)
library(ggpubr)
```

# Loading data
```{r}

raw_data <- bind_rows(
read_csv("../data/data_r1.csv")%>%mutate(id = paste(id,"r1",sep = "_")) ,
read_csv("../data/data_r2.csv")%>%mutate(id = paste(id,"r2",sep = "_"))
)%>%
  filter(task !="training")

complete_ids <- raw_data %>%
  group_by(subage,id)%>%
  summarise(testdays = length(unique(test_day)))%>%
  filter(testdays == 2)%>%
  pull(id)

data <- raw_data%>%
  filter(task != "training", 
         id %in% complete_ids)%>%
  mutate(test_day = ifelse(test_day == 1, "day1", "day2"),
         z_trial = scale(trial))

```
# Descriütives

```{r}
data %>%
  group_by(task)%>%
  summarise(n = length(unique(id)))
```

# Simple correaltions

```{r}
data%>%
  droplevels()%>%
  group_by(id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  group_by(task)%>%
  summarize(reli = cor.test(day1,day2)$estimate,
            lci = cor.test(day1,day2)$conf.int[1],
            uci = cor.test(day1,day2)$conf.int[2],
            p = cor.test(day1,day2)$p.value)%>%
  mutate_if(is.numeric, round, digits = 2)

```
## Visualize simple correlations
```{r}
data%>%
  droplevels()%>%
  group_by(id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  ggplot( aes(x = day1, y = day2))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_count(alpha = .5)+
  facet_wrap( ~ task)+
  stat_cor(method = "pearson",  aes(x = day1, y = day2), size = 2)+
  theme_minimal()+
  theme(aspect.ratio = 1)
```

# Model by task sensu Rouder and Haaf

## Task: Mutual exclusivity
```{r}
me_data <- data %>%
  filter(task == "mutual_exclusivity")
```

### 2020-11-25 experiments/rmts.js
chnage wording for rmts intro

@@ -95,7 +95,7 @@ var rmts = {
           showMatchR("images/rmts/match_" + rmts.sample[0] + ".png");
           showMatchL("images/rmts/dis_" + rmts.sample[0] + ".png")
         }
-      }, 2000)
+      }, 1000)
 
 
   $("#rmts_text").text("Schau mal, hier ist eine Karte!");
@@ -103,7 +103,7 @@ var rmts = {
 
 setTimeout(function () {
     $("#rmts_text_bottom").text("Hier sind noch zwei Karten. Welche von den Karten passt besser zur Ersten? Welches Karte ist ähnlicher zur ersten Karte?");
-  }, 2000)
+  }, 1000)
 
         $(".match_l").click(function () {
 

### 2021-05-26 analysis/reliability.Rmd
update to run study

@@
 )%>%
-  filter(task !="training")
+  filter(task !="training")%>%
+  mutate(item = ifelse(task == "mutual_exclusivity" & item == "t22", "carrot", item),
+         item = ifelse(task == "mutual_exclusivity" & item == "t37", "duck", item),
+         item = ifelse(task == "mutual_exclusivity" & item == "t24", "duck", item))
 
+data %>%
+  filter(task == "mutual_exclusivity")%>%
+  group_by(subage,item)%>%
+  summarise(mean= mean(correct))
 ```

### 2021-10-14 analysis/data_round3.Rmd
add data file

--- 2020-03-26 analysis/data_round2.Rmd
@@
 library(reshape2)
-library(psych)
-library(readODS)
+library(ggpubr)
+#library(psych)
+#library(readODS)
 library(brms)
 library(psy)
+library(tidyboot)
+library(lubridate)
+library(BayesFactor)
+library(lavaan)
+library(lavaanPlot)
+library(blavaan)
 
@@
 ```{r}
-## die flogenden Zeilen kannst du überspringen. Weiter gehts in Zeile 68
-files <- dir("~/Work/PragBat/raw_data2/")
+files <- dir("~/Work/Cloud/PragBat/data_pragBat_3/")
+
+files <- files[!(files %in% "Readme.md")]
+
+files <- files[!(files %in% "Zoom_cm_ds_mOiwQPmhNRhg3z2Gkbp4KkeEaAgbCMsKgSXO4@h1k-gahL5FRePqGv_k0e14986e25507af5_.exe")]
 
@@
 for (f in files) {
-  jf <- paste("~/Work/PragBat/raw_data2/",f,sep="")
+  jf <- paste("~/Work/Cloud/PragBat/data_pragBat_3/",f,sep="")
   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-  date <- str_sub(jf,34,str_length(jf)-11)
-  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date,
+  date <- str_sub(jf,-22,str_length(jf)-14)
+  id <- as_data_frame(jd) %>% mutate(test_date = date,
                                               trial = as.character(trial))
@@
 task_data <- raw_data%>%
-  filter(trial != "training",
-         trial != "filler1",
-         trial != "filler2",
-         trial != "train",
-         trial != "train1",
-         trial != "train2",
-         task != "training")%>%
+  filter(!grepl("train",trial),
+         !grepl("fill",trial))%>%
   filter(phase == "shape" | is.na(phase))%>%
-  separate(subid, into = c("id","test_day"), sep="_")
+  mutate(subid = ifelse(subid == "265011", "260934", subid))
 
-log <- read_xlsx("../../pragBat2_vp_list.xlsx", sheet = 1)%>%
-  mutate(age = as.numeric(difftime(test_day_1, birthday, units = "days"))/365.25,
-         id = paste("VP",ID, sep = ""))%>%
-  select(id, age, status)
+log <- read_xlsx("../../../../Cloud/PragBat/vpl_pragBat3.xlsx", sheet = 1)%>%
+  mutate(age = as.numeric(difftime(as.Date(as.character(test_day),format="%Y%m%d"), as.Date(as.character(birthday),format="%Y%m%d"), units = "days"))/365.25,
+         age_num_month = lubridate::time_length(difftime(as.Date(as.character(test_day),format="%Y%m%d"), as.Date(as.character(birthday),format="%Y%m%d")), "month"),
+          age_month = round(age_num_month)/12,
+         id = ID,
+         subid = as.character(`Data ID`))%>%
+  select(id, subid, age, gender,age_month, status)
 
-data <- task_data %>%
-  left_join(log)%>%
+data <- log %>%
+  left_join(task_data)%>%
   filter(status == "keep")%>%
   mutate(check_age = ifelse(subage == substr(age,1,1),T,F),
-         subage = factor(as.numeric(substr(age,1,1))),
+         subage = as.numeric(substr(age,1,1)),
+          subage = ifelse(subage == 5, 4, subage),
+         subage = factor(subage),
          trial = as.numeric(trial))%>%
-  mutate(trial = ifelse(test_day == "2", 
-                        ifelse(task == "card_sorting", trial + 6, trial +5),
-                        trial),
-         z_age = age - mean(age),
-         z_trial = trial - mean(trial))%>%
-    select(id, test_day, subage,age, task, trial, agent, correct, z_age, z_trial)
+    select(id, subage,age,gender, task,item, trial, correct)
 
-write_csv(data, "../data/data_tom.csv")
+write_csv(data, "../data/data_r3.csv")
 
-data <- read_csv("../data/data_tom.csv")
+data <- read_csv("../data/data_r3.csv")
 
@@
 data%>%
-  group_by(subage)%>%
+  group_by(subage, gender)%>%
+  summarise(n= length(unique(id)))
+
+data%>%
   summarise(n= length(unique(id)))
@@
 ```{r}
-unique(data$id)
+data%>%
+  group_by(id)%>%
+  summarise(n= n())
 ```
@@
 ```{r}
-data %>%
-  group_by(subage,id)%>%
-  summarise(testdays = length(unique(test_day)))%>%
-  filter(testdays == 2)%>%
-  summarise(complete_retest_data = length(id))
-```
-
-```{r}
-raw_data%>%
-  filter(task == "simple_inf")%>%
-  separate(subid, into = c("id","test_day"), sep="_")%>%
-  filter(trial == "filler1" | trial == "filler2")%>%
+data%>%
   group_by(id)%>%
-  summarise(mean = mean(correct))
+  summarise(age = min(age))%>%
+  ggplot(aes(x = age, y = 0))+
+  geom_point(alpha = 0.25, size = 5)+
+  xlim(3,5)+
+  ylim(-0.1,0.1)+
+  theme_minimal()+
+  labs(x = "Age", y = "")+
+  theme(axis.text.y = element_blank())
 ```
@@
   group_by(subage,task)%>%
-  multi_boot_standard(col = "mean")%>%
-  mutate(chance = ifelse(task == "discourse_continuity", 1/3, 1/2))
+  tidyboot_mean(column = mean)%>%
+  mutate(chance = 1/2)
 
@@
   geom_smooth(data = p1, aes(x = age, y = mean), method = "lm", col = "black", size = 1)+
-  geom_jitter(data = p1, aes(x = age, y = mean), alpha = .5, width = .05, height = .01)+
+  geom_point(data = p1, aes(x = age, y = mean), alpha = .5, width = .05, height = .01)+
   geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = subage))+
@@
   ylim(-0.05, 1.05)+
+  xlim(3,5)+
   theme_few()+
@@
 ```{r}
-p3 <- data%>%
-  filter(task != "training")%>%
-  group_by(id,task, test_day)%>%
-  summarise(mean = mean(correct))%>%
-  spread(test_day, mean)%>%
-  rename("Day1" = `1`,
-         "Day2" = `2`)%>%
-  na.omit()
+x <- ttestBF(p1%>%filter(task == "match_to_sample")%>%pull(mean), mu = 0.5)
 
-ggplot(p3, aes(x = Day1, y = Day2))+
-  geom_jitter(width = .05, height = .05, alpha = .5)+
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
-  geom_smooth(method = "lm", col = "#af6300", se = T)+
-  facet_grid(~task)+
-  coord_fixed()+
-  xlim(-.1,1.1)+
-  ylim(-.1,1.1)+
-  theme_few()
-
+extractBF(x)
 ```
@@
 ```{r}
-reli <- data%>%
-  filter(task != "training")%>%
-  droplevels()%>%
-  group_by(id,task, test_day)%>%
+data%>%
+  filter(task !="training")%>%
+  mutate(test_half = ifelse( trial %% 2, "even", "odd"))%>%
+  group_by(id, task, test_half)%>%
   summarise(mean = mean(correct))%>%
-  spread(test_day, mean)%>%
-  na.omit()%>%
-  rename("Day1" = `1`,
-         "Day2" = `2`)%>%
+  pivot_wider(names_from = test_half, values_from = mean)%>%
   group_by(task)%>%
-  summarize(reli = cor.test(Day1,Day2)$estimate,
-            lci = cor.test(Day1,Day2)$conf.int[1],
-            uci = cor.test(Day1,Day2)$conf.int[2],
-            p = cor.test(Day1,Day2)$p.value)%>%
-  mutate_if(is.numeric, round, digits = 2)
+  summarise(cor = cor (even, odd))
 ```
@@
   select(-id)%>%
-  corrr::correlate(diagonal = reli$reli)%>%
-  gather(task, cor, -rowname)%>%
+  corrr::correlate()%>%
+  gather(task, cor, -term)%>%
   mutate(cor = replace(cor, duplicated(cor), NA))%>%
@@
 
-ggplot(cor, aes(x = rowname, y = task, fill = cor))+
+ggplot(cor, aes(x = term, y = task, fill = cor))+
   geom_tile(color = "white")+
@@
   theme(legend.justification = c(1, 0),
-        legend.position = c(0.55, 0.7),
+        legend.position = c(0.55, 0.75),
         legend.direction = "horizontal",
-        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
+        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
+        legend.background = element_blank())+
   guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
@@
 ```
+
+```{r}
+cp <- data%>%
+  group_by(id,age, subage,task)%>%
+  filter(task != "training")%>%
+  summarise(mean_task1 = mean(correct))%>%
+  left_join(p1 %>% rename(task2 = task, mean_task2 = mean),by = c("id","age","subage"))%>%
+  filter(task != task2)%>%
+  rowwise()%>%
+  mutate(ex = paste(sort(c(task, task2)), collapse = " - "))%>%
+  distinct(ex, .keep_all = T)
+
+ggplot(cp, aes(x = mean_task1, y = mean_task2))+
+  geom_count( alpha = .25)+
+  geom_abline(intercept = 0 , slope = 1, lty = 2, alpha = .4)+
+  facet_grid(task2~task)+
+  theme_few()+
+  geom_smooth(method = lm)+
+  stat_cor(method = "pearson", size = 3, r.accuracy = 0.01, cor.coef.name = "r")+
+  scale_x_continuous(breaks = c(0,1))+
+  scale_y_continuous(breaks = c(0,1))
+
+```
+# Models 
+```{r}
+data_card <- data%>%
+  filter(task == "card_sorting")%>%
+  mutate(z_age = scale(age),
+         z_trial = scale(trial))
+
+m_card <- brm(correct ~ z_age + z_trial + (z_trial|id),
+                    data = data_card, family = bernoulli(),
+          control = list(adapt_delta = 0.8),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          iter = 2000)
+
+data_me<- data%>%
+  filter(task == "mutual_exclusivity")%>%
+  mutate(z_age = scale(age),
+         z_trial = scale(trial))
+
+m_card <- brm(correct ~ z_age + z_trial + (z_trial|id),
+                    data = data_card, family = bernoulli(),
+          control = list(adapt_delta = 0.8),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          iter = 2000)
+
+```
+
+# SEM playground
+
+```{r}
+library(lavaan)
+library(OpenMx)
+library(tidySEM)
+library(blavaan)
+```
+
+```{r}
+semd <- p1%>%
+  pivot_wider(names_from = "task", values_from = "mean")%>%
+  ungroup()%>%
+  filter(!is.na(ad_hoc_implicature),
+         !is.na(card_sorting),
+         !is.na(match_to_sample),
+         !is.na(mutual_exclusivity),
+         !is.na(simple_inf))%>%
+  mutate(ad_hoc_implicature = scale(ad_hoc_implicature),
+         card_sorting = scale(card_sorting),
+         match_to_sample = scale(match_to_sample),
+         mutual_exclusivity = scale(mutual_exclusivity),
+         simple_inf = scale(simple_inf))
+
+model <- 'prag  =~ ad_hoc_implicature + mutual_exclusivity + simple_inf
+          card  =~ card_sorting
+          match =~ match_to_sample'
+
+model2 <- 'fac  =~ ad_hoc_implicature + mutual_exclusivity + simple_inf + card_sorting + match_to_sample'
+
+model3 <- 'ad  =~ ad_hoc_implicature
+           simp  =~ simple_inf
+           mut  =~ mutual_exclusivity
+           card  =~ card_sorting
+           match =~ match_to_sample'
+```
+
+```{r}
+ffit <- cfa(model, data = semd)
+
+ffit2 <- cfa(model2, data = semd)
+
+ffit3 <- cfa(model3, data = semd)
+
+summary(ffit, fit.measures=TRUE, standardized = TRUE)
+
+lavTestLRT(ffit,ffit2 )
+```
+
+```{r}
+lay <- get_layout("card", "", "prag","","match",
+                  "card_sorting", "ad_hoc_implicature", "mutual_exclusivity", "simple_inf", "match_to_sample", rows = 2)
+
+graph_sem(model = ffit, layout = lay)
+```
+
+```{r}
+fit <- bcfa(model, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 3, burnin = 2000, sample = 2000)
+
+fit2 <- bcfa(model2, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 3, burnin = 2000, sample = 2000)
+
+fit3 <- bcfa(model3, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 3, burnin = 2000, sample = 2000)
+
+blavCompare(fit, fit2)
+
+blavCompare(fit, fit3)
+
+blavInspect(fit, "lvs")
+```
+
+```{r}
+summary(fit, fit.measures=TRUE, standardized = TRUE)
+```

### 2021-10-21 analysis/data_round3.Rmd
add data r3

@@
   geom_point(data = p1, aes(x = age, y = mean), alpha = .5, width = .05, height = .01)+
-  geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = subage))+
+  geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = factor(subage)))+
   facet_wrap(~task)+
@@
 
-summary(ffit, fit.measures=TRUE, standardized = TRUE)
+summary(ffit, fit.measures=TRUE, standardized = TRUE, rsquare = T)
 

### 2022-01-21 analysis/data_round3.Rmd
add data round 3

@@
   filter(phase == "shape" | is.na(phase))%>%
-  mutate(subid = ifelse(subid == "265011", "260934", subid))
+  mutate(subid = ifelse(subid == "265011", "260934", subid),
+         item = ifelse(task == "mutual_exclusivity",
+                       ifelse(correct_location == "left", rightObject, leftObject), item))
 
@@
          trial = as.numeric(trial))%>%
-    select(id, subage,age,gender, task,item, trial, correct)
+    select(id, subage,age,age_month,gender, task,item, trial, correct)
 
@@
 data <- read_csv("../data/data_r3.csv")
+
+# data for RSA model 
+data %>%
+  filter(task != "card_sorting",
+         task != "match_to_sample")%>%
+  select(id, subage, age, age_month, task, trial, item, correct)%>%
+  mutate(c_age_month = age_month - min(age_month),
+         c_age = age - min(age))%>%
+  write_json("../../../Spin-off/spin-off/data/data_r3.json")
 

### 2022-01-21 analysis/summary.Rmd
add data round 3

--- 2020-10-28 analysis/summary.Rmd
@@
 library(lavaan)
+library(blavaan)
+library(tidySEM)
+library(semPlot)
 ```
@@
 data <- bind_rows(
-  read_csv("../data/data_r1.csv") %>%filter(task != "training") %>%mutate(round = "R1"),
-  read_csv("../data/data_r2.csv") %>%mutate(round = "R2")
+  read_csv("../data/data_r1.csv") %>%filter(task != "training") %>%mutate(study = "S1"),
+  read_csv("../data/data_r2.csv") %>%mutate(study = "S2")
   ) %>%
-  mutate(round = factor(round),
-         id = paste(round, id, sep = "_"))
+  mutate(study = factor(study),
+         id = paste(study, id, sep = "_"))
 
@@
 
-# Sample size
+# Study 1 and 2
+
+## Sample size
 
@@
 data %>%
-  group_by(subage,id,round) %>%
+  group_by(subage,id,study) %>%
   summarise(testdays = length(unique(test_day))) %>%
-  group_by(round,subage) %>%
+  group_by(study,subage) %>%
   summarise(n = length(unique(id)),
@@
 
-# Results by Task
+## Results by Task
 
@@
 
-Round 1 included the following tasks:
+Study 1 included the following tasks:
 
@@
 
-Round 2 included the following tasks:
+Study 2 included the following tasks:
 
@@
 p1 <- data %>%
-  group_by(round, id,age, subage,task) %>%
+  group_by(study, id,age, subage,task) %>%
   filter(task != "training") %>%
@@
 p2 <- p1 %>%
-  group_by(round,subage,task) %>%
+  group_by(study,subage,task) %>%
   tidyboot_mean(column = mean) %>%
@@
   geom_hline(data = p2, aes(yintercept = chance), lty = 2)+
-  geom_smooth(data = p1, aes(x = age, y = mean, lty = round), method = "lm", col = "black", size = 1)+
-  geom_jitter(data = p1, aes(x = age, y = mean, pch = round), alpha = .5, width = .05, height = .01)+
-  geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = factor(subage), pch = round), position = position_dodge(width = .5))+
+  geom_smooth(data = p1, aes(x = age, y = mean, lty = study), method = "lm", col = "black", size = 1)+
+  geom_jitter(data = p1, aes(x = age, y = mean, pch = study), alpha = .5, width = .05, height = .01)+
+  geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = factor(subage), pch = study), position = position_dodge(width = .5))+
   facet_wrap(~task)+
@@
 
-# Reliability
+## Reliability
 
@@
   droplevels() %>%
-  group_by(round,id,task, test_day) %>%
+  group_by(study,id,task, test_day) %>%
   summarise(mean = mean(correct)) %>%
@@
 reli <- wide_data %>%
-  group_by(round, task) %>%
+  group_by(study, task) %>%
   summarize(reli = cor.test(Day1,Day2)$estimate,
@@
 ```
-Explore consolidating across rounds.
+Explore consolidating across studies.
 
@@
 
-# Correlations between tasks
+## Correlations between tasks
 
@@
 cor_r1 <- data %>%
-  filter(round == "R1") %>%
+  filter(study == "S1") %>%
   droplevels() %>%
@@
   corrr::correlate(diagonal = reli %>%
-                     filter(round == "R1") %>%
+                     filter(study == "S1") %>%
                      pull(reli)) %>%
-  gather(task, cor, -rowname) %>%
+  gather(task, cor, -term) %>%
   mutate(cor = replace(cor, duplicated(cor), NA)) %>%
@@
   na.omit() %>%
-  mutate(round = "R1")
+  mutate(study = "S1")
 
 cor_r2 <- data%>%
-  filter(round == "R2") %>%
+  filter(study == "S2") %>%
   droplevels() %>%
@@
   select(-id) %>%
-  corrr::correlate(diagonal = reli%>%filter(round == "R2") %>%pull(reli)) %>%
-  gather(task, cor, -rowname) %>%
+  corrr::correlate(diagonal = reli%>%filter(study == "S2") %>%pull(reli)) %>%
+  gather(task, cor, -term) %>%
   mutate(cor = replace(cor, duplicated(cor), NA)) %>%
@@
   na.omit() %>%
-  mutate(round = "R2")
+  mutate(study = "S2")
 
@@
 ggarrange(
-ggplot(cor_r1, aes(x = rowname, y = task, fill = cor))+
+ggplot(cor_r1, aes(x = term, y = task, fill = cor))+
   geom_tile(color = "white")+
@@
   geom_text(aes(label = cor), color = "black", size = 3) +
-  ggtitle("Round 1")+
+  ggtitle("Study 1")+
   theme(
@@
 
-ggplot(cor_r2, aes(x = rowname, y = task, fill = cor))+
+ggplot(cor_r2, aes(x = term, y = task, fill = cor))+
   geom_tile(color = "white")+
@@
   geom_text(aes(label = cor), color = "black", size = 3) +
-  ggtitle("Round 2")+
+  ggtitle("Study 2")+
   theme(
@@
 
-# Factor analysis
+# Study 3
 
-## EFA
+The goal of Study 3 was to select some tasks from Study 1 and 2 and collect data from a larger sample to look more closely at the relations between tasks. We aimed for 120 children (60 3yo, 60 4yo).
 
-Average across task days.
+Study 3 included the following tasks:
 
+* Simple informativeness (same setup and stimuli as in Frank & Goodman, 2014, same as S2)
+* Ad-hoc implicature (same stimuli as Yoon & Frank, 2019, same as S2)
+* Mutual exclusivity (as in SPIN, with fewer items, same as S1 and S2)
+* Card sorting (DCCS sensu Zelazo, 2006, same as S1 and S2)
+* Match to sample (setup and stimuli from Christie & Gentner, 2013)
+
+In contrast to Study 1 and 2, we tested participants only once, with 5 or 6 trials per task.
+
+## Sample size
 ```{r}
-efa_data <- filter(data, round == "R1") %>%
-  group_by(id, task) %>% 
-  summarise(correct = mean(correct)) %>%
-  pivot_wider(names_from = task, values_from = correct)
+data3 <- read_csv("../data/data_r3.csv")
 ```
@@
 ```{r}
-fa_data <- as.matrix(dplyr::select(ungroup(efa_data), -1))
-f1 <- factanal(fa_data, 1)
-f1
+data3%>%
+  group_by(subage)%>%
+  summarise(n= length(unique(id)))%>%
+  kable()
+```
+
+## Results by task 
+```{r}
+p31 <- data3%>%
+  group_by(id,age, subage,task)%>%
+  filter(task != "training")%>%
+  summarise(mean = mean(correct))
+
+p32 <- p31 %>%
+  group_by(subage,task)%>%
+  tidyboot_mean(column = mean)%>%
+  mutate(chance = 1/2)
+
+ggplot()+
+  geom_hline(data = p32, aes(yintercept = chance), lty = 2)+
+  geom_smooth(data = p31, aes(x = age, y = mean), method = "lm", col = "black", size = 1)+
+  geom_point(data = p31, aes(x = age, y = mean), alpha = .5, width = .05, height = .01)+
+  geom_pointrange(data = p32, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = factor(subage)))+
+  facet_wrap(~task)+
+  labs(x = "Age Group", y = "Proportion Correct")+
+  scale_color_ptol(name = "Age")+
+  ylim(-0.05, 1.05)+
+  xlim(3,5)+
+  theme_few()+
+  theme(legend.position = c(.85,.2), legend.direction = "horizontal")
+```
+Results replicate the previous studies.
+The newly added match-to-sample task did not work too well in that we have no solid group-level performance above chance for the two age groups and no age effect.
+Reliability for the task is also unknown as it was not part of the previous studies.
+
+## Correlations between tasks
+
+```{r}
+cor3 <- data3%>%
+  filter(task != "training")%>%
+  droplevels()%>%
+  group_by(id,task)%>%
+  summarise(mean = mean(correct))%>%
+  spread(task, mean)%>%
+  ungroup()%>%
+  select(-id)%>%
+  corrr::correlate()%>%
+  gather(task, cor, -term)%>%
+  mutate(cor = replace(cor, duplicated(cor), NA))%>%
+  mutate_if(is.numeric, round, digits = 2)%>%
+  na.omit()
+
+ggplot(cor3, aes(x = term, y = task, fill = cor))+
+  geom_tile(color = "white")+
+  labs(x = "", y = "")+
+  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white", 
+   midpoint = 0, limit = c(-1,1), space = "Lab", 
+   name="Correlation") +
+   coord_fixed()+
+  theme_few(base_size = 12)+
+  geom_text(aes(label = cor), color = "black", size = 3) +
+  theme(legend.justification = c(1, 0),
+        legend.position = c(0.55, 0.75),
+        legend.direction = "horizontal",
+        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
+        legend.background = element_blank())+
+  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
+                title.position = "top", title.hjust = 0.5))
+```
+
+Correlations between tasks are lower compared to Study 1 and 2.
+This was expected since we only have half the number of trials in this study (Study 1 and 2 both had two test days, here we only had 1).
+Nevertheless, the overall pattern seems similar to study 2.
+
+## Factor analysis
+
+Given the low number of tasks, exploratory factor analysis does not make much sense because a one factor model will always be favored.
+Instead, I fit the CFA model that I thought best represents our theoretical view of the data.
+That is, a pragmatics factor with the three tasks as indicators, which is then correlated with the match-to-sample and the card sorting task:
+
+`prag  =~ ad_hoc_implicature + mutual_exclusivity + simple_inf`
+
+`card  =~ card_sorting`
+
+`match =~ match_to_sample`
+
+Figure below shows the result from the frequentist model.
+A Bayesian version produces essentially the same results (but takes forever to run and is more difficult to visualize).
+All fit indices for the frequentist and the Bayesian model show a good fit (see below for frequentist model - hints for interpretation: https://easystats.github.io/effectsize/reference/interpret_gfi.html).
+
+```{r}
+semd <- p31%>%
+  pivot_wider(names_from = "task", values_from = "mean")%>%
+  ungroup()%>%
+  filter(!is.na(ad_hoc_implicature),
+         !is.na(card_sorting),
+         !is.na(match_to_sample),
+         !is.na(mutual_exclusivity),
+         !is.na(simple_inf))%>%
+  mutate(ad_hoc_implicature = scale(ad_hoc_implicature),
+         card_sorting = scale(card_sorting),
+         match_to_sample = scale(match_to_sample),
+         mutual_exclusivity = scale(mutual_exclusivity),
+         simple_inf = scale(simple_inf))
+
+model <- 'prag  =~ ad_hoc_implicature + mutual_exclusivity + simple_inf
+          card  =~ card_sorting
+          match =~ match_to_sample'
+
+model2 <- 'fac  =~ ad_hoc_implicature + mutual_exclusivity + simple_inf + card_sorting + match_to_sample'
+
+model3 <- 'ad  =~ ad_hoc_implicature
+           simp  =~ simple_inf
+           mut  =~ mutual_exclusivity
+           card  =~ card_sorting
+           match =~ match_to_sample'
 ```
@@
 ```{r}
-f2 <- factanal(fa_data, 2)
-f2
-```
-`
+ffit <- cfa(model, data = semd)
 
-## CFA
-[https://lavaan.ugent.be/tutorial/cfa.html]()
-
-Data
-
-```{r}
-lavaan_data <- filter(data, round == "R1", test_day == 1) %>%
-  group_by(id, task) %>%
-  summarise(correct = mean(correct)) %>%
-  pivot_wider(names_from = task, values_from = correct)
+# ffit2 <- cfa(model2, data = semd)
+# 
+# ffit3 <- cfa(model3, data = semd)
 ```
@@
 ```{r}
-model1 <- 'pragmatic  =~ informativeness + novelty + preference + mutual_exclusivity 
-          ef =~ card_sorting'
+#summary(ffit, fit.measures=TRUE, standardized = TRUE, rsquare = T)
 
-fit <- cfa(model1, data=lavaan_data)
-summary(fit)
+fitMeasures(ffit, c("chisq", "df", "pvalue", "cfi", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))%>%
+  as_tibble(rownames = "index")%>%
+  kable()
 ```
+
+```{r}
+cfa_scores <- lavPredict(ffit)%>%
+  as_tibble(rownames = "id")%>%
+  mutate(id = paste("VP",id, sep = ""))
+```
+
+Graph below shows standardized model coefficients from frequentist model. As you can see the pragmatics factor is related to the card sorting task but not to the match-to-sample task.
+
+```{r}
+lay <- get_layout("card", "", "prag","","match",
+                  "card_sorting", "ad_hoc_implicature", "mutual_exclusivity", "simple_inf", "match_to_sample", rows = 2)
+
+graph_sem(model = ffit, layout = lay)
+```
+
+In a Bayesian model comparison via WAIC the model above does better compared to two (not very strong) alternative models: a `single factor model` and a `one factor per task model`.
+
+```{r}
+# fit <- bcfa(model, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 3, burnin = 3000, sample = 3000)
+# 
+# fit2 <- bcfa(model2, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 3, burnin = 3000, sample = 3000)
+# 
+# fit3 <- bcfa(model3, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 3, burnin = 3000, sample = 3000)
+```
+
+```{r}
+# blavCompare(fit, fit2)
+# 
+# blavCompare(fit, fit3)
+# 
+# blavInspect(fit, "lvs")
+```
+
+```{r}
+# summary(fit, ci = T)
+# 
+# summary(fit, fit.measures=TRUE, standardized = TRUE, rsquare = T)
+# 
+# semPaths(fit, whatLabels="std", intercepts=FALSE, style="lisrel",
+#                        nCharNodes=0, 
+#                        nCharEdges=0,
+#                        curveAdjacent = TRUE,title=TRUE, layout = lay,node.width = 2)
+```
+
+## RSA model
+
+One of the reasons we picked the three pragmatics tasks we did was that we can all model them via RSA.
+That is, we can estimate a value for $\alpha$ for each participant based on the data from those three tasks.
+To account for different difficulties, there is an additional scale parameter that adjusts $\alpha$ for each task.
+In the end, we can treat the participant specific $\alpha$ estimate like a factor score and correlate it with the other two tasks.
+The results are quite similar to the CFA model above.
+
+```{r}
+rsa_est <- read.csv("../../../Spin-off/spin-off/data/rsa_est.csv")%>%
+  mutate(mode = scale(mode))
+```
+
+```{r}
+p31%>%
+  filter(task == "card_sorting" | task == "match_to_sample")%>%
+  group_by(task)%>%
+  mutate(mean = scale(mean))%>%
+  ungroup()%>%
+  left_join(rsa_est)%>%
+  ggplot(aes(x = mean, y = mode))+
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = .75)+
+  geom_point()+
+  geom_smooth(method = "lm", col= "firebrick")+
+  stat_cor()+
+  labs(x = "mean task performance (scaled)", y = "alpha (RSA) estimate (scaled)")+
+  facet_grid(~task)+
+  theme_minimal()
+```
+
+## Things to discuss
+
+* should we take out the match-to-sample task (unknown reliability, unsure if it "worked") and instead include the data from study 2 in the CFA/RSA model?
+* RSA or CFA or both?

### 2022-02-08 analysis/summary.Rmd
add model weights formula

@@
 ```
+
 Results replicate the previous studies.
@@
 ```{r}
-# fit <- bcfa(model, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 3, burnin = 3000, sample = 3000)
-# 
-# fit2 <- bcfa(model2, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 3, burnin = 3000, sample = 3000)
-# 
-# fit3 <- bcfa(model3, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 3, burnin = 3000, sample = 3000)
+fit <- bcfa(model, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
+
+saveRDS(fit, "../saves/bcfa_prag")
+
+fit2 <- bcfa(model2, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
+
+saveRDS(fit2, "../saves/bcfa_single")
+
+fit3 <- bcfa(model3, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
+
+saveRDS(fit3, "../saves/bcfa_separate")
 ```
@@
 ```{r}
-# blavCompare(fit, fit2)
-# 
-# blavCompare(fit, fit3)
-# 
-# blavInspect(fit, "lvs")
+blavCompare(fit, fit2)
+
+blavCompare(fit, fit3)
+
+blavInspect(fit, "lvs")
+```
+
+```{r}
+#model weights
+w1 <- exp(-0.5*0)/(exp(-0.5*0)+exp(-0.5*6.7)+exp(-0.5*7.1)+exp(-0.5*8.9))
 ```

### 2022-02-08 analysis/summary.Rmd
add bfcs models

@@
 library(blavaan)
-library(tidySEM)
-library(semPlot)
+#library(tidySEM)
+#library(semPlot)
 ```
@@
 ```{r}
-fit <- bcfa(model, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
+# fit <- bcfa(model, data = semd, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
+# saveRDS(fit, "../saves/bcfa_prag.rds")
+fit <- readRDS("../saves/bcfa_prag.rds")
 
-saveRDS(fit, "../saves/bcfa_prag")
+# fit2 <- bcfa(model2, data = semd, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
+# saveRDS(fit2, "../saves/bcfa_single.rds")
+fit2 <- readRDS("../saves/bcfa_single.rds")
 
-fit2 <- bcfa(model2, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
-
-saveRDS(fit2, "../saves/bcfa_single")
-
-fit3 <- bcfa(model3, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
-
-saveRDS(fit3, "../saves/bcfa_separate")
+# fit3 <- bcfa(model3, data = semd, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
+# saveRDS(fit3, "../saves/bcfa_separate.rds")
+fit3 <- readRDS("../saves/bcfa_separate.rds")
 ```
@@
 ```{r}
-blavCompare(fit, fit2)
+# blavCompare(fit, fit2)
+# 
+# blavCompare(fit, fit3)
 
-blavCompare(fit, fit3)
-
-blavInspect(fit, "lvs")
 ```
@@
 ```{r}
-#model weights
-w1 <- exp(-0.5*0)/(exp(-0.5*0)+exp(-0.5*6.7)+exp(-0.5*7.1)+exp(-0.5*8.9))
+# fit_waic <- fitmeasures(fit)%>%as_tibble(rownames = "index")%>%filter(index == "waic")%>%pull(value)
+# fit2_waic <- fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%filter(index == "waic")%>%pull(value)
+# fit3_waic <- fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%filter(index == "waic")%>%pull(value)
+# 
+# fit_se_waic <- fitmeasures(fit)%>%as_tibble(rownames = "index")%>%filter(index == "se_waic")%>%pull(value)
+# fit2_se_waic <- fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%filter(index == "se_waic")%>%pull(value)
+# fit3_se_waic <- fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%filter(index == "se_waic")%>%pull(value)
+# 
+# fit_looic <- fitmeasures(fit)%>%as_tibble(rownames = "index")%>%filter(index == "looic")%>%pull(value)
+# fit2_looic <- fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%filter(index == "looic")%>%pull(value)
+# fit3_looic <- fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%filter(index == "looic")%>%pull(value)
+# 
+# fit_se_looic <- fitmeasures(fit)%>%as_tibble(rownames = "index")%>%filter(index == "se_loo")%>%pull(value)
+# fit2_se_looic <- fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%filter(index == "se_loo")%>%pull(value)
+# fit3_se_looic <- fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%filter(index == "se_loo")%>%pull(value)
+# 
+# #model weights
+# ## waic
+# w1 <- exp(-0.5*(fit_waic-fit_waic))/(exp(-0.5*(fit_waic-fit_waic))+exp(-0.5*(fit2_waic-fit_waic))+exp(-0.5*7.1)+exp(-0.5*(fit3_waic-fit_waic)))
+# w2 <- exp(-0.5*(fit2_waic-fit_waic))/(exp(-0.5*(fit_waic-fit_waic))+exp(-0.5*(fit2_waic-fit_waic))+exp(-0.5*7.1)+exp(-0.5*(fit3_waic-fit_waic)))
+# w3 <- exp(-0.5*(fit3_waic-fit_waic))/(exp(-0.5*(fit_waic-fit_waic))+exp(-0.5*(fit2_waic-fit_waic))+exp(-0.5*7.1)+exp(-0.5*(fit3_waic-fit_waic)))
+# ## looic
+# l1 <- exp(-0.5*(fit_looic-fit_looic))/(exp(-0.5*(fit_looic-fit_looic))+exp(-0.5*(fit2_looic-fit_looic))+exp(-0.5*7.1)+exp(-0.5*(fit3_looic-fit_waic)))
+# l2 <- exp(-0.5*(fit2_looic-fit_looic))/(exp(-0.5*(fit_looic-fit_looic))+exp(-0.5*(fit2_looic-fit_looic))+exp(-0.5*7.1)+exp(-0.5*(fit3_looic-fit_waic)))
+# l3 <- exp(-0.5*(fit3_looic-fit_looic))/(exp(-0.5*(fit_looic-fit_looic))+exp(-0.5*(fit2_looic-fit_looic))+exp(-0.5*7.1)+exp(-0.5*(fit3_looic-fit_waic)))
+# 
+# model_comparison <- tibble(
+#   model = c("fit1", "fit2", "fit3"),
+#   waic = c(fit_waic, fit2_waic, fit3_waic), 
+#   waic_se = c(fit_se_waic, fit2_se_waic, fit3_se_waic), 
+#   waic_weight = c(w1, w2, w3),
+#   looic = c(fit_looic, fit2_looic, fit3_looic),
+#   looic_se = c(fit_se_looic, fit2_se_looic, fit3_se_looic),
+#   looic_weight = c(l1, l2, l3)
+# )%>%
+#   arrange(waic)%>%
+#   write_csv(., "../saves/bcfa_model_comparison.csv")
+
+model_comparison <- read_csv("../saves/bcfa_model_comparison.csv")
 ```

### 2022-02-19 analysis/analysis.Rmd
add age models

---
title: "PragBat Models"
output: html_document
---

```{r}
library("papaja")
library(tidyverse)
library(knitr)
library(ggthemes)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
library(brms)
library(psy)
library(tidyboot)
library(ggpubr)
library(blavaan)
```

```{r}
data <- bind_rows(
  read_csv("../data/data_r1.csv") %>%filter(task != "training") %>%mutate(study = "study1"),
  read_csv("../data/data_r2.csv") %>%filter(task != "training")%>%mutate(study = "study2"),
  read_csv("../data/data_r3.csv") %>%filter(task != "training")%>%mutate(study = "study3")
  ) %>%
  mutate(study = factor(study),
         id = paste(study, id, sep = "_"))

data%>%
  group_by(task)%>%
  summarise(trials = length(unique(trial)))
```

# Age effects

```{r}
# Models
## card sorting
# bm_cs_s1 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "card_sorting", study == "study1"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_cs_s1, "../saves/card_sorting_model_s1.rds")
# 
# bm_cs_s2 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "card_sorting", study == "study2"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_cs_s2, "../saves/card_sorting_model_s2.rds")
# 
# bm_cs_s3 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "card_sorting", study == "study3"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_cs_s3, "../saves/card_sorting_model_s3.rds")
# 
# # mutual exclusivity
# bm_me_s1 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "mutual_exclusivity", study == "study1"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_me_s1, "../saves/mutual_exclusivity_model_s1.rds")
# 
# bm_me_s2 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "mutual_exclusivity", study == "study2"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_me_s2, "../saves/mutual_exclusivity_model_s2.rds")
# 
# bm_me_s3 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "mutual_exclusivity", study == "study3"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_me_s3, "../saves/mutual_exclusivity_model_s3.rds")
# 
# 
# # ad hoc implicature
# bm_ad_s2 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "ad_hoc_implicature", study == "study2"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_ad_s2, "../saves/ad_hoc_implicature_model_s2.rds")
# 
# bm_ad_s3 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "ad_hoc_implicature", study == "study3"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_ad_s3, "../saves/ad_hoc_implicature_model_s3.rds")
# 
# # discourse_continuity
# bm_dis_s2 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "discourse_continuity", study == "study2"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_dis_s2, "../saves/discourse_continuity_model_s2.rds")
# 
# # informativeness
# bm_inf_s1 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "informativeness", study == "study1"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_inf_s1, "../saves/informativeness_model_s1.rds")
# 
# #match_to_sample
# bm_ms_s3 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "match_to_sample", study == "study3"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_ms_s3, "../saves/match_to_sample_model_s3.rds")
# 
# #novelty
# bm_nov_s1 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "novelty", study == "study1"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_nov_s1, "../saves/novelty_model_s1.rds")
# 
# #preference
# bm_pref_s1 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "preference", study == "study1"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_pref_s1, "../saves/preference_model_s1.rds")
# 
# #simple_inf
# bm_simpinf_s2 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "simple_inf", study == "study2"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_simpinf_s2, "../saves/simple_inf_model_s2.rds")
# 
# bm_simpinf_s3 <- brm(correct ~ z_age + z_trial + (z_trial|id),
#           family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           data = data%>%filter(task == "simple_inf", study == "study3"),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           iter = 4000)%>%
#   add_criterion("waic")
# 
# saveRDS(bm_simpinf_s3, "../saves/simple_inf_model_s3.rds")

bm_cs_s1 <- readRDS( "../saves/card_sorting_model_s1.rds")
bm_cs_s2 <- readRDS( "../saves/card_sorting_model_s2.rds")
bm_cs_s3 <- readRDS( "../saves/card_sorting_model_s3.rds")

bm_me_s1 <- readRDS( "../saves/mutual_exclusivity_model_s1.rds")
bm_me_s2 <- readRDS( "../saves/mutual_exclusivity_model_s2.rds")
bm_me_s3 <- readRDS( "../saves/mutual_exclusivity_model_s3.rds")

bm_ad_s2 <- readRDS( "../saves/ad_hoc_implicature_model_s2.rds")
bm_ad_s3 <- readRDS( "../saves/ad_hoc_implicature_model_s3.rds")

bm_dis_s2 <- readRDS( "../saves/discourse_continuity_model_s2.rds")

bm_inf_s1 <- readRDS( "../saves/informativeness_model_s1.rds")

bm_nov_s1 <- readRDS( "../saves/novelty_model_s1.rds")

bm_pref_s1 <- readRDS( "../saves/preference_model_s1.rds")

bm_ms_s3 <- readRDS( "../saves/match_to_sample_model_s3.rds")

bm_simpinf_s2 <- readRDS( "../saves/simple_inf_model_s2.rds")
bm_simpinf_s3 <- readRDS( "../saves/simple_inf_model_s3.rds")

```

```{r}
#Predictions
nd1 <- data%>%
  filter(study == "study1", trial == "1", task == "mutual_exclusivity", test_day == 1)%>%
  select(-z_trial,-correct, -task, -test_day, -age_month, -gender, -item, -subage)%>%
  mutate(z_trial = 0)
nd2 <- data%>%
  filter(study == "study2", trial == "1", task == "mutual_exclusivity", test_day == 1)%>%
  select(-z_trial,-correct, -task, -test_day, -age_month, -gender, -item, -subage)%>%
  mutate(z_trial = 0)
nd3 <- data%>%
  filter(study == "study3", trial == "1", task == "mutual_exclusivity")%>%
  select(-z_trial,-correct, -task, -test_day, -age_month, -gender, -item, -subage)%>%
  mutate(z_trial = 0)

pred <- bind_rows(
fitted(bm_cs_s1, newdata = nd1, re_formula = NA) %>% as_tibble() %>% bind_cols(nd1)%>%mutate(study = "study1", task = "card_sorting"),
fitted(bm_cs_s2, newdata = nd2, re_formula = NA) %>% as_tibble() %>% bind_cols(nd2)%>%mutate(study = "study2", task = "card_sorting"),
fitted(bm_cs_s3, newdata = nd3, re_formula = NA) %>% as_tibble() %>% bind_cols(nd3)%>%mutate(study = "study3", task = "card_sorting"),

fitted(bm_me_s1, newdata = nd1, re_formula = NA) %>% as_tibble() %>% bind_cols(nd1)%>%mutate(study = "study1", task = "mutual_exclusivity"),
fitted(bm_me_s2, newdata = nd2, re_formula = NA) %>% as_tibble() %>% bind_cols(nd2)%>%mutate(study = "study2", task = "mutual_exclusivity"),
fitted(bm_me_s3, newdata = nd3, re_formula = NA) %>% as_tibble() %>% bind_cols(nd3)%>%mutate(study = "study3", task = "mutual_exclusivity"),

fitted(bm_ad_s2, newdata = nd2, re_formula = NA) %>% as_tibble() %>% bind_cols(nd2)%>%mutate(study = "study2", task = "ad_hoc_implicature"),
fitted(bm_ad_s3, newdata = nd3, re_formula = NA) %>% as_tibble() %>% bind_cols(nd3)%>%mutate(study = "study3", task = "ad_hoc_implicature"),

fitted(bm_dis_s2, newdata = nd2, re_formula = NA) %>% as_tibble() %>% bind_cols(nd2)%>%mutate(study = "study2", task = "discourse_continuity"),

fitted(bm_inf_s1, newdata = nd1, re_formula = NA) %>% as_tibble() %>% bind_cols(nd1)%>%mutate(study = "study1", task = "informativeness"),

fitted(bm_ms_s3, newdata = nd3, re_formula = NA) %>% as_tibble() %>% bind_cols(nd3)%>%mutate(study = "study3", task = "match_to_sample"),

fitted(bm_nov_s1, newdata = nd1, re_formula = NA) %>% as_tibble() %>% bind_cols(nd1)%>%mutate(study = "study1", task = "novelty"),

fitted(bm_pref_s1, newdata = nd1, re_formula = NA) %>% as_tibble() %>% bind_cols(nd1)%>%mutate(study = "study1", task = "preference"),

fitted(bm_simpinf_s2, newdata = nd2, re_formula = NA) %>% as_tibble() %>% bind_cols(nd2)%>%mutate(study = "study2", task = "simple_inf"),
fitted(bm_simpinf_s3, newdata = nd3, re_formula = NA) %>% as_tibble() %>% bind_cols(nd3)%>%mutate(study = "study3", task = "simple_inf")

)%>%
  mutate(task = factor(task, levels = c("mutual_exclusivity", "informativeness", "simple_inf", "preference", "novelty","card_sorting", "discourse_continuity", "ad_hoc_implicature", "match_to_sample")))
```

```{r}
p1 <- data %>%
  group_by(study, id,age, subage,task) %>%
  filter(task != "training") %>%
  summarise(mean = mean(correct))%>%
  mutate(task = factor(task, levels = c("mutual_exclusivity", "informativeness", "simple_inf", "preference", "novelty","card_sorting", "discourse_continuity", "ad_hoc_implicature", "match_to_sample")))

p2 <- p1 %>%
  group_by(study,subage,task) %>%
  tidyboot_mean(column = mean) %>%
  mutate(chance = ifelse(task == "discourse_continuity", 1/3, 1/2))

task_names <- c(
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"
                    )

pf2 <- ggplot()+
  geom_hline(data = p2, aes(yintercept = chance), lty = 3)+
  geom_jitter(data = p1, aes(x = age, y = mean, pch = study), alpha = .25, width = .05, height = .01)+
  geom_smooth(data = pred, aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5, lty =study), stat = "identity", col = "black", size = 1, alpha = .25)+
  facet_wrap(~task, nrow = 2, labeller = as_labeller(task_names))+
    geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = factor(subage), pch = study), position = position_dodge(width = .5))+
  labs(x = "Age", y = "Proportion correct") +
  scale_color_ptol(name = "Age group", labels = c("3-year-olds", "4-year-olds")) +
  ylim(-0.05, 1.05)+
  scale_shape_manual(values=c(1, 2, 4), name = "Study", labels = c("Study 1", "Study 2", "Study 3"))+
  scale_linetype_manual(values=c(1, 2, 3), name = "Study", labels = c("Study 1", "Study 2", "Study 3"))+
  theme_few()+
  theme(legend.position = c(.9,.225), legend.direction = "vertical", legend.box = "horizontal")+
  guides(shape = guide_legend(order = 2),linetype = guide_legend(order = 2), col = guide_legend(order = 1))

ggsave(plot = pf2,"../paper/figures/figure2.png", width = 10, height = 4, scale = 1.25)
```

```{r}

est <- bind_rows(
posterior_samples(bm_cs_s1, pars = "b_z_age")%>%mutate(study = "study1", task = "card_sorting"),
posterior_samples(bm_cs_s2, pars = "b_z_age")%>%mutate(study = "study2", task = "card_sorting"),
posterior_samples(bm_cs_s3, pars = "b_z_age")%>%mutate(study = "study3", task = "card_sorting"),

posterior_samples(bm_me_s1, pars = "b_z_age")%>%mutate(study = "study1", task = "mutual_exclusivity"),
posterior_samples(bm_me_s2, pars = "b_z_age")%>%mutate(study = "study2", task = "mutual_exclusivity"),
posterior_samples(bm_me_s3, pars = "b_z_age")%>%mutate(study = "study3", task = "mutual_exclusivity"),

posterior_samples(bm_ad_s2, pars = "b_z_age")%>%mutate(study = "study2", task = "ad_hoc_implicature"),
posterior_samples(bm_ad_s3, pars = "b_z_age")%>%mutate(study = "study3", task = "ad_hoc_implicature"),

posterior_samples(bm_dis_s2, pars = "b_z_age")%>%mutate(study = "study2", task = "discourse_continuity"),

posterior_samples(bm_inf_s1, pars = "b_z_age")%>%mutate(study = "study1", task = "informativeness"),

posterior_samples(bm_ms_s3, pars = "b_z_age")%>%mutate(study = "study3", task = "match_to_sample"),

posterior_samples(bm_nov_s1, pars = "b_z_age")%>%mutate(study = "study1", task = "novelty"),

posterior_samples(bm_pref_s1, pars = "b_z_age")%>%mutate(study = "study1", task = "preference"),

posterior_samples(bm_simpinf_s2, pars = "b_z_age")%>%mutate(study = "study2", task = "simple_inf"),
posterior_samples(bm_simpinf_s3, pars = "b_z_age")%>%mutate(study = "study3", task = "simple_inf")

)%>%
  mutate(task = factor(task, levels = c("mutual_exclusivity", "informativeness", "simple_inf", "preference", "novelty","card_sorting", "discourse_continuity", "ad_hoc_implicature", "match_to_sample")),
         task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"))

pest <- ggplot(est, aes(y = task, x = b_z_age, fill = study))+
geom_density_ridges(alpha = .5)+
  labs(y="", x="Model estimate for age")+
  geom_vline(xintercept = 0, col = "black", lty = 2, alpha = 0.75)+
  #scale_fill_manual(values = c("#FF0000A0", "#A0A0A0A0", "#FF0000A0"))+
  scale_fill_colorblind(name = "Study", labels = c("Study 1", "Study 2", "Study 3"))+
  #guides(fill = F)+
  theme_few()+ 
  xlim(-2,12)+
  scale_y_discrete(limits=rev)

ggsave(plot = pest,"../paper/figures/figure3.png", width = 7, height = 5, scale = 1.25)
```

```{r}

range <- bind_rows(
fixef(bm_cs_s1)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study1", task = "card_sorting"),
fixef(bm_cs_s2)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study2", task = "card_sorting"),
fixef(bm_cs_s3)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study3", task = "card_sorting"),

fixef(bm_me_s1)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study1", task = "mutual_exclusivity"),
fixef(bm_me_s2)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study2", task = "mutual_exclusivity"),
fixef(bm_me_s3)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study3", task = "mutual_exclusivity"),

fixef(bm_ad_s2)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study2", task = "ad_hoc_implicature"),
fixef(bm_ad_s3)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study3", task = "ad_hoc_implicature"),

fixef(bm_dis_s2)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study2", task = "discourse_continuity"),

fixef(bm_inf_s1)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study1", task = "informativeness"),

fixef(bm_ms_s3)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study3", task = "match_to_sample"),

fixef(bm_nov_s1)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study1", task = "novelty"),

fixef(bm_pref_s1)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study1", task = "preference"),

fixef(bm_simpinf_s2)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study2", task = "simple_inf"),
fixef(bm_simpinf_s3)%>%as_tibble(rownames = "parameter")%>%filter(parameter == "z_age")%>%mutate(study = "study3", task = "simple_inf")

)%>%
  mutate(task = factor(task, levels = c("mutual_exclusivity", "informativeness", "simple_inf", "preference", "novelty","card_sorting", "discourse_continuity", "ad_hoc_implicature", "match_to_sample")),
         task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"))

prange<- ggplot(range, aes(y = task, x = Estimate, col = study))+
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), position = position_dodge(width = 0.5), height = 0)+
  geom_point( position = position_dodge(width = 0.5),  size =1.5)+
  labs(y="", x="Model estimate for age")+
  geom_vline(xintercept = 0, col = "black", lty = 2, alpha = 0.75)+
  #scale_fill_manual(values = c("#FF0000A0", "#A0A0A0A0", "#FF0000A0"))+
  scale_color_colorblind(name = "Study", labels = c("Study 1", "Study 2", "Study 3"))+
  #guides(fill = F)+
  theme_few()+ 
  #xlim(-2,12)+
  scale_y_discrete(limits=rev)+
  theme(legend.position = c(.8,.8))

ggsave(plot = prange,"../paper/figures/figure3.png", width = 4, height = 2.5, scale = 1.5)
```
# Reliability
```{r}
model_cor <- data_frame()

tasks1 <- unique(data$task[data$study == "study1"])

for(i in tasks1) {

  model <- brm(correct ~  z_age + (0+test_day|id),
            data = data%>%filter(study == "study1", task == i), 
            family = bernoulli(),
          #control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          #save_all_pars = TRUE,
          iter = 2000)

          cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_dayday1,test_dayday2)")%>%mutate(task = i , study = "study1")

          model_cor <- bind_rows(model_cor, cor)

}

tasks2 <- unique(data$task[data$study == "study2"])

for(i in tasks2) {

  model <- brm(correct ~  z_age + (0+test_day|id),
            data = data%>%filter(study == "study2", task == i), 
            family = bernoulli(),
          #control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          #save_all_pars = TRUE,
          iter = 2000)

          cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_dayday1,test_dayday2)")%>%mutate(task = i , study = "study2")

          model_cor <- bind_rows(model_cor, cor)

}

mcor <- model_cor %>%
    mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"),
           term = task, 
           mcor = Estimate, 
           mcor_lci = `l-95% CI`, 
           mcor_uci = `u-95% CI`)%>%
  select(study, term, task, mcor, mcor_lci, mcor_uci)

saveRDS(mcor, "../saves/model_based_reliability.rds")

mcor <- readRDS("../saves/model_based_reliability.rds")
```

```{r}
wide_data <- data %>%
  mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"))%>%
  filter(study != "study3",
         task != "training") %>%
  droplevels() %>%
  group_by(study,id,task, test_day) %>%
  summarise(mean = mean(correct)) %>%
  spread(test_day, mean) %>%
  na.omit() %>%
  rename("Day1" = `day1`,
         "Day2" = `day2`)

reli <- wide_data %>%
  group_by(study, task) %>%
  summarize(reli = cor.test(Day1,Day2)$estimate,
            lci = cor.test(Day1,Day2)$conf.int[1],
            uci = cor.test(Day1,Day2)$conf.int[2],
            p = cor.test(Day1,Day2)$p.value,
            n = n()) %>%
  mutate_if(is.numeric, round, digits = 2)

cor_r1 <- data %>%
  mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"))%>%
  filter(study == "study1") %>%
  droplevels() %>%
  group_by(id,task) %>%
  summarise(mean = mean(correct)) %>%
  spread(task, mean) %>%
  ungroup() %>%
  select(-id) %>%
  corrr::correlate(diagonal = reli %>%
                     filter(study == "study1") %>%
                     pull(reli)) %>%
  gather(task, cor, -term) %>%
  mutate(cor = replace(cor, duplicated(cor), NA)) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  na.omit() %>%
  mutate(study = "study1")%>%
  left_join(mcor)%>%
  mutate(cor2 = ifelse(!is.na(mcor), paste0(" ",cor,"\n"," [",round(mcor,2), "]"), cor))

cor_r2 <- data%>%
    mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"))%>%
  filter(study == "study2") %>%
  droplevels() %>%
  group_by(id,task) %>%
  summarise(mean = mean(correct)) %>%
  spread(task, mean) %>%
  ungroup() %>%
  select(-id) %>%
  corrr::correlate(diagonal = reli%>%filter(study == "study2") %>%pull(reli)) %>%
  gather(task, cor, -term) %>%
  mutate(cor = replace(cor, duplicated(cor), NA)) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  na.omit() %>%
  mutate(study = "study2")%>%
  left_join(mcor)%>%
  mutate(cor2 = ifelse(!is.na(mcor), paste0(" ",cor,"\n"," [",round(mcor,2), "]"), cor))

cor3 <- data%>%
    mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"))%>%
  filter(study == "study3")%>%
  filter(task != "training")%>%
  droplevels()%>%
  group_by(id,task)%>%
  summarise(mean = mean(correct))%>%
  spread(task, mean)%>%
  ungroup()%>%
  select(-id)%>%
  corrr::correlate(diagonal = c(1,1.1,1.2,1.3,1.4))%>%
  gather(task, cor, -term)%>%
  mutate(cor = replace(cor, duplicated(cor), NA))%>%
  mutate_if(is.numeric, round, digits = 2)%>%
  na.omit()%>%
  mutate(study = "study3",
         cor = ifelse(cor>0.99,NA,cor))

cp1 <- ggplot(cor_r1, aes(x = term, y = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white",
   midpoint = 0, limit = c(-1,1), space = "Lab",
   name="Correlation") +
   coord_fixed()+
  theme_few()+
  geom_text(aes(label = cor2), color = "black", size = 3) +
  #ggtitle("Study 1")+
  theme(
        legend.position = "right",
        legend.direction = "vertical",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

cp2 <- ggplot(cor_r2, aes(x = term, y = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white",
   midpoint = 0, limit = c(-1,1), space = "Lab",
   name="Correlation") +
   coord_fixed()+
  theme_few()+
  geom_text(aes(label = cor2), color = "black", size = 3) +
  #ggtitle("Study 2")+
  theme(
        legend.position = "right",
        legend.direction = "vertical",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

cp3 <- ggplot(cor3, aes(x = term, y = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white",
   midpoint = 0, limit = c(-1,1), space = "Lab",
   name="Correlation") +
   coord_fixed()+
  theme_few(base_size = 12)+
  #ggtitle("Study 3")+
  geom_text(aes(label = cor), color = "black", size = 3) +
  theme(legend.justification = c(1, 0),
        legend.position = c(0.55, 0.75),
        legend.direction = "vertical",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.background = element_blank())+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5))

pf4 <- ggarrange(cp1, cp2, cp3, common.legend = T, legend = "right", nrow = 1, labels = c("A","B","C"), hjust = -1.5)

ggsave(plot = pf4,"./figures/figure4.png", width = 10, height = 3, scale = 1.5, bg = "white")
```

#Relations between tasks

```{r}
study = unique(data$study)
task1 = unique(data$task)
task2 = unique(data$task)

cor_data <- data_frame()

for (i in study){
  for(j in task1){
    for(k in task2){

  d <- data%>%
  filter(study == i,
         task == j | task == k,
         j != k)%>%
  group_by(id,task)%>%
  summarise(mean = mean(correct))%>%
  spread(task, mean)

  if(j != k  & ncol(d)>2){

  d <- d%>%rename(task1 = 2, task2 = 3)

  rho =cor.test(d$task1,d$task2)$estimate
  lci =cor.test(d$task1,d$task2)$conf.int[1]
  uci =cor.test(d$task1,d$task2)$conf.int[2]
  p =cor.test(d$task1,d$task2)$p.value

  cor = tibble(study = i, task1 = j, task2 = k, rho = rho, lci = lci, uci = uci, p = p)
  } else {
  cor = tibble(study = i, task1 = j, task2 = k, rho = NA, lci = NA, uci = NA, p = NA)
  }

  cor_data <- bind_rows(cor_data, cor)

    }
  }
}

cors <- cor_data%>%
  filter(!is.na(rho))%>%
  mutate_if(is.numeric, round,2)

write_csv(cors, "../saves/by_task_correlations.csv")
```

# Confirmatory factor analysis

```{r}
cfad <- data%>%
  group_by(id,age, subage,task)%>%
  filter(task != "training")%>%
  summarise(mean = mean(correct))%>%
  pivot_wider(names_from = "task", values_from = "mean")%>%
  ungroup()%>%
  filter(!is.na(ad_hoc_implicature),
         !is.na(card_sorting),
         !is.na(match_to_sample),
         !is.na(mutual_exclusivity),
         !is.na(simple_inf))%>%
  mutate(ad_hoc_implicature = scale(ad_hoc_implicature),
         card_sorting = scale(card_sorting),
         match_to_sample = scale(match_to_sample),
         mutual_exclusivity = scale(mutual_exclusivity),
         simple_inf = scale(simple_inf))
```

```{r}
model <- 'prag  =~ " mutual_exclusivity + ad_hoc_implicature + simple_inf
          card  =~ card_sorting
          match =~ match_to_sample'

model2 <- 'fac  =~ mutual_exclusivity + ad_hoc_implicature+ simple_inf + card_sorting + match_to_sample'

model3 <- 'ad  =~ ad_hoc_implicature
           simp  =~ simple_inf
           mut  =~ mutual_exclusivity
           card  =~ card_sorting
           match =~ match_to_sample'
```

```{r}
fit <- bcfa(model, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
saveRDS(fit, "../saves/bcfa_prag.rds")
fit <- readRDS("../saves/bcfa_prag.rds")

fit2 <- bcfa(model2, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
saveRDS(fit2, "../saves/bcfa_single.rds")
fit2 <- readRDS("../saves/bcfa_single.rds")

fit3 <- bcfa(model3, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
saveRDS(fit3, "../saves/bcfa_separate.rds")
fit3 <- readRDS("../saves/bcfa_separate.rds")
```

```{r}
fitmeasures(fit)%>%as_tibble(rownames = "index")

x <- summary(fit, fit.measures=TRUE, standardized = TRUE, rsquare = T)

blavInspect(fit, what = "postmean")%>%as_tibble(rownames = "index")%>%
  left_join(blavInspect(fit, what = "hpd")%>%as_tibble(rownames = "index"))

```

```{r}
# fit_waic <- fitmeasures(fit)%>%as_tibble(rownames = "index")%>%filter(index == "waic")%>%pull(value)
# fit2_waic <- fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%filter(index == "waic")%>%pull(value)
# fit3_waic <- fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%filter(index == "waic")%>%pull(value)
# 
# fit_se_waic <- fitmeasures(fit)%>%as_tibble(rownames = "index")%>%filter(index == "se_waic")%>%pull(value)
# fit2_se_waic <- fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%filter(index == "se_waic")%>%pull(value)
# fit3_se_waic <- fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%filter(index == "se_waic")%>%pull(value)
# 
# fit_looic <- fitmeasures(fit)%>%as_tibble(rownames = "index")%>%filter(index == "looic")%>%pull(value)
# fit2_looic <- fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%filter(index == "looic")%>%pull(value)
# fit3_looic <- fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%filter(index == "looic")%>%pull(value)
# 
# fit_se_looic <- fitmeasures(fit)%>%as_tibble(rownames = "index")%>%filter(index == "se_loo")%>%pull(value)
# fit2_se_looic <- fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%filter(index == "se_loo")%>%pull(value)
# fit3_se_looic <- fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%filter(index == "se_loo")%>%pull(value)
# 
# #model weights
# ## waic
# w1 <- exp(-0.5*(fit_waic-fit_waic))/(exp(-0.5*(fit_waic-fit_waic))+exp(-0.5*(fit2_waic-fit_waic))+exp(-0.5*7.1)+exp(-0.5*(fit3_waic-fit_waic)))
# w2 <- exp(-0.5*(fit2_waic-fit_waic))/(exp(-0.5*(fit_waic-fit_waic))+exp(-0.5*(fit2_waic-fit_waic))+exp(-0.5*7.1)+exp(-0.5*(fit3_waic-fit_waic)))
# w3 <- exp(-0.5*(fit3_waic-fit_waic))/(exp(-0.5*(fit_waic-fit_waic))+exp(-0.5*(fit2_waic-fit_waic))+exp(-0.5*7.1)+exp(-0.5*(fit3_waic-fit_waic)))
# ## looic
# l1 <- exp(-0.5*(fit_looic-fit_looic))/(exp(-0.5*(fit_looic-fit_looic))+exp(-0.5*(fit2_looic-fit_looic))+exp(-0.5*7.1)+exp(-0.5*(fit3_looic-fit_waic)))
# l2 <- exp(-0.5*(fit2_looic-fit_looic))/(exp(-0.5*(fit_looic-fit_looic))+exp(-0.5*(fit2_looic-fit_looic))+exp(-0.5*7.1)+exp(-0.5*(fit3_looic-fit_waic)))
# l3 <- exp(-0.5*(fit3_looic-fit_looic))/(exp(-0.5*(fit_looic-fit_looic))+exp(-0.5*(fit2_looic-fit_looic))+exp(-0.5*7.1)+exp(-0.5*(fit3_looic-fit_waic)))
# 
# model_comparison <- tibble(
#   model = c("fit1", "fit2", "fit3"),
#   waic = c(fit_waic, fit2_waic, fit3_waic), 
#   waic_se = c(fit_se_waic, fit2_se_waic, fit3_se_waic), 
#   waic_weight = c(w1, w2, w3),
#   looic = c(fit_looic, fit2_looic, fit3_looic),
#   looic_se = c(fit_se_looic, fit2_se_looic, fit3_se_looic),
#   looic_weight = c(l1, l2, l3)
# )%>%
#   arrange(waic)%>%
#   write_csv(., "../saves/bcfa_model_comparison.csv")

model_comparison <- read_csv("../saves/bcfa_model_comparison.csv")

```

### 2022-02-19 analysis/data_processing.Rmd
add age models

@@
 ## die flogenden Zeilen kannst du überspringen. Weiter gehts in Zeile 68
-# files <- dir("~/Work/PragBat/raw_data/")
-# 
-# raw_data <- data_frame()
-# for (f in files) {
-#   jf <- paste("~/Work/PragBat/raw_data/",f,sep="")
-#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-#   date <- str_sub(jf,33,str_length(jf)-11)
-#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date,
-#                                                trial = as.character(trial))
-#   raw_data <- bind_rows(raw_data, id)
-# }
-# 
-# unique(raw_data$subid)
-# 
-# 
-# task_data <- raw_data %>%
-#   filter(trial != "training",
-#          trial != "filler1",
-#          trial != "filler2",
-#          trial != "train",
-#          trial != "train2")%>%
-#   filter(phase == "shape" | is.na(phase))%>%
-#   mutate(subid = recode(subid, `13.2` = "Vp13.2",
-#                         `13.2` = "Vp13.2",
-#                         `14.2` = "Vp14.2",
-#                         `16.2` = "Vp16.2",
-#                         `19.1` = "Vp19.1",
-#                         `12.1` = "Vp12.1",
-#                         `29.2` = "Vp29.2",
-#                         `26.1` = "Vp26.2",
-#                         `37.1` = "Vp37.1",
-#                         `38.1` = "Vp38.1"
-#                         ),
-#          item = ifelse(task == "card_sorting", sample,leftObject))%>%
-#   select(subid, subage, test_date, task,item, trial, correct)%>%
-#   separate(subid, into = c("id","test_day"), sep="\\.")%>%
-#   mutate(test_day = ifelse(id == "Vp12" & test_date =="2019-11-26", 2, test_day))
-# 
-# 
-# #task_data <- read_csv("../data/data.csv")
-# 
-# # damit du das daten file mit dem log file (deine Liste) mergen kannst (brauchen wir für das numerische alter) legst du deine liste in den gleichen ordner in dem auch ader repository ordner liegt.
+files <- dir("~/Work/Local/PragBat/raw_data/")
+
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/Local/PragBat/raw_data/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  date <- str_sub(jf,33,str_length(jf)-11)
+  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date,
+                                               trial = as.character(trial))
+  raw_data <- bind_rows(raw_data, id)
+}
+
+unique(raw_data$subid)
+
+task_data <- raw_data %>%
+  filter(task != "training", 
+         trial != "training",
+         trial != "filler1",
+         trial != "filler2",
+         trial != "train",
+         trial != "train2")%>%
+  filter(phase == "shape" | is.na(phase))%>%
+  mutate(subid = recode(subid, `13.2` = "Vp13.2",
+                        `13.2` = "Vp13.2",
+                        `14.2` = "Vp14.2",
+                        `16.2` = "Vp16.2",
+                        `19.1` = "Vp19.1",
+                        `12.1` = "Vp12.1",
+                        `29.2` = "Vp29.2",
+                        `26.1` = "Vp26.2",
+                        `37.1` = "Vp37.1",
+                        `38.1` = "Vp38.1"
+                        ),
+         item = ifelse(task == "card_sorting", sample,leftObject),
+         item = ifelse(task == "mutual_exclusivity",
+                       ifelse(correct_location == "left", rightObject, leftObject), item))%>%
+  select(subid, subage, test_date, task,item, trial, correct)%>%
+  separate(subid, into = c("id","test_day"), sep="\\.")%>%
+  mutate(test_day = ifelse(id == "Vp12" & test_date =="2019-11-26", 2, test_day))
+
+#task_data <- read_csv("../data/data.csv")
+
+# damit du das daten file mit dem log file (deine Liste) mergen kannst (brauchen wir für das numerische alter) legst du deine liste in den gleichen ordner in dem auch ader repository ordner liegt.
 Dann sollte es klappen.
-# 
-# log <- read_ods("../../VP Liste_Manuel.ods", sheet = 2)%>%
-#   mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
-#          id = paste("Vp",`ID `, sep = ""))%>%
-#   select(id, age, status)
-# 
-# 
-# data <- task_data %>%
-#   left_join(log)%>%
-#   filter(status == "keep")%>%
-#   mutate(check_age = ifelse(subage == substr(age,1,1),T,F),
-#          subage = factor(as.numeric(substr(age,1,1))),
-#          trial = as.numeric(trial))%>%
-#   select(-test_date, - status, -check_age)%>%
-#   mutate(trial = ifelse(test_day == "2", 
-#                         ifelse(task == "card_sorting", trial + 6, trial +5),
-#                         trial),
-#          z_age = age - mean(age),
-#          z_trial = trial - mean(trial))
-# 
-# write_csv(data, "../data/data.csv")
+
+log <- read_ods("../../VP Liste_Manuel.ods", sheet = 2)%>%
+  mutate(age = as.numeric(difftime(test_day_1, `birthday`, units = "days"))/365.25,
+         delay = as.numeric(difftime(test_day_2,test_day_1, units = "days")),
+         id = paste("Vp",`ID`, sep = ""))%>%
+  select(id, age, gender,status)
+
+data <- task_data %>%
+  left_join(log)%>%
+  filter(status == "keep")%>%
+  mutate(check_age = ifelse(subage == substr(age,1,1),T,F),
+         subage = factor(as.numeric(substr(age,1,1))),
+         trial = as.numeric(trial))%>%
+  select(-test_date, - status, -check_age)%>%
+  mutate(trial = ifelse(test_day == "2",
+                        ifelse(task == "card_sorting", trial + 6, trial +5),
+                        trial),
+         z_age = age - mean(age),
+         z_trial = trial - mean(trial))
+
+write_csv(data, "../data/data_r1.csv")
 

### 2022-02-19 analysis/data_round2.Rmd
add age models

@@
   mutate(age = as.numeric(difftime(as.Date(as.character(test_day_1),format="%Y%m%d"), as.Date(as.character(birthday),format="%Y%m%d"), units = "days"))/365.25,
+         delay = as.numeric(difftime(as.Date(as.character(test_day_2),format="%Y%m%d"), as.Date(as.character(test_day_1),format="%Y%m%d"), units = "days")),
          age_num_month = lubridate::time_length(difftime(as.Date(as.character(test_day_1),format="%Y%m%d"), as.Date(as.character(birthday),format="%Y%m%d")), "month"),
@@
          id = paste("VP",ID, sep = ""))%>%
-  select(id, age, age_month, status)
+  select(id, age, gender, status)
 
@@
          z_trial = trial - mean(trial),
-         item = ifelse(task == "card_sorting", sample, ifelse(task == "discourse_continuity", target1, leftObject)))%>%
-    select(id, test_day, subage,age,age_month, task,item, trial, correct, z_age, z_trial)
+         item = ifelse(task == "card_sorting", sample, ifelse(task == "discourse_continuity", target1, leftObject)),
+         item = ifelse(task == "mutual_exclusivity",
+                       ifelse(correct_location == "left", rightObject, leftObject), item))%>%
+    select(id, test_day, subage,age,gender, task,item, trial, correct, z_age, z_trial)
 
- # write_csv(data, "../data/data_r2.csv")
+ write_csv(data, "../data/data_r2.csv")
 ```

### 2022-02-19 analysis/data_round3.Rmd
add age models

@@
          id = ID,
-         subid = as.character(`Data ID`))%>%
+         subid = as.character(`Data ID`),
+         gender = ifelse(gender == "w", "f", gender))%>%
   select(id, subid, age, gender,age_month, status)
@@
          trial = as.numeric(trial))%>%
-    select(id, subage,age,age_month,gender, task,item, trial, correct)
+    select(id, subage,age,gender, task,item, trial, correct)%>%
+  mutate(z_age = age - mean(age),
+         z_trial = trial -mean(trial))
 

### 2022-02-19 analysis/reliability_rouder_haaf.Rmd
update to run study
add age models

@@
 raw_data <- bind_rows(
-read_csv("../data/data_r1.csv")%>%mutate(id = paste(id,"r1",sep = "_")) ,
-read_csv("../data/data_r2.csv")%>%mutate(id = paste(id,"r2",sep = "_"))
+read_csv("../data/data_r1.csv")%>%mutate(id = paste(id,"r1",sep = "_"),study = "s1") ,
+read_csv("../data/data_r2.csv")%>%mutate(id = paste(id,"r2",sep = "_"), study = "s2")
 )%>%
@@
 ```
-# Descriütives
+# Descriptives
 
@@
 me_data <- data %>%
-  filter(task == "mutual_exclusivity")
+  filter(study == "s2", 
+         task == "mutual_exclusivity")
 ```
+
+```{r}
+bme <-  brm(correct ~  z_age + test_day + (0+test_day|id),
+                    data = me_data, 
+            family = bernoulli(),
+          #control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          #save_all_pars = TRUE,
+          iter = 2000)
+
+rme <- ranef(bme)
+
+rel_me <- as_tibble(rme$id[,,"test_dayday1"], rownames = "id")%>%
+  left_join(as_tibble(rme$id[,,"test_dayday2"], rownames = "id")%>%
+              rename(Estimate_d2 = Estimate,
+                     Q2.5_d2 = Q2.5, 
+                     Q97.5_2 = Q97.5, 
+                     Est.Error_2 = Est.Error))
+
+ggplot(rel_me, aes(x = Estimate, y = Estimate_d2))+
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
+    geom_point(size = 5, pch = 4)+
+  geom_errorbar(aes(ymin = Q2.5_d2, ymax = Q97.5_2),width = 0, alpha = .4)+
+  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), height = 0, alpha = .4)+
+  labs(x = "Day 1", y = "Day 2")+
+  #facet_grid(~chain)+
+  stat_cor(method = "pearson", aes(x = Estimate, y = Estimate_d2), inherit.aes = F, size = 3)+
+  theme_minimal()
+```
+
+```{r}
+me_age <- as_tibble(rme$id[,,"test_dayday1"], rownames = "id")%>%
+  left_join(me_data)
+
+cor(me_age$age, me_age$Estimate)
+
+me_data%>%
+  group_by(id)%>%
+  summarise(age = mean(age),
+            perf = mean(correct))%>%
+  ungroup()%>%
+  summarise(cor = cor(age ,perf))
+
+```
+
+## Task: Informativeness
+```{r}
+inf_data <- data %>%
+  filter(#study == "s2", 
+         task == "informativeness")
+```
+
+```{r}
+binf <-  brm(correct ~  z_age + (0+test_day|id),
+                    data = inf_data, 
+            family = bernoulli(),
+          #control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          #save_all_pars = TRUE,
+          iter = 2000)
+
+rinf <- ranef(binf)
+
+rel_inf <- as_tibble(rinf$id[,,"test_dayday1"], rownames = "id")%>%
+  left_join(as_tibble(rinf$id[,,"test_dayday2"], rownames = "id")%>%
+              rename(Estimate_d2 = Estimate,
+                     Q2.5_d2 = Q2.5, 
+                     Q97.5_2 = Q97.5, 
+                     Est.Error_2 = Est.Error))
+
+ggplot(rel_inf, aes(x = Estimate, y = Estimate_d2))+
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
+    geom_point(size = 5, pch = 4)+
+  geom_errorbar(aes(ymin = Q2.5_d2, ymax = Q97.5_2),width = 0, alpha = .4)+
+  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), height = 0, alpha = .4)+
+  labs(x = "Day 1", y = "Day 2")+
+  #facet_grid(~chain)+
+  stat_cor(method = "pearson", aes(x = Estimate, y = Estimate_d2), inherit.aes = F, size = 3)+
+  theme_minimal()
+```
+
+```{r}
+inf_age <- as_tibble(rinf$id[,,"test_dayday1"], rownames = "id")%>%
+  left_join(inf_data)
+
+cor(inf_age$age, inf_age$Estimate)
+```
+
+## Task: Card Sorting
+```{r}
+card_data <- data %>%
+  filter(study == "s2", 
+         task == "card_sorting")
+```
+
+```{r}
+bcard <-  brm(correct ~  z_age + (0+test_day|id),
+                    data = card_data, 
+            family = bernoulli(),
+          #control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          #save_all_pars = TRUE,
+          iter = 2000)
+
+rcard <- ranef(bcard)
+
+rel_card <- as_tibble(rcard$id[,,"test_dayday1"], rownames = "id")%>%
+  left_join(as_tibble(rcard$id[,,"test_dayday2"], rownames = "id")%>%
+              rename(Estimate_d2 = Estimate,
+                     Q2.5_d2 = Q2.5, 
+                     Q97.5_2 = Q97.5, 
+                     Est.Error_2 = Est.Error))
+
+ggplot(rel_card, aes(x = Estimate, y = Estimate_d2))+
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
+    geom_point(size = 5, pch = 4)+
+  geom_errorbar(aes(ymin = Q2.5_d2, ymax = Q97.5_2),width = 0, alpha = .4)+
+  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), height = 0, alpha = .4)+
+  labs(x = "Day 1", y = "Day 2")+
+  #facet_grid(~chain)+
+  stat_cor(method = "pearson", aes(x = Estimate, y = Estimate_d2), inherit.aes = F, size = 3)+
+  theme_minimal()
+```
+
+```{r}
+card_age <- as_tibble(rcard$id[,,"test_dayday1"], rownames = "id")%>%
+  left_join(card_data)
+
+cor(card_age$age, card_age$Estimate)
+
+card_data%>%
+  group_by(id)%>%
+  summarise(age = mean(age),
+            perf = mean(correct))%>%
+  ungroup()%>%
+  summarise(cor = cor(age ,perf))
+```
+
+```{r}
+s1_data <- data %>%
+  filter(study == "s1")
+```
+
+```{r}
+bs1 <-  brm(correct ~  z_age + (0+test_day|id/task),
+                    data = s1_data, 
+            family = bernoulli(),
+          #control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          chains = 4,
+          cores = 4,
+          #save_all_pars = TRUE,
+          iter = 2000)
+```

### 2022-02-19 analysis/summary.Rmd
add age models

@@
 library(blavaan)
-#library(tidySEM)
-#library(semPlot)
+library(tidySEM)
+library(semPlot)
 ```
@@
 model_comparison <- read_csv("../saves/bcfa_model_comparison.csv")
+
+```
+
+```{r}
+summary(fit, fit.measures=TRUE, standardized = TRUE, rsquare = T)
+
+library(parameters)
+library(effectsize)
+model_parameters(fit, standardize = T)
 ```
@@
 # 
-# summary(fit, fit.measures=TRUE, standardized = TRUE, rsquare = T)
+summary(fit, fit.measures=TRUE, standardized = TRUE, rsquare = T)
 # 
-# semPaths(fit, whatLabels="std", intercepts=FALSE, style="lisrel",
-#                        nCharNodes=0, 
-#                        nCharEdges=0,
-#                        curveAdjacent = TRUE,title=TRUE, layout = lay,node.width = 2)
+semPaths(fit, whatLabels="std", intercepts=FALSE, style="lisrel",
+                       nCharNodes=0,
+                       nCharEdges=0,
+                       curveAdjacent = TRUE,title=TRUE, layout = lay,node.width = 2)
 ```

### 2022-02-19 paper/figures/cfa_fig.tex
add age models

\documentclass[border=5mm]{standalone}
\usepackage{tikz} 
\usetikzlibrary{positioning,arrows.meta,quotes}
\begin{document}
% latent variable model
\begin{tikzpicture}[
  transform shape, node distance=0cm,
  roundnode/.style={circle, draw=black, very thick, minimum size=2.5cm},
  squarednode/.style={rectangle, draw=black, very thick, minimum width=3cm},
  arrow/.style = {semithick,-Stealth},
  path/.style = {semithick,-Stealth},
  dotnode/.style={fill,inner sep=0pt,minimum size=2pt,circle} % <- this is new
]

%Nodes
\node[roundnode] (prag) {Pragmatic};
\node[squarednode, align=center,below=2.5cm of prag,xshift=0cm] (X2) {Ad-hoc \\ Implicature}; 
\node[squarednode, align=center,left=1cm of X2]    (X1) {Mutual \\ Exclusivity};
\node[squarednode, align=center,right=1cm of X2]    (X3) {Informativeness \\ Inference};

\node[squarednode, align=center,left=1.5cm of X1]    (X4) {Card \\ Sorting};
\node[squarednode, align=center,right=1.5cm of X3]    (X5) {Match to \\ Sample};

\node[roundnode, align = center, above = 2.5cm of X4] (card) {Executive \\ Functions};
\node[roundnode, align = center, above = 2.5cm of X5] (rmts) {Analogical \\ Reasoning};

%Letters
\node[below=0.5cm of X1] (e1) {0.56};
\node[below=0.5cm of X4] (e4) {0.00};
\node[below=0.5cm of X5] (e5) {0.00};
\node[below=0.5cm of X2] (e2) {0.65};
\node[below=0.5cm of X3] (e3) {0.88};
%\node[left=1cm of Xk] (ek) {$e_k$};
%
%%Arrows
\draw[arrow] (prag) -- node[align = center, fill=white, anchor=base] {\textbf{ 0.66} \\ \footnotesize{1.21 (0.38 -- 3.27)}} (X1.north);
\draw[arrow] (prag) -- node[align = center,fill=white, anchor=base] {\textbf{ 0.59} \\ \footnotesize{1.00 }} (X2.north);
\draw[arrow] (prag) -- node[align = center,fill=white, anchor=base] {\textbf{ 0.34} \\ \footnotesize{0.58 (0.08 -- 1.46)}} (X3.north);

\draw[arrow] (card) -- node[align = center,fill=white, anchor=base] {1.00 } (X4.north);
\draw[arrow] (rmts) -- node[align = center,fill=white, anchor=base] {1.00 } (X5.north);

% Correlations

\draw [>=Stealth, semithick, <-> ] (prag.north) to ["\textbf{0.33} \\ \footnotesize{0.20 (0.03 -- 0.41)}"align = center, out=140,in=40] (card.north);
\draw [>=Stealth, semithick, <-> ] (rmts.north) to ["0.06 \\ \footnotesize{0.04 (-0.11 -- 0.18)}" align = center, out=140,in=40] (prag.north);
\draw [>=Stealth, semithick, <-> ] (rmts.north) to ["-0.04 \\ \footnotesize{-0.04 (-0.22 -- 0.15)}" align = center, out=140,in=40] (card.north);

%
\draw[arrow] (e1) -- (X1);
\draw[arrow] (e2) -- (X2);
\draw[arrow] (e3) -- (X3);
\draw[arrow] (e4) -- (X4);
\draw[arrow] (e5) -- (X5);
%\draw[arrow] (ek) -- (Xk);

\end{tikzpicture}
\end{document}

### 2022-02-19 paper/manuscript.Rmd
add age models

---
title             : "An individual differences perspective on the development of pragmatic reasoning"
shorttitle        : "Individual differences in pragmatic reasoning"

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "manuel_bohn@eva.mpg.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Analysis
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Michael Henry Tessler"
    affiliation   : "2,3"
    role:
      - Analysis
      - Writing - Review & Editing
  - name          : "Clara Kordt"
    affiliation   : "4"
    role:
      - Data collection
  - name          : "Tom Hausmann"
    affiliation   : "5"
    role:
      - Data collection
  - name          : "Michael C. Frank"
    affiliation   : "6"
    role:
      - Conceptualization
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
  - id            : "2"
    institution   : "DeepMind, London, UK"
  - id            : "3"
    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
  - id            : "4"
    institution   : "Martin Luther University Halle-Wittenberg"
  - id            : "5"
    institution   : "Brandenburg Medical School Theodor Fontane"
  - id            : "6"
    institution   : "Department of Psychology, Stanford University"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  We are very thankful to Stella Christie for sharing the material for the relational match-to-sample task with us.

  M. Bohn received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no. 749229. M. H. Tessler was funded by the National Science Foundation SBE Postdoctoral Research Fellowship Grant No. 1911790. M. C. Frank was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition. The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : "../../../References/library.bib"

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
library(knitr)
library(brms)

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r}
data <- bind_rows(
  read_csv("../data/data_r1.csv") %>%filter(task != "training") %>%mutate(study = "study1"),
  read_csv("../data/data_r2.csv") %>%filter(task != "training")%>%mutate(study = "study2"),
  read_csv("../data/data_r3.csv") %>%filter(task != "training")%>%mutate(study = "study3")
  ) %>%
  mutate(study = factor(study),
         id = paste(study, id, sep = "_"), 
         test_day = paste0("day", test_day))

```
# Introduction

# Facets of pragmatic reasoning

# The challenges of studying individual differences

# The current study

# Study 1

Methods and sample size were pre-registered at https://osf.io/6a723. All analysis scripts and data files can be found in the following repository: https://github.com/manuelbohn/pragBat. The same repository also contains the code to run the experiments.

## Participants
```{r}
dem <- data%>%
  group_by(id)%>%
  summarise(study = unique(study),
            gender = unique(gender),
            age = unique(age),
            testdays = length(unique(test_day)))%>%
  group_by(study)%>%
  summarise(n = length(id),
            reli_n = sum(testdays == 2),
            female = sum(gender == "f"),
            mage = mean(age),
            lrange = range(age)[1],
            urange = range(age)[2])
```

For Study 1, we collected data from `r dem%>%filter(study == "study1")%>%pull(n)` children ($m_{age}$ = `r dem%>%filter(study == "study1")%>%pull(mage)`, range$_{age}$: `r dem%>%filter(study == "study1")%>%pull(lrange)` - `r dem%>%filter(study == "study1")%>%pull(urange)`, `r dem%>%filter(study == "study1")%>%pull(female)` girls) of which `r dem%>%filter(study == "study1")%>%pull(reli_n)` were tested twice. For most children, the two test sessions were two days apart; the longest time difference was six days. Children came from an ethnically homogeneous, mid-size German city (~550,000 inhabitants, median income €1,974 per month as of 2020); were mostly monolingual and had mixed socioeconomic backgrounds. The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. Data was collected between November 2019 and January 2020.

## Material and Methods

The study was presented as an interactive picture book on a tablet computer. The tasks were programmed in `HTML/JavaScript` and run in a web browser. Pre-recorded sound files were used to address the child (one native German speaker per animal). Children responded by touching objects on the screen. Children were tested in a quiet room in their daycare or in a separate room in a child laboratory. An experimenter guided the child through the study, selecting the different tasks and advancing within each task. In the beginning of the study, children completed a touch training to familiarize themselves with selecting objects. After a short introduction to the different animal characters, children completed the following six tasks. Figure \@ref(fig:fig1) shows screenshots for each task and the order in which they were presented.

### Training

An animal was standing on a pile between two tables. On each table, a familiar object was located. The animal asked the child to give them one of the objects (e.g., "Can you give me the car"). the objects were chosen so that children of the youngest age group would easily understand them (car and ball). This procedure familiarized the child with the general logic of the animals making requests and the child touching objects. There were two training trials.

### Mutual exclusivity

This task was directly taken from @bohn2021young. The task layout and the procedure was the same as in the training. In each trial, one object was a novel object (drawn for the purpose of this study) while the other one was likely to be familiar to children. Both object types changed from trial to trial. Following @bohn2021young, the familiar objects varied in terms of the likelihood that they would be familiar to children in the age range (carrot, duck, eggplant, garlic, horseshoe). For example, we assumed that most 3-year-olds would recognize a carrot, whereas fewer children would recognize a horseshoe. The animal always used a novel non-word (e.g., gepsa) in their request. We reasoned that children would identify the novel object as the referent of the novel word because they assumed the animal would have used the familiar word if they wanted to request the familiar object. Children's response was thus coded as correct if they selected the novel object. There were five trials, with the side on which the novel object appeared pseudo-randomized.

### Informativeness inference

The task was directly taken from @bohn_tessler_merrick_frank_2019. Th animal was standing between two trees with objects hanging in them. In one tree, there were two objects (type A and B) and in the other tree there was only one (type B). The animal turned to the tree with the two objects and labelled one of the objects. It was unclear from the animal's utterance, which of the two objects they were referring to. We assumed that children would map the novel word onto the object of type A because they expected the animal to turn to the tree with only the object of type B if their intention was to provide a label for an object of type B. Next, the trees were replaced by new ones, one of which carried an object of type A and the other of type B. The animal then said that one of the trees had the same object as they labelled previously (using the same label) and asked the child to touch the tree. We coded as correct if the child selected the tree with the object of type A. The first two trials were training trials, in which there was only one object in each tree. There were five test trials. The location of the tree with the two objects in the beginning of each trial was pseudo-randomized and so was the location of the objects when the new trees appeared.

### Speaker preference

This task was also taken from @bohn_tessler_merrick_frank_2019. The animal was standing between the two tables, each of which had a novel object (drawn for the purpose of the study) on it. The animal turned to one table, pointed at the object and said that they very much liked this object (using a pronoun instead of a label). Next, the animal turned to the other table and said that they really did not like the object (again, using a pronoun and no label). Then the animal turned towards the participant and used a novel label to request an object in an excited tone. We assumed that children would track the animal's preference and identify the previously liked object as the referent. Thus, we coded as correct if the child selected the object the animal expressed preference for. There were five test trials. The location of the preferred object as well as whether the animal first expressed liking or disliking was pseudo-randomized across trials

### Discourse novelty

This task was taken from @bohn2021young. Once again, the animal was standing between the two tables. One table was empty whereas there was a novel object on the other table. The animal turned towards the empty table and commented on its emptiness. Next, the animal turned to the other table and commented (in a neutral tone) on the presence of the object (not using a label). The animal then briefly disappeared. In the absence of the animal a second novel object appeared on the previously empty table. Then the animal returned and, facing the participant, asked for an object in an excited tone. We assumed that children would track which object was new to the ongoing interaction and identify the object that was new in context as the referent. We coded as correct when children selected the object that appeared later. There were five test trials. The location of the empty table and whether the animal first commented on the presence or absence of an object was pseudo-randomized across trials

### Card sorting

This task was modeled after @zelazo2006dimensional. The child saw to cards, a blue rabbit on the left and a red boat on the right. The experimenter introduced the child to the color game they would be playing next. In this game, all blue cards (irrespective of object depicted) would go to the left card and all red cards to the right. Next, a third card appeared in the middle of the screen (red rabbit or blue boat) and the experimenter demonstrated the color sorting by moving the card to the one with the same color. After a second demonstration trial, the child started to do the color sorting by themselves. After six trials, the experimenter said that they were now going to play a different game, the shape game, according to which all rabbits would go to the card with the rabbit (left) and all boats to the card with the boat (right). The experimenter repeated these instructions once and without any demonstration the child continued with the sorting according to the new rule. There were six test trials. The shape on the card was pseudo-randomized across trials. We only coded the trials after the rule change and coded as correct when the child sorted according to shape.

Each child received exactly the same version of each task and completed the tasks in the same order, with the same order on the two days. This ensured comparability of performance across children.

(ref:figlab1) Overview of the tasks used in Study 1 to 3. Pictures show screenshots from each task. The vertical order corresponds to the order of presentation in each study. The colors group the tasks along the (Assumed) cognitive processes involved. Blue: utterance-based inferences. Red common ground/discourse-based inferences. Green: Executive functions. Green: Analogical reasoning.

```{r fig1, include = T, fig.align = "center", fig.cap = "(ref:figlab1)", out.width="100%"}
knitr::include_graphics("./figures/figure1.png")
```

## Analysis

We analysed the data in three steps. First we investigated developmental effects in each task, then we assessed re-test reliability and finally, we analysed relations between the tasks.

All analysis were run in `R` [@R-base] version 4.1.2. Regression models were fit as Bayesian generalized linear mixed models (GLMM) using the function `brm` from the package `brms` [@burkner2017brms]. We used default priors for all analysis.

To estimate developmental effects in each task, we fit a GLMM predicting correct responses (0/1) by age (centered at the mean) and trial number (also centered). The model included random intercepts for each participant and random slopes for trial within participants (model notation in `R`: `correct ~ age + trial + (trial|id)` ). For each task, we inspected and visualized the posterior distribution (mean and 95% Credible Interval (CrI)) for the age estimate.

We assessed re-test reliability in two ways. First, for each task we computed the proportion of correct trials for each individual in the two test sessions and then used  Pearson correlations to quantify re-test reliability. Second, we used a GLMM based approach suggested by @rouder2019psychometrics. Here, a GLMM was fitted to the trial-by-trial data for each task with a fixed effect of age, a random intercept for each participant and a random slope for test day (`correct ~ age + (0+test_day|id)`)^[The notation `0+test_day` yields a separate intercept estimate for each test day and subject instead of an intercept estimate for day 1 and a slope for the difference between day 1 and day 2. As a consequence, the model estimates the correlation between the two test days instead of a correlation between an intercept and the slope for test day.]. The model yields a participant specific estimate for each test day and also estimates the correlation between the two. This correlation can be interpreted as the re-test reliability. This approach has several advantages. First, it uses the trial-by-trial data and avoids information loss that comes with data aggregation. Second, it uses hierarchical shrinkage to obtain better participant specific estimates. Finally, it allows us to get an age-independent estimate for reliability. One worry when assessing re-test reliability in developmental studies is that re-test correlations can be high because of domain general cognitive gains and not because of task-specific individual differences. By including age as a fixed effect in the model, the estimates for each participant are independent of age and so is the correlation between estimates for the two test days -- the re-test reliability.

Finally, we used that aggregated data from both test days for each participant and task to compute Pearson correlations between the different tasks. Given the small sample size in Study 1, this part of the analysis is mostly exploratory.

## Results

We found developmental effects in most of the tasks. Figure \@ref(fig:fig2) shows the data and visualizes the developmental trajectories based on the model. Figure \@ref(fig:fig3) shows the model estimates for age. In the mutual exclusivity task, performance was reliably above chance level and increased with age. For informative inference, the pattern was quite different: Performance was at chance level with only minor developmental gains. In the speaker preference task, performance was again clearly above chance with developmental gains resulting in a ceiling effect for older children. In the discourse novelty task, performance was also above chance with no clear developmental effects. The card sorting task showed the strongest developmental effects with younger children performing largely below chance and older children performing above chance.

Re-test reliability was high for most tasks (see Figure \@ref(fig:fig2)). Raw correlations between the two test sessions was above .7 for mutual exclusivity, speaker preference and discourse novelty. With .62 it was slightly lower for card sorting. The model based -- age independent -- reliability estimates yielded similar results suggesting that the tasks did capture task specific individual differences. A notable exception was the informativeness inference task, which was not reliable according to any of the methods of computing re-test correlations. We suspect the overall low variation in performance to be responsible for this.

```{r, echo = F}
cors <- read_csv("../saves/by_task_correlations.csv")
```

Most correlations between the tasks were low and ranged between *r* = -0.2 and 0.2 (see Figure \@ref(fig:fig2)). A notable exception was the correlation between mutual exclusivity and card sorting with *r* = `r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(rho)` (95% CI[`r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(lci)` - `r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(uci)`]).

(ref:figlab2) Results by task for studies 1 to 3. Each panel shows the results for one task. Regression lines show the predicted developmental trajectories (with 95% CrI) based on by-task GLMMs, with the line type indicating the study. Colored points show age group means (with 95% CI based on non-parametric bootstrap) with the different shapes corresponding to the different studies. Light shapes show the mean performance for each subject by study. Dotted line shows level of performance expected by chance.

```{r fig2, include = T, fig.align = "center", fig.cap = "(ref:figlab2)", out.width="100%"}
knitr::include_graphics("./figures/figure2.png")
```

(ref:figlab3) Model estimates (with 95% CrI) for age based on GLMMs for each task and study.

```{r fig3, include = T, fig.align = "center", fig.cap = "(ref:figlab3)", out.width="60%"}
knitr::include_graphics("./figures/figure3.png")
```

(ref:figlab4) xxx.

```{r fig4, include = T, fig.align = "center", fig.cap = "(ref:figlab4)", out.width="100%"}
knitr::include_graphics("./figures/figure4.png")
```

## Discussion

Study 1 showed that the different tasks were age appropriate and reliable. A notable exception was the informativeness inference task which generated to systematic variation in the age range we studied here. Correlations between the tasks were generally low, with the notable exception of the relation between mutual exclusivity and card sorting. Given the small sample size, we want to avoid overly strong claims, however, it was interesting to see that the relation between the two tasks tapping into common ground based inferences (speaker preference and discourse novelty) were -- if anything -- negatively correlated.

# Study 2

Based on these results od Study 1, we compiled a new set of tasks for Study 2. We retained the mutual exclusivity and card sorting tasks because of the interesting relation between the two found in Study 2. We simplified the informativeness inference task to be more age appropriate with the hope to induce more variation in performance. We removed the speaker preference and discourse novelty tasks -- despite their excellent re-test reliability -- because they seemed to be unrelated to one another and also unrelated to the other tasks. The new tasks focused on ad-hoc implicature and discourse continuity. As noted in the introduction, we had theoretical reasons to expected the ad-hoc implicature task to be related to the mutual exclusivity and informativeness inference tasks. We had no such strong predictions for the discourse continuity task.

Methods and sample size were pre-registered at https://osf.io/hp9f7. Data, analysis scripts and experiment code can be found in the associated online repository.

## Participants

Participants for Study 2 were recruited from the same general population. We collected data from `r dem%>%filter(study == "study2")%>%pull(n)` children ($m_{age}$ = `r dem%>%filter(study == "study2")%>%pull(mage)`, range$_{age}$: `r dem%>%filter(study == "study2")%>%pull(lrange)` - `r dem%>%filter(study == "study2")%>%pull(urange)`, `r dem%>%filter(study == "study2")%>%pull(female)` girls) of which `r dem%>%filter(study == "study2")%>%pull(reli_n)` were tested twice. The two test sessions were again two days apart; the longest time difference was 14 days. Data was collected between March and October 2020.

## Material and Methods

The general setup and mode of presentation was the same as in Study 1. We added two new tasks and modified the informativeness inferences task, which we will describe in detail below. The mutual exclusivity and card sorting tasks were the same as in Study 1.

### Informativeness inference

The general structure of the task was the same as in Study 1, however, we replaced the stimuli by the ones used by @frank2014inferring. We suspected that children did not treat the novel objects hanging in the tree as properties of the tree but the tree as a "container" for the novel objects. The alleged inference, however, relies on seeing the objects as properties of the referent. With the new stimuli, we emphasized that the novel objects were mere properties of the referent by making the referent more salient and more different across trials. The animal was located between two identical objects, which had different properties (see Figure \@ref(fig:fig1)). For example, the child saw two bears, one with a Pharaoh-style crown and a match in its hand, the other only with the match. The animal then turned to the object with the two properties and described it by referring to one of the properties (e.g., a bear with a [non-word]). Next, the objects disappeared, and the same objects re-appeared but this time, each of them had only one property (e.g., one bear with a crown, the other with the match). The animal then asked which of these objects had the aforementioned property (e.g., which bear has a [non-word]). We coded as correct if the child selected the object with the property that was unique to the object during labeling. The first two trials were training trials, in which each object only had one property. There were five test trials. The location of the object with the two properties in the beginning of each trial was pseudo-randomized and so was the location of the properties when the new objects appeared.

### Discourse continuity

This task was directly taken from @bohn_le_peloquin_koymen_frank_2020. Children were told that they were going to visit the animals at their place. The animal greeted the child and told them that they would show them their things. During exposure trials, the child saw three objects from three different categories (e.g., train (vehicle), drum (instrument), orange (fruit); see Figure \@ref(fig:fig1)). The animal named of the objects and asked the child to touch it. On the next exposure trial, the child saw three new objects but from the same categories (e.g., bus (vehicle), flute (instrument), apple (fruit)). The animal asked the child to touch the object from the same category as previously (only naming the object, not the category). There were 5 such exposure trials. On the following test trial, the animal used a pronoun to refer to one of the objects (i.e., can you touch *it*). We assumed that children would use the exposure trials to infer that the animal was talking about a certain category and would use this knowledge to identify the referent of the pronoun.Children received five test trials, each with a different category as the target. The position of the objects in exposure trials as well as test trials was pseudo-randomized.

### Ad-hoc implicature

This task used the general procedure and stimuli developed in @yoon2019role. The animal was located in a window, looking out over two objects (see Figure \@ref(fig:fig1)). Both objects were of the same kind, but had different properties. As properties we chose objects that were well known to children of that age range. One object had one property (A) and while the other had two (A and B). For example, objects were lunchboxes, one with an orange and the other with an orange and an apple. The animal then asked the child to hand them their object which was the one with the property that both objects shared (A). We assumed that children would pick the object with only property A because they expected the animal to name  property B if they had wanted to refer to the object with both properties. There were five test trials, preceded by two training trials in which the objects did not share a common property. The positioning of the objects (left and right) was pseudo-randomized

## Analysis

We used the same methods to analyse the data as in Study 1.

## Results

We found substantial developmental gains in all five tasks (Figure \@ref(fig:fig2) and \@ref(fig:fig3)). For mutual exclusivity and ad-hoc implicature performance was above chance across the entire age range. For the informativeness inference and discourse continuity tasks, performance was close to chance for younger children and reliably above it for older children. Like in Study 1, we found the strongest developmental effect for card sorting, with performance below chance for 3-year-olds and above chance for 4-year-olds.

Re-test reliability based on aggregated data was good for all tasks with most estimates around 0.7. The model-based reliability estimates were similar, with lower values for ad-hoc implicature and higher ones for discourse continuity. Notably, the informativeness inference task showed a much-improved re-test reliability compared to Study 1.

Correlations between tasks were generally higher compared to Study 1. In fact, confidence intervals for correlation coefficients were not overlapping with 0 except for the correlation between the discourse continuity and informativeness inference tasks (Figure \@ref(fig:fig4). Once again, we found the strongest relation between card sorting and mutual exclusivity (*r* = `r cors%>%filter(study == "study2", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(rho)`, 95% CI[`r cors%>%filter(study == "study2", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(lci)` - `r cors%>%filter(study == "study2", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(uci)`]). Other notable relations were those between card sorting and informativeness inference (*r* = `r cors%>%filter(study == "study2", task1 == "simple_inf", task2 == "card_sorting")%>%pull(rho)`, 95% CI[`r cors%>%filter(study == "study2", task1 == "simple_inf", task2 == "card_sorting")%>%pull(lci)` - `r cors%>%filter(study == "study2", task1 == "simple_inf", task2 == "card_sorting")%>%pull(uci)`]) as well as between ad-hoc implicature and informativeness inference (*r* = `r cors%>%filter(study == "study2", task1 == "simple_inf", task2 == "ad_hoc_implicature")%>%pull(rho)`, 95% CI[`r cors%>%filter(study == "study2", task1 == "simple_inf", task2 == "ad_hoc_implicature")%>%pull(lci)` - `r cors%>%filter(study == "study2", task1 == "simple_inf", task2 == "ad_hoc_implicature")%>%pull(uci)`]).

## Discussion

In Study 2 we found good results from a measurement perspective: all tasks had acceptable re-test reliability. This included the informativeness inference task which had deficits in that respect in Study 1. Higher average performance and increased variability suggest that our changes to the stimuli did make the task easier for children.

Like in Study 1, we found a relatively strong correlation between the mutual exclusivity and card sorting tasks. This corroborates the idea that these tasks share common processes. We also found substantial relations between the three utterance-based inference tasks (mutual exclusivity, ad-hoc implicature, informativeness inference). Furthermore, the correlations between tasks were lower when discourse continuity was involved -- though the numerical difference was minimal.

# Study 3

In Study 3, we focused explicitly on the relations between the different tasks. In particular, we explored the idea that the three utterance-based inference tasks share common cognitive processes. Once again, we also included the card sorting task and added a new task of analogical reasoning for which we did not expect strong relations with the other tasks. To be able to test these predictions, we collected data from a comparatively larger sample of children.

The reliability estimates from Study 1 and 2 helped us plan the sample size for Study 3. The focal tasks had a re-test reliability around 0.7. Because the highest plausible correlation between two tasks is the product of their reliabilities (higher correlations would mean that the task is more strongly related to a different task than to itself), the highest we could expect were correlations between two tasks around 0.7 * 0.7 = 0.49. We planned our sample so that we could detect correlations between two tasks of 0.3 with 95% power^[The first author drafted a pre-registration and shared it with the last author but forgot to register it at OSF. Thus, the study was not officially pre-registered.]. Data, analysis scripts and experiment code can be found in the associated online repository.

## Participants

For Study 3, we collected data from `r dem%>%filter(study == "study3")%>%pull(n)` children ($m_{age}$ = `r dem%>%filter(study == "study3")%>%pull(mage)`, range$_{age}$: `r dem%>%filter(study == "study3")%>%pull(lrange)` - `r dem%>%filter(study == "study3")%>%pull(urange)`, `r dem%>%filter(study == "study3")%>%pull(female)` girls) from the same general population. Data was collected between June and November 2021. Children were tested only once.

## Materials and Methods

From Study 2, we used the the mutual exclusivity, ad-hoc implicature, informativeness inference and card_sorting tasks. We added the relational match-to-sample task, which we now describe in more detail.

### Realtional match-to--sample

The task was modeled after and used the original stimuli from @christie2014language. The child saw three cards, one on top (the sample) and two at the bottom (the potential matches; see Figure \@ref(fig:fig1)). The experimenter guided the child through the study and read out the instructions. The child was instructed to match the sample card to one of the lower ones based on similarity, that is, they were instructed to pick the card that was "like" the sample. All cards had two geometrical shapes of the same color on them. The sample card showed to identical shapes and so did one of the potential matches. The other card showed two different shapes. We assumed that children would match the sample to the match that showed the same relation between shapes (sameness). Children received six test trial, preceded by two training trials in which one of the potential matches was identical to the sample. The position of the same-match was pseudo randomized.

## Analysis

Study 3 had only one test session. Therefore, we did not investigate re-test reliability. We estimated age effects and raw correlations between tasks in the same way as in Studies 1 and 2. We used two additional methods to investigate the structure of individual differences between tasks.

First, we used Confirmatory Factor Analysis (CFA). As outlined above, our focal model assumed that mutual exclusivity, ad-hoc implicature and informativeness inference load on a common pragmatics factor. The card sorting and relational match-to-sample tasks were included as separate factors. We used Posterior Predictive P-Values (PPP) to evaluate model fit [@lee2012basic]. A good model fit is indicated by a PPP close to 0.5 and should not be smaller than 0.1 [@cain2019fit]. We also fit two alternative models: one including only a single factor on which all tasks loaded and a second with a separate factor for each task. We compared models using WAIC (widely applicable information criterion) scores and weights [@mcelreath2018statistical]. WAIC is an indicator of out-of-sample predictive accuracy with lower values indicating better fit. WAIC weights transform WAIC values to give the probability that a particular model (out of the models considered) provides the best out-of-sample predictions. Within the focal model, we inspected the posterior estimates (with 95%CrI) for the factor loadings and the variance in the task explained by the factor for the three pragmatics tasks. In addition, we evaluated the correlations between the pragmatics factor and the other two tasks.

Second, we used computational cognitive models from the Rational Speech Act (RSA) framework to relate the three pragmatics tasks to one another [@frank2012predicting; @goodman2016pragmatic]. In contrast to the CFA model above, the RSA models are models of the tasks, and not of the data. That is, they include a schematic representation of the experimental tasks and provide a computational account of how participants make inferences in this context. RSA models see pragmatic inferences as a form of Bayesian social reasoning where the listener tries to infer the speaker' meaning (here: the intended referent) by assuming that the speaker is helpful and informative. Being helpful and informative means that the speaker chooses a message based on the probability that it would help the listener would recover the speaker's intended meaning. Thus, RSA models have a recursive structure in which the the listener reasons about a speaker who is reasoning about the listener. To avoid an infinite regress, the speaker is assumed to reason about a literal listener, who interprets words according to their literal semantics.

The studies from which we took the mutual exclusivity and informativeness inference tasks also formalized these tasks in an RSA-style model [@bohn_tessler_merrick_frank_2019; @bohn2021young]. We refer to this earlier work for more details and a mathematical description of the models. For the present study, we formalized the ad-hoc implicature task within the same RSA framework. The corresponding model code can be found in the associated online repository. All three models shared one common parameter: $\alpha$. Within the RSA framework, $\alpha$ has the conceptual role of indicating how informative the listener thinks the speaker is. This commonality offers a way of relating performance in the three tasks to one another by constraining the three models to use the same value for $\alpha$ for the other two tasks. We then used Bayesian inference to estimate the posterior distribution for $\alpha$ that best explained performance in the three tasks. To adapt this framework to the study of individual differences, we allowed a separate parameter for each participant (  $\alpha_i$). We estimated $\alpha_i$ in a hierarchical model as a deviation from a superordinate parameter: $\alpha_i \sim \mathcal{N}(\alpha_j, \sigma^\alpha)$. Given the developmental nature of our data, we defined $\alpha_j$ via a linear regression as a function of the child's age -- $\alpha_j = \beta^\alpha_0 + age \cdot \beta^\alpha_1$. Thus, the participant specific value for $\alpha$ was not only informed by the performance in the three tasks but also by the child's age.

To account for differences in difficulty between the tasks due to other factors, we also added a scale parameter to the model that scaled $\alpha$ for each task up or down in comparison to a reference task (mutual exclusivity).

$\alpha_i$ was estimated via a linear regression -- $\alpha_i = \beta^\alpha_0 + i \cdot \beta^\alpha_1$ -- in which $\beta^\alpha_0$ and $\beta^\alpha_1$ defined a general developmental trajectory

To validate this approach -- and to its advantages -- we first applied this modelling approach to the data from each test session of Study 2. This allowed us to compute the re-test reliability of $\alpha$ -

## Results

```{r}
model_comparison <- read_csv("../saves/bcfa_model_comparison.csv")
```

## Discussion

(ref:figlab5) xxx.

```{r fig5, include = T, fig.align = "center", fig.cap = "(ref:figlab5)", out.width="100%"}
knitr::include_graphics("./figures/figure5.png")
```

# General Discussion

The advantage of using a cognitive model to study individual differences is that the parameters have a more psychologically plausible interpretation compared to data analytic methods

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2022-02-19 paper/manuscript.tex
add age models

--- 2022-02-19 paper/manuscript.Rmd
@@
----
-title             : "An individual differences perspective on the development of pragmatic reasoning"
-shorttitle        : "Individual differences in pragmatic reasoning"
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  english,
+  man,floatsintext]{apa6}
+\title{An individual differences perspective on the development of pragmatic reasoning}
+\author{Manuel Bohn\textsuperscript{1}, Michael Henry Tessler\textsuperscript{2,3}, Clara Kordt\textsuperscript{4}, Tom Hausmann\textsuperscript{5}, \& Michael C. Frank\textsuperscript{6}}
+\date{}
 
-author: 
-  - name          : "Manuel Bohn"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
-    email         : "manuel_bohn@eva.mpg.de"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Analysis
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
-  - name          : "Michael Henry Tessler"
-    affiliation   : "2,3"
-    role:
-      - Analysis
-      - Writing - Review & Editing
-  - name          : "Clara Kordt"
-    affiliation   : "4"
-    role:
-      - Data collection
-  - name          : "Tom Hausmann"
-    affiliation   : "5"
-    role:
-      - Data collection
-  - name          : "Michael C. Frank"
-    affiliation   : "6"
-    role:
-      - Conceptualization
-      - Writing - Review & Editing
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={An individual differences perspective on the development of pragmatic reasoning},
+  pdfauthor={Manuel Bohn1, Michael Henry Tessler2,3, Clara Kordt4, Tom Hausmann5, \& Michael C. Frank6},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+% Manuscript styling
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
 
-affiliation:
-  - id            : "1"
-    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
-  - id            : "2"
-    institution   : "DeepMind, London, UK"
-  - id            : "3"
-    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
-  - id            : "4"
-    institution   : "Martin Luther University Halle-Wittenberg"
-  - id            : "5"
-    institution   : "Brandenburg Medical School Theodor Fontane"
-  - id            : "6"
-    institution   : "Department of Psychology, Stanford University"
+% Table formatting
+\usepackage{longtable}
+\usepackage{lscape}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
 
-authornote: |
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
+
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
+\makeatother
+\shorttitle{Individual differences in pragmatic reasoning}
+\keywords{keywords\newline\indent Word count: X}
+\usepackage{lineno}
+
+\linenumbers
+\usepackage{csquotes}
+\ifXeTeX
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\fi
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+
+\authornote{
+
 Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
@@
 M.
-Bohn received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
+Bohn received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
 749229.
@@
 H.
-Tessler was funded by the National Science Foundation SBE Postdoctoral Research Fellowship Grant No.
-1911790.
+Tessler was funded by the National Science Foundation SBE Postdoctoral Research Fellowship Grant No.~1911790.
 M.
@@
 
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+The authors made the following contributions.
+Manuel Bohn: Conceptualization, Analysis, Writing - Original Draft Preparation, Writing - Review \& Editing; Michael Henry Tessler: Analysis, Writing - Review \& Editing; Clara Kordt: Data collection; Tom Hausmann: Data collection; Michael C.
+Frank: Conceptualization, Writing - Review \& Editing.
 
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+Correspondence concerning this article should be addressed to Manuel Bohn, Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany.
+E-mail: \href{mailto:manuel_bohn@eva.mpg.de}{\nolinkurl{manuel\_bohn@eva.mpg.de}}
 
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
+}
 
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany\\\textsuperscript{2} DeepMind, London, UK\\\textsuperscript{3} Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology\\\textsuperscript{4} Martin Luther University Halle-Wittenberg\\\textsuperscript{5} Brandenburg Medical School Theodor Fontane\\\textsuperscript{6} Department of Psychology, Stanford University}
 
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
+\abstract{
+One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
 
-  One or two sentences to put the results into a more **general context**.
+Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
 
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
 
-  <!-- https://tinyurl.com/ybremelq -->
+One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
 
-keywords          : "keywords"
-wordcount         : "X"
+Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
 
-bibliography      : "../../../References/library.bib"
+One or two sentences to put the results into a more \textbf{general context}.
 
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
+Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
+}
 
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
----
+\begin{document}
+\maketitle
 
-```{r setup, include = FALSE}
-library("papaja")
-library(tidyverse)
-library(knitr)
-library(brms)
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-```
+\hypertarget{facets-of-pragmatic-reasoning}{%
+\section{Facets of pragmatic reasoning}\label{facets-of-pragmatic-reasoning}}
 
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
+\hypertarget{the-challenges-of-studying-individual-differences}{%
+\section{The challenges of studying individual differences}\label{the-challenges-of-studying-individual-differences}}
 
-```{r}
-data <- bind_rows(
-  read_csv("../data/data_r1.csv") %>%filter(task != "training") %>%mutate(study = "study1"),
-  read_csv("../data/data_r2.csv") %>%filter(task != "training")%>%mutate(study = "study2"),
-  read_csv("../data/data_r3.csv") %>%filter(task != "training")%>%mutate(study = "study3")
-  ) %>%
-  mutate(study = factor(study),
-         id = paste(study, id, sep = "_"), 
-         test_day = paste0("day", test_day))
+\hypertarget{the-current-study}{%
+\section{The current study}\label{the-current-study}}
 
-```
-# Introduction
+\hypertarget{study-1}{%
+\section{Study 1}\label{study-1}}
 
-# Facets of pragmatic reasoning
-
-# The challenges of studying individual differences
-
-# The current study
-
-# Study 1
-
-Methods and sample size were pre-registered at https://osf.io/6a723.
-All analysis scripts and data files can be found in the following repository: https://github.com/manuelbohn/pragBat.
+Methods and sample size were pre-registered at \url{https://osf.io/6a723}.
+All analysis scripts and data files can be found in the following repository: \url{https://github.com/manuelbohn/pragBat}.
 The same repository also contains the code to run the experiments.
 
-## Participants
-```{r}
-dem <- data%>%
-  group_by(id)%>%
-  summarise(study = unique(study),
-            gender = unique(gender),
-            age = unique(age),
-            testdays = length(unique(test_day)))%>%
-  group_by(study)%>%
-  summarise(n = length(id),
-            reli_n = sum(testdays == 2),
-            female = sum(gender == "f"),
-            mage = mean(age),
-            lrange = range(age)[1],
-            urange = range(age)[2])
-```
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
-For Study 1, we collected data from `r dem%>%filter(study == "study1")%>%pull(n)` children ($m_{age}$ = `r dem%>%filter(study == "study1")%>%pull(mage)`, range$_{age}$: `r dem%>%filter(study == "study1")%>%pull(lrange)` - `r dem%>%filter(study == "study1")%>%pull(urange)`, `r dem%>%filter(study == "study1")%>%pull(female)` girls) of which `r dem%>%filter(study == "study1")%>%pull(reli_n)` were tested twice.
+For Study 1, we collected data from 48 children (\(m_{age}\) = 3.99, range\(_{age}\): 3.10 - 4.99, 23 girls) of which 41 were tested twice.
 For most children, the two test sessions were two days apart; the longest time difference was six days.
-Children came from an ethnically homogeneous, mid-size German city (~550,000 inhabitants, median income €1,974 per month as of 2020); were mostly monolingual and had mixed socioeconomic backgrounds.
+Children came from an ethnically homogeneous, mid-size German city (\textasciitilde550,000 inhabitants, median income €1,974 per month as of 2020); were mostly monolingual and had mixed socioeconomic backgrounds.
 The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
@@
 
-## Material and Methods
+\hypertarget{material-and-methods}{%
+\subsection{Material and Methods}\label{material-and-methods}}
 
 The study was presented as an interactive picture book on a tablet computer.
-The tasks were programmed in `HTML/JavaScript` and run in a web browser.
+The tasks were programmed in \texttt{HTML/JavaScript} and run in a web browser.
 Pre-recorded sound files were used to address the child (one native German speaker per animal).
@@
 After a short introduction to the different animal characters, children completed the following six tasks.
-Figure \@ref(fig:fig1) shows screenshots for each task and the order in which they were presented.
+Figure \ref{fig:fig1} shows screenshots for each task and the order in which they were presented.
 
-### Training
+\hypertarget{training}{%
+\subsubsection{Training}\label{training}}
 
@@
 On each table, a familiar object was located.
-The animal asked the child to give them one of the objects (e.g., "Can you give me the car").
+The animal asked the child to give them one of the objects (e.g., ``Can you give me the car'').
 the objects were chosen so that children of the youngest age group would easily understand them (car and ball).
@@
 
-### Mutual exclusivity
+\hypertarget{mutual-exclusivity}{%
+\subsubsection{Mutual exclusivity}\label{mutual-exclusivity}}
 
-This task was directly taken from @bohn2021young.
+This task was directly taken from Bohn, Tessler, Merrick, and Frank (2021).
 The task layout and the procedure was the same as in the training.
@@
 Both object types changed from trial to trial.
-Following @bohn2021young, the familiar objects varied in terms of the likelihood that they would be familiar to children in the age range (carrot, duck, eggplant, garlic, horseshoe).
+Following Bohn et al.
+(2021), the familiar objects varied in terms of the likelihood that they would be familiar to children in the age range (carrot, duck, eggplant, garlic, horseshoe).
 For example, we assumed that most 3-year-olds would recognize a carrot, whereas fewer children would recognize a horseshoe.
@@
 
-### Informativeness inference
+\hypertarget{informativeness-inference}{%
+\subsubsection{Informativeness inference}\label{informativeness-inference}}
 
-The task was directly taken from @bohn_tessler_merrick_frank_2019.
+The task was directly taken from Bohn, Tessler, Merrick, and Frank (2022).
 Th animal was standing between two trees with objects hanging in them.
@@
 
-### Speaker preference
+\hypertarget{speaker-preference}{%
+\subsubsection{Speaker preference}\label{speaker-preference}}
 
-This task was also taken from @bohn_tessler_merrick_frank_2019.
+This task was also taken from Bohn et al.
+(2022).
 The animal was standing between the two tables, each of which had a novel object (drawn for the purpose of the study) on it.
@@
 
-### Discourse novelty
+\hypertarget{discourse-novelty}{%
+\subsubsection{Discourse novelty}\label{discourse-novelty}}
 
-This task was taken from @bohn2021young.
+This task was taken from Bohn et al.
+(2021).
 Once again, the animal was standing between the two tables.
@@
 
-### Card sorting
+\hypertarget{card-sorting}{%
+\subsubsection{Card sorting}\label{card-sorting}}
 
-This task was modeled after @zelazo2006dimensional.
+This task was modeled after Zelazo (2006).
 The child saw to cards, a blue rabbit on the left and a red boat on the right.
@@
 
-(ref:figlab1) Overview of the tasks used in Study 1 to 3.
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{./figures/figure1}
+
+}
+
+\caption{Overview of the tasks used in Study 1 to 3.
 Pictures show screenshots from each task.
@@
 Green: Executive functions.
-Green: Analogical reasoning.
+Green: Analogical reasoning.}\label{fig:fig1}
+\end{figure}
 
-```{r fig1, include = T, fig.align = "center", fig.cap = "(ref:figlab1)", out.width="100%"}
-knitr::include_graphics("./figures/figure1.png")
-```
-
-## Analysis
+\hypertarget{analysis}{%
+\subsection{Analysis}\label{analysis}}
 
@@
 
-All analysis were run in `R` [@R-base] version 4.1.2.
-Regression models were fit as Bayesian generalized linear mixed models (GLMM) using the function `brm` from the package `brms` [@burkner2017brms].
+All analysis were run in \texttt{R} (R Core Team, 2018) version 4.1.2.
+Regression models were fit as Bayesian generalized linear mixed models (GLMM) using the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017).
 We used default priors for all analysis.
@@
 To estimate developmental effects in each task, we fit a GLMM predicting correct responses (0/1) by age (centered at the mean) and trial number (also centered).
-The model included random intercepts for each participant and random slopes for trial within participants (model notation in `R`: `correct ~ age + trial + (trial|id)` ).
-For each task, we inspected and visualized the posterior distribution (mean and 95% Credible Interval (CrI)) for the age estimate.
+The model included random intercepts for each participant and random slopes for trial within participants (model notation in \texttt{R}: \texttt{correct\ \textasciitilde{}\ age\ +\ trial\ +\ (trial\textbar{}id)} ).
+For each task, we inspected and visualized the posterior distribution (mean and 95\% Credible Interval (CrI)) for the age estimate.
 
@@
 First, for each task we computed the proportion of correct trials for each individual in the two test sessions and then used Pearson correlations to quantify re-test reliability.
-Second, we used a GLMM based approach suggested by @rouder2019psychometrics.
-Here, a GLMM was fitted to the trial-by-trial data for each task with a fixed effect of age, a random intercept for each participant and a random slope for test day (`correct ~ age + (0+test_day|id)`)^[The notation `0+test_day` yields a separate intercept estimate for each test day and subject instead of an intercept estimate for day 1 and a slope for the difference between day 1 and day 2.
-As a consequence, the model estimates the correlation between the two test days instead of a correlation between an intercept and the slope for test day.].
+Second, we used a GLMM based approach suggested by Rouder and Haaf (2019).
+Here, a GLMM was fitted to the trial-by-trial data for each task with a fixed effect of age, a random intercept for each participant and a random slope for test day (\texttt{correct\ \textasciitilde{}\ age\ +\ (0+test\_day\textbar{}id)})\footnote{The notation \texttt{0+test\_day} yields a separate intercept estimate for each test day and subject instead of an intercept estimate for day 1 and a slope for the difference between day 1 and day 2.
+As a consequence, the model estimates the correlation between the two test days instead of a correlation between an intercept and the slope for test day.}.
 The model yields a participant specific estimate for each test day and also estimates the correlation between the two.
@@
 
-## Results
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
 
 We found developmental effects in most of the tasks.
-Figure \@ref(fig:fig2) shows the data and visualizes the developmental trajectories based on the model.
-Figure \@ref(fig:fig3) shows the model estimates for age.
+Figure \ref{fig:fig2} shows the data and visualizes the developmental trajectories based on the model.
+Figure \ref{fig:fig3} shows the model estimates for age.
 In the mutual exclusivity task, performance was reliably above chance level and increased with age.
@@
 
-Re-test reliability was high for most tasks (see Figure \@ref(fig:fig2)).
+Re-test reliability was high for most tasks (see Figure \ref{fig:fig2}).
 Raw correlations between the two test sessions was above .7 for mutual exclusivity, speaker preference and discourse novelty.
@@
 
-```{r, echo = F}
-cors <- read_csv("../saves/by_task_correlations.csv")
-```
+Most correlations between the tasks were low and ranged between \emph{r} = -0.2 and 0.2 (see Figure \ref{fig:fig2}).
+A notable exception was the correlation between mutual exclusivity and card sorting with \emph{r} = 0.31 (95\% CI{[}0.03 - 0.55{]}.
 
-Most correlations between the tasks were low and ranged between *r* = -0.2 and 0.2 (see Figure \@ref(fig:fig2)).
-A notable exception was the correlation between mutual exclusivity and card sorting with *r* = `r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(rho)` (95% CI[`r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(lci)` - `r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(uci)`]).
+\begin{figure}
 
-(ref:figlab2) Results by task for studies 1 to 3.
+{\centering \includegraphics[width=1\linewidth]{./figures/figure2}
+
+}
+
+\caption{Results by task for studies 1 to 3.
 Each panel shows the results for one task.
-Regression lines show the predicted developmental trajectories (with 95% CrI) based on by-task GLMMs, with the line type indicating the study.
-Colored points show age group means (with 95% CI based on non-parametric bootstrap) with the different shapes corresponding to the different studies.
+Regression lines show the predicted developmental trajectories (with 95\% CrI) based on by-task GLMMs, with the line type indicating the study.
+Colored points show age group means (with 95\% CI based on non-parametric bootstrap) with the different shapes corresponding to the different studies.
 Light shapes show the mean performance for each subject by study.
-Dotted line shows level of performance expected by chance.
+Dotted line shows level of performance expected by chance.}\label{fig:fig2}
+\end{figure}
 
-```{r fig2, include = T, fig.align = "center", fig.cap = "(ref:figlab2)", out.width="100%"}
-knitr::include_graphics("./figures/figure2.png")
-```
+\begin{figure}
 
-(ref:figlab3) Model estimates (with 95% CrI) for age based on GLMMs for each task and study.
+{\centering \includegraphics[width=0.6\linewidth]{./figures/figure3}
 
-```{r fig3, include = T, fig.align = "center", fig.cap = "(ref:figlab3)", out.width="60%"}
-knitr::include_graphics("./figures/figure3.png")
-```
+}
 
-(ref:figlab4) xxx.
+\caption{Model estimates (with 95\% CrI) for age based on GLMMs for each task and study.}\label{fig:fig3}
+\end{figure}
 
-```{r fig4, include = T, fig.align = "center", fig.cap = "(ref:figlab4)", out.width="100%"}
-knitr::include_graphics("./figures/figure4.png")
-```
+\begin{figure}
 
-## Discussion
+{\centering \includegraphics[width=1\linewidth]{./figures/figure4}
+
+}
+
+\caption{xxx.}\label{fig:fig4}
+\end{figure}
+
+\hypertarget{discussion}{%
+\subsection{Discussion}\label{discussion}}
 
@@
 
-# Study 2
+\hypertarget{study-2}{%
+\section{Study 2}\label{study-2}}
 
@@
 
-Methods and sample size were pre-registered at https://osf.io/hp9f7. Data, analysis scripts and experiment code can be found in the associated online repository.
+Methods and sample size were pre-registered at \url{https://osf.io/hp9f7}. Data, analysis scripts and experiment code can be found in the associated online repository.
 
-## Participants
+\hypertarget{participants-1}{%
+\subsection{Participants}\label{participants-1}}
 
 Participants for Study 2 were recruited from the same general population.
-We collected data from `r dem%>%filter(study == "study2")%>%pull(n)` children ($m_{age}$ = `r dem%>%filter(study == "study2")%>%pull(mage)`, range$_{age}$: `r dem%>%filter(study == "study2")%>%pull(lrange)` - `r dem%>%filter(study == "study2")%>%pull(urange)`, `r dem%>%filter(study == "study2")%>%pull(female)` girls) of which `r dem%>%filter(study == "study2")%>%pull(reli_n)` were tested twice.
+We collected data from 54 children (\(m_{age}\) = 3.97, range\(_{age}\): 3.09 - 4.93, 24 girls) of which 40 were tested twice.
 The two test sessions were again two days apart; the longest time difference was 14 days.
@@
 
-## Material and Methods
+\hypertarget{material-and-methods-1}{%
+\subsection{Material and Methods}\label{material-and-methods-1}}
 
@@
 
-### Informativeness inference
+\hypertarget{informativeness-inference-1}{%
+\subsubsection{Informativeness inference}\label{informativeness-inference-1}}
 
-The general structure of the task was the same as in Study 1, however, we replaced the stimuli by the ones used by @frank2014inferring.
-We suspected that children did not treat the novel objects hanging in the tree as properties of the tree but the tree as a "container" for the novel objects.
+The general structure of the task was the same as in Study 1, however, we replaced the stimuli by the ones used by Frank and Goodman (2014).
+We suspected that children did not treat the novel objects hanging in the tree as properties of the tree but the tree as a ``container'' for the novel objects.
 The alleged inference, however, relies on seeing the objects as properties of the referent.
 With the new stimuli, we emphasized that the novel objects were mere properties of the referent by making the referent more salient and more different across trials.
-The animal was located between two identical objects, which had different properties (see Figure \@ref(fig:fig1)).
+The animal was located between two identical objects, which had different properties (see Figure \ref{fig:fig1}).
 For example, the child saw two bears, one with a Pharaoh-style crown and a match in its hand, the other only with the match.
-The animal then turned to the object with the two properties and described it by referring to one of the properties (e.g., a bear with a [non-word]).
+The animal then turned to the object with the two properties and described it by referring to one of the properties (e.g., a bear with a {[}non-word{]}).
 Next, the objects disappeared, and the same objects re-appeared but this time, each of them had only one property (e.g., one bear with a crown, the other with the match).
-The animal then asked which of these objects had the aforementioned property (e.g., which bear has a [non-word]).
+The animal then asked which of these objects had the aforementioned property (e.g., which bear has a {[}non-word{]}).
 We coded as correct if the child selected the object with the property that was unique to the object during labeling.
@@
 
-### Discourse continuity
+\hypertarget{discourse-continuity}{%
+\subsubsection{Discourse continuity}\label{discourse-continuity}}
 
-This task was directly taken from @bohn_le_peloquin_koymen_frank_2020.
+This task was directly taken from Bohn, Le, Peloquin, Köymen, and Frank (2021).
 Children were told that they were going to visit the animals at their place.
 The animal greeted the child and told them that they would show them their things.
-During exposure trials, the child saw three objects from three different categories (e.g., train (vehicle), drum (instrument), orange (fruit); see Figure \@ref(fig:fig1)).
+During exposure trials, the child saw three objects from three different categories (e.g., train (vehicle), drum (instrument), orange (fruit); see Figure \ref{fig:fig1}).
 The animal named of the objects and asked the child to touch it.
@@
 There were 5 such exposure trials.
-On the following test trial, the animal used a pronoun to refer to one of the objects (i.e., can you touch *it*).
+On the following test trial, the animal used a pronoun to refer to one of the objects (i.e., can you touch \emph{it}).
 We assumed that children would use the exposure trials to infer that the animal was talking about a certain category and would use this knowledge to identify the referent of the pronoun.Children received five test trials, each with a different category as the target.
@@
 
-### Ad-hoc implicature
+\hypertarget{ad-hoc-implicature}{%
+\subsubsection{Ad-hoc implicature}\label{ad-hoc-implicature}}
 
-This task used the general procedure and stimuli developed in @yoon2019role.
-The animal was located in a window, looking out over two objects (see Figure \@ref(fig:fig1)).
+This task used the general procedure and stimuli developed in Yoon and Frank (2019).
+The animal was located in a window, looking out over two objects (see Figure \ref{fig:fig1}).
 Both objects were of the same kind, but had different properties.
@@
 
-## Analysis
+\hypertarget{analysis-1}{%
+\subsection{Analysis}\label{analysis-1}}
 
@@
 
-## Results
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
 
-We found substantial developmental gains in all five tasks (Figure \@ref(fig:fig2) and \@ref(fig:fig3)).
+We found substantial developmental gains in all five tasks (Figure \ref{fig:fig2} and \ref{fig:fig3}).
 For mutual exclusivity and ad-hoc implicature performance was above chance across the entire age range.
@@
 Correlations between tasks were generally higher compared to Study 1.
-In fact, confidence intervals for correlation coefficients were not overlapping with 0 except for the correlation between the discourse continuity and informativeness inference tasks (Figure \@ref(fig:fig4).
-Once again, we found the strongest relation between card sorting and mutual exclusivity (*r* = `r cors%>%filter(study == "study2", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(rho)`, 95% CI[`r cors%>%filter(study == "study2", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(lci)` - `r cors%>%filter(study == "study2", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(uci)`]).
-Other notable relations were those between card sorting and informativeness inference (*r* = `r cors%>%filter(study == "study2", task1 == "simple_inf", task2 == "card_sorting")%>%pull(rho)`, 95% CI[`r cors%>%filter(study == "study2", task1 == "simple_inf", task2 == "card_sorting")%>%pull(lci)` - `r cors%>%filter(study == "study2", task1 == "simple_inf", task2 == "card_sorting")%>%pull(uci)`]) as well as between ad-hoc implicature and informativeness inference (*r* = `r cors%>%filter(study == "study2", task1 == "simple_inf", task2 == "ad_hoc_implicature")%>%pull(rho)`, 95% CI[`r cors%>%filter(study == "study2", task1 == "simple_inf", task2 == "ad_hoc_implicature")%>%pull(lci)` - `r cors%>%filter(study == "study2", task1 == "simple_inf", task2 == "ad_hoc_implicature")%>%pull(uci)`]).
+In fact, confidence intervals for correlation coefficients were not overlapping with 0 except for the correlation between the discourse continuity and informativeness inference tasks (Figure \ref{fig:fig4}.
+Once again, we found the strongest relation between card sorting and mutual exclusivity (\emph{r} = 0.60, 95\% CI{[}0.40 - 0.75{]}).
+Other notable relations were those between card sorting and informativeness inference (\emph{r} = 0.47, 95\% CI{[}0.23 - 0.65{]}) as well as between ad-hoc implicature and informativeness inference (\emph{r} = 0.49, 95\% CI{[}0.25 - 0.67{]}).
 
-## Discussion
+\hypertarget{discussion-1}{%
+\subsection{Discussion}\label{discussion-1}}
 
@@
 
-# Study 3
+\hypertarget{study-3}{%
+\section{Study 3}\label{study-3}}
 
@@
 Because the highest plausible correlation between two tasks is the product of their reliabilities (higher correlations would mean that the task is more strongly related to a different task than to itself), the highest we could expect were correlations between two tasks around 0.7 * 0.7 = 0.49.
-We planned our sample so that we could detect correlations between two tasks of 0.3 with 95% power^[The first author drafted a pre-registration and shared it with the last author but forgot to register it at OSF.
-Thus, the study was not officially pre-registered.].
+We planned our sample so that we could detect correlations between two tasks of 0.3 with 95\% power\footnote{The first author drafted a pre-registration and shared it with the last author but forgot to register it at OSF.
+Thus, the study was not officially pre-registered.}.
 Data, analysis scripts and experiment code can be found in the associated online repository.
 
-## Participants
+\hypertarget{participants-2}{%
+\subsection{Participants}\label{participants-2}}
 
-For Study 3, we collected data from `r dem%>%filter(study == "study3")%>%pull(n)` children ($m_{age}$ = `r dem%>%filter(study == "study3")%>%pull(mage)`, range$_{age}$: `r dem%>%filter(study == "study3")%>%pull(lrange)` - `r dem%>%filter(study == "study3")%>%pull(urange)`, `r dem%>%filter(study == "study3")%>%pull(female)` girls) from the same general population.
-Data was collected between June and November 2021.
-Children were tested only once.
+For Study 3, we collected data from 126 children (\(m_{age}\) = 4.00, range\(_{age}\): 3.00 - 5.02, 74 girls) from the same general population. Data was collected between June and November 2021.
 
-## Materials and Methods
+\hypertarget{materials-and-methods}{%
+\subsection{Materials and Methods}\label{materials-and-methods}}
 
-From Study 2, we used the the mutual exclusivity, ad-hoc implicature, informativeness inference and card_sorting tasks.
+From Study 2, we used the the mutual exclusivity, ad-hoc implicature, informativeness inference and card\_sorting tasks.
 We added the relational match-to-sample task, which we now describe in more detail.
 
-### Realtional match-to--sample
+\hypertarget{realtional-match-tosample}{%
+\subsubsection{Realtional match-to--sample}\label{realtional-match-tosample}}
 
-The task was modeled after and used the original stimuli from @christie2014language.
-The child saw three cards, one on top (the sample) and two at the bottom (the potential matches; see Figure \@ref(fig:fig1)).
+The task was modeled after and used the original stimuli from Christie and Gentner (2014).
+The child saw three cards, one on top (the sample) and two at the bottom (the potential matches; see Figure \ref{fig:fig1}).
 The experimenter guided the child through the study and read out the instructions.
-The child was instructed to match the sample card to one of the lower ones based on similarity, that is, they were instructed to pick the card that was "like" the sample.
-All cards had two geometrical shapes of the same color on them.
-The sample card showed to identical shapes and so did one of the potential matches.
-The other card showed two different shapes.
-We assumed that children would match the sample to the match that showed the same relation between shapes (sameness).
-Children received six test trial, preceded by two training trials in which one of the potential matches was identical to the sample.
-The position of the same-match was pseudo randomized.
+The child was instructed to match the sample card to one of the lower ones based on similarity, that is, they were instructed to pick the card that was ``like'' the sample.
+All cards had two geometical shapes on them.
 
-## Analysis
+\hypertarget{analysis-2}{%
+\subsection{Analysis}\label{analysis-2}}
 
-Study 3 had only one test session.
-Therefore, we did not investigate re-test reliability.
-We estimated age effects and raw correlations between tasks in the same way as in Studies 1 and 2.
-We used two additional methods to investigate the structure of individual differences between tasks.
+Conf FA - evaluate: PPP, RMSAE. model comparison to alternative models based on WAIC (the lower the better) - out of sample predictive accuracy
 
-First, we used Confirmatory Factor Analysis (CFA).
-As outlined above, our focal model assumed that mutual exclusivity, ad-hoc implicature and informativeness inference load on a common pragmatics factor.
-The card sorting and relational match-to-sample tasks were included as separate factors.
-We used Posterior Predictive P-Values (PPP) to evaluate model fit [@lee2012basic].
-A good model fit is indicated by a PPP close to 0.5 and should not be smaller than 0.1 [@cain2019fit].
-We also fit two alternative models: one including only a single factor on which all tasks loaded and a second with a separate factor for each task.
-We compared models using WAIC (widely applicable information criterion) scores and weights [@mcelreath2018statistical].
-WAIC is an indicator of out-of-sample predictive accuracy with lower values indicating better fit.
-WAIC weights transform WAIC values to give the probability that a particular model (out of the models considered) provides the best out-of-sample predictions.
-Within the focal model, we inspected the posterior estimates (with 95%CrI) for the factor loadings and the variance in the task explained by the factor for the three pragmatics tasks.
-In addition, we evaluated the correlations between the pragmatics factor and the other two tasks.
+\hypertarget{results-2}{%
+\subsection{Results}\label{results-2}}
 
-Second, we used computational cognitive models from the Rational Speech Act (RSA) framework to relate the three pragmatics tasks to one another [@frank2012predicting; @goodman2016pragmatic].
-In contrast to the CFA model above, the RSA models are models of the tasks, and not of the data.
-That is, they include a schematic representation of the experimental tasks and provide a computational account of how participants make inferences in this context.
-RSA models see pragmatic inferences as a form of Bayesian social reasoning where the listener tries to infer the speaker' meaning (here: the intended referent) by assuming that the speaker is helpful and informative.
-Being helpful and informative means that the speaker chooses a message based on the probability that it would help the listener would recover the speaker's intended meaning.
-Thus, RSA models have a recursive structure in which the the listener reasons about a speaker who is reasoning about the listener.
-To avoid an infinite regress, the speaker is assumed to reason about a literal listener, who interprets words according to their literal semantics.
+\hypertarget{discussion-2}{%
+\subsection{Discussion}\label{discussion-2}}
 
-The studies from which we took the mutual exclusivity and informativeness inference tasks also formalized these tasks in an RSA-style model [@bohn_tessler_merrick_frank_2019; @bohn2021young].
-We refer to this earlier work for more details and a mathematical description of the models.
-For the present study, we formalized the ad-hoc implicature task within the same RSA framework.
-The corresponding model code can be found in the associated online repository.
-All three models shared one common parameter: $\alpha$.
-Within the RSA framework, $\alpha$ has the conceptual role of indicating how informative the listener thinks the speaker is.
-This commonality offers a way of relating performance in the three tasks to one another by constraining the three models to use the same value for $\alpha$ for the other two tasks.
-We then used Bayesian inference to estimate the posterior distribution for $\alpha$ that best explained performance in the three tasks.
-To adapt this framework to the study of individual differences, we allowed a separate parameter for each participant (  $\alpha_i$).
-We estimated $\alpha_i$ in a hierarchical model as a deviation from a superordinate parameter: $\alpha_i \sim \mathcal{N}(\alpha_j, \sigma^\alpha)$.
-Given the developmental nature of our data, we defined $\alpha_j$ via a linear regression as a function of the child's age -- $\alpha_j = \beta^\alpha_0 + age \cdot \beta^\alpha_1$.
-Thus, the participant specific value for $\alpha$ was not only informed by the performance in the three tasks but also by the child's age.
+\begin{figure}
 
-To account for differences in difficulty between the tasks due to other factors, we also added a scale parameter to the model that scaled $\alpha$ for each task up or down in comparison to a reference task (mutual exclusivity).
+{\centering \includegraphics[width=1\linewidth]{./figures/figure5}
 
-$\alpha_i$ was estimated via a linear regression -- $\alpha_i = \beta^\alpha_0 + i \cdot \beta^\alpha_1$ -- in which $\beta^\alpha_0$ and $\beta^\alpha_1$ defined a general developmental trajectory
+}
 
-To validate this approach -- and to its advantages -- we first applied this modelling approach to the data from each test session of Study 2.
-This allowed us to compute the re-test reliability of $\alpha$ -
+\caption{xxx.}\label{fig:fig5}
+\end{figure}
 
-## Results
-
-```{r}
-model_comparison <- read_csv("../saves/bcfa_model_comparison.csv")
-```
-
-## Discussion
-
-(ref:figlab5) xxx.
-
-```{r fig5, include = T, fig.align = "center", fig.cap = "(ref:figlab5)", out.width="100%"}
-knitr::include_graphics("./figures/figure5.png")
-```
-
-# General Discussion
-
-The advantage of using a cognitive model to study individual differences is that the parameters have a more psychologically plausible interpretation compared to data analytic methods
+\hypertarget{general-discussion}{%
+\section{General Discussion}\label{general-discussion}}
 
@@
 
-# References
+\hypertarget{references}{%
+\section{References}\label{references}}
 
@@
 
-<div id="refs" custom-style="Bibliography"></div>
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-bohn_le_peloquin_koymen_frank_2020}{}}%
+Bohn, M., Le, K. N., Peloquin, B., Köymen, B., \& Frank, M. C. (2021). Children's interpretation of ambiguous pronouns based on prior discourse. \emph{Developmental Science}, \emph{24}(3), e13049.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bohn2021young}{}}%
+Bohn, M., Tessler, M. H., Merrick, M., \& Frank, M. C. (2021). How young children integrate information sources to infer the meaning of words. \emph{Nature Human Behaviour}, \emph{5}(8), 1046--1054.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bohn_tessler_merrick_frank_2019}{}}%
+Bohn, M., Tessler, M.
+H., Merrick, M., \& Frank, M.
+C.
+(2022).
+Predicting pragmatic cue integration in adults' and children's inferences about novel word meanings.
+\emph{Journal of Experimental Psychology: General}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-burkner2017brms}{}}%
+Bürkner, P.-C. (2017). Brms: An r package for bayesian multilevel models using stan. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28.
+
+\leavevmode\vadjust pre{\hypertarget{ref-christie2014language}{}}%
+Christie, S., \& Gentner, D. (2014). Language helps children succeed on a classic analogy task. \emph{Cognitive Science}, \emph{38}(2), 383--397.
+
+\leavevmode\vadjust pre{\hypertarget{ref-frank2014inferring}{}}%
+Frank, M. C., \& Goodman, N. D. (2014). Inferring word meanings by assuming that speakers are informative. \emph{Cognitive Psychology}, \emph{75}, 80--96.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
+R Core Team. (2018). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rouder2019psychometrics}{}}%
+Rouder, J. N., \& Haaf, J. M. (2019). A psychometrics of individual differences in experimental tasks. \emph{Psychonomic Bulletin \& Review}, \emph{26}(2), 452--467.
+
+\leavevmode\vadjust pre{\hypertarget{ref-yoon2019role}{}}%
+Yoon, E. J., \& Frank, M. C. (2019). The role of salience in young children's processing of ad hoc implicatures. \emph{Journal of Experimental Child Psychology}, \emph{186}, 99--116.
+
+\leavevmode\vadjust pre{\hypertarget{ref-zelazo2006dimensional}{}}%
+Zelazo, P. D. (2006). The dimensional change card sort (DCCS): A method of assessing executive function in children. \emph{Nature Protocols}, \emph{1}(1), 297--301.
+
+\end{CSLReferences}
+
 \endgroup
+
+\end{document}

### 2022-02-22 analysis/analysis.Rmd
add cfa estimates

@@
 library(reshape2)
+library(coda)
+#library(ggdist)
+#library(psy)
+#library(tidyboot)
+#library(ggpubr)
+#library(blavaan)
 library(brms)
-library(psy)
-library(tidyboot)
-library(ggpubr)
-library(blavaan)
+
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
 ```
+# Data
 
@@
   mutate(study = factor(study),
-         id = paste(study, id, sep = "_"))
-
-data%>%
-  group_by(task)%>%
-  summarise(trials = length(unique(trial)))
+         id = paste(study, id, sep = "_"),
+         test_day = factor(test_day))
 ```
@@
 ```
+
 # Reliability
+
 ```{r}
@@
 ```{r}
-model <- 'prag  =~ " mutual_exclusivity + ad_hoc_implicature + simple_inf
+model <- 'prag  =~ ad_hoc_implicature + mutual_exclusivity + simple_inf
           card  =~ card_sorting
@@
 
-model2 <- 'fac  =~ mutual_exclusivity + ad_hoc_implicature+ simple_inf + card_sorting + match_to_sample'
+model2 <- 'fac  =~ ad_hoc_implicature + mutual_exclusivity+ simple_inf + card_sorting + match_to_sample'
 
@@
 ```{r}
-fit <- bcfa(model, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
-saveRDS(fit, "../saves/bcfa_prag.rds")
+# fit <- bcfa(model, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
+# saveRDS(fit, "../saves/bcfa_prag.rds")
 fit <- readRDS("../saves/bcfa_prag.rds")
 
-fit2 <- bcfa(model2, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
-saveRDS(fit2, "../saves/bcfa_single.rds")
+# fit2 <- bcfa(model2, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
+# saveRDS(fit2, "../saves/bcfa_single.rds")
 fit2 <- readRDS("../saves/bcfa_single.rds")
 
-fit3 <- bcfa(model3, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
-saveRDS(fit3, "../saves/bcfa_separate.rds")
+# fit3 <- bcfa(model3, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
+# saveRDS(fit3, "../saves/bcfa_separate.rds")
 fit3 <- readRDS("../saves/bcfa_separate.rds")
+
 ```
@@
 ```{r}
-fitmeasures(fit)%>%as_tibble(rownames = "index")
+bind_rows(
+fitmeasures(fit)%>%as_tibble(rownames = "index")%>%
+  mutate(model = "fit1"),
+fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%
+  mutate(model = "fit2"),
+fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%
+  mutate(model = "fit3")
+)%>%
+  write_csv("../saves/cfa_fit_measures.csv")
 
-x <- summary(fit, fit.measures=TRUE, standardized = TRUE, rsquare = T)
+summary(fit2, fit.measures=TRUE, standardized = TRUE, rsquare = T)
 
 blavInspect(fit, what = "postmean")%>%as_tibble(rownames = "index")%>%
-  left_join(blavInspect(fit, what = "hpd")%>%as_tibble(rownames = "index"))
+  left_join(blavInspect(fit, what = "hpd")%>%as_tibble(rownames = "index"))%>%
+  write_csv("../saves/cfa_estimates.csv")
 
@@
 ```
+
+# RSA model
+
+```{r}
+rsa_model <- readRDS("../../../Spin-off/spin-off/model/output/model_pragBat3.rds")
+```
+
+```{r}
+scale <- rsa_model %>%
+  filter(parameter == "speaker_optimality",
+         token == "scale_parameter")
+
+pscale <- ggplot(scale, aes(x = value))+
+  geom_density( alpha = 0.3, aes(fill = id), col = "black", adjust = 3)+
+  geom_vline(xintercept = 1, lty = 2, col = "black", alpha = .75)+
+  xlab("Scale parameter")+
+  ylab("Density")+
+  #facet_grid(~id, scale = "free_x")+
+  theme_few()+
+  scale_fill_viridis_d(name = "Task", labels = c("Informativeness inference", "Mutual exclusivity"))+
+  theme(legend.position = c(.6,.7))
+```
+
+```{r}
+so_est <- rsa_model %>%
+  filter(parameter == "speaker_optimality",
+         type == "subj_parameter",
+         token == "speaker_optimality")%>%
+  group_by(id)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+rsa <- data%>%
+  filter(study == "study3", task == "card_sorting" | task == "match_to_sample")%>%
+  group_by(id, task)%>%
+  summarise(mean = mean(correct))%>%
+  mutate(id = str_remove(id, "study3_"))%>%
+  ungroup()%>%
+  left_join(so_est)%>%
+    mutate(task = recode(task,
+                    `card_sorting` = "Card Sorting",
+                    `match_to_sample` = "Relational Match-to-sample"))
+
+cor <- rsa%>%
+  group_by(task)%>%
+  summarize(cor = round(cor.test(mean,mode)$estimate,2),
+            lci =  round(cor.test(mean,mode)$conf.int[1],2),
+            uci =  round(cor.test(mean,mode)$conf.int[2],2))%>%
+  mutate(label = paste0("r = ", cor, " (",lci, " - ", uci,")"))
+
+write_csv(cor, "../saves/rsa_cor_estimates.csv")
+
+prsacor <- ggplot(rsa, aes(x = mean, y = mode))+
+  #geom_abline(intercept = 2, slope = 1, lty = 2, alpha = .75)+
+  geom_point(pch = 1, alpha = .75)+
+  geom_smooth(method = "lm", col= "firebrick")+
+  geom_text(data = cor, aes(label = label),y = 4.9, x = 0.2)+
+  labs(x = "Mean proportion correct", y = "RSA model estimate (\u03b1)")+
+  facet_grid(~task)+
+  theme_few()
+
+```
+
+```{r}
+rel_rsa_model <- readRDS("../../../Spin-off/spin-off/data/rsa_rel_est.rds")
+```
+
+```{r}
+so_id_summary <- rel_rsa_model%>%
+  group_by(day,id)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))%>%
+  pivot_wider(names_from = c(day), values_from = c(mode,uci,lci))
+
+cor <- tibble(cor =  paste0(
+  "r = ",
+  round(cor.test(so_id_summary$mode_1, so_id_summary$mode_2)$estimate, 2),
+  " (",
+  round(cor.test(so_id_summary$mode_1, so_id_summary$mode_2)$conf.int[1], 2),
+  " - ",
+  round(cor.test(so_id_summary$mode_1, so_id_summary$mode_2)$conf.int[2], 2),
+  ")"
+  )
+  )
+
+prelrsa <- ggplot(so_id_summary, aes(x = mode_1, y = mode_2))+
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
+  geom_errorbar(aes(ymin = lci_2, ymax = uci_2),width = 0, alpha = .5, col = "grey")+
+  geom_errorbarh(aes(xmin = lci_1, xmax = uci_1), height = 0, alpha = .5, col = "grey")+
+    geom_point(pch = 1, size = 2)+
+    labs(x = "Day 1", y = "Day 2")+
+  scale_y_continuous(limits=c(0,8),oob=squish)+
+  #facet_grid(~chain)+
+  geom_text(data = cor, aes(label =  cor), x = 0, y =7.5, hjust = 0)+
+  #stat_cor(method = "pearson", aes(x = mode_1, y = mode_2), inherit.aes = F, size = 3)+
+  theme_few()
+```
+
+```{r}
+prsa <- ggarrange(
+  prsacor,
+  ggarrange(prelrsa, pscale, nrow = 2  , labels = c("", "C")),
+  widths = c(3,1),
+  labels = c("A", "B")
+)
+
+ggsave(plot = prsa,"../paper/figures/figure6.png", width = 10, height = 4, scale = 1.25)
+```

### 2022-02-22 analysis/summary.Rmd
add cfa estimates

@@
 ```{r}
-p31%>%
+prsa <- p31%>%
   filter(task == "card_sorting" | task == "match_to_sample")%>%
@@
   ungroup()%>%
-  left_join(rsa_est)%>%
-  ggplot(aes(x = mean, y = mode))+
+  left_join(rsa_est)
+
+corrsa <- cor.test(prsa%>%filter(task == "card_sorting")%>%pull(mode), prsa%>%filter(task == "card_sorting")%>%pull(mean))
+
+ggplot(prsa, aes(x = mean, y = mode))+
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = .75)+

### 2022-02-22 paper/manuscript.Rmd
add cfa estimates

@@
 
-(ref:figlab4) xxx.
+(ref:figlab4) Re-test and task correlations for Study 1 (A), 2 (B) and 3 (C).
+The diagonal in A and B shows the re-test reliability based on aggregated raw test scores (top row) and based on a GLMM that accounted for participant age (see main text for details).
 
@@
 
-From Study 2, we used the the mutual exclusivity, ad-hoc implicature, informativeness inference and card_sorting tasks.
+From Study 2, we used the the mutual exclusivity, ad-hoc implicature, informativeness inference and card sorting tasks.
 We added the relational match-to-sample task, which we now describe in more detail.
 
-### Realtional match-to--sample
+### Relational match-to-sample
 
@@
 First, we used Confirmatory Factor Analysis (CFA).
+Models were fit in a Bayesian framework using the `R` package `blavaan` [@merkle2018blavaan] using default priors.
 As outlined above, our focal model assumed that mutual exclusivity, ad-hoc implicature and informativeness inference load on a common pragmatics factor.
@@
 For the present study, we formalized the ad-hoc implicature task within the same RSA framework.
-The corresponding model code can be found in the associated online repository.
 All three models shared one common parameter: $\alpha$.
 Within the RSA framework, $\alpha$ has the conceptual role of indicating how informative the listener thinks the speaker is.
-This commonality offers a way of relating performance in the three tasks to one another by constraining the three models to use the same value for $\alpha$ for the other two tasks.
+
+This commonality offers a way of relating performance in the three tasks to one another by constraining the three models to use the same value for $\alpha$.
 We then used Bayesian inference to estimate the posterior distribution for $\alpha$ that best explained performance in the three tasks.
-To adapt this framework to the study of individual differences, we allowed a separate parameter for each participant (  $\alpha_i$).
-We estimated $\alpha_i$ in a hierarchical model as a deviation from a superordinate parameter: $\alpha_i \sim \mathcal{N}(\alpha_j, \sigma^\alpha)$.
-Given the developmental nature of our data, we defined $\alpha_j$ via a linear regression as a function of the child's age -- $\alpha_j = \beta^\alpha_0 + age \cdot \beta^\alpha_1$.
-Thus, the participant specific value for $\alpha$ was not only informed by the performance in the three tasks but also by the child's age.
+To adapt this framework to the study of individual differences, we allowed a separate parameter for each participant ($\alpha_i$).
+We estimated $\alpha_i$ in a hierarchical model as a deviation from a hyper parameter: $\alpha_i \sim \mathcal{N}(\alpha_j, \sigma^\alpha)$.
+Given the developmental nature of our data, we defined $\alpha_j$ via a linear regression as a function of the child's age ($age_i$): $\alpha_j = \beta^\alpha_0 + age_i \cdot \beta^\alpha_1$.
+Thus, the participant specific value for $\alpha$ was not only constrained by the performance in the three tasks but also by the child's age.
 
-To account for differences in difficulty between the tasks due to other factors, we also added a scale parameter to the model that scaled $\alpha$ for each task up or down in comparison to a reference task (mutual exclusivity).
+To account for differences in difficulty between the tasks due to other factors, we added a scale parameter to the model that adjusted $\alpha$ for each task in comparison to a reference task (ad-hoc implicature).
 
-$\alpha_i$ was estimated via a linear regression -- $\alpha_i = \beta^\alpha_0 + i \cdot \beta^\alpha_1$ -- in which $\beta^\alpha_0$ and $\beta^\alpha_1$ defined a general developmental trajectory
-
-To validate this approach -- and to its advantages -- we first applied this modelling approach to the data from each test session of Study 2.
-This allowed us to compute the re-test reliability of $\alpha$ -
+To validate this approach, we first applied this model to the data from Study 2 -- separate for each test session.
+This allowed us to compute the re-test reliability of $\alpha$ and see if it captures individual differences equally well compared to the raw test scores.
+After finding excellent re-test reliability, we applied it to the data from Study 3 and correlated the results with the the card sorting and relational match-to sample tasks.
+For these correlational analysis, we converted the posterior distribution for each participant into a single value by taking the mode (and 95% highest density interval -- HDI).
+The cognitive models were implemented in `WebPPL` [@dippl] and the corresponding code, including information on prior distributions, can be found in the associated online repository.
 
@@
 
+The age effects in Study 3 largely replicate those of Study 2 for the four overlapping tasks (see Figure \@ref(fig:fig2) and \@ref(fig:fig3).
+There were no substantial developmental gains in the newly added relational match-to-sample task and performance was close to chance for both age groups.
+Thus -- in the absence of information on re-test reliability -- it is unclear if the variation in performance reflects systematic individual differences in analogical reasoning or not.
+
+Overall, the correlations between the tasks were lower compared to Study 2.
+This was to some extend expected given that there were only half the number of trials per task in Study 3 and, with that, less room for capturing individual differences.
+Nevertheless, the overall pattern rsembles that found in Study 2 (Figure \@ref(fig:fig4)).
+We saw the strongest bi-variate relation between the mutual exclusivity and the ad-hoc implicature task (*r* = `r cors%>%filter(study == "study3", task1 == "mutual_exclusivity", task2 == "ad_hoc_implicature")%>%pull(rho)`, 95% CI[`r cors%>%filter(study == "study3", task1 == "mutual_exclusivity", task2 == "ad_hoc_implicature")%>%pull(lci)` - `r cors%>%filter(study == "study3", task1 == "mutual_exclusivity", task2 == "ad_hoc_implicature")%>%pull(uci)`]) followed by ad-hoc implicature and card sorting (*r* = `r cors%>%filter(study == "study3", task1 == "card_sorting", task2 == "ad_hoc_implicature")%>%pull(rho)`, 95% CI[`r cors%>%filter(study == "study3", task1 == "card_sorting", task2 == "ad_hoc_implicature")%>%pull(lci)` - `r cors%>%filter(study == "study3", task1 == "card_sorting", task2 == "ad_hoc_implicature")%>%pull(uci)`]).
+The relational match-to-sample task showed no substantial correlations with any of the other tasks.
+
 ```{r}
 model_comparison <- read_csv("../saves/bcfa_model_comparison.csv")
+
+model_fit <- read_csv("../saves/cfa_fit_measures.csv")
+
+model_est <- read_csv("../saves/cfa_estimates.csv")
 ```
 
-## Discussion
-
-(ref:figlab5) xxx.
+(ref:figlab5) Graphical overview of CFA model for Study 3.
+Arrows from latent variable (circles) to observed variable (rectangles) show factor loadings.
+Bottom arrows to observed variables give the residual variance not explained by the factor.
+Bent arrows between latent variables show correlations.
+Bottom rows show model estimates with 95% CrI.
+Top rows show standardized estimates (bold if 95 % CrI does not include 0).
 
@@
 
+Our focal model in the confirmatory factor analysis including a latent factor for pragmatic reasoning fit the data well (PPP = `r round(model_fit%>%filter(index == "ppp", model == "fit1")%>%pull(value),3)`) and with a WAIC of `r round(model_comparison%>%filter(model == "fit1")%>%pull(waic),2)` (se = `r round(model_comparison%>%filter(model == "fit1")%>%pull(waic_se),2)`, weight = `r round(model_comparison%>%filter(model == "fit1")%>%pull(waic_weight),2)`) better compared to the two alternative models (individual factors model: PPP = `r round(model_fit%>%filter(index == "ppp", model == "fit3")%>%pull(value),3)`, WAIC = `r round(model_comparison%>%filter(model == "fit3")%>%pull(waic),2)`, se = `r round(model_comparison%>%filter(model == "fit3")%>%pull(waic_se),2)`, weight = `r round(model_comparison%>%filter(model == "fit3")%>%pull(waic_weight),2)`; one factor model: PPP = `r round(model_fit%>%filter(index == "ppp", model == "fit2")%>%pull(value),3)`, WAIC = `r round(model_comparison%>%filter(model == "fit2")%>%pull(waic),2)`, se = `r round(model_comparison%>%filter(model == "fit2")%>%pull(waic_se),2)`, weight = `r round(model_comparison%>%filter(model == "fit2")%>%pull(waic_weight),2)`).
+Figure \@ref(fig:fig5) shows that factor loadings for the individual tasks as well as their residual variance.
+The latent pragmatic reasoning factor best explained the mutual exclusivity task, followed by the ad-hoc implicature and the informativeness inference task.
+The correlation between pragmatic reasoning and executive functions (indicated by the card sorting task) was estimated to be reliably different from zero (*r* = 0.33; model estimate = `r round(model_est%>%filter(index == "prag~~card")%>%pull(value),2)`, 95% CrI [`r round(model_est%>%filter(index == "prag~~card")%>%pull(lower),2)` - `r round(model_est%>%filter(index == "prag~~card")%>%pull(upper),2)`]).
+There was no systematic relation between pragmatic reasoning and analogical reasoning (as indicated by the relational match-to-sample task): *r* = 0.06; model estimate = `r round(model_est%>%filter(index == "prag~~match")%>%pull(value),2)`, 95% CrI [`r round(model_est%>%filter(index == "prag~~match")%>%pull(lower),2)` - `r round(model_est%>%filter(index == "prag~~match")%>%pull(upper),2)`].
+However, the latter result should be taken with a groin of salt given the unknown psychometric properties of the relational match-to-sample task.
+
+```{r}
+
+rsa_cor <- read_csv("../saves/rsa_cor_estimates.csv")
+
+```
+
+The results of the analysis based on the cognitive model yield similar conclusions compared to the confirmatory factor analysis (Figure \@ref(fig:fig6)).
+Participant specific speaker informativeness parameters ($\alpha$) were correlated with performance in the card sorting (*r* = `r rsa_cor%>%filter(task == "Card Sorting")%>%pull(cor)`, 95% CI[`r rsa_cor%>%filter(task == "Card Sorting")%>%pull(lci)` - `r rsa_cor%>%filter(task == "Card Sorting")%>%pull(uci)`]) but not the relational match-to-sample task (*r* = `r rsa_cor%>%filter(task == "Relational Match-to-sample")%>%pull(cor)`, 95% CI[`r rsa_cor%>%filter(task == "Relational Match-to-sample")%>%pull(lci)` - `r rsa_cor%>%filter(task == "Relational Match-to-sample")%>%pull(uci)`]).
+The same limitations apply to the latter result as for the confirmatory factor analysis.
+
+(ref:figlab6) Results of cognitive model analyses.
+A: Correlation between the speaker informativeness parameter $\alpha$ and the paerformance in the card sorting and relational match to sample tasks.
+Regression line (with 95% CI) is based on a linear model.
+B: Re-test reliability for $\alpha$ based on the data from Study 2.
+C: Scale parameter for $\alpha$ in relation to the ad-hoc implicature task.
+Values below 1 indicate a more difficult task, values above 1 an easier task.
+Correlation coefficients show Pearson correlation with 95% CI.
+
+```{r fig6, include = T, fig.align = "center", fig.cap = "(ref:figlab6)", out.width="100%"}
+knitr::include_graphics("./figures/figure6.png")
+```
+
+## Discussion
+
 # General Discussion
 
-The advantage of using a cognitive model to study individual differences is that the parameters have a more psychologically plausible interpretation compared to data analytic methods
+Present six, reliable (even when corrected for age) and ready to use tasks that cover a range of phenomena subsumed under pragmatic inference.
+WE divided them up into utternace based and interaction based and more systematic realtions between utternace based.
+Nevertehless, the others need to be explored more
+
+Across studies we saw relations between utterance based inference tasks.
+From different theoretical perspectives, they might be more or less obvious, especially for ME.
+From our perspective they make a lot of sense - we explicate this view in our model.
+
+Why is there this relation with card sorting?
+The advantage of using a cognitive model to study individual differences is that the parameters have a more psychologically plausible interpretation compared to data analytic methods.
+If e take the model for real, we can speculate why card sorting matters.
+Switching rules requires seeing stimuli in different light - focus on different aspect of them, consider alternative ways of seeing them, not go with what you did previously.
+The inference in the model is driven by not going just with what is true but  considering alternative utterances - some commonalities here that might be responsible - need to be modeled explicitly and contrasted to alternative views.
+(check other theoretical accounts on that)
 

### 2022-02-22 paper/manuscript.tex
add cfa estimates

@@
 Most correlations between the tasks were low and ranged between \emph{r} = -0.2 and 0.2 (see Figure \ref{fig:fig2}).
-A notable exception was the correlation between mutual exclusivity and card sorting with \emph{r} = 0.31 (95\% CI{[}0.03 - 0.55{]}.
+A notable exception was the correlation between mutual exclusivity and card sorting with \emph{r} = 0.31 (95\% CI{[}0.03 - 0.55{]}).
 
@@
 
-\caption{xxx.}\label{fig:fig4}
+\caption{Re-test and task correlations for Study 1 (A), 2 (B) and 3 (C).
+The diagonal in A and B shows the re-test reliability based on aggregated raw test scores (top row) and based on a GLMM that accounted for participant age (see main text for details).}\label{fig:fig4}
 \end{figure}
@@
 
-For Study 3, we collected data from 126 children (\(m_{age}\) = 4.00, range\(_{age}\): 3.00 - 5.02, 74 girls) from the same general population. Data was collected between June and November 2021.
+For Study 3, we collected data from 126 children (\(m_{age}\) = 4.00, range\(_{age}\): 3.00 - 5.02, 74 girls) from the same general population.
+Data was collected between June and November 2021.
+Children were tested only once.
 
@@
 
-From Study 2, we used the the mutual exclusivity, ad-hoc implicature, informativeness inference and card\_sorting tasks.
+From Study 2, we used the the mutual exclusivity, ad-hoc implicature, informativeness inference and card sorting tasks.
 We added the relational match-to-sample task, which we now describe in more detail.
 
-\hypertarget{realtional-match-tosample}{%
-\subsubsection{Realtional match-to--sample}\label{realtional-match-tosample}}
+\hypertarget{relational-match-to-sample}{%
+\subsubsection{Relational match-to-sample}\label{relational-match-to-sample}}
 
@@
 The child was instructed to match the sample card to one of the lower ones based on similarity, that is, they were instructed to pick the card that was ``like'' the sample.
-All cards had two geometical shapes on them.
+All cards had two geometrical shapes of the same color on them.
+The sample card showed to identical shapes and so did one of the potential matches.
+The other card showed two different shapes.
+We assumed that children would match the sample to the match that showed the same relation between shapes (sameness).
+Children received six test trial, preceded by two training trials in which one of the potential matches was identical to the sample.
+The position of the same-match was pseudo randomized.
 
@@
 
-Conf FA - evaluate: PPP, RMSAE. model comparison to alternative models based on WAIC (the lower the better) - out of sample predictive accuracy
+Study 3 had only one test session.
+Therefore, we did not investigate re-test reliability.
+We estimated age effects and raw correlations between tasks in the same way as in Studies 1 and 2.
+We used two additional methods to investigate the structure of individual differences between tasks.
+
+First, we used Confirmatory Factor Analysis (CFA).
+Models were fit in a Bayesian framework using the \texttt{R} package \texttt{blavaan} (Merkle \& Rosseel, 2018) using default priors.
+As outlined above, our focal model assumed that mutual exclusivity, ad-hoc implicature and informativeness inference load on a common pragmatics factor.
+The card sorting and relational match-to-sample tasks were included as separate factors.
+We used Posterior Predictive P-Values (PPP) to evaluate model fit (Lee \& Song, 2012).
+A good model fit is indicated by a PPP close to 0.5 and should not be smaller than 0.1 (Cain \& Zhang, 2019).
+We also fit two alternative models: one including only a single factor on which all tasks loaded and a second with a separate factor for each task.
+We compared models using WAIC (widely applicable information criterion) scores and weights (McElreath, 2018).
+WAIC is an indicator of out-of-sample predictive accuracy with lower values indicating better fit.
+WAIC weights transform WAIC values to give the probability that a particular model (out of the models considered) provides the best out-of-sample predictions.
+Within the focal model, we inspected the posterior estimates (with 95\%CrI) for the factor loadings and the variance in the task explained by the factor for the three pragmatics tasks.
+In addition, we evaluated the correlations between the pragmatics factor and the other two tasks.
+
+Second, we used computational cognitive models from the Rational Speech Act (RSA) framework to relate the three pragmatics tasks to one another (Frank \& Goodman, 2012; Goodman \& Frank, 2016).
+In contrast to the CFA model above, the RSA models are models of the tasks, and not of the data.
+That is, they include a schematic representation of the experimental tasks and provide a computational account of how participants make inferences in this context.
+RSA models see pragmatic inferences as a form of Bayesian social reasoning where the listener tries to infer the speaker' meaning (here: the intended referent) by assuming that the speaker is helpful and informative.
+Being helpful and informative means that the speaker chooses a message based on the probability that it would help the listener would recover the speaker's intended meaning.
+Thus, RSA models have a recursive structure in which the the listener reasons about a speaker who is reasoning about the listener.
+To avoid an infinite regress, the speaker is assumed to reason about a literal listener, who interprets words according to their literal semantics.
+
+The studies from which we took the mutual exclusivity and informativeness inference tasks also formalized these tasks in an RSA-style model (Bohn et al., 2021, 2022).
+We refer to this earlier work for more details and a mathematical description of the models.
+For the present study, we formalized the ad-hoc implicature task within the same RSA framework.
+All three models shared one common parameter: \(\alpha\).
+Within the RSA framework, \(\alpha\) has the conceptual role of indicating how informative the listener thinks the speaker is.
+
+This commonality offers a way of relating performance in the three tasks to one another by constraining the three models to use the same value for \(\alpha\).
+We then used Bayesian inference to estimate the posterior distribution for \(\alpha\) that best explained performance in the three tasks.
+To adapt this framework to the study of individual differences, we allowed a separate parameter for each participant (\(\alpha_i\)).
+We estimated \(\alpha_i\) in a hierarchical model as a deviation from a hyper parameter: \(\alpha_i \sim \mathcal{N}(\alpha_j, \sigma^\alpha)\).
+Given the developmental nature of our data, we defined \(\alpha_j\) via a linear regression as a function of the child's age (\(age_i\)): \(\alpha_j = \beta^\alpha_0 + age_i \cdot \beta^\alpha_1\).
+Thus, the participant specific value for \(\alpha\) was not only constrained by the performance in the three tasks but also by the child's age.
+
+To account for differences in difficulty between the tasks due to other factors, we added a scale parameter to the model that adjusted \(\alpha\) for each task in comparison to a reference task (ad-hoc implicature).
+
+To validate this approach, we first applied this model to the data from Study 2 -- separate for each test session.
+This allowed us to compute the re-test reliability of \(\alpha\) and see if it captures individual differences equally well compared to the raw test scores.
+After finding excellent re-test reliability, we applied it to the data from Study 3 and correlated the results with the the card sorting and relational match-to sample tasks.
+For these correlational analysis, we converted the posterior distribution for each participant into a single value by taking the mode (and 95\% highest density interval -- HDI).
+The cognitive models were implemented in \texttt{WebPPL} (Goodman \& Stuhlmüller, 2014) and the corresponding code, including information on prior distributions, can be found in the associated online repository.
 
@@
 
-\hypertarget{discussion-2}{%
-\subsection{Discussion}\label{discussion-2}}
+The age effects in Study 3 largely replicate those of Study 2 for the four overlapping tasks (see Figure \ref{fig:fig2} and \ref{fig:fig3}.
+There were no substantial developmental gains in the newly added relational match-to-sample task and performance was close to chance for both age groups.
+Thus -- in the absence of information on re-test reliability -- it is unclear if the variation in performance reflects systematic individual differences in analogical reasoning or not.
+
+Overall, the correlations between the tasks were lower compared to Study 2.
+This was to some extend expected given that there were only half the number of trials per task in Study 3 and, with that, less room for capturing individual differences.
+Nevertheless, the overall pattern rsembles that found in Study 2 (Figure \ref{fig:fig4}).
+We saw the strongest bi-variate relation between the mutual exclusivity and the ad-hoc implicature task (\emph{r} = 0.33, 95\% CI{[}0.16 - 0.48{]}) followed by ad-hoc implicature and card sorting (\emph{r} = 0.28, 95\% CI{[}0.11 - 0.44{]}).
+The relational match-to-sample task showed no substantial correlations with any of the other tasks.
 
@@
 
-\caption{xxx.}\label{fig:fig5}
+\caption{Graphical overview of CFA model for Study 3.
+Arrows from latent variable (circles) to observed variable (rectangles) show factor loadings.
+Bottom arrows to observed variables give the residual variance not explained by the factor.
+Bent arrows between latent variables show correlations.
+Bottom rows show model estimates with 95\% CrI.
+Top rows show standardized estimates (bold if 95 \% CrI does not include 0).}\label{fig:fig5}
 \end{figure}
+
+Our focal model in the confirmatory factor analysis including a latent factor for pragmatic reasoning fit the data well (PPP = 0.50) and with a WAIC of 1,753.45 (se = 32.02, weight = 0.74) better compared to the two alternative models (individual factors model: PPP = 0.51, WAIC = 1,756.48, se = 32.51, weight = 0.16; one factor model: PPP = 0.36, WAIC = 1,758.10, se = 32.37, weight = 0.07).
+Figure \ref{fig:fig5} shows that factor loadings for the individual tasks as well as their residual variance.
+The latent pragmatic reasoning factor best explained the mutual exclusivity task, followed by the ad-hoc implicature and the informativeness inference task.
+The correlation between pragmatic reasoning and executive functions (indicated by the card sorting task) was estimated to be reliably different from zero (\emph{r} = 0.33; model estimate = 0.20, 95\% CrI {[}0.02 - 0.39{]}).
+There was no systematic relation between pragmatic reasoning and analogical reasoning (as indicated by the relational match-to-sample task): \emph{r} = 0.06; model estimate = 0.04, 95\% CrI {[}-0.11 - 0.18{]}.
+However, the latter result should be taken with a groin of salt given the unknown psychometric properties of the relational match-to-sample task.
+
+The results of the analysis based on the cognitive model yield similar conclusions compared to the confirmatory factor analysis.
+Participant specific speaker informativeness parameters (\(\alpha\)) were correlated with performance in the card sorting (\emph{r} = 0.31, 95\% CI{[}0.15 - 0.47{]}) but not the relational match-to-sample task (\emph{r} = 0.03, 95\% CI{[}-0.15 - 0.20{]})
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{./figures/figure6}
+
+}
+
+\caption{Results of cognitive model analyses.
+A: Correlation between the speaker informativeness parameter \(\alpha\) and the paerformance in the card sorting and relational match to sample tasks.
+Regression line (with 95\% CI) is based on a linear model.
+B: Re-test reliability for \(\alpha\) based on the data from Study 2.
+C: Scale parameter for \(\alpha\) in relation to the ad-hoc implicature task.
+Values below 1 indicate a more difficult task, values above 1 an easier task.
+Correlation coefficients show Pearson correlation with 95\% CI.}\label{fig:fig6}
+\end{figure}
+
+\hypertarget{discussion-2}{%
+\subsection{Discussion}\label{discussion-2}}
 
@@
 \section{General Discussion}\label{general-discussion}}
+
+Present six, reliable (even when corrected for age) and ready to use tasks that cover a range of phenomena subsumed under pragmatic inference.
+WE divided them up into utternace based and interaction based and more systematic realtions between utternace based.
+Nevertehless, the others need to be explored more
+
+Across studies we saw relations between utterance based inference tasks.
+From different theoretical perspectives, they might be more or less obvious, especially for ME.
+From our perspective they make a lot of sense - we explicate this view in our model.
+
+Why is there this relation with card sorting?
+The advantage of using a cognitive model to study individual differences is that the parameters have a more psychologically plausible interpretation compared to data analytic methods.
+If e take the model for real, we can speculate why card sorting matters.
+Switching rules requires seeing stimuli in different light - focus on different aspect of them, consider alternative ways of seeing them, not go with what you did previously.
+The inference in the model is driven by not going just with what is true but considering alternative utterances - some commonalities here that might be responsible - need to be modeled explicitly and contrasted to alternative views.
+(check other theoretical accounts on that)
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-cain2019fit}{}}%
+Cain, M.
+K., \& Zhang, Z.
+(2019).
+Fit for a bayesian: An evaluation of PPP and DIC for structural equation modeling.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{26}(1), 39--50.
+
 \leavevmode\vadjust pre{\hypertarget{ref-christie2014language}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-frank2012predicting}{}}%
+Frank, M. C., \& Goodman, N. D. (2012). Predicting pragmatic reasoning in language games. \emph{Science}, \emph{336}(6084), 998--998.
+
 \leavevmode\vadjust pre{\hypertarget{ref-frank2014inferring}{}}%
 Frank, M. C., \& Goodman, N. D. (2014). Inferring word meanings by assuming that speakers are informative. \emph{Cognitive Psychology}, \emph{75}, 80--96.
+
+\leavevmode\vadjust pre{\hypertarget{ref-goodman2016pragmatic}{}}%
+Goodman, N. D., \& Frank, M. C. (2016). Pragmatic language interpretation as probabilistic inference. \emph{Trends in Cognitive Sciences}, \emph{20}(11), 818--829.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dippl}{}}%
+Goodman, N. D., \& Stuhlmüller, A. (2014). {The design and implementation of probabilistic programming languages}. \url{http://dippl.org}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lee2012basic}{}}%
+Lee, S.-Y., \& Song, X.-Y. (2012). \emph{Basic and advanced bayesian structural equation modeling: With applications in the medical and behavioral sciences}. John Wiley \& Sons.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcelreath2018statistical}{}}%
+McElreath, R. (2018). \emph{Statistical rethinking: A bayesian course with examples in r and stan}. Chapman; Hall/CRC.
+
+\leavevmode\vadjust pre{\hypertarget{ref-merkle2018blavaan}{}}%
+Merkle, E. C., \& Rosseel, Y. (2018). Blavaan: Bayesian structural equation models via parameter expansion. \emph{Journal of Statistical Software}, \emph{85}, 1--30.
 

### 2022-02-25 paper/manuscript.Rmd
first draft intor for paper

@@
 ---
-title             : "An individual differences perspective on the development of pragmatic reasoning"
+title             : "An individual differences perspective on the development of pragmatic reasoning in the preschool years"
 shorttitle        : "Individual differences in pragmatic reasoning"
@@
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
   We are very thankful to Stella Christie for sharing the material for the relational match-to-sample task with us.
@@
 
-# Facets of pragmatic reasoning
+Communication predates language.
+Before children produce their first words, they communicate with the world around them using vocalizations and gestures [@bruner1974communication; @bates1979emergence].
+The process of language learning recruits many of the social-cognitive processes that underlay pre-verbal communication [@bohn2019pervasive; @tomasello2009constructing; @clark2009first].
+Even for proficient language users is communication not reducible to the words being exchanged.
+The common thread running through these different aspects of human communication is its inferential nature: what a speaker means -- verbal or otherwise -- is underdetermined by the parts that make up the utterance.
+It takes contextual social inferences to recover the intended meaning [@grice1991studies; @clark1996using; @sperber2001relevance; @levinson2000presumptive].
+These contextual social inferences are often referred to as *pragmatic* inferences [e.g., @bohn2019pervasive].
 
-# The challenges of studying individual differences
+The development of pragmatics has been widely studied in recent years [for a recent review see @bohn2019pervasive].
+This research covers a range of different phenomena ranging from so-called *pure pragmatics* [@matthews2014pragmatic] in non-verbal communication in infancy to sophisticated linguistic inferences developing much later [@huang2009online; @papafragou2016scalar].
+A growing portion of this work is devoted to studying individual differences [@matthews2018individual; @wilson2021pragmatic].
+The motivation behind this is twofold: on the one hand, individual differences offer insights into the underlying psychological processes [@kidd2018individual; @matthews2018individual; @wilson2022novel].
+On the other hand, deficits in pragmatic abilities have been linked to behavioral problems and forms of language impairment [@helland2014stable].
 
-# The current study
+In their recent review of individual differences in children's pragmatic ability, @matthews2018individual identified three issues that significantly limit what we can learn from individual differences research.
+First, most studies have insufficient sample sizes so that small and medium sized correlations among pragmatics tasks and between pragmatics tasks and measures for other cognitive abilities cannot be reliably detected.
+Second, the tasks used to assess pragmatic abilities often have poor or unknown psychometric properties.
+For example, many tasks only have a single trial and are therefore unable to capture variation between children.
+Reliability is not assessed, making it unclear if the task captures stable characteristics [see also @russell2008assessing].
+Third, the cognitive processes underlying pragmatic inferences in a particular task are underspecified.
+As a consequence, there is no clear rationale for why a task should correlate with another cognitive measure.
+
+The studies presented here directly address the issues identified by Matthews and colleagues [@matthews2018individual].
+We identified six pragmatic reasoning tasks in children between three and five years of age and investigated their psychometric properties, in particular their re-test reliability.
+Reliable tasks are a necessary precondition for meaningful individual differences research [@hedge2018reliability; @fried2018measurement].
+Next, we investigated the relations among different pragmatic reasoning tasks as well as between pragmatic reasoning and executive functions in a sample large enough to detect small to medium sized correlations.
+Finally, we introduced computational cognitive models of pragmatic reasoning to the study of individual differences.
+This allowed us to formalize the cognitive processes we think underlay pragmatic reasoning and thereby provide a substantive theoretical account for why certain pragmatic reasoning tasks are related to one another and why executive functions relate to them.
+
+The six tasks we selected were developmental adaptations of referential communication games inspired by research in experimental pragmatics [@noveck2008experimental; @noveck2004experimental].
+They all share a common trial-by-trial structure in which the test event always involved an agent producing an ambiguous utterance that children had to resolve using pragmatic reasoning.
+This allowed us to run multiple trials per task, and with that, to capture individual differences.
+We grouped the tasks into two broad categories (Figure \@ref(fig:fig1)).
+On the one hand, utterance-based tasks asked children to derive inferences from the words and gestures the speaker produced in context.
+On the other hand, common ground/discourse-based tasks asked children to derive inferences from the social interaction that preceded the utterance.
+
+For the utterance-based category, we selected a mutual exclusivity, informativeness inference, and ad-hoc implicature task.
+Mutual exclusivity -- or principle of contrast -- describes the phenomenon that children tend to map a novel word to an unknown object [@markman1988children; @halberda2003development; @bion2013fast; @merriman1989mutual; @clark1988logic; @lewis2020role].
+Informativeness inferences describe situations in which children identify the referent of a novel word by assuming that the speaker is trying to be informative.
+Being informative translates to using words that have smaller extensions in context [@frank2014inferring].
+Ad-hoc implicature describes inferences that ask the child to contrast an utterance with alternatives that the speaker could have used but did not [@stiller2015ad; @yoon2019role; @katsos2011pragmatic].
+
+For the discourse-based category, we selected a speaker preference, discourse novelty and discourse continuity task.
+In the speaker preference task, the child had to track the preference of a speaker in order to identify the referent of a novel word [@saylor2009preschoolers].
+Discourse novelty refers to a situation in which the child tracks the temporal appearance of objects in context and expects the speaker to refer to objects that are new in context [@akhtar1996role; @diesendruck2004two].
+In the discourse continuity task, the child had to infer and track the topic of an ongoing conversation to resolve ambiguity [@bohn_le_peloquin_koymen_frank_2020; @akhtar2002relevance].
+
+In addition to the pragmatics tasks, we also included a tasks for executive functions [@zelazo2006dimensional] and of analogical reasoning [@christie2014language].
+Executive functions refer to a family of top-down mental processes that enable us to inhibit automatic or intuitive responses and allow us to concentrate and focus attention on particulars [@diamond2013executive].
+A substantial body of research has investigated the link between executive functions and pragmatics -- with mixed results [@matthews2018individual; @nilsen2009relations].
+Analogical reasoning refers to the ability to reason about abstract relations between stimuli [@carstensen2021graded] -- an ability that has not been linked to pragmatics, at least not to the same extent as executive functions.
+
+After finding in Study 1 and 2 that most of the pragmatics tasks showed good to excellent re-test reliability, we studied a larger sample of children in Study 3 to investigate relations between the three utterance-based tasks.
+We focused on these tasks for theoretical reasons: we assume that -- computationally -- they share a common contrastive inference process according to which the listener compares the utterance the speaker made to alternative possible utterances.
+The listener expects the speaker to be helpful and informative, that is, to choose the utterance that best communicates the intended message.
+We formalize these assumptions in a computational cognitive model which we then use to study individual differences in this alleged process.
+Study 3 also included tasks for executive functions and analogical reasoning.
+Across analytical approaches, we found systematic relations among the pragmatics tasks as well as between pragmatics and executive functions, but not analogical reasoning.
 
@@
 
-The study was presented as an interactive picture book on a tablet computer.
+(ref:figlab1) Overview of the tasks used in Study 1 to 3.
+Pictures show screenshots from each task.
+The vertical order corresponds to the order of presentation in each study.
+The colors group the tasks along the (Assumed) cognitive processes involved.
+Blue: utterance-based inferences.
+Red common ground/discourse-based inferences.
+Green: Executive functions.
+Yellow: Analogical reasoning.
+
+```{r fig1, include = T, fig.align = "center", fig.cap = "(ref:figlab1)", out.width="100%"}
+knitr::include_graphics("./figures/figure1.png")
+```
+
+The study was presented as an interactive picture book on a tablet computer [@frank2016using].
 The tasks were programmed in `HTML/JavaScript` and run in a web browser.
@@
 
-(ref:figlab1) Overview of the tasks used in Study 1 to 3.
-Pictures show screenshots from each task.
-The vertical order corresponds to the order of presentation in each study.
-The colors group the tasks along the (Assumed) cognitive processes involved.
-Blue: utterance-based inferences.
-Red common ground/discourse-based inferences.
-Green: Executive functions.
-Green: Analogical reasoning.
-
-```{r fig1, include = T, fig.align = "center", fig.cap = "(ref:figlab1)", out.width="100%"}
-knitr::include_graphics("./figures/figure1.png")
-```
-
 ## Analysis
 
-We analysed the data in three steps. First we investigated developmental effects in each task, then we assessed re-test reliability and finally, we analysed relations between the tasks.
+We analysed the data in three steps. First we investigated developmental effects in each task, then we assessed re-test reliability and finally, we looked at relations between the tasks.
 
@@
 
+(ref:figlab2) Results by task for studies 1 to 3.
+Each panel shows the results for one task.
+Regression lines show the predicted developmental trajectories (with 95% CrI) based on by-task GLMMs, with the line type indicating the study.
+Colored points show age group means (with 95% CI based on non-parametric bootstrap) with the different shapes corresponding to the different studies.
+Light shapes show the mean performance for each subject by study.
+Dotted line shows level of performance expected by chance.
+
+```{r fig2, include = T, fig.align = "center", fig.cap = "(ref:figlab2)", out.width="100%"}
+knitr::include_graphics("./figures/figure2.png")
+```
+
 We found developmental effects in most of the tasks.
@@
 A notable exception was the correlation between mutual exclusivity and card sorting with *r* = `r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(rho)` (95% CI[`r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(lci)` - `r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(uci)`]).
-
-(ref:figlab2) Results by task for studies 1 to 3.
-Each panel shows the results for one task.
-Regression lines show the predicted developmental trajectories (with 95% CrI) based on by-task GLMMs, with the line type indicating the study.
-Colored points show age group means (with 95% CI based on non-parametric bootstrap) with the different shapes corresponding to the different studies.
-Light shapes show the mean performance for each subject by study.
-Dotted line shows level of performance expected by chance.
-
-```{r fig2, include = T, fig.align = "center", fig.cap = "(ref:figlab2)", out.width="100%"}
-knitr::include_graphics("./figures/figure2.png")
-```
 
@@
 For the present study, we formalized the ad-hoc implicature task within the same RSA framework.
-All three models shared one common parameter: $\alpha$.
-Within the RSA framework, $\alpha$ has the conceptual role of indicating how informative the listener thinks the speaker is.
+The three models share the same contrastive inference process according to which the listener compares the speaker's utterance to alternative, possible ones.
+The speaker then expects the listener to be informative (with degree $\alpha$), that is, choose the utterance that best communicates the intended message.
+In the mutual exclusivity task, the alternative utterance would be to use a familiar word.
+In the case of the informative inference task, the alternative was point to the object with only one property.
+For the ad-hoc implicature task it was to single out the property that was shared by both objects.
+In all cases, these alternative utterances would be better suited to communicate about the respective other referent.
 
+As noted above, all models shared one common parameter: the speaker informativeness parameter $\alpha$.
 This commonality offers a way of relating performance in the three tasks to one another by constraining the three models to use the same value for $\alpha$.
@@
 model_est <- read_csv("../saves/cfa_estimates.csv")
+
 ```
@@
 
-Our focal model in the confirmatory factor analysis including a latent factor for pragmatic reasoning fit the data well (PPP = `r round(model_fit%>%filter(index == "ppp", model == "fit1")%>%pull(value),3)`) and with a WAIC of `r round(model_comparison%>%filter(model == "fit1")%>%pull(waic),2)` (se = `r round(model_comparison%>%filter(model == "fit1")%>%pull(waic_se),2)`, weight = `r round(model_comparison%>%filter(model == "fit1")%>%pull(waic_weight),2)`) better compared to the two alternative models (individual factors model: PPP = `r round(model_fit%>%filter(index == "ppp", model == "fit3")%>%pull(value),3)`, WAIC = `r round(model_comparison%>%filter(model == "fit3")%>%pull(waic),2)`, se = `r round(model_comparison%>%filter(model == "fit3")%>%pull(waic_se),2)`, weight = `r round(model_comparison%>%filter(model == "fit3")%>%pull(waic_weight),2)`; one factor model: PPP = `r round(model_fit%>%filter(index == "ppp", model == "fit2")%>%pull(value),3)`, WAIC = `r round(model_comparison%>%filter(model == "fit2")%>%pull(waic),2)`, se = `r round(model_comparison%>%filter(model == "fit2")%>%pull(waic_se),2)`, weight = `r round(model_comparison%>%filter(model == "fit2")%>%pull(waic_weight),2)`).
+Next, we turn to the results of the confirmatory factor analysis.
+Our focal model -- including a latent factor for pragmatic reasoning -- fit the data well (PPP = `r round(model_fit%>%filter(index == "ppp", model == "fit1")%>%pull(value),3)`) and with a WAIC of `r round(model_comparison%>%filter(model == "fit1")%>%pull(waic),2)` (se = `r round(model_comparison%>%filter(model == "fit1")%>%pull(waic_se),2)`, weight = `r round(model_comparison%>%filter(model == "fit1")%>%pull(waic_weight),2)`) better compared to the two alternative models (individual factors model: PPP = `r round(model_fit%>%filter(index == "ppp", model == "fit3")%>%pull(value),3)`, WAIC = `r round(model_comparison%>%filter(model == "fit3")%>%pull(waic),2)`, se = `r round(model_comparison%>%filter(model == "fit3")%>%pull(waic_se),2)`, weight = `r round(model_comparison%>%filter(model == "fit3")%>%pull(waic_weight),2)`; one factor model: PPP = `r round(model_fit%>%filter(index == "ppp", model == "fit2")%>%pull(value),3)`, WAIC = `r round(model_comparison%>%filter(model == "fit2")%>%pull(waic),2)`, se = `r round(model_comparison%>%filter(model == "fit2")%>%pull(waic_se),2)`, weight = `r round(model_comparison%>%filter(model == "fit2")%>%pull(waic_weight),2)`).
 Figure \@ref(fig:fig5) shows that factor loadings for the individual tasks as well as their residual variance.
@@
 There was no systematic relation between pragmatic reasoning and analogical reasoning (as indicated by the relational match-to-sample task): *r* = 0.06; model estimate = `r round(model_est%>%filter(index == "prag~~match")%>%pull(value),2)`, 95% CrI [`r round(model_est%>%filter(index == "prag~~match")%>%pull(lower),2)` - `r round(model_est%>%filter(index == "prag~~match")%>%pull(upper),2)`].
-However, the latter result should be taken with a groin of salt given the unknown psychometric properties of the relational match-to-sample task.
+However, the latter result should be taken with a grain of salt given the unknown psychometric properties of the relational match-to-sample task.
 
@@
 
-The results of the analysis based on the cognitive model yield similar conclusions compared to the confirmatory factor analysis (Figure \@ref(fig:fig6)).
-Participant specific speaker informativeness parameters ($\alpha$) were correlated with performance in the card sorting (*r* = `r rsa_cor%>%filter(task == "Card Sorting")%>%pull(cor)`, 95% CI[`r rsa_cor%>%filter(task == "Card Sorting")%>%pull(lci)` - `r rsa_cor%>%filter(task == "Card Sorting")%>%pull(uci)`]) but not the relational match-to-sample task (*r* = `r rsa_cor%>%filter(task == "Relational Match-to-sample")%>%pull(cor)`, 95% CI[`r rsa_cor%>%filter(task == "Relational Match-to-sample")%>%pull(lci)` - `r rsa_cor%>%filter(task == "Relational Match-to-sample")%>%pull(uci)`]).
+Finally, we present the results of the cognitive modeling analysis.
+Using the data from Study 2, we could show that participant specific speaker informativeness parameters ($\alpha$) were highly reliable (Figure \@ref(fig:fig6)B).
+The scale parameter suggested that the mutual exclusivity task was easier and the informativeness inference task was harder compared to the ad-hoc implicature task (Figure \@ref(fig:fig6)C).
+When correlating $\alpha$ with performance in the other two tasks, the cognitive modeling approach yielded similar conclusions compared to the confirmatory factor analysis (Figure \@ref(fig:fig6)A): There was a substantial correlation with the card sorting (*r* = `r rsa_cor%>%filter(task == "Card Sorting")%>%pull(cor)`, 95% CI[`r rsa_cor%>%filter(task == "Card Sorting")%>%pull(lci)` - `r rsa_cor%>%filter(task == "Card Sorting")%>%pull(uci)`]) but not the relational match-to-sample task (*r* = `r rsa_cor%>%filter(task == "Relational Match-to-sample")%>%pull(cor)`, 95% CI[`r rsa_cor%>%filter(task == "Relational Match-to-sample")%>%pull(lci)` - `r rsa_cor%>%filter(task == "Relational Match-to-sample")%>%pull(uci)`]).
 The same limitations apply to the latter result as for the confirmatory factor analysis.
@@
 
+Using a diversity of different analytical tools, we found that performance in the three utterance-based pragmatic inference tasks was related in a way that points to shared cognitive processes.
+In the confirmatory factor analysis, we found that a model including a latent pragmatic reasoning factor fit the data well and better compared to alternative models.
+The latent factor explained substantial portions of the variance in each of the three tasks.
+The cognitive modelling approach provides an explicit theory of what the shared cognitive processes may look like: according to the model, the pragmatic inference in each task was driven by contrasting the utterance the speaker produced and alternative utterances.
+Individual differences were thought to arise from differential expectations about how informative the speaker is.
+
+Both analytic strategies point to systematic relations between pragmatic reasoning and executive functions as indicated by the card sorting test.
+We found no such relations with analogical reasoning as indicated by the relational match-to-sample task.
+However, given the unknown psychometric properties of the latter task, this result should be interpreted with caution.
+
 # General Discussion
 
-Present six, reliable (even when corrected for age) and ready to use tasks that cover a range of phenomena subsumed under pragmatic inference.
-WE divided them up into utternace based and interaction based and more systematic realtions between utternace based.
-Nevertehless, the others need to be explored more
+In this paper, we explored the development of pragmatic inferences in the preschool years.
+We identified six tasks covering a broad range of pragmatic phenomena.
+We found them to have good psychometric properties, in particular good to excellent re-test reliability.
+We then selected three utterance-based inference tasks for well-powered study of relations among different types of pragmatic abilities and between pragmatics and other cognitive processes.
+The results showed systematic relations between the tasks.
+We used a computational cognitive model of pragmatic reasoning to formalize the cognitive processes we believed the tasks to share.
+Finally, we found pragmatic abilities to be related to a task of executive functions.
 
-Across studies we saw relations between utterance based inference tasks.
-From different theoretical perspectives, they might be more or less obvious, especially for ME.
-From our perspective they make a lot of sense - we explicate this view in our model.
+One of the main contributions of this paper is that if presents six pragmatic inference tasks that are highly robust and reliable.
+Whenever we used a task in two studies (mutual exclusivity, informativeness inference, ad-hoc implicature), we found the developmental results to closely replicate.
+in Study 1 and 2, all tasks showed good re-test reliability -- even when corrected for age.
+A notable exception was the informativeness inference task in Study 1.
+However, after making some procedural changes, it turned out to be robust and reliable as well.
+Taken together, the tasks are highly suitable for individual differences research.
+The material is freely available via the online repository associated with the study.
 
-Why is there this relation with card sorting?
-The advantage of using a cognitive model to study individual differences is that the parameters have a more psychologically plausible interpretation compared to data analytic methods.
-If e take the model for real, we can speculate why card sorting matters.
+We grouped the tasks into utterance-based and common ground/discourse based.
+This grouping broadly captured the kind of information that we assumed to be relevant to compute the inference.
+For Study 3, we focused on the three utterance-based tasks.
+The main reason was theoretical.
+We were able to build on earlier work and formalize the inferences involved in these tasks in a common computational framework.
+We specified the structural overlap between the tasks and identified a parameter in the model that we used to capture individual differences.
+The shared structural features involve a recursive social inference process according to which the listener expects the speaker to select the most informative of a set of possible utterances.
+The individual difference parameter captured how informative the listener expected the speaker to be^[this interpretation follows from the conceptual role the parameter plays in the RSA framework.
+Technically, it acts as an amplifier of the basic inference].
+Previous accounts, in particular of mutual exclusivity [reviewed in @lewis2020role], would not have predicted such an overlap.
+The results of Study 3 (and also Study 2) supported our assumptions as we found systematic relations between the three tasks.
+
+Our formal model also allows us to speculate about why we saw a systematic relation across the three studies between pragmatic inference and the card sorting task as a measure of executive functions.
+Before we do so, we want to emphasize that the model is first and foremost a computational description of the tasks an not a model of a psychological process [cf.
+@goodman2016pragmatic].
+For the following, we assume more psychological realism than perhaps warranted.
+The card sorting task asks the child to switch between rules half way.
+This requires inhibiting a previously dominant response and attending to different features of the cards.
+The pragmatic inference in the model involves contrasting the observed utterance with alternative utterances.
+This could be described as requiring inhibiting interpretations that follow from other plausible interpretations and considering that there would have been better ways of saying it??
+However should find a common representation and model this explicitly.
+
 Switching rules requires seeing stimuli in different light - focus on different aspect of them, consider alternative ways of seeing them, not go with what you did previously.
 The inference in the model is driven by not going just with what is true but  considering alternative utterances - some commonalities here that might be responsible - need to be modeled explicitly and contrasted to alternative views.
-(check other theoretical accounts on that)
+(check other theoretical accounts on that).
+
+We did not look at the other tasks in the same level of detail
+
+Cartoon picture book presentation - not real speakers. But results match those of earlier in personn studies and generally tablet based tasks seem to be fine.
+
+Studies only weird kids from one cultural background, Nevertheless the tasks had been developed in eglish and were now used in German - suggets some portability. More needs to be done obviously.
 

### 2022-02-25 paper/manuscript.tex
first draft intor for paper

@@
   man,floatsintext]{apa6}
-\title{An individual differences perspective on the development of pragmatic reasoning}
+\title{An individual differences perspective on the development of pragmatic reasoning in the preschool years}
 \author{Manuel Bohn\textsuperscript{1}, Michael Henry Tessler\textsuperscript{2,3}, Clara Kordt\textsuperscript{4}, Tom Hausmann\textsuperscript{5}, \& Michael C. Frank\textsuperscript{6}}
@@
 \hypersetup{
-  pdftitle={An individual differences perspective on the development of pragmatic reasoning},
+  pdftitle={An individual differences perspective on the development of pragmatic reasoning in the preschool years},
   pdfauthor={Manuel Bohn1, Michael Henry Tessler2,3, Clara Kordt4, Tom Hausmann5, \& Michael C. Frank6},
@@
 
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
 We are very thankful to Stella Christie for sharing the material for the relational match-to-sample task with us.
@@
 
-\hypertarget{facets-of-pragmatic-reasoning}{%
-\section{Facets of pragmatic reasoning}\label{facets-of-pragmatic-reasoning}}
+Communication predates language.
+Before children produce their first words, they communicate with the world around them using vocalizations and gestures (Bates, Benigni, Bretherton, Camaioni, \& Volterra, 1979; Bruner, 1974).
+The process of language learning recruits many of the social-cognitive processes that underlay pre-verbal communication (Bohn \& Frank, 2019; E.
+V.
+Clark, 2009; Tomasello, 2009).
+Even for proficient language users is communication not reducible to the words being exchanged.
+The common thread running through these different aspects of human communication is its inferential nature: what a speaker means -- verbal or otherwise -- is underdetermined by the parts that make up the utterance.
+It takes contextual social inferences to recover the intended meaning (H.
+H.
+Clark, 1996; Grice, 1991; Levinson, 2000; Sperber \& Wilson, 2001).
+These contextual social inferences are often referred to as \emph{pragmatic} inferences (e.g., Bohn \& Frank, 2019).
 
-\hypertarget{the-challenges-of-studying-individual-differences}{%
-\section{The challenges of studying individual differences}\label{the-challenges-of-studying-individual-differences}}
+The development of pragmatics has been widely studied in recent years (for a recent review see Bohn \& Frank, 2019).
+This research covers a range of different phenomena ranging from so-called \emph{pure pragmatics} (Matthews, 2014) in non-verbal communication in infancy to sophisticated linguistic inferences developing much later (Huang \& Snedeker, 2009; Papafragou \& Skordos, 2016).
+A growing portion of this work is devoted to studying individual differences (Matthews, Biney, \& Abbot-Smith, 2018; E.
+Wilson \& Katsos, 2021).
+The motivation behind this is twofold: on the one hand, individual differences offer insights into the underlying psychological processes (Kidd, Donnelly, \& Christiansen, 2018; Matthews et al., 2018; A.
+C.
+Wilson \& Bishop, 2022).
+On the other hand, deficits in pragmatic abilities have been linked to behavioral problems and forms of language impairment (Helland, Lundervold, Heimann, \& Posserud, 2014).
 
-\hypertarget{the-current-study}{%
-\section{The current study}\label{the-current-study}}
+In their recent review of individual differences in children's pragmatic ability, Matthews et al.
+(2018) identified three issues that significantly limit what we can learn from individual differences research.
+First, most studies have insufficient sample sizes so that small and medium sized correlations among pragmatics tasks and between pragmatics tasks and measures for other cognitive abilities cannot be reliably detected.
+Second, the tasks used to assess pragmatic abilities often have poor or unknown psychometric properties.
+For example, many tasks only have a single trial and are therefore unable to capture variation between children.
+Reliability is not assessed, making it unclear if the task captures stable characteristics (see also Russell \& Grizzle, 2008).
+Third, the cognitive processes underlying pragmatic inferences in a particular task are underspecified.
+As a consequence, there is no clear rationale for why a task should correlate with another cognitive measure.
+
+The studies presented here directly address the issues identified by Matthews and colleagues (Matthews et al., 2018).
+We identified six pragmatic reasoning tasks in children between three and five years of age and investigated their psychometric properties, in particular their re-test reliability.
+Reliable tasks are a necessary precondition for meaningful individual differences research (Fried \& Flake, 2018; Hedge, Powell, \& Sumner, 2018).
+Next, we investigated the relations among different pragmatic reasoning tasks as well as between pragmatic reasoning and executive functions in a sample large enough to detect small to medium sized correlations.
+Finally, we introduced computational cognitive models of pragmatic reasoning to the study of individual differences.
+This allowed us to formalize the cognitive processes we think underlay pragmatic reasoning and thereby provide a substantive theoretical account for why certain pragmatic reasoning tasks are related to one another and why executive functions relate to them.
+
+The six tasks we selected were developmental adaptations of referential communication games inspired by research in experimental pragmatics (Noveck \& Reboul, 2008; Noveck \& Sperber, 2004).
+They all share a common trial-by-trial structure in which the test event always involved an agent producing an ambiguous utterance that children had to resolve using pragmatic reasoning.
+This allowed us to run multiple trials per task, and with that, to capture individual differences.
+We grouped the tasks into two broad categories (Figure \ref{fig:fig1}).
+On the one hand, utterance-based tasks asked children to derive inferences from the words and gestures the speaker produced in context.
+On the other hand, common ground/discourse-based tasks asked children to derive inferences from the social interaction that preceded the utterance.
+
+For the utterance-based category, we selected a mutual exclusivity, informativeness inference, and ad-hoc implicature task.
+Mutual exclusivity -- or principle of contrast -- describes the phenomenon that children tend to map a novel word to an unknown object (Bion, Borovsky, \& Fernald, 2013; E.
+V.
+Clark, 1988; Halberda, 2003; Lewis, Cristiano, Lake, Kwan, \& Frank, 2020; Markman \& Wachtel, 1988; Merriman, Bowman, \& MacWhinney, 1989).
+Informativeness inferences describe situations in which children identify the referent of a novel word by assuming that the speaker is trying to be informative.
+Being informative translates to using words that have smaller extensions in context (Frank \& Goodman, 2014).
+Ad-hoc implicature describes inferences that ask the child to contrast an utterance with alternatives that the speaker could have used but did not (Katsos \& Bishop, 2011; Stiller, Goodman, \& Frank, 2015; Yoon \& Frank, 2019).
+
+For the discourse-based category, we selected a speaker preference, discourse novelty and discourse continuity task.
+In the speaker preference task, the child had to track the preference of a speaker in order to identify the referent of a novel word (Saylor, Sabbagh, Fortuna, \& Troseth, 2009).
+Discourse novelty refers to a situation in which the child tracks the temporal appearance of objects in context and expects the speaker to refer to objects that are new in context (Akhtar, Carpenter, \& Tomasello, 1996; Diesendruck, Markson, Akhtar, \& Reudor, 2004).
+In the discourse continuity task, the child had to infer and track the topic of an ongoing conversation to resolve ambiguity (Akhtar, 2002; Bohn, Le, Peloquin, Köymen, \& Frank, 2021).
+
+In addition to the pragmatics tasks, we also included a tasks for executive functions (Zelazo, 2006) and of analogical reasoning (Christie \& Gentner, 2014).
+Executive functions refer to a family of top-down mental processes that enable us to inhibit automatic or intuitive responses and allow us to concentrate and focus attention on particulars (Diamond, 2013).
+A substantial body of research has investigated the link between executive functions and pragmatics -- with mixed results (Matthews et al., 2018; Nilsen \& Graham, 2009).
+Analogical reasoning refers to the ability to reason about abstract relations between stimuli (Carstensen \& Frank, 2021) -- an ability that has not been linked to pragmatics, at least not to the same extent as executive functions.
+
+After finding in Study 1 and 2 that most of the pragmatics tasks showed good to excellent re-test reliability, we studied a larger sample of children in Study 3 to investigate relations between the three utterance-based tasks.
+We focused on these tasks for theoretical reasons: we assume that -- computationally -- they share a common contrastive inference process according to which the listener compares the utterance the speaker made to alternative possible utterances.
+The listener expects the speaker to be helpful and informative, that is, to choose the utterance that best communicates the intended message.
+We formalize these assumptions in a computational cognitive model which we then use to study individual differences in this alleged process.
+Study 3 also included tasks for executive functions and analogical reasoning.
+Across analytical approaches, we found systematic relations among the pragmatics tasks as well as between pragmatics and executive functions, but not analogical reasoning.
 
@@
 
-The study was presented as an interactive picture book on a tablet computer.
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{./figures/figure1}
+
+}
+
+\caption{Overview of the tasks used in Study 1 to 3.
+Pictures show screenshots from each task.
+The vertical order corresponds to the order of presentation in each study.
+The colors group the tasks along the (Assumed) cognitive processes involved.
+Blue: utterance-based inferences.
+Red common ground/discourse-based inferences.
+Green: Executive functions.
+Yellow: Analogical reasoning.}\label{fig:fig1}
+\end{figure}
+
+The study was presented as an interactive picture book on a tablet computer (Frank, Sugarman, Horowitz, Lewis, \& Yurovsky, 2016).
 The tasks were programmed in \texttt{HTML/JavaScript} and run in a web browser.
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{./figures/figure1}
-
-}
-
-\caption{Overview of the tasks used in Study 1 to 3.
-Pictures show screenshots from each task.
-The vertical order corresponds to the order of presentation in each study.
-The colors group the tasks along the (Assumed) cognitive processes involved.
-Blue: utterance-based inferences.
-Red common ground/discourse-based inferences.
-Green: Executive functions.
-Green: Analogical reasoning.}\label{fig:fig1}
-\end{figure}
-
 \hypertarget{analysis}{%
@@
 
-We analysed the data in three steps. First we investigated developmental effects in each task, then we assessed re-test reliability and finally, we analysed relations between the tasks.
+We analysed the data in three steps. First we investigated developmental effects in each task, then we assessed re-test reliability and finally, we looked at relations between the tasks.
 
@@
 
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{./figures/figure2}
+
+}
+
+\caption{Results by task for studies 1 to 3.
+Each panel shows the results for one task.
+Regression lines show the predicted developmental trajectories (with 95\% CrI) based on by-task GLMMs, with the line type indicating the study.
+Colored points show age group means (with 95\% CI based on non-parametric bootstrap) with the different shapes corresponding to the different studies.
+Light shapes show the mean performance for each subject by study.
+Dotted line shows level of performance expected by chance.}\label{fig:fig2}
+\end{figure}
+
 We found developmental effects in most of the tasks.
@@
 A notable exception was the correlation between mutual exclusivity and card sorting with \emph{r} = 0.31 (95\% CI{[}0.03 - 0.55{]}).
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{./figures/figure2}
-
-}
-
-\caption{Results by task for studies 1 to 3.
-Each panel shows the results for one task.
-Regression lines show the predicted developmental trajectories (with 95\% CrI) based on by-task GLMMs, with the line type indicating the study.
-Colored points show age group means (with 95\% CI based on non-parametric bootstrap) with the different shapes corresponding to the different studies.
-Light shapes show the mean performance for each subject by study.
-Dotted line shows level of performance expected by chance.}\label{fig:fig2}
-\end{figure}
 
@@
 
-This task was directly taken from Bohn, Le, Peloquin, Köymen, and Frank (2021).
+This task was directly taken from Bohn et al.
+(2021).
 Children were told that they were going to visit the animals at their place.
@@
 For the present study, we formalized the ad-hoc implicature task within the same RSA framework.
-All three models shared one common parameter: \(\alpha\).
-Within the RSA framework, \(\alpha\) has the conceptual role of indicating how informative the listener thinks the speaker is.
+The three models share the same contrastive inference process according to which the listener compares the speaker's utterance to alternative, possible ones.
+The speaker then expects the listener to be informative (with degree \(\alpha\)), that is, choose the utterance that best communicates the intended message.
+In the mutual exclusivity task, the alternative utterance would be to use a familiar word.
+In the case of the informative inference task, the alternative was point to the object with only one property.
+For the ad-hoc implicature task it was to single out the property that was shared by both objects.
+In all cases, these alternative utterances would be better suited to communicate about the respective other referent.
 
+As noted above, all models shared one common parameter: the speaker informativeness parameter \(\alpha\).
 This commonality offers a way of relating performance in the three tasks to one another by constraining the three models to use the same value for \(\alpha\).
@@
 
-Our focal model in the confirmatory factor analysis including a latent factor for pragmatic reasoning fit the data well (PPP = 0.50) and with a WAIC of 1,753.45 (se = 32.02, weight = 0.74) better compared to the two alternative models (individual factors model: PPP = 0.51, WAIC = 1,756.48, se = 32.51, weight = 0.16; one factor model: PPP = 0.36, WAIC = 1,758.10, se = 32.37, weight = 0.07).
+Next, we turn to the results of the confirmatory factor analysis.
+Our focal model -- including a latent factor for pragmatic reasoning -- fit the data well (PPP = 0.50) and with a WAIC of 1,753.45 (se = 32.02, weight = 0.74) better compared to the two alternative models (individual factors model: PPP = 0.51, WAIC = 1,756.48, se = 32.51, weight = 0.16; one factor model: PPP = 0.36, WAIC = 1,758.10, se = 32.37, weight = 0.07).
 Figure \ref{fig:fig5} shows that factor loadings for the individual tasks as well as their residual variance.
@@
 There was no systematic relation between pragmatic reasoning and analogical reasoning (as indicated by the relational match-to-sample task): \emph{r} = 0.06; model estimate = 0.04, 95\% CrI {[}-0.11 - 0.18{]}.
-However, the latter result should be taken with a groin of salt given the unknown psychometric properties of the relational match-to-sample task.
+However, the latter result should be taken with a grain of salt given the unknown psychometric properties of the relational match-to-sample task.
 
-The results of the analysis based on the cognitive model yield similar conclusions compared to the confirmatory factor analysis.
-Participant specific speaker informativeness parameters (\(\alpha\)) were correlated with performance in the card sorting (\emph{r} = 0.31, 95\% CI{[}0.15 - 0.47{]}) but not the relational match-to-sample task (\emph{r} = 0.03, 95\% CI{[}-0.15 - 0.20{]})
+Finally, we present the results of the cognitive modeling analysis.
+Using the data from Study 2, we could show that participant specific speaker informativeness parameters (\(\alpha\)) were highly reliable (Figure \ref{fig:fig6}B).
+The scale parameter suggested that the mutual exclusivity task was easier and the informativeness inference task was harder compared to the ad-hoc implicature task (Figure \ref{fig:fig6}C).
+When correlating \(\alpha\) with performance in the other two tasks, the cognitive modeling approach yielded similar conclusions compared to the confirmatory factor analysis (Figure \ref{fig:fig6}A): There was a substantial correlation with the card sorting (\emph{r} = 0.31, 95\% CI{[}0.15 - 0.47{]}) but not the relational match-to-sample task (\emph{r} = 0.03, 95\% CI{[}-0.15 - 0.20{]}).
+The same limitations apply to the latter result as for the confirmatory factor analysis.
 
@@
 
+Using a diversity of different analytical tools, we found that performance in the three utterance-based pragmatic inference tasks was related in a way that points to shared cognitive processes.
+In the confirmatory factor analysis, we found that a model including a latent pragmatic reasoning factor fit the data well and better compared to alternative models.
+The latent factor explained substantial portions of the variance in each of the three tasks.
+The cognitive modelling approach provides an explicit theory of what the shared cognitive processes may look like: according to the model, the pragmatic inference in each task was driven by contrasting the utterance the speaker produced and alternative utterances.
+Individual differences were thought to arise from differential expectations about how informative the speaker is.
+
+Both analytic strategies point to systematic relations between pragmatic reasoning and executive functions as indicated by the card sorting test.
+We found no such relations with analogical reasoning as indicated by the relational match-to-sample task.
+However, given the unknown psychometric properties of the latter task, this result should be interpreted with caution.
+
 \hypertarget{general-discussion}{%
@@
 
-Present six, reliable (even when corrected for age) and ready to use tasks that cover a range of phenomena subsumed under pragmatic inference.
-WE divided them up into utternace based and interaction based and more systematic realtions between utternace based.
-Nevertehless, the others need to be explored more
+In this paper, we explored the development of pragmatic inferences in the preschool years.
+We identified six tasks covering a broad range of pragmatic phenomena.
+We found them to have good psychometric properties, in particular good to excellent re-test reliability.
+We then selected three utterance-based inference tasks for well-powered study of relations among different types of pragmatic abilities and between pragmatics and other cognitive processes.
+The results showed systematic relations between the tasks.
+We used a computational cognitive model of pragmatic reasoning to formalize the cognitive processes we believed the tasks to share.
+Finally, we found pragmatic abilities to be related to a task of executive functions.
 
-Across studies we saw relations between utterance based inference tasks.
-From different theoretical perspectives, they might be more or less obvious, especially for ME.
-From our perspective they make a lot of sense - we explicate this view in our model.
+One of the main contributions of this paper is that if presents six pragmatic inference tasks that are highly robust and reliable.
+Whenever we used a task in two studies (mutual exclusivity, informativeness inference, ad-hoc implicature), we found the developmental results to closely replicate.
+in Study 1 and 2, all tasks showed good re-test reliability -- even when corrected for age.
+A notable exception was the informativeness inference task in Study 1.
+However, after making some procedural changes, it turned out to be robust and reliable as well.
+Taken together, the tasks are highly suitable for individual differences research.
+The material is freely available via the online repository associated with the study.
 
-Why is there this relation with card sorting?
-The advantage of using a cognitive model to study individual differences is that the parameters have a more psychologically plausible interpretation compared to data analytic methods.
-If e take the model for real, we can speculate why card sorting matters.
+We grouped the tasks into utterance-based and common ground/discourse based.
+This grouping broadly captured the kind of information that we assumed to be relevant to compute the inference.
+For Study 3, we focused on the three utterance-based tasks.
+The main reason was theoretical.
+We were able to build on earlier work and formalize the inferences involved in these tasks in a common computational framework.
+We specified the structural overlap between the tasks and identified a parameter in the model that we used to capture individual differences.
+The shared structural features involve a recursive social inference process according to which the listener expects the speaker to select the most informative of a set of possible utterances.
+The individual difference parameter captured how informative the listener expected the speaker to be\footnote{this interpretation follows from the conceptual role the parameter plays in the RSA framework.
+Technically, it acts as an amplifier of the basic inference}.
+Previous accounts, in particular of mutual exclusivity (reviewed in Lewis et al., 2020), would not have predicted such an overlap.
+The results of Study 3 (and also Study 2) supported our assumptions as we found systematic relations between the three tasks.
+
+Our formal model also allows us to speculate about why we saw a systematic relation across the three studies between pragmatic inference and the card sorting task as a measure of executive functions.
+Before we do so, we want to emphasize that the model is first and foremost a computational description of the tasks an not a model of a psychological process (cf.
+Goodman \& Frank, 2016).
+For the following, we assume more psychological realism than perhaps warranted.
+The card sorting task asks the child to switch between rules half way.
+This requires inhibiting a previously dominant response and attending to different features of the cards.
+The pragmatic inference in the model involves contrasting the observed utterance with alternative utterances.
+This could be described as requiring inhibiting interpretations that follow from other plausible interpretations and considering that there would have been better ways of saying it??
+However should find a common representation and model this explicitly.
+
 Switching rules requires seeing stimuli in different light - focus on different aspect of them, consider alternative ways of seeing them, not go with what you did previously.
 The inference in the model is driven by not going just with what is true but considering alternative utterances - some commonalities here that might be responsible - need to be modeled explicitly and contrasted to alternative views.
-(check other theoretical accounts on that)
+(check other theoretical accounts on that).
+
+We did not look at the other tasks in the same level of detail
+
+Cartoon picture book presentation - not real speakers. But results match those of earlier in personn studies and generally tablet based tasks seem to be fine.
+
+Studies only weird kids from one cultural background, Nevertheless the tasks had been developed in eglish and were now used in German - suggets some portability. More needs to be done obviously.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-akhtar2002relevance}{}}%
+Akhtar, N. (2002). Relevance and early word learning. \emph{Journal of Child Language}, \emph{29}(3), 677--686.
+
+\leavevmode\vadjust pre{\hypertarget{ref-akhtar1996role}{}}%
+Akhtar, N., Carpenter, M., \& Tomasello, M. (1996). The role of discourse novelty in early word learning. \emph{Child Development}, \emph{67}(2), 635--645.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bates1979emergence}{}}%
+Bates, E., Benigni, L., Bretherton, I., Camaioni, L., \& Volterra, V. (1979). \emph{The emergence of symbols: Cognition and communication in infancy}. New York: Academic Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bion2013fast}{}}%
+Bion, R.
+A., Borovsky, A., \& Fernald, A.
+(2013).
+Fast mapping, slow learning: Disambiguation of novel word--object mappings in relation to vocabulary learning at 18, 24, and 30 months.
+\emph{Cognition}, \emph{126}(1), 39--53.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bohn2019pervasive}{}}%
+Bohn, M., \& Frank, M. C. (2019). The pervasive role of pragmatics in early language. \emph{Annual Review of Developmental Psychology}, \emph{1}(1), 223--249.
+
 \leavevmode\vadjust pre{\hypertarget{ref-bohn_le_peloquin_koymen_frank_2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bruner1974communication}{}}%
+Bruner, J. S. (1974). From communication to language---a psychological perspective. \emph{Cognition}, \emph{3}(3), 255--287.
+
 \leavevmode\vadjust pre{\hypertarget{ref-burkner2017brms}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-carstensen2021graded}{}}%
+Carstensen, A., \& Frank, M. C. (2021). Do graded representations support abstract thought? \emph{Current Opinion in Behavioral Sciences}, \emph{37}, 90--97.
+
 \leavevmode\vadjust pre{\hypertarget{ref-christie2014language}{}}%
 Christie, S., \& Gentner, D. (2014). Language helps children succeed on a classic analogy task. \emph{Cognitive Science}, \emph{38}(2), 383--397.
+
+\leavevmode\vadjust pre{\hypertarget{ref-clark1988logic}{}}%
+Clark, E. V. (1988). On the logic of contrast. \emph{Journal of Child Language}, \emph{15}(2), 317--335.
+
+\leavevmode\vadjust pre{\hypertarget{ref-clark2009first}{}}%
+Clark, E. V. (2009). \emph{First language acquisition}. Cambridge: Cambridge University Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-clark1996using}{}}%
+Clark, H. H. (1996). \emph{Using language}. Cambridge: Cambridge University Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-diamond2013executive}{}}%
+Diamond, A. (2013). Executive functions. \emph{Annual Review of Psychology}, \emph{64}, 135--168.
+
+\leavevmode\vadjust pre{\hypertarget{ref-diesendruck2004two}{}}%
+Diesendruck, G., Markson, L., Akhtar, N., \& Reudor, A.
+(2004).
+Two-year-olds' sensitivity to speakers' intent: An alternative account of samuelson and smith.
+\emph{Developmental Science}, \emph{7}(1), 33--41.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-frank2016using}{}}%
+Frank, M. C., Sugarman, E., Horowitz, A. C., Lewis, M. L., \& Yurovsky, D. (2016). Using tablets to collect data from young children. \emph{Journal of Cognition and Development}, \emph{17}(1), 1--17.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fried2018measurement}{}}%
+Fried, E. I., \& Flake, J. K. (2018). Measurement matters. \emph{APS Observer}, \emph{31}(3).
+
 \leavevmode\vadjust pre{\hypertarget{ref-goodman2016pragmatic}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-grice1991studies}{}}%
+Grice, H. P. (1991). \emph{Studies in the way of words}. Cambridge, MA: Harvard University Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-halberda2003development}{}}%
+Halberda, J. (2003). The development of a word-learning strategy. \emph{Cognition}, \emph{87}(1), B23--B34.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hedge2018reliability}{}}%
+Hedge, C., Powell, G., \& Sumner, P.
+(2018).
+The reliability paradox: Why robust cognitive tasks do not produce reliable individual differences.
+\emph{Behavior Research Methods}, \emph{50}(3), 1166--1186.
+
+\leavevmode\vadjust pre{\hypertarget{ref-helland2014stable}{}}%
+Helland, W.
+A., Lundervold, A.
+J., Heimann, M., \& Posserud, M.-B.
+(2014).
+Stable associations between behavioral problems and language impairments across childhood--the importance of pragmatic language problems.
+\emph{Research in Developmental Disabilities}, \emph{35}(5), 943--951.
+
+\leavevmode\vadjust pre{\hypertarget{ref-huang2009online}{}}%
+Huang, Y. T., \& Snedeker, J. (2009). Online interpretation of scalar quantifiers: Insight into the semantics--pragmatics interface. \emph{Cognitive Psychology}, \emph{58}(3), 376--415.
+
+\leavevmode\vadjust pre{\hypertarget{ref-katsos2011pragmatic}{}}%
+Katsos, N., \& Bishop, D. V. (2011). Pragmatic tolerance: Implications for the acquisition of informativeness and implicature. \emph{Cognition}, \emph{120}(1), 67--81.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kidd2018individual}{}}%
+Kidd, E., Donnelly, S., \& Christiansen, M. H. (2018). Individual differences in language acquisition and processing. \emph{Trends in Cognitive Sciences}, \emph{22}(2), 154--169.
+
 \leavevmode\vadjust pre{\hypertarget{ref-lee2012basic}{}}%
 Lee, S.-Y., \& Song, X.-Y. (2012). \emph{Basic and advanced bayesian structural equation modeling: With applications in the medical and behavioral sciences}. John Wiley \& Sons.
+
+\leavevmode\vadjust pre{\hypertarget{ref-levinson2000presumptive}{}}%
+Levinson, S. C. (2000). \emph{Presumptive meanings: The theory of generalized conversational implicature}. Cambridge, MA: MIT press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lewis2020role}{}}%
+Lewis, M., Cristiano, V., Lake, B.
+M., Kwan, T., \& Frank, M.
+C.
+(2020).
+The role of developmental change and linguistic experience in the mutual exclusivity effect.
+\emph{Cognition}, \emph{198}, 104191.
+
+\leavevmode\vadjust pre{\hypertarget{ref-markman1988children}{}}%
+Markman, E. M., \& Wachtel, G. F. (1988). Children's use of mutual exclusivity to constrain the meanings of words. \emph{Cognitive Psychology}, \emph{20}(2), 121--157.
+
+\leavevmode\vadjust pre{\hypertarget{ref-matthews2014pragmatic}{}}%
+Matthews, D. (2014). \emph{Pragmatic development in first language acquisition} (Vol. 10). John Benjamins Publishing Company.
+
+\leavevmode\vadjust pre{\hypertarget{ref-matthews2018individual}{}}%
+Matthews, D., Biney, H., \& Abbot-Smith, K.
+(2018).
+Individual differences in children's pragmatic ability: A review of associations with formal language, social cognition, and executive functions.
+\emph{Language Learning and Development}, \emph{14}(3), 186--223.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-merriman1989mutual}{}}%
+Merriman, W. E., Bowman, L. L., \& MacWhinney, B. (1989). The mutual exclusivity bias in children's word learning. \emph{Monographs of the Society for Research in Child Development}, i--129.
+
+\leavevmode\vadjust pre{\hypertarget{ref-nilsen2009relations}{}}%
+Nilsen, E. S., \& Graham, S. A. (2009). The relations between children's communicative perspective-taking and executive functioning. \emph{Cognitive Psychology}, \emph{58}(2), 220--249.
+
+\leavevmode\vadjust pre{\hypertarget{ref-noveck2008experimental}{}}%
+Noveck, I. A., \& Reboul, A. (2008). Experimental pragmatics: A gricean turn in the study of language. \emph{Trends in Cognitive Sciences}, \emph{12}(11), 425--431.
+
+\leavevmode\vadjust pre{\hypertarget{ref-noveck2004experimental}{}}%
+Noveck, I. A., \& Sperber, D. (2004). \emph{Experimental pragmatics}. Springer.
+
+\leavevmode\vadjust pre{\hypertarget{ref-papafragou2016scalar}{}}%
+Papafragou, A., \& Skordos, D. (2016). Scalar implicature. In J. Lidz, W. Snyder, \& J. Pater (Eds.), \emph{The Oxford Hanbook of Developmental Linguistics} (pp. 611--632). Oxford University Press.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
@@
 Rouder, J. N., \& Haaf, J. M. (2019). A psychometrics of individual differences in experimental tasks. \emph{Psychonomic Bulletin \& Review}, \emph{26}(2), 452--467.
+
+\leavevmode\vadjust pre{\hypertarget{ref-russell2008assessing}{}}%
+Russell, R.
+L., \& Grizzle, K.
+L.
+(2008).
+Assessing child and adolescent pragmatic language competencies: Toward evidence-based assessments.
+\emph{Clinical Child and Family Psychology Review}, \emph{11}(1), 59--73.
+
+\leavevmode\vadjust pre{\hypertarget{ref-saylor2009preschoolers}{}}%
+Saylor, M. M., Sabbagh, M. A., Fortuna, A., \& Troseth, G. (2009). Preschoolers use speakers' preferences to learn words. \emph{Cognitive Development}, \emph{24}(2), 125--132.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sperber2001relevance}{}}%
+Sperber, D., \& Wilson, D. (2001). \emph{Relevance: Communication and cognition} (2nd ed.). Cambridge, MA: Blackwell Publishers.
+
+\leavevmode\vadjust pre{\hypertarget{ref-stiller2015ad}{}}%
+Stiller, A. J., Goodman, N. D., \& Frank, M. C. (2015). Ad-hoc implicature in preschool children. \emph{Language Learning and Development}, \emph{11}(2), 176--190.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tomasello2009constructing}{}}%
+Tomasello, M. (2009). \emph{Constructing a language}. Cambridge, MA: Harvard University Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-wilson2022novel}{}}%
+Wilson, A.
+C., \& Bishop, D.
+V.
+(2022).
+A novel online assessment of pragmatic and core language skills: An attempt to tease apart language domains in children.
+\emph{Journal of Child Language}, \emph{49}(1), 38--59.
+
+\leavevmode\vadjust pre{\hypertarget{ref-wilson2021pragmatic}{}}%
+Wilson, E., \& Katsos, N.
+(2021).
+Pragmatic, linguistic and cognitive factors in young children's development of quantity, relevance and word learning inferences.
+\emph{Journal of Child Language}, 1--28.
 

### 2022-03-01 experiments/novelty.js
fix experiment positioning

@@ -1,342 +1,343 @@
-
 // the actual experiment
 var novelty = {
-  // Parameters for this sequence.
-  trial: [1,2,3,4,5],
-  agents: ["Monkey","Bunny","Cat","Dog","Frog"],
-  novel:["right", "left", "right", "right", "left"],
-  agentOrient: [    
-    ["straight", "point_r", "point_l", "disappear","gone","down"],
-    ["straight", "point_l", "point_r", "disappear","gone","down"],
-    ["straight", "point_r", "point_l", "disappear","gone","down"],
-    ["straight", "point_l", "point_r", "disappear","gone","down"],
-    ["straight", "point_r", "point_l", "disappear","gone","down"]],
-  leftObject: ["t26","t27","t28","t29","t30"],
-  rightObject: ["t31","t32","t33","t34","t35"],
-  back: [1,6,3,8,5],
-  data: [],
-    
+    // Parameters for this sequence.
+    trial: [1, 2, 3, 4, 5],
+    agents: ["Monkey", "Bunny", "Cat", "Dog", "Frog"],
+    novel: ["right", "left", "right", "right", "left"],
+    agentOrient: [
+        ["straight", "point_r", "point_l", "disappear", "gone", "down"],
+        ["straight", "point_l", "point_r", "disappear", "gone", "down"],
+        ["straight", "point_r", "point_l", "disappear", "gone", "down"],
+        ["straight", "point_l", "point_r", "disappear", "gone", "down"],
+        ["straight", "point_r", "point_l", "disappear", "gone", "down"]
+    ],
+    leftObject: ["t26", "t27", "t28", "t29", "t30"],
+    rightObject: ["t31", "t32", "t33", "t34", "t35"],
+    back: [1, 6, 3, 8, 5],
+    data: [],
 
-// end of the experiment
-  end: function() {
-    // Show the finish slide.
-    showSlide("select");
-    setTimeout(function() { turk.submit(novelty) }, 1000);
-  },
-    
- 
-// what happens between trials - display agent from previous trial and click on it to move on to the next trial    
-   eat: function(event) {
-    
-    setTimeout(function() {novelty.eat2() }, 1500);
-       
-    showSlide("choice");  
-       
-    event.target.style.border = '5px solid blue';
-    
-    sourceSound("sound/end.mp3");
-    playSound();
-    
-       
-    $(".fruit_r").unbind("click");
-    $(".fruit_l").unbind("click");
 
-      var pick_src = event.target.src;   
-    // get time for reaction time
[…]

### 2022-03-01 experiments/pragBat.js

@@ -1,95 +1,95 @@
 // preload
-var preFruits = ["duck.png","car.png","car_me.png","bear.png","ball.png","t01.png", "t02.png", "t03.png", "t04.png", "t05.png", "t06.png", "t07.png", "t08.png", "t09.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t17.png", "carrot.png","bread.png","apple_me.png","kite.png", "t18.png","t19.png","t20.png","t21.png","t22.png","t23.png","t24.png","t25.png","t26.png","t27.png","t28.png","t29.png","t30.png","t31.png","t32.png","t33.png","t34.png","t35.png", "t36.png","t37.png","t38.png","t39.png","t44.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png", "bear_me.png"];
+var preFruits = ["duck.png", "car.png", "car_me.png", "bear.png", "ball.png", "t01.png", "t02.png", "t03.png", "t04.png", "t05.png", "t06.png", "t07.png", "t08.png", "t09.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t17.png", "carrot.png", "bread.png", "apple_me.png", "kite.png", "t18.png", "t19.png", "t20.png", "t21.png", "t22.png", "t23.png", "t24.png", "t25.png", "t26.png", "t27.png", "t28.png", "t29.png", "t30.png", "t31.png", "t32.png", "t33.png", "t34.png", "t35.png", "t36.png", "t37.png", "t38.png", "t39.png", "t44.png", "back1.jpg", "back2.jpg", "back3.jpg", "back4.jpg", "back5.jpg", "back6.jpg", "back7.jpg", "back8.jpg", "back9.jpg", "back10.jpg", "empty.png", "bear_me.png"];
 //for critical trials and fillers
 var images = new Array();
 for (i = 0; i < preFruits.length; i++) {
-	images[i] = new Image();
-	images[i].src = "images/" + preFruits[i];
+    images[i] = new Image();
+    images[i].src = "images/" + preFruits[i];
 }
 
 
 var preSounds = [
-         "Monkey_hello.mp3",
+    "Monkey_hello.mp3",
     "Monkey_filler_inf_intro.mp3",
[…]

### 2022-03-01 analysis/analysis.Rmd
first draft manuscript and analysis

@@
 ---
-title: "PragBat Models"
+title: "PragBat Analysis"
 output: html_document
@@
 
+In the next section, we run the same model for each task and each study.
+Model outputs are saved in the repository and can be loaded at the end of the following code section in order to reproduce the exact results from the paper.
+
 ```{r}
 # Models
-## card sorting
+# ## card sorting
 # bm_cs_s1 <- brm(correct ~ z_age + z_trial + (z_trial|id),
@@
 # 
-# saveRDS(bm_cs_s1, "../saves/card_sorting_model_s1.rds")
+# #saveRDS(bm_cs_s1, "../saves/card_sorting_model_s1.rds")
 # 
@@
 # 
-# saveRDS(bm_cs_s2, "../saves/card_sorting_model_s2.rds")
+# #saveRDS(bm_cs_s2, "../saves/card_sorting_model_s2.rds")
 # 
@@
 # 
-# saveRDS(bm_cs_s3, "../saves/card_sorting_model_s3.rds")
+# #saveRDS(bm_cs_s3, "../saves/card_sorting_model_s3.rds")
 # 
@@
 # 
-# saveRDS(bm_me_s1, "../saves/mutual_exclusivity_model_s1.rds")
+# #saveRDS(bm_me_s1, "../saves/mutual_exclusivity_model_s1.rds")
 # 
@@
 # 
-# saveRDS(bm_me_s2, "../saves/mutual_exclusivity_model_s2.rds")
+# #saveRDS(bm_me_s2, "../saves/mutual_exclusivity_model_s2.rds")
 # 
@@
 # 
-# saveRDS(bm_ad_s2, "../saves/ad_hoc_implicature_model_s2.rds")
+# #saveRDS(bm_ad_s2, "../saves/ad_hoc_implicature_model_s2.rds")
 # 
@@
 # 
-# saveRDS(bm_ad_s3, "../saves/ad_hoc_implicature_model_s3.rds")
+# #saveRDS(bm_ad_s3, "../saves/ad_hoc_implicature_model_s3.rds")
 # 
@@
 # 
-# saveRDS(bm_dis_s2, "../saves/discourse_continuity_model_s2.rds")
+# #saveRDS(bm_dis_s2, "../saves/discourse_continuity_model_s2.rds")
 # 
@@
 # 
-# saveRDS(bm_inf_s1, "../saves/informativeness_model_s1.rds")
+# #saveRDS(bm_inf_s1, "../saves/informativeness_model_s1.rds")
 # 
@@
 # 
-# saveRDS(bm_ms_s3, "../saves/match_to_sample_model_s3.rds")
+# #saveRDS(bm_ms_s3, "../saves/match_to_sample_model_s3.rds")
 # 
@@
 # 
-# saveRDS(bm_nov_s1, "../saves/novelty_model_s1.rds")
+# #saveRDS(bm_nov_s1, "../saves/novelty_model_s1.rds")
 # 
@@
 # 
-# saveRDS(bm_pref_s1, "../saves/preference_model_s1.rds")
+# #saveRDS(bm_pref_s1, "../saves/preference_model_s1.rds")
 # 
@@
 # 
-# saveRDS(bm_simpinf_s2, "../saves/simple_inf_model_s2.rds")
+# #saveRDS(bm_simpinf_s2, "../saves/simple_inf_model_s2.rds")
 # 
@@
 # 
-# saveRDS(bm_simpinf_s3, "../saves/simple_inf_model_s3.rds")
+# #saveRDS(bm_simpinf_s3, "../saves/simple_inf_model_s3.rds")
 
+# Load saved model outputs
 bm_cs_s1 <- readRDS( "../saves/card_sorting_model_s1.rds")
@@
 
+The following code section produces the model predictions included in Figure 2.
+
 ```{r}
@@
   filter(study == "study1", trial == "1", task == "mutual_exclusivity", test_day == 1)%>%
-  select(-z_trial,-correct, -task, -test_day, -age_month, -gender, -item, -subage)%>%
+  select(-z_trial,-correct, -task, -test_day, -gender, -item, -subage)%>%
   mutate(z_trial = 0)
@@
   filter(study == "study2", trial == "1", task == "mutual_exclusivity", test_day == 1)%>%
-  select(-z_trial,-correct, -task, -test_day, -age_month, -gender, -item, -subage)%>%
+  select(-z_trial,-correct, -task, -test_day, -gender, -item, -subage)%>%
   mutate(z_trial = 0)
@@
   filter(study == "study3", trial == "1", task == "mutual_exclusivity")%>%
-  select(-z_trial,-correct, -task, -test_day, -age_month, -gender, -item, -subage)%>%
+  select(-z_trial,-correct, -task, -test_day, -gender, -item, -subage)%>%
   mutate(z_trial = 0)
@@
 ```
+
+The next code section produces Figure 2 in the manuscript
 
@@
 ```
+
+The following two sections extract the age estimates from the models for the different tasks and studies and visualizes them. The second plot is Figure 3 from the paper.
 
@@
 
+The following section implements the Rouder and Haaf (2019) method of estimating re-test reliability based on a GLMM.
+
 ```{r}
@@
 ```
+
+The next section computes re-test reliability and correlations between tasks based on the aggregated raw scores. The plot generated at the end is Figure 4 from the paper.
 
@@
 
+The following section computes the correlation between tasks, including 95% confidence intervals.
+
 ```{r}
@@
 
+The next section prepares the data file for the CFA.
+
 ```{r}
@@
 
+Here we specify the different CFA models, with `model` being the focal model.
+
 ```{r}
@@
 ```
+
+Here we run the three CFA models.
 
@@
 
+The following section extracts the fit measures (e.g., PPP) for the three models.
+
 ```{r}
@@
   write_csv("../saves/cfa_fit_measures.csv")
+```
 
-summary(fit2, fit.measures=TRUE, standardized = TRUE, rsquare = T)
-
-blavInspect(fit, what = "postmean")%>%as_tibble(rownames = "index")%>%
-  left_join(blavInspect(fit, what = "hpd")%>%as_tibble(rownames = "index"))%>%
-  write_csv("../saves/cfa_estimates.csv")
-
-```
+Here we extract the WAIC value for each model and compute the WAIC weight. We do the same for LOO.
 
@@
 
+First we read in the saved model output
+
 ```{r}
-rsa_model <- readRDS("../../../Spin-off/spin-off/model/output/model_pragBat3.rds")
+rsa_model <- readRDS("../saves/model_pragBat3.rds")
 ```
+
+The next section visualizes the scale parameter
 
@@
 ```
+
+Here we extract and summarize the person specific $\alpha$ estimates and correalte them to performance in the card sorting and relational match-to-sample tasks.
 
@@
 
+The next section reads in the output from the RSA-based reliability model for Study 2
+
 ```{r}
-rel_rsa_model <- readRDS("../../../Spin-off/spin-off/data/rsa_rel_est.rds")
+rel_rsa_model <- readRDS("../saves/rsa_rel_est.rds")
 ```
+
+Here we summarise the parameter esteimates for each test session and correlate them to get a measure of re-test reliability.
 
@@
 
+Here we combine the plots for the correlation between $\alpha$ estimates and the card sorting and relational match-to-sample tasks with the plot for the scale parameter and the RSA based reliability plot to generate Figure 6 in the manuscript.
+
 ```{r}

### 2022-03-01 paper/manuscript.Rmd
first draft manuscript and analysis

@@
 ---
-title             : "An individual differences perspective on the development of pragmatic reasoning in the preschool years"
-shorttitle        : "Individual differences in pragmatic reasoning"
+title             : "An individual differences perspective on the development of pragmatic abilities in the preschool years"
+shorttitle        : "Individual differences in pragmatic abilities"
 
@@
       - Data collection
+      - Writing - Review & Editing
   - name          : "Tom Hausmann"
@@
       - Data collection
+      - Writing - Review & Editing
   - name          : "Michael C. Frank"
@@
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+  Pragmatic abilities are fundamental to successful language use and learning.
+Individual differences studies contribute to understanding the psychological processes involved in pragmatic reasoning as well as the link to other cognitive abilities.
+Small sample sizes, insufficient measurement tools, and a lack of theoretical precision have hindered progress.
+Three studies addressed these challenges in a sample of three- to five-year-old German-speaking children (*N* = 228, 121 female).
+Studies 1 and 2 assessed the psychometric properties of six pragmatics tasks.
+Study 3 investigated relations among pragmatics tasks and between pragmatics and other cognitive abilities.
+The shared cognitive processes were formalized in a computational cognitive model of pragmatic reasoning.
+Results showed substantive relations among pragmatic tasks and between pragmatic abilities and executive functions.
 
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
+keywords          : "Pragmatics, language development, individual differences, cognitive modeling"
 wordcount         : "X"
@@
 library(knitr)
-library(brms)
 
@@
          test_day = paste0("day", test_day))
-
 ```
@@
 The common thread running through these different aspects of human communication is its inferential nature: what a speaker means -- verbal or otherwise -- is underdetermined by the parts that make up the utterance.
-It takes contextual social inferences to recover the intended meaning [@grice1991studies; @clark1996using; @sperber2001relevance; @levinson2000presumptive].
-These contextual social inferences are often referred to as *pragmatic* inferences [e.g., @bohn2019pervasive].
+It takes contextual social inferences to recover the intended meaning [@grice1991studies; @clark1996using; @sperber2001relevance; @levinson2000presumptive; @bohn2018common].
+These inferences are often referred to as *pragmatic* inferences [e.g., @bohn2019pervasive].
 
@@
 
-In their recent review of individual differences in children's pragmatic ability, @matthews2018individual identified three issues that significantly limit what we can learn from individual differences research.
+In their recent review, @matthews2018individual identified three issues that significantly limit what we can learn from individual differences research on pragmatic abilities.
 First, most studies have insufficient sample sizes so that small and medium sized correlations among pragmatics tasks and between pragmatics tasks and measures for other cognitive abilities cannot be reliably detected.
@@
 The six tasks we selected were developmental adaptations of referential communication games inspired by research in experimental pragmatics [@noveck2008experimental; @noveck2004experimental].
-They all share a common trial-by-trial structure in which the test event always involved an agent producing an ambiguous utterance that children had to resolve using pragmatic reasoning.
+They all share a common trial-by-trial structure in which the test event always involved an agent producing an ambiguous utterance that the child had to resolve using pragmatic reasoning.
 This allowed us to run multiple trials per task, and with that, to capture individual differences.
@@
 In the speaker preference task, the child had to track the preference of a speaker in order to identify the referent of a novel word [@saylor2009preschoolers].
-Discourse novelty refers to a situation in which the child tracks the temporal appearance of objects in context and expects the speaker to refer to objects that are new in context [@akhtar1996role; @diesendruck2004two].
+Discourse novelty refers to a situation in which the child tracks the temporal appearance of objects and expects the speaker to refer to objects that are new in context [@akhtar1996role; @diesendruck2004two].
 In the discourse continuity task, the child had to infer and track the topic of an ongoing conversation to resolve ambiguity [@bohn_le_peloquin_koymen_frank_2020; @akhtar2002relevance].
 
-In addition to the pragmatics tasks, we also included a tasks for executive functions [@zelazo2006dimensional] and of analogical reasoning [@christie2014language].
+In addition to the pragmatics tasks, we also included tasks for executive functions [@zelazo2006dimensional] and of analogical reasoning [@christie2014language].
 Executive functions refer to a family of top-down mental processes that enable us to inhibit automatic or intuitive responses and allow us to concentrate and focus attention on particulars [@diamond2013executive].
 A substantial body of research has investigated the link between executive functions and pragmatics -- with mixed results [@matthews2018individual; @nilsen2009relations].
-Analogical reasoning refers to the ability to reason about abstract relations between stimuli [@carstensen2021graded] -- an ability that has not been linked to pragmatics, at least not to the same extent as executive functions.
+Analogical reasoning refers to the ability to reason about abstract relations between stimuli [@carstensen2021graded] -- an ability that has not been linked to pragmatics -- at least not to the same extent as executive functions.
 
@@
 
+Study 1 focused on the psychometric properties of four pragmatics tasks, in particular, their re-test reliability.
+two of the tasks were from the utterance-based group and two from the common ground/discourse-based group.
+As a fifth task, we included a measure of executive functions.
 Methods and sample size were pre-registered at https://osf.io/6a723.
@@
 The vertical order corresponds to the order of presentation in each study.
-The colors group the tasks along the (Assumed) cognitive processes involved.
+The colors group the tasks along the (assumed) cognitive processes involved.
 Blue: utterance-based inferences.
@@
 The animal asked the child to give them one of the objects (e.g., "Can you give me the car").
-the objects were chosen so that children of the youngest age group would easily understand them (car and ball).
+The objects were chosen so that children of the youngest age group would easily understand them (car and ball).
 This procedure familiarized the child with the general logic of the animals making requests and the child touching objects.
@@
 
-This task was directly taken from @bohn2021young.
+This task was adapted from @bohn2021young.
 The task layout and the procedure was the same as in the training.
@@
 
-The task was directly taken from @bohn_tessler_merrick_frank_2019.
+The task was adapted from @bohn_tessler_merrick_frank_2019.
 Th animal was standing between two trees with objects hanging in them.
@@
 
-This task was also taken from @bohn_tessler_merrick_frank_2019.
+This task was also adapted from @bohn_tessler_merrick_frank_2019.
 The animal was standing between the two tables, each of which had a novel object (drawn for the purpose of the study) on it.
@@
 
-This task was taken from @bohn2021young.
+This task was adapted from @bohn2021young.
 Once again, the animal was standing between the two tables.
@@
 
-We analysed the data in three steps. First we investigated developmental effects in each task, then we assessed re-test reliability and finally, we looked at relations between the tasks.
-
+We analysed the data in three steps.
+First we investigated developmental effects in each task, then we assessed re-test reliability and finally, we looked at relations between the tasks.
 All analysis were run in `R` [@R-base] version 4.1.2.
@@
 To estimate developmental effects in each task, we fit a GLMM predicting correct responses (0/1) by age (centered at the mean) and trial number (also centered).
-The model included random intercepts for each participant and random slopes for trial within participants (model notation in `R`: `correct ~ age + trial + (trial|id)` ).
+The model included random intercepts for each participant and random slopes for trial within participants (model notation in `R`: `correct ~ age + trial + (trial|id)` )^[We pre-registered the inclusion of random intercepts for item.
+We deviate from this here for the following reason: the order of items was fixed and the same for all participants so that trial and item were confounded.].
 For each task, we inspected and visualized the posterior distribution (mean and 95% Credible Interval (CrI)) for the age estimate.
@@
 Finally, we used that aggregated data from both test days for each participant and task to compute Pearson correlations between the different tasks.
-Given the small sample size in Study 1, this part of the analysis is mostly exploratory.
+Given the small sample size in Study 1, this part of the analysis was mostly exploratory.
 
@@
 
-Re-test reliability was high for most tasks (see Figure \@ref(fig:fig2)).
-Raw correlations between the two test sessions was above .7 for mutual exclusivity, speaker preference and discourse novelty.
+Re-test reliability was high for most tasks (see Figure \@ref(fig:fig4)).
+Raw correlation between the two test sessions was above .7 for mutual exclusivity, speaker preference and discourse novelty.
 With .62 it was slightly lower for card sorting.
 The model based -- age independent -- reliability estimates yielded similar results suggesting that the tasks did capture task specific individual differences.
-A notable exception was the informativeness inference task, which was not reliable according to any of the methods of computing re-test correlations.
-We suspect the overall low variation in performance to be responsible for this.
+A notable exception was the informativeness inference task, which was not reliable according to any of the methods of computing re-test reliability (Figure \@ref(fig:fig4)).
+We suspected the overall low variation in performance to be responsible for this.
 
@@
 Study 1 showed that the different tasks were age appropriate and reliable.
-A notable exception was the informativeness inference task which generated to systematic variation in the age range we studied here.
+A notable exception was the informativeness inference task which generated no systematic variation in the age range we studied here.
 Correlations between the tasks were generally low, with the notable exception of the relation between mutual exclusivity and card sorting.
-Given the small sample size, we want to avoid overly strong claims, however, it was interesting to see that the relation between the two tasks tapping into common ground based inferences (speaker preference and discourse novelty) were -- if anything -- negatively correlated.
+Given the small sample size, we want to avoid overly strong claims, however, it was interesting to see that the relation between the two tasks tapping into discourse-based inferences (speaker preference and discourse novelty) were -- if anything -- negatively correlated.
 
@@
 We added two new tasks and modified the informativeness inferences task, which we will describe in detail below.
-The mutual exclusivity and card sorting tasks were the same as in Study 1.
+The training, mutual exclusivity and card sorting tasks were the same as in Study 1.
 
@@
 
-This task was directly taken from @bohn_le_peloquin_koymen_frank_2020.
-Children were told that they were going to visit the animals at their place.
-The animal greeted the child and told them that they would show them their things.
+This task was adapted from @bohn_le_peloquin_koymen_frank_2020.
+Children were told that they were going to visit the animals in their home.
+An animal greeted the child and told them that they would show them their things.
 During exposure trials, the child saw three objects from three different categories (e.g., train (vehicle), drum (instrument), orange (fruit); see Figure \@ref(fig:fig1)).
-The animal named of the objects and asked the child to touch it.
+The animal named one of the objects and asked the child to touch it.
 On the next exposure trial, the child saw three new objects but from the same categories (e.g., bus (vehicle), flute (instrument), apple (fruit)).
@@
 On the following test trial, the animal used a pronoun to refer to one of the objects (i.e., can you touch *it*).
-We assumed that children would use the exposure trials to infer that the animal was talking about a certain category and would use this knowledge to identify the referent of the pronoun.Children received five test trials, each with a different category as the target.
+We assumed that children would use the exposure trials to infer that the animal was talking about a certain category and would use this knowledge to identify the referent of the pronoun.
+Children received five test trials, each with a different category as the target.
 The position of the objects in exposure trials as well as test trials was pseudo-randomized.
@@
 All cards had two geometrical shapes of the same color on them.
-The sample card showed to identical shapes and so did one of the potential matches.
+The sample card showed two identical shapes and so did one of the potential matches.
 The other card showed two different shapes.
@@
 That is, they include a schematic representation of the experimental tasks and provide a computational account of how participants make inferences in this context.
-RSA models see pragmatic inferences as a form of Bayesian social reasoning where the listener tries to infer the speaker' meaning (here: the intended referent) by assuming that the speaker is helpful and informative.
-Being helpful and informative means that the speaker chooses a message based on the probability that it would help the listener would recover the speaker's intended meaning.
+RSA models see pragmatic inferences as a form of Bayesian social reasoning where the listener tries to infer the speaker's meaning (here: the intended referent) by assuming that the speaker is helpful and informative.
+Being helpful and informative means that the speaker chooses a message based on the probability that it would help the listener to recover the speaker's intended meaning.
 Thus, RSA models have a recursive structure in which the the listener reasons about a speaker who is reasoning about the listener.
-To avoid an infinite regress, the speaker is assumed to reason about a literal listener, who interprets words according to their literal semantics.
+To avoid an infinite regress, the speaker is assumed to reason about a literal listener, who interprets utterances according to their literal semantics.
 
@@
 
-The age effects in Study 3 largely replicate those of Study 2 for the four overlapping tasks (see Figure \@ref(fig:fig2) and \@ref(fig:fig3).
+The age effects in Study 3 largely replicate those of Study 2 for the four overlapping tasks (see Figure \@ref(fig:fig2) and \@ref(fig:fig3)).
 There were no substantial developmental gains in the newly added relational match-to-sample task and performance was close to chance for both age groups.
@@
 Overall, the correlations between the tasks were lower compared to Study 2.
-This was to some extend expected given that there were only half the number of trials per task in Study 3 and, with that, less room for capturing individual differences.
+This was to some extent expected given that there were only half the number of trials per task in Study 3 and, with that, less room for capturing individual differences.
 Nevertheless, the overall pattern rsembles that found in Study 2 (Figure \@ref(fig:fig4)).
@@
 
-Using a diversity of different analytical tools, we found that performance in the three utterance-based pragmatic inference tasks was related in a way that points to shared cognitive processes.
+Using a diversity of analytical tools, we found that performance in the three utterance-based pragmatic inference tasks was related in a way that points to shared cognitive processes.
 In the confirmatory factor analysis, we found that a model including a latent pragmatic reasoning factor fit the data well and better compared to alternative models.
@@
 We found them to have good psychometric properties, in particular good to excellent re-test reliability.
-We then selected three utterance-based inference tasks for well-powered study of relations among different types of pragmatic abilities and between pragmatics and other cognitive processes.
+We then selected three utterance-based inference tasks for a well-powered study of relations among different types of pragmatic abilities and between pragmatics and other cognitive abilities.
 The results showed systematic relations between the tasks.
@@
 
-One of the main contributions of this paper is that if presents six pragmatic inference tasks that are highly robust and reliable.
+One of the main contributions of this paper is that it presents six pragmatic inference tasks that are highly robust and reliable.
 Whenever we used a task in two studies (mutual exclusivity, informativeness inference, ad-hoc implicature), we found the developmental results to closely replicate.
@@
 Taken together, the tasks are highly suitable for individual differences research.
-The material is freely available via the online repository associated with the study.
+The material is freely available via the associated online repository.
 
@@
 The main reason was theoretical.
-We were able to build on earlier work and formalize the inferences involved in these tasks in a common computational framework.
+We were able to build on earlier work [@bohn_tessler_merrick_frank_2019; @bohn2021young] and formalize the inferences involved in these tasks in a common computational framework.
 We specified the structural overlap between the tasks and identified a parameter in the model that we used to capture individual differences.
 The shared structural features involve a recursive social inference process according to which the listener expects the speaker to select the most informative of a set of possible utterances.
-The individual difference parameter captured how informative the listener expected the speaker to be^[this interpretation follows from the conceptual role the parameter plays in the RSA framework.
+The individual difference parameter captured how informative the listener expected the speaker to be^[This interpretation follows from the conceptual role the parameter plays in the RSA framework.
 Technically, it acts as an amplifier of the basic inference].
@@
 
-Our formal model also allows us to speculate about why we saw a systematic relation across the three studies between pragmatic inference and the card sorting task as a measure of executive functions.
+Our formal model also allowed us to speculate about why we saw a systematic relation across the three studies between pragmatic inference and the card sorting task as a measure of executive functions.
 Before we do so, we want to emphasize that the model is first and foremost a computational description of the tasks an not a model of a psychological process [cf.
@@
 The card sorting task asks the child to switch between rules half way.
-This requires inhibiting a previously dominant response and attending to different features of the cards.
+This requires inhibiting a pre-potent response and attending to different features of the cards.
 The pragmatic inference in the model involves contrasting the observed utterance with alternative utterances.
-This could be described as requiring inhibiting interpretations that follow from other plausible interpretations and considering that there would have been better ways of saying it??
-However should find a common representation and model this explicitly.
+This could be described as requiring inhibiting available, plausible interpretations and contrasting different interpretations instead before making a response.
+The next step should be to jointly model card sorting and the pragmatics tasks to substantiate such a verbal analysis.
+The model we presented here lays the foundation for such a project.
 
-Switching rules requires seeing stimuli in different light - focus on different aspect of them, consider alternative ways of seeing them, not go with what you did previously.
-The inference in the model is driven by not going just with what is true but  considering alternative utterances - some commonalities here that might be responsible - need to be modeled explicitly and contrasted to alternative views.
-(check other theoretical accounts on that).
+## Limitations
 
-We did not look at the other tasks in the same level of detail
+The studies we presented here have important limitations.
+Our focus on the utterance-based pragmatic inference tasks meant that we did no study and analyse the common ground/discourse-based tasks with the same level of detail.
+That is, we did not formalize them in a cognitive model and did not study relations between them in a larger sample.
+Future research should address these shortcomings.
+Nevertheless, the work presented here is an important first step because it showed that the tasks themselves have good psychometric properties and are therefore suitable for individual differences research.
 
-Cartoon picture book presentation - not real speakers. But results match those of earlier in personn studies and generally tablet based tasks seem to be fine.
+We presented the tasks as interactive picture books on a tablet computer with animal characters as agents.
+This improved the quality of our measurement because it allowed us to experimentally isolate the different inferences and run multiple trials in each task.
+However, it also means that -- like most experimental work -- our tasks lack ecological validity.
+In real-world conversations, multiple information sources are available to listeners to draw inferences from [@bohn2021young; @bohn_tessler_merrick_frank_2019].
+Furthermore, the setup prevented the use of strategies that are an integral part of real-world conversations, like asking questions or seeking clarification [@arkel2020simple; @clark1991grounding].
+However, we want to highlight that the tasks replicated many classical findings from interactive tasks [e.g., @markman1988children; @akhtar1996role; @saylor2009preschoolers; @frank2014inferring].
 
-Studies only weird kids from one cultural background, Nevertheless the tasks had been developed in eglish and were now used in German - suggets some portability. More needs to be done obviously.
+Finally, we only studied one sample of children from a Western, affluent setting.
+Thus, it is unclear if and how the results would transfer to other settings [@nielsen2017persistent].
+The tasks used here were largely developed and tested with English-speaking children in the US.
+The fact that they transferred well to the German setting of the current studies is at least a small hint that they might also be suitable to study pragmatic inference in other cultural and linguistic settings.
+Future research will hopefully test whether that is the case.
+
+## Conclusion
+
+The studies reported here addressed some fundamental challenges in the study of individual differences in pragmatic abilities [cf.
+@matthews2018individual].
+We developed and validated new methodological and theoretical tools that helped to study the relations between different types of pragmatic inferences as well as between pragmatics and other cognitive abilities in a more reliable and valid way.
+This approach emphasizes the interdependent nature of theoretical and methodological progress and provides a roadmap for future work.
 

### 2022-03-01 paper/manuscript.tex
first draft manuscript and analysis

@@
 \documentclass[
-  english,
   man,floatsintext]{apa6}
-\title{An individual differences perspective on the development of pragmatic reasoning in the preschool years}
-\author{Manuel Bohn\textsuperscript{1}, Michael Henry Tessler\textsuperscript{2,3}, Clara Kordt\textsuperscript{4}, Tom Hausmann\textsuperscript{5}, \& Michael C. Frank\textsuperscript{6}}
-\date{}
-
 \usepackage{amsmath,amssymb}
@@
 \hypersetup{
-  pdftitle={An individual differences perspective on the development of pragmatic reasoning in the preschool years},
+  pdftitle={An individual differences perspective on the development of pragmatic abilities in the preschool years},
   pdfauthor={Manuel Bohn1, Michael Henry Tessler2,3, Clara Kordt4, Tom Hausmann5, \& Michael C. Frank6},
   pdflang={en-EN},
-  pdfkeywords={keywords},
+  pdfkeywords={Pragmatics, language development, individual differences, cognitive modeling},
   hidelinks,
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 % Manuscript styling
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
@@
 % \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
 
@@
 \makeatother
-\shorttitle{Individual differences in pragmatic reasoning}
-\keywords{keywords\newline\indent Word count: X}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
+\keywords{Pragmatics, language development, individual differences, cognitive modeling\newline\indent Word count: X}
 \usepackage{lineno}
@@
 \usepackage{csquotes}
-\ifXeTeX
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
 \ifLuaTeX
@@
 \fi
+
+\title{An individual differences perspective on the development of pragmatic abilities in the preschool years}
+\author{Manuel Bohn\textsuperscript{1}, Michael Henry Tessler\textsuperscript{2,3}, Clara Kordt\textsuperscript{4}, Tom Hausmann\textsuperscript{5}, \& Michael C. Frank\textsuperscript{6}}
+\date{}
+
+\shorttitle{Individual differences in pragmatic abilities}
 
@@
 The authors made the following contributions.
-Manuel Bohn: Conceptualization, Analysis, Writing - Original Draft Preparation, Writing - Review \& Editing; Michael Henry Tessler: Analysis, Writing - Review \& Editing; Clara Kordt: Data collection; Tom Hausmann: Data collection; Michael C.
+Manuel Bohn: Conceptualization, Analysis, Writing - Original Draft Preparation, Writing - Review \& Editing; Michael Henry Tessler: Analysis, Writing - Review \& Editing; Clara Kordt: Data collection, Writing - Review \& Editing; Tom Hausmann: Data collection, Writing - Review \& Editing; Michael C.
 Frank: Conceptualization, Writing - Review \& Editing.
@@
 
-\abstract{
-One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
-
-Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general context}.
-
-Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
+\abstract{%
+Pragmatic abilities are fundamental to successful language use and learning.
+Individual differences studies contribute to understanding the psychological processes involved in pragmatic reasoning as well as the link to other cognitive abilities.
+Small sample sizes, insufficient measurement tools, and a lack of theoretical precision have hindered progress.
+Three studies addressed these challenges in a sample of three- to five-year-old German-speaking children (\emph{N} = 228, 121 female).
+Studies 1 and 2 assessed the psychometric properties of six pragmatics tasks.
+Study 3 investigated relations among pragmatics tasks and between pragmatics and other cognitive abilities.
+The shared cognitive processes were formalized in a computational cognitive model of pragmatic reasoning.
+Results showed substantive relations among pragmatic tasks and between pragmatic abilities and executive functions.
 }
@@
 The common thread running through these different aspects of human communication is its inferential nature: what a speaker means -- verbal or otherwise -- is underdetermined by the parts that make up the utterance.
-It takes contextual social inferences to recover the intended meaning (H.
+It takes contextual social inferences to recover the intended meaning (Bohn \& Köymen, 2018; H.
 H.
 Clark, 1996; Grice, 1991; Levinson, 2000; Sperber \& Wilson, 2001).
-These contextual social inferences are often referred to as \emph{pragmatic} inferences (e.g., Bohn \& Frank, 2019).
+These inferences are often referred to as \emph{pragmatic} inferences (e.g., Bohn \& Frank, 2019).
 
@@
 
-In their recent review of individual differences in children's pragmatic ability, Matthews et al.
-(2018) identified three issues that significantly limit what we can learn from individual differences research.
+In their recent review, Matthews et al.
+(2018) identified three issues that significantly limit what we can learn from individual differences research on pragmatic abilities.
 First, most studies have insufficient sample sizes so that small and medium sized correlations among pragmatics tasks and between pragmatics tasks and measures for other cognitive abilities cannot be reliably detected.
@@
 The six tasks we selected were developmental adaptations of referential communication games inspired by research in experimental pragmatics (Noveck \& Reboul, 2008; Noveck \& Sperber, 2004).
-They all share a common trial-by-trial structure in which the test event always involved an agent producing an ambiguous utterance that children had to resolve using pragmatic reasoning.
+They all share a common trial-by-trial structure in which the test event always involved an agent producing an ambiguous utterance that the child had to resolve using pragmatic reasoning.
 This allowed us to run multiple trials per task, and with that, to capture individual differences.
@@
 In the speaker preference task, the child had to track the preference of a speaker in order to identify the referent of a novel word (Saylor, Sabbagh, Fortuna, \& Troseth, 2009).
-Discourse novelty refers to a situation in which the child tracks the temporal appearance of objects in context and expects the speaker to refer to objects that are new in context (Akhtar, Carpenter, \& Tomasello, 1996; Diesendruck, Markson, Akhtar, \& Reudor, 2004).
+Discourse novelty refers to a situation in which the child tracks the temporal appearance of objects and expects the speaker to refer to objects that are new in context (Akhtar, Carpenter, \& Tomasello, 1996; Diesendruck, Markson, Akhtar, \& Reudor, 2004).
 In the discourse continuity task, the child had to infer and track the topic of an ongoing conversation to resolve ambiguity (Akhtar, 2002; Bohn, Le, Peloquin, Köymen, \& Frank, 2021).
 
-In addition to the pragmatics tasks, we also included a tasks for executive functions (Zelazo, 2006) and of analogical reasoning (Christie \& Gentner, 2014).
+In addition to the pragmatics tasks, we also included tasks for executive functions (Zelazo, 2006) and of analogical reasoning (Christie \& Gentner, 2014).
 Executive functions refer to a family of top-down mental processes that enable us to inhibit automatic or intuitive responses and allow us to concentrate and focus attention on particulars (Diamond, 2013).
 A substantial body of research has investigated the link between executive functions and pragmatics -- with mixed results (Matthews et al., 2018; Nilsen \& Graham, 2009).
-Analogical reasoning refers to the ability to reason about abstract relations between stimuli (Carstensen \& Frank, 2021) -- an ability that has not been linked to pragmatics, at least not to the same extent as executive functions.
+Analogical reasoning refers to the ability to reason about abstract relations between stimuli (Carstensen \& Frank, 2021) -- an ability that has not been linked to pragmatics -- at least not to the same extent as executive functions.
 
@@
 
+Study 1 focused on the psychometric properties of four pragmatics tasks, in particular, their re-test reliability.
+two of the tasks were from the utterance-based group and two from the common ground/discourse-based group.
+As a fifth task, we included a measure of executive functions.
 Methods and sample size were pre-registered at \url{https://osf.io/6a723}.
@@
 The animal asked the child to give them one of the objects (e.g., ``Can you give me the car'').
-the objects were chosen so that children of the youngest age group would easily understand them (car and ball).
+The objects were chosen so that children of the youngest age group would easily understand them (car and ball).
 This procedure familiarized the child with the general logic of the animals making requests and the child touching objects.
@@
 
-This task was directly taken from Bohn, Tessler, Merrick, and Frank (2021).
+This task was adapted from Bohn, Tessler, Merrick, and Frank (2021).
 The task layout and the procedure was the same as in the training.
@@
 Both object types changed from trial to trial.
-Following Bohn et al.
+Following Bohn, Tessler, et al.
 (2021), the familiar objects varied in terms of the likelihood that they would be familiar to children in the age range (carrot, duck, eggplant, garlic, horseshoe).
@@
 
-The task was directly taken from Bohn, Tessler, Merrick, and Frank (2022).
+The task was adapted from Bohn, Tessler, Merrick, and Frank (2022).
 Th animal was standing between two trees with objects hanging in them.
@@
 
-This task was also taken from Bohn et al.
+This task was also adapted from Bohn et al.
 (2022).
@@
 
-This task was taken from Bohn et al.
+This task was adapted from Bohn, Tessler, et al.
 (2021).
@@
 
-We analysed the data in three steps. First we investigated developmental effects in each task, then we assessed re-test reliability and finally, we looked at relations between the tasks.
-
+We analysed the data in three steps.
+First we investigated developmental effects in each task, then we assessed re-test reliability and finally, we looked at relations between the tasks.
 All analysis were run in \texttt{R} (R Core Team, 2018) version 4.1.2.
@@
 To estimate developmental effects in each task, we fit a GLMM predicting correct responses (0/1) by age (centered at the mean) and trial number (also centered).
-The model included random intercepts for each participant and random slopes for trial within participants (model notation in \texttt{R}: \texttt{correct\ \textasciitilde{}\ age\ +\ trial\ +\ (trial\textbar{}id)} ).
+The model included random intercepts for each participant and random slopes for trial within participants (model notation in \texttt{R}: \texttt{correct\ \textasciitilde{}\ age\ +\ trial\ +\ (trial\textbar{}id)} )\footnote{We pre-registered the inclusion of random intercepts for item.
+We deviate from this here for the following reason: the order of items was fixed and the same for all participants so that trial and item were confounded.}.
 For each task, we inspected and visualized the posterior distribution (mean and 95\% Credible Interval (CrI)) for the age estimate.
@@
 
-Re-test reliability was high for most tasks (see Figure \ref{fig:fig2}).
-Raw correlations between the two test sessions was above .7 for mutual exclusivity, speaker preference and discourse novelty.
+Re-test reliability was high for most tasks (see Figure \ref{fig:fig4}).
+Raw correlation between the two test sessions was above .7 for mutual exclusivity, speaker preference and discourse novelty.
 With .62 it was slightly lower for card sorting.
 The model based -- age independent -- reliability estimates yielded similar results suggesting that the tasks did capture task specific individual differences.
-A notable exception was the informativeness inference task, which was not reliable according to any of the methods of computing re-test correlations.
-We suspect the overall low variation in performance to be responsible for this.
+A notable exception was the informativeness inference task, which was not reliable according to any of the methods of computing re-test reliability (Figure \ref{fig:fig4}).
+We suspected the overall low variation in performance to be responsible for this.
 
@@
 
-This task was directly taken from Bohn et al.
+This task was adapted from Bohn, Le, et al.
 (2021).
-Children were told that they were going to visit the animals at their place.
-The animal greeted the child and told them that they would show them their things.
+Children were told that they were going to visit the animals in their home.
+An animal greeted the child and told them that they would show them their things.
 During exposure trials, the child saw three objects from three different categories (e.g., train (vehicle), drum (instrument), orange (fruit); see Figure \ref{fig:fig1}).
-The animal named of the objects and asked the child to touch it.
+The animal named one of the objects and asked the child to touch it.
 On the next exposure trial, the child saw three new objects but from the same categories (e.g., bus (vehicle), flute (instrument), apple (fruit)).
@@
 On the following test trial, the animal used a pronoun to refer to one of the objects (i.e., can you touch \emph{it}).
-We assumed that children would use the exposure trials to infer that the animal was talking about a certain category and would use this knowledge to identify the referent of the pronoun.Children received five test trials, each with a different category as the target.
+We assumed that children would use the exposure trials to infer that the animal was talking about a certain category and would use this knowledge to identify the referent of the pronoun.
+Children received five test trials, each with a different category as the target.
 The position of the objects in exposure trials as well as test trials was pseudo-randomized.
@@
 That is, they include a schematic representation of the experimental tasks and provide a computational account of how participants make inferences in this context.
-RSA models see pragmatic inferences as a form of Bayesian social reasoning where the listener tries to infer the speaker' meaning (here: the intended referent) by assuming that the speaker is helpful and informative.
-Being helpful and informative means that the speaker chooses a message based on the probability that it would help the listener would recover the speaker's intended meaning.
+RSA models see pragmatic inferences as a form of Bayesian social reasoning where the listener tries to infer the speaker's meaning (here: the intended referent) by assuming that the speaker is helpful and informative.
+Being helpful and informative means that the speaker chooses a message based on the probability that it would help the listener to recover the speaker's intended meaning.
 Thus, RSA models have a recursive structure in which the the listener reasons about a speaker who is reasoning about the listener.
-To avoid an infinite regress, the speaker is assumed to reason about a literal listener, who interprets words according to their literal semantics.
-
-The studies from which we took the mutual exclusivity and informativeness inference tasks also formalized these tasks in an RSA-style model (Bohn et al., 2021, 2022).
+To avoid an infinite regress, the speaker is assumed to reason about a literal listener, who interprets utterances according to their literal semantics.
+
+The studies from which we took the mutual exclusivity and informativeness inference tasks also formalized these tasks in an RSA-style model (Bohn, Tessler, et al., 2021; Bohn et al., 2022).
 We refer to this earlier work for more details and a mathematical description of the models.
@@
 
-The age effects in Study 3 largely replicate those of Study 2 for the four overlapping tasks (see Figure \ref{fig:fig2} and \ref{fig:fig3}.
+The age effects in Study 3 largely replicate those of Study 2 for the four overlapping tasks (see Figure \ref{fig:fig2} and \ref{fig:fig3}).
 There were no substantial developmental gains in the newly added relational match-to-sample task and performance was close to chance for both age groups.
@@
 Overall, the correlations between the tasks were lower compared to Study 2.
-This was to some extend expected given that there were only half the number of trials per task in Study 3 and, with that, less room for capturing individual differences.
+This was to some extent expected given that there were only half the number of trials per task in Study 3 and, with that, less room for capturing individual differences.
 Nevertheless, the overall pattern rsembles that found in Study 2 (Figure \ref{fig:fig4}).
@@
 The main reason was theoretical.
-We were able to build on earlier work and formalize the inferences involved in these tasks in a common computational framework.
+We were able to build on earlier work (Bohn, Tessler, et al., 2021; Bohn et al., 2022) and formalize the inferences involved in these tasks in a common computational framework.
 We specified the structural overlap between the tasks and identified a parameter in the model that we used to capture individual differences.
 The shared structural features involve a recursive social inference process according to which the listener expects the speaker to select the most informative of a set of possible utterances.
-The individual difference parameter captured how informative the listener expected the speaker to be\footnote{this interpretation follows from the conceptual role the parameter plays in the RSA framework.
+The individual difference parameter captured how informative the listener expected the speaker to be\footnote{This interpretation follows from the conceptual role the parameter plays in the RSA framework.
 Technically, it acts as an amplifier of the basic inference}.
@@
 
-Our formal model also allows us to speculate about why we saw a systematic relation across the three studies between pragmatic inference and the card sorting task as a measure of executive functions.
+Our formal model also allowed us to speculate about why we saw a systematic relation across the three studies between pragmatic inference and the card sorting task as a measure of executive functions.
 Before we do so, we want to emphasize that the model is first and foremost a computational description of the tasks an not a model of a psychological process (cf.
@@
 The card sorting task asks the child to switch between rules half way.
-This requires inhibiting a previously dominant response and attending to different features of the cards.
+This requires inhibiting a pre-potent response and attending to different features of the cards.
 The pragmatic inference in the model involves contrasting the observed utterance with alternative utterances.
-This could be described as requiring inhibiting interpretations that follow from other plausible interpretations and considering that there would have been better ways of saying it??
-However should find a common representation and model this explicitly.
-
-Switching rules requires seeing stimuli in different light - focus on different aspect of them, consider alternative ways of seeing them, not go with what you did previously.
-The inference in the model is driven by not going just with what is true but considering alternative utterances - some commonalities here that might be responsible - need to be modeled explicitly and contrasted to alternative views.
-(check other theoretical accounts on that).
-
-We did not look at the other tasks in the same level of detail
-
-Cartoon picture book presentation - not real speakers. But results match those of earlier in personn studies and generally tablet based tasks seem to be fine.
-
-Studies only weird kids from one cultural background, Nevertheless the tasks had been developed in eglish and were now used in German - suggets some portability. More needs to be done obviously.
+This could be described as requiring inhibiting available, plausible interpretations and contrasting different interpretations instead before making a response.
+The next step should be to jointly model card sorting and the pragmatics tasks to substantiate such a verbal analysis.
+The model we presented here lays the foundation for such a project.
+
+\hypertarget{limitations}{%
+\subsection{Limitations}\label{limitations}}
+
+The studies we presented here have important limitations.
+Our focus on the utterance-based pragmatic inference tasks meant that we did no study and analyse the common ground/discourse-based tasks with the same level of detail.
+That is, we did not formalize them in a cognitive model and did not study relations between them in a larger sample.
+Future research should address these shortcomings.
+Nevertheless, the work presented here is an important first step because it showed that the tasks themselves have good psychometric properties and are therefore suitable for individual differences research.
+
+We presented the tasks as interactive picture books on a tablet computer with animal characters as agents.
+This improved the quality of our measurement because it allowed us to experimentally isolate the different inferences and run multiple trials in each task.
+However, it also means that -- like most experimental work -- our tasks lack ecological validity.
+In real-world conversations, multiple information sources are available to listeners to draw inferences from (Bohn, Tessler, et al., 2021; Bohn et al., 2022).
+Furthermore, the setup prevented the use of strategies that are an integral part of real-world conversations, like asking questions or seeking clarification (Arkel, Woensdregt, Dingemanse, \& Blokpoel, 2020; H.
+H.
+Clark \& Brennan, 1991).
+However, we want to highlight that the tasks replicated many classical findings from interactive tasks (Akhtar et al., 1996; Frank \& Goodman, 2014; e.g., Markman \& Wachtel, 1988; Saylor et al., 2009).
+
+Finally, we only studied one sample of children from a Western, affluent setting.
+Thus, it is unclear if and how the results would transfer to other settings (Nielsen, Haun, Kärtner, \& Legare, 2017).
+The tasks used here were largely developed and tested with English-speaking children in the US.
+The fact that they transferred well to the German setting of the current studies is at least a small hint that they might also be suitable to study pragmatic inference in other cultural and linguistic settings.
+Future research will hopefully test whether that is the case.
+
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
+
+The studies reported here addressed some fundamental challenges in the study of individual differences in pragmatic abilities (cf.
+Matthews et al., 2018).
+We developed and validated new methodological and theoretical tools that helped to study the relations between different types of pragmatic inferences as well as between pragmatics and other cognitive abilities in a more reliable and valid way.
+This approach emphasizes the interdependent nature of theoretical and methodological progress and provides a roadmap for future work.
 
@@
 Akhtar, N., Carpenter, M., \& Tomasello, M. (1996). The role of discourse novelty in early word learning. \emph{Child Development}, \emph{67}(2), 635--645.
+
+\leavevmode\vadjust pre{\hypertarget{ref-arkel2020simple}{}}%
+Arkel, J. van, Woensdregt, M., Dingemanse, M., \& Blokpoel, M. (2020). \emph{A simple repair mechanism can alleviate computational demands of pragmatic reasoning: Simulations and complexity analysis}.
 
@@
 Bohn, M., \& Frank, M. C. (2019). The pervasive role of pragmatics in early language. \emph{Annual Review of Developmental Psychology}, \emph{1}(1), 223--249.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bohn2018common}{}}%
+Bohn, M., \& Köymen, B. (2018). Common ground and development. \emph{Child Development Perspectives}, \emph{12}(2), 104--108.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-clark1991grounding}{}}%
+Clark, H.
+H., \& Brennan, S.
+E.
+(1991).
+Grounding in communication.
+In L.
+B.
+Resnick, J.
+M.
+Levine, \& S.
+D.
+Teasley (Eds.), \emph{Perspectives on socially shared cognition.} (pp.
+127--149).
+American Psychological Association.
+
 \leavevmode\vadjust pre{\hypertarget{ref-diamond2013executive}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-dippl}{}}%
-Goodman, N. D., \& Stuhlmüller, A. (2014). {The design and implementation of probabilistic programming languages}. \url{http://dippl.org}.
+Goodman, N. D., \& Stuhlmüller, A. (2014). \emph{{The design and implementation of probabilistic programming languages}}. \url{http://dippl.org}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-nielsen2017persistent}{}}%
+Nielsen, M., Haun, D., Kärtner, J., \& Legare, C.
+H.
+(2017).
+The persistent sampling bias in developmental psychology: A call to action.
+\emph{Journal of Experimental Child Psychology}, \emph{162}, 31--38.
+
 \leavevmode\vadjust pre{\hypertarget{ref-nilsen2009relations}{}}%

### 2022-03-01 experiments/ad_hoc.js
chnage to data download

@@ -1,173 +1,173 @@
-
 // the actual experiment
 var adhoc = {
-  trial: ["train1","train2",1,2,3,4,5],
-  agents: ["Sheep"],
-  agentOrient: [
-          ["straight","down"],
-          ["straight","down"],
-          ["straight","down"],
-          ["straight","down"],
-          ["straight","down"],
-        ["straight","down"],
-      ["straight","down"]],
-  stimulus: ["house_train","friend_train","box","chair","table","plate","house"],
-  infPos: ["left", "right","left", "right", "right", "left", "right"],
-  data: [],
+    trial: ["train1", "train2", 1, 2, 3, 4, 5],
+    agents: ["Sheep"],
+    agentOrient: [
+        ["straight", "down"],
+        ["straight", "down"],
+        ["straight", "down"],
+        ["straight", "down"],
+        ["straight", "down"],
+        ["straight", "down"],
+        ["straight", "down"]
+    ],
+    stimulus: ["house_train", "friend_train", "box", "chair", "table", "plate", "house"],
+    infPos: ["left", "right", "left", "right", "right", "left", "right"],
+    data: [],
 
 
 
-// end of the experiment
-  end: function() {
-    // Show the finish slide.
-    showSlide("select");
-    setTimeout(function() { downloadData(adhoc.data) }, 500);
-  },
+    // end of the experiment
+    end: function() {
+        // Show the finish slide.
+        showSlide("select");
+        setTimeout(function() { downloadData(adhoc.data) }, 500);
+    },
 
 
-// what happens between trials - display agent from previous trial and click on it to move on to the next trial
-   eat: function(event) {
+    // what happens between trials - display agent from previous trial and click on it to move on to the next trial
+    eat: function(event) {
 
-    setTimeout(function() {adhoc.eat2() }, 1500);
+        setTimeout(function() { adhoc.eat2() }, 1500);
 
-    showSlide("adhoc");
+        showSlide("adhoc");
 
-    event.target.style.border = '5px solid blue';
+        event.target.style.border = '5px solid blue';
 
-    sourceSound("sound/end.mp3");
-    playSound();
+        sourceSound("sound/end.mp3");
+        playSound();
 
 
-    $(".object_r").unbind("click");
-    $(".object_l").unbind("click");
+        $(".object_r").unbind("click");
[…]

### 2022-03-01 experiments/discourse_continuity.js

@@ -1,4 +1,3 @@
-
 var backgroundImages = new Array();
 for (i = 1; i <= 12; i++) {
     backgroundImages[i] = new Image();
@@ -277,7 +276,13 @@ function shuffleByIndex(array) {
 shuffleByIndex(trialTargets);
 shuffleByIndex(trialFamiliarItems);
 
-var posDist = shuffle([[6, 0, 0], [6, 0, 0], [6, 0, 0], [6, 0, 0],[6, 0, 0]]);
+var posDist = shuffle([
+    [6, 0, 0],
+    [6, 0, 0],
+    [6, 0, 0],
+    [6, 0, 0],
+    [6, 0, 0]
+]);
 
 //distribution for each trial
 var trainingDist = new Array();
@@ -332,13 +337,13 @@ var discon = {
 
     sound: new Audio(),
 
-    introAll: function () {
+    introAll: function() {
         showSlide("introAll");
         document.getElementById("text_introAll").innerHTML = "In diesem Spiel nehmen Dich die Tiere mit zu sich nach Hause. Jedes der Tiere wohnt in einem Haus und jedes hat viele verschiedene Dinge zu hause. Jedes Tier erzählt Dir von den Dingen die es zu Hasue hat.";
         document.getElementById("text_introAll_2").innerHTML = "Deine Aufgabe ist es, das Ding zu berühren, über das das Tier spricht. Pass also gut auf und finde heraus welches Du berühren musst.";
     },
 
-    intro: function () {
+    intro: function() {
 
         $(".agent_transition").unbind("click");
 
@@ -353,17 +358,17 @@ var discon = {
 
         sound = document.getElementById("sound");
 
-        sound.onended = function () {
+        sound.onended = function() {
             sourceSound("sound/" + "intro_" + trainingAgents[trials[0]] + ".mp3");
             playSound();
             sound = document.getElementById("sound");
-            sound.onended = function () {
+            sound.onended = function() {
                 $(".agent_transition").click(discon.train);
             };
         };
     },
 
-    train: function () {
+    train: function() {
         backgroundDis("images/backgrounds/back_int" + discon.backgrounds[0] + ".jpg");
 
         showSlide("input");
@@ -392,7 +397,7 @@ var discon = {
         hideRightItem();
 
         // pause for 1s before images appear
-        setTimeout(function () {
+        setTimeout(function() {
 
             showLeftItem();
             showMiddleItem();
@@ -403,7 +408,7 @@ var discon = {
[…]

### 2022-03-01 experiments/novelty.js

@@ -21,7 +21,7 @@ var novelty = {
     end: function() {
         // Show the finish slide.
         showSlide("select");
-        setTimeout(function() { turk.submit(novelty) }, 1000);
+        setTimeout(function() { downloadData(novelty.data) }, 0);
     },
 
 

### 2022-03-01 experiments/pragBat.js

@@ -109,6 +109,20 @@ function submitButtonStyle(_this) {
     _this.style.backgroundColor = "green";
 }
 
+// download data as .json file
+function downloadData(safe) {
+    var toSave = JSON.stringify(safe)
+
+    var date = new Date().toISOString()
+    var day = date.substr(0, 10)
+    var time = date.substr(11, 8)
+
+    var hiddenElement = document.createElement('a');
+    hiddenElement.href = 'data:text/json;charset=utf-8,' + encodeURI(toSave);
+    hiddenElement.target = '_blank';
+    hiddenElement.download = 'pragBat-' + train.subid + '-' + data.task + '-' + day + '-' + time + '.json';
+    hiddenElement.click();
+}
 
 // ## Helper functions
 
@@ -381,7 +395,7 @@ var train = {
     end: function() {
         // Show the finish slide.
         showSlide("select");
-        setTimeout(function() { turk.submit(train) }, 500);
+        setTimeout(function() { downloadData(train.data) }, 0);
     },
 
     // end of training  

### 2022-03-01 experiments/preference.js

@@ -1,238 +1,239 @@
 // beginning of actual experiment
 var preference = {
-  // Parameters for this sequence.
-  trial: [1,2,3,4,5],
-  agents: ["Monkey","Bunny","Cat","Dog","Frog"],
-  agentOrient: [
-    ["straight","point_r", "point_l","down"],
-    ["straight","point_l", "point_r","down"],
-    ["straight","point_r", "point_l","down"],
-    ["straight","point_l", "point_r","down"],
-    ["straight","point_r", "point_l","down"]],
-  rightFruit: ["t01","t02","t03","t04","t05"],
-  leftFruit: ["t07","t06","t08","t09","t10"],
-  pref: ["right", "left", "left", "right", "left"],
-  back: [1,2,3,4,5],
-  data: [],
-   
-    
-  
-// end of the experiment
-  end: function() {
-    // Show the finish slide.
-    showSlide("select");
-    setTimeout(function() {turk.submit(preference) }, 500);
-  },
-    
+    // Parameters for this sequence.
+    trial: [1, 2, 3, 4, 5],
+    agents: ["Monkey", "Bunny", "Cat", "Dog", "Frog"],
+    agentOrient: [
+        ["straight", "point_r", "point_l", "down"],
+        ["straight", "point_l", "point_r", "down"],
+        ["straight", "point_r", "point_l", "down"],
+        ["straight", "point_l", "point_r", "down"],
+        ["straight", "point_r", "point_l", "down"]
+    ],
+    rightFruit: ["t01", "t02", "t03", "t04", "t05"],
+    leftFruit: ["t07", "t06", "t08", "t09", "t10"],
+    pref: ["right", "left", "left", "right", "left"],
+    back: [1, 2, 3, 4, 5],
+    data: [],
 
-// what happens between trials - display agent from previous trial and click on it to move on to the next trial  
+
+
+    // end of the experiment
+    end: function() {
+        // Show the finish slide.
+        showSlide("select");
+        setTimeout(function() { downloadData(preference.data) }, 0);
+    },
+
+
+    // what happens between trials - display agent from previous trial and click on it to move on to the next trial  
     eat: function(event) {
 
-    setTimeout(function() {preference.eat2() }, 1500);
-     
-    $(".fruit_r").unbind("click");
-    $(".fruit_l").unbind("click");    
-        
-    showSlide("choice");  
-       
-    event.target.style.border = '5px solid blue';
-    
-    sourceSound("sound/end.mp3");
-    playSound();
[…]

### 2022-04-07 analysis/analysis.Rmd
run reli models

@@
 ```{r}
-library("papaja")
 library(tidyverse)
@@
 library(coda)
-#library(ggdist)
-#library(psy)
-#library(tidyboot)
-#library(ggpubr)
-#library(blavaan)
+library(blavaan)
 library(brms)
+library(ggpubr)
+library(scales)
+library(tidyboot)
+library(ggridges)
 
@@
   geom_hline(data = p2, aes(yintercept = chance), lty = 3)+
-  geom_jitter(data = p1, aes(x = age, y = mean, pch = study), alpha = .25, width = .05, height = .01)+
-  geom_smooth(data = pred, aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5, lty =study), stat = "identity", col = "black", size = 1, alpha = .25)+
+  geom_jitter(data = p1, aes(x = age, y = mean, col = study), alpha = .25, width = .05, height = .01)+
+  geom_smooth(data = pred, aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5, col =study), stat = "identity", size = 1, alpha = .25)+
   facet_wrap(~task, nrow = 2, labeller = as_labeller(task_names))+
-    geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = factor(subage), pch = study), position = position_dodge(width = .5))+
+    geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = study), position = position_dodge(width = .5))+
   labs(x = "Age", y = "Proportion correct") +
-  scale_color_ptol(name = "Age group", labels = c("3-year-olds", "4-year-olds")) +
+  scale_color_colorblind(name = "Study", labels = c("Study 1", "Study 2", "Study 3"))+
   ylim(-0.05, 1.05)+
-  scale_shape_manual(values=c(1, 2, 4), name = "Study", labels = c("Study 1", "Study 2", "Study 3"))+
-  scale_linetype_manual(values=c(1, 2, 3), name = "Study", labels = c("Study 1", "Study 2", "Study 3"))+
+  #scale_shape_manual(values=c(1, 2, 4), name = "Study", labels = c("Study 1", "Study 2", "Study 3"))+
+  #scale_linetype_manual(values=c(1, 2, 3), name = "Study", labels = c("Study 1", "Study 2", "Study 3"))+
   theme_few()+
-  theme(legend.position = c(.9,.225), legend.direction = "vertical", legend.box = "horizontal")+
-  guides(shape = guide_legend(order = 2),linetype = guide_legend(order = 2), col = guide_legend(order = 1))
+  theme(legend.position = c(.9,.225), legend.direction = "vertical", legend.box = "horizontal")
+  #theme(legend.position = "bottom", legend.direction = "horizontal", legend.box = "horizontal")
+  #guides(shape = guide_legend(order = 2),linetype = guide_legend(order = 2), col = guide_legend(order = 1))
 
-ggsave(plot = pf2,"../paper/figures/figure2.png", width = 10, height = 4, scale = 1.25)
+ggsave(plot = pf2,"../paper/figures/figure2_2.png", width = 10, height = 4.5, scale = 1)
 ```
@@
 
-Here we extract and summarize the person specific $\alpha$ estimates and correalte them to performance in the card sorting and relational match-to-sample tasks.
+Here we extract and summarize the person specific $\alpha$ estimates and correlate them to performance in the card sorting and relational match-to-sample tasks.
 
@@
 
-prsacor <- ggplot(rsa, aes(x = mean, y = mode))+
+prsacor <- ggplot(rsa, aes(x = mode, y = mean))+
   #geom_abline(intercept = 2, slope = 1, lty = 2, alpha = .75)+
@@
   geom_smooth(method = "lm", col= "firebrick")+
-  geom_text(data = cor, aes(label = label),y = 4.9, x = 0.2)+
-  labs(x = "Mean proportion correct", y = "RSA model estimate (\u03b1)")+
+  geom_text(data = cor, aes(label = label),x = 1, y = 0.9)+
+  labs(y = "Mean proportion correct", x = "RSA model estimate (\u03b1)")+
   facet_grid(~task)+
@@
 
-Here we summarise the parameter esteimates for each test session and correlate them to get a measure of re-test reliability.
+Here we summarize the parameter estimates for each test session and correlate them to get a measure of re-test reliability.
 
@@
 
-ggsave(plot = prsa,"../paper/figures/figure6.png", width = 10, height = 4, scale = 1.25)
+ggsave(plot = prsa,"../paper/figures/figure6.png", width = 10, height = 4, scale = 1.25, bg = "white")
 ```

### 2022-04-07 analysis/analysis.Rmd
update run

--- 2022-02-22 analysis/analysis.Rmd
@@
 library(reshape2)
-library(coda)
-#library(ggdist)
-#library(psy)
-#library(tidyboot)
-#library(ggpubr)
-#library(blavaan)
 library(brms)
-
-estimate_mode <- function(s) {
-  d <- density(s)
-  return(d$x[which.max(d$y)])
-}
-
-hdi_upper<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","upper"])
-}
-
-hdi_lower<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","lower"])
-}
+library(psy)
+library(tidyboot)
+library(ggpubr)
+library(blavaan)
 ```
-# Data
 
@@
   mutate(study = factor(study),
-         id = paste(study, id, sep = "_"),
-         test_day = factor(test_day))
+         id = paste(study, id, sep = "_"))
+
+data%>%
+  group_by(task)%>%
+  summarise(trials = length(unique(trial)))
 ```
@@
 ```
-
 # Reliability
-
 ```{r}
@@
 ```{r}
-model <- 'prag  =~ ad_hoc_implicature + mutual_exclusivity + simple_inf
+model <- 'prag  =~ " mutual_exclusivity + ad_hoc_implicature + simple_inf
           card  =~ card_sorting
@@
 
-model2 <- 'fac  =~ ad_hoc_implicature + mutual_exclusivity+ simple_inf + card_sorting + match_to_sample'
+model2 <- 'fac  =~ mutual_exclusivity + ad_hoc_implicature+ simple_inf + card_sorting + match_to_sample'
 
@@
 ```{r}
-# fit <- bcfa(model, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
-# saveRDS(fit, "../saves/bcfa_prag.rds")
+fit <- bcfa(model, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
+saveRDS(fit, "../saves/bcfa_prag.rds")
 fit <- readRDS("../saves/bcfa_prag.rds")
 
-# fit2 <- bcfa(model2, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
-# saveRDS(fit2, "../saves/bcfa_single.rds")
+fit2 <- bcfa(model2, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
+saveRDS(fit2, "../saves/bcfa_single.rds")
 fit2 <- readRDS("../saves/bcfa_single.rds")
 
-# fit3 <- bcfa(model3, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
-# saveRDS(fit3, "../saves/bcfa_separate.rds")
+fit3 <- bcfa(model3, data = cfad, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
+saveRDS(fit3, "../saves/bcfa_separate.rds")
 fit3 <- readRDS("../saves/bcfa_separate.rds")
-
 ```
@@
 ```{r}
-bind_rows(
-fitmeasures(fit)%>%as_tibble(rownames = "index")%>%
-  mutate(model = "fit1"),
-fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%
-  mutate(model = "fit2"),
-fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%
-  mutate(model = "fit3")
-)%>%
-  write_csv("../saves/cfa_fit_measures.csv")
+fitmeasures(fit)%>%as_tibble(rownames = "index")
 
-summary(fit2, fit.measures=TRUE, standardized = TRUE, rsquare = T)
+x <- summary(fit, fit.measures=TRUE, standardized = TRUE, rsquare = T)
 
 blavInspect(fit, what = "postmean")%>%as_tibble(rownames = "index")%>%
-  left_join(blavInspect(fit, what = "hpd")%>%as_tibble(rownames = "index"))%>%
-  write_csv("../saves/cfa_estimates.csv")
+  left_join(blavInspect(fit, what = "hpd")%>%as_tibble(rownames = "index"))
 
@@
 ```
-
-# RSA model
-
-```{r}
-rsa_model <- readRDS("../../../Spin-off/spin-off/model/output/model_pragBat3.rds")
-```
-
-```{r}
-scale <- rsa_model %>%
-  filter(parameter == "speaker_optimality",
-         token == "scale_parameter")
-
-pscale <- ggplot(scale, aes(x = value))+
-  geom_density( alpha = 0.3, aes(fill = id), col = "black", adjust = 3)+
-  geom_vline(xintercept = 1, lty = 2, col = "black", alpha = .75)+
-  xlab("Scale parameter")+
-  ylab("Density")+
-  #facet_grid(~id, scale = "free_x")+
-  theme_few()+
-  scale_fill_viridis_d(name = "Task", labels = c("Informativeness inference", "Mutual exclusivity"))+
-  theme(legend.position = c(.6,.7))
-```
-
-```{r}
-so_est <- rsa_model %>%
-  filter(parameter == "speaker_optimality",
-         type == "subj_parameter",
-         token == "speaker_optimality")%>%
-  group_by(id)%>%
-  summarise(mode = estimate_mode(value),
-            uci = hdi_upper(value),
-            lci = hdi_lower(value))
-
-rsa <- data%>%
-  filter(study == "study3", task == "card_sorting" | task == "match_to_sample")%>%
-  group_by(id, task)%>%
-  summarise(mean = mean(correct))%>%
-  mutate(id = str_remove(id, "study3_"))%>%
-  ungroup()%>%
-  left_join(so_est)%>%
-    mutate(task = recode(task,
-                    `card_sorting` = "Card Sorting",
-                    `match_to_sample` = "Relational Match-to-sample"))
-
-cor <- rsa%>%
-  group_by(task)%>%
-  summarize(cor = round(cor.test(mean,mode)$estimate,2),
-            lci =  round(cor.test(mean,mode)$conf.int[1],2),
-            uci =  round(cor.test(mean,mode)$conf.int[2],2))%>%
-  mutate(label = paste0("r = ", cor, " (",lci, " - ", uci,")"))
-
-write_csv(cor, "../saves/rsa_cor_estimates.csv")
-
-prsacor <- ggplot(rsa, aes(x = mean, y = mode))+
-  #geom_abline(intercept = 2, slope = 1, lty = 2, alpha = .75)+
-  geom_point(pch = 1, alpha = .75)+
-  geom_smooth(method = "lm", col= "firebrick")+
-  geom_text(data = cor, aes(label = label),y = 4.9, x = 0.2)+
-  labs(x = "Mean proportion correct", y = "RSA model estimate (\u03b1)")+
-  facet_grid(~task)+
-  theme_few()
-
-```
-
-```{r}
-rel_rsa_model <- readRDS("../../../Spin-off/spin-off/data/rsa_rel_est.rds")
-```
-
-```{r}
-so_id_summary <- rel_rsa_model%>%
-  group_by(day,id)%>%
-  summarise(mode = estimate_mode(value),
-            uci = hdi_upper(value),
-            lci = hdi_lower(value))%>%
-  pivot_wider(names_from = c(day), values_from = c(mode,uci,lci))
-
-cor <- tibble(cor =  paste0(
-  "r = ",
-  round(cor.test(so_id_summary$mode_1, so_id_summary$mode_2)$estimate, 2),
-  " (",
-  round(cor.test(so_id_summary$mode_1, so_id_summary$mode_2)$conf.int[1], 2),
-  " - ",
-  round(cor.test(so_id_summary$mode_1, so_id_summary$mode_2)$conf.int[2], 2),
-  ")"
-  )
-  )
-
-prelrsa <- ggplot(so_id_summary, aes(x = mode_1, y = mode_2))+
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
-  geom_errorbar(aes(ymin = lci_2, ymax = uci_2),width = 0, alpha = .5, col = "grey")+
-  geom_errorbarh(aes(xmin = lci_1, xmax = uci_1), height = 0, alpha = .5, col = "grey")+
-    geom_point(pch = 1, size = 2)+
-    labs(x = "Day 1", y = "Day 2")+
-  scale_y_continuous(limits=c(0,8),oob=squish)+
-  #facet_grid(~chain)+
-  geom_text(data = cor, aes(label =  cor), x = 0, y =7.5, hjust = 0)+
-  #stat_cor(method = "pearson", aes(x = mode_1, y = mode_2), inherit.aes = F, size = 3)+
-  theme_few()
-```
-
-```{r}
-prsa <- ggarrange(
-  prsacor,
-  ggarrange(prelrsa, pscale, nrow = 2  , labels = c("", "C")),
-  widths = c(3,1),
-  labels = c("A", "B")
-)
-
-ggsave(plot = prsa,"../paper/figures/figure6.png", width = 10, height = 4, scale = 1.25)
-```

### 2022-04-07 paper/manuscript.Rmd

@@
       - Conceptualization
-      - Analysis
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
+      - Methodology
+      - Formal Analysis
+      - Visualization
+      - Writing – original draft
+      - Writing – review & editing
   - name          : "Michael Henry Tessler"
@@
     role:
-      - Analysis
-      - Writing - Review & Editing
+      - Formal Analysis
+      - Writing – review & editing
   - name          : "Clara Kordt"
@@
     role:
-      - Data collection
-      - Writing - Review & Editing
+      - Investigation
+      - Writing – review & editing
   - name          : "Tom Hausmann"
@@
     role:
-      - Data collection
-      - Writing - Review & Editing
+      - Investigation
+      - Writing – review & editing
   - name          : "Michael C. Frank"
@@
       - Conceptualization
-      - Writing - Review & Editing
+      - Writing – review & editing
 
@@
   - id            : "3"
-    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
+    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology, Cambridge, USA"
   - id            : "4"
-    institution   : "Martin Luther University Halle-Wittenberg"
+    institution   : "Martin Luther University Halle-Wittenberg, Halle (Saale), Germany"
   - id            : "5"
-    institution   : "Brandenburg Medical School Theodor Fontane"
+    institution   : "Brandenburg Medical School Theodor Fontane, Neuruppin, Germany"
   - id            : "6"
-    institution   : "Department of Psychology, Stanford University"
+    institution   : "Department of Psychology, Stanford University, Stanford, USA"
 
@@
 The model included random intercepts for each participant and random slopes for trial within participants (model notation in `R`: `correct ~ age + trial + (trial|id)` )^[We pre-registered the inclusion of random intercepts for item.
-We deviate from this here for the following reason: the order of items was fixed and the same for all participants so that trial and item were confounded.].
+We deviate from this here because the order of items was fixed and the same for all participants so that trial and item were confounded.].
 For each task, we inspected and visualized the posterior distribution (mean and 95% Credible Interval (CrI)) for the age estimate.

### 2022-04-07 analysis/analysis.Rmd
add model based reliability file

--- 2022-04-07 analysis/analysis.Rmd
@@
           #save_all_pars = TRUE,
-          iter = 2000)
+          iter = 4000)
 

### 2022-04-07 analysis/analysis.Rmd
add model based rli

@@
 
-          cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_dayday1,test_dayday2)")%>%mutate(task = i , study = "study1")
+          cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_day1,test_day2)")%>%mutate(task = i , study = "study1")
 
@@
 
-          cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_dayday1,test_dayday2)")%>%mutate(task = i , study = "study2")
+          cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_day1,test_day2)")%>%mutate(task = i , study = "study2")
 

### 2022-04-07 analysis/analysis.Rmd
prep merge

@@
 ```{r}
-model_cor <- data_frame()
-
-tasks1 <- unique(data$task[data$study == "study1"])
-
-for(i in tasks1) {
-
-  model <- brm(correct ~  z_age + (0+test_day|id),
-            data = data%>%filter(study == "study1", task == i), 
-            family = bernoulli(),
-          #control = list(adapt_delta = 0.99),
-          sample_prior = F,
-          chains = 4,
-          cores = 4,
-          #save_all_pars = TRUE,
-          iter = 4000)
-
-          cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_day1,test_day2)")%>%mutate(task = i , study = "study1")
-
-          model_cor <- bind_rows(model_cor, cor)
-
-}
-
-tasks2 <- unique(data$task[data$study == "study2"])
-
-for(i in tasks2) {
-
-  model <- brm(correct ~  z_age + (0+test_day|id),
-            data = data%>%filter(study == "study2", task == i), 
-            family = bernoulli(),
-          #control = list(adapt_delta = 0.99),
-          sample_prior = F,
-          chains = 4,
-          cores = 4,
-          #save_all_pars = TRUE,
-          iter = 4000)
-
-          cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_day1,test_day2)")%>%mutate(task = i , study = "study2")
-
-          model_cor <- bind_rows(model_cor, cor)
-
-}
-
-mcor <- model_cor %>%
-    mutate(task = recode(task,
-                    `mutual_exclusivity` = "Mutual Exclusivity",
-                    `informativeness` = "Informativeness Inference (1)",
-                    `simple_inf` = "Informativeness Inference (2)",
-                    `preference` = "Speaker Preference",
-                    `novelty` = "Discourse Novelty",
-                    `card_sorting` = "Card Sorting",
-                    `discourse_continuity` = "Discourse Continuity",
-                    `ad_hoc_implicature` = "Ad-hoc Implicature",
-                    `match_to_sample` = "Relational Match-to-sample"),
-           term = task, 
-           mcor = Estimate, 
-           mcor_lci = `l-95% CI`, 
-           mcor_uci = `u-95% CI`)%>%
-  select(study, term, task, mcor, mcor_lci, mcor_uci)
-
-saveRDS(mcor, "../saves/model_based_reliability.rds")
+# model_cor <- data_frame()
+# 
+# tasks1 <- unique(data$task[data$study == "study1"])
+# 
+# for(i in tasks1) {
+# 
+#   model <- brm(correct ~  z_age + (0+test_day|id),
+#             data = data%>%filter(study == "study1", task == i), 
+#             family = bernoulli(),
+#           #control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           #save_all_pars = TRUE,
+#           iter = 4000)
+# 
+#           cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_dayday1,test_dayday2)")%>%mutate(task = i , study = "study1")
+#           
+#           model_cor <- bind_rows(model_cor, cor)
+#   
+# }
+# 
+# tasks2 <- unique(data$task[data$study == "study2"])
+# 
+# for(i in tasks2) {
+# 
+#   model <- brm(correct ~  z_age + (0+test_day|id),
+#             data = data%>%filter(study == "study2", task == i), 
+#             family = bernoulli(),
+#           #control = list(adapt_delta = 0.99),
+#           sample_prior = F,
+#           chains = 4,
+#           cores = 4,
+#           #save_all_pars = TRUE,
+#           iter = 4000)
+# 
+#           cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_dayday1,test_dayday2)")%>%mutate(task = i , study = "study2")
+#           
+#           model_cor <- bind_rows(model_cor, cor)
+#   
+# }
+# 
+# 
+# mcor <- model_cor %>%
+#     mutate(task = recode(task,
+#                     `mutual_exclusivity` = "Mutual Exclusivity",
+#                     `informativeness` = "Informativeness Inference (1)",
+#                     `simple_inf` = "Informativeness Inference (2)",
+#                     `preference` = "Speaker Preference",
+#                     `novelty` = "Discourse Novelty",
+#                     `card_sorting` = "Card Sorting",
+#                     `discourse_continuity` = "Discourse Continuity",
+#                     `ad_hoc_implicature` = "Ad-hoc Implicature",
+#                     `match_to_sample` = "Relational Match-to-sample"),
+#            term = task, 
+#            mcor = Estimate, 
+#            mcor_lci = `l-95% CI`, 
+#            mcor_uci = `u-95% CI`)%>%
+#   select(study, term, task, mcor, mcor_lci, mcor_uci)
+# 
+# saveRDS(mcor, "../saves/model_based_reliability.rds")
 
@@
   na.omit() %>%
-  rename("Day1" = `day1`,
-         "Day2" = `day2`)
+  rename("Day1" = `1`,
+         "Day2" = `2`)
 
@@
    midpoint = 0, limit = c(-1,1), space = "Lab",
-   name="Correlation") +
+   name="") +
    coord_fixed()+
@@
   #ggtitle("Study 1")+
-  theme(
-        legend.position = "right",
+  theme(legend.text=element_text(size=8),
+        legend.background = element_blank(),
+        legend.position = c(0.15, 0.75),
         legend.direction = "vertical",
@@
   theme_few()+
+  guides(fill = "none")+
   geom_text(aes(label = cor2), color = "black", size = 3) +
@@
   theme(
-        legend.position = "right",
-        legend.direction = "vertical",
         axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
@@
   theme_few(base_size = 12)+
+  guides(fill = "none")+
   #ggtitle("Study 3")+
   geom_text(aes(label = cor), color = "black", size = 3) +
-  theme(legend.justification = c(1, 0),
-        legend.position = c(0.55, 0.75),
-        legend.direction = "vertical",
-        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
-        legend.background = element_blank())+
-  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
-                title.position = "top", title.hjust = 0.5))
+  theme(
+        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
 
-pf4 <- ggarrange(cp1, cp2, cp3, common.legend = T, legend = "right", nrow = 1, labels = c("A","B","C"), hjust = -1.5)
+pf4 <- ggarrange(cp1, cp2, cp3, common.legend = F, nrow = 1, labels = c("A","B","C"), hjust = -1.5)
 
-ggsave(plot = pf4,"./figures/figure4.png", width = 10, height = 3, scale = 1.5, bg = "white")
+ggsave(plot = pf4,"../paper/figures/figure4.png", width = 10, height = 3, scale = 1.5, bg = "white")
 ```

### 2022-04-07 analysis/analysis.Rmd
prep submission

@@
 ---
-title: "PragBat Analysis"
+title: "Analysis"
 output: html_document
@@
                     `mutual_exclusivity` = "Mutual Exclusivity",
-                    `informativeness` = "Informativeness Inference (1)",
-                    `simple_inf` = "Informativeness Inference (2)",
+                    `informativeness` = "Informativeness Inf. (1)",
+                    `simple_inf` = "Informativeness Inf. (2)",
                     `preference` = "Speaker Preference",
@@
                     `ad_hoc_implicature` = "Ad-hoc Implicature",
-                    `match_to_sample` = "Relational Match-to-sample"))%>%
+                    `match_to_sample` = "Rel. Match-to-sample"))%>%
   filter(study != "study3",
@@
                     `ad_hoc_implicature` = "Ad-hoc Implicature",
-                    `match_to_sample` = "Relational Match-to-sample"))%>%
+                    `match_to_sample` = "Rel. Match-to-sample"))%>%
   filter(study == "study1") %>%
@@
                     `ad_hoc_implicature` = "Ad-hoc Implicature",
-                    `match_to_sample` = "Relational Match-to-sample"))%>%
+                    `match_to_sample` = "Rel. Match-to-sample"))%>%
   filter(study == "study2") %>%
@@
                     `ad_hoc_implicature` = "Ad-hoc Implicature",
-                    `match_to_sample` = "Relational Match-to-sample"))%>%
+                    `match_to_sample` = "Rel. Match-to-sample"))%>%
   filter(study == "study3")%>%
@@
 
-ggsave(plot = pf4,"../paper/figures/figure4.png", width = 10, height = 3, scale = 1.5, bg = "white")
+ggsave(plot = pf4,"../paper/figures/figure4.png", width = 10, height = 3, scale = 1.3, bg = "white")
 ```

### 2022-04-07 paper/manuscript.Rmd
prep submission

@@
   We are very thankful to Stella Christie for sharing the material for the relational match-to-sample task with us.
-
 M.
@@
 Individual differences studies contribute to understanding the psychological processes involved in pragmatic reasoning as well as the link to other cognitive abilities.
-Small sample sizes, insufficient measurement tools, and a lack of theoretical precision have hindered progress.
+Small sample sizes, insufficient measurement tools, and a lack of theoretical precision have hindered progress, however.
 Three studies addressed these challenges in a sample of three- to five-year-old German-speaking children (*N* = 228, 121 female).
@@
 The shared cognitive processes were formalized in a computational cognitive model of pragmatic reasoning.
-Results showed substantive relations among pragmatic tasks and between pragmatic abilities and executive functions.
+The tasks were found to measure stable variation between individuals on a shared latent construct relating to pragmatic inference.
 
 keywords          : "Pragmatics, language development, individual differences, cognitive modeling"
-wordcount         : "X"
+wordcount         : "8491"
 
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_docx
 ---
@@
          id = paste(study, id, sep = "_"), 
-         test_day = paste0("day", test_day))
+         test_day =  factor(test_day))
 ```
@@
 Before children produce their first words, they communicate with the world around them using vocalizations and gestures [@bruner1974communication; @bates1979emergence].
-The process of language learning recruits many of the social-cognitive processes that underlay pre-verbal communication [@bohn2019pervasive; @tomasello2009constructing; @clark2009first].
-Even for proficient language users is communication not reducible to the words being exchanged.
+The process of language learning recruits many of the social-cognitive processes that underlie pre-verbal communication [@bohn2019pervasive; @tomasello2009constructing; @clark2009first].
+Even for proficient language users, communication not reducible to the words being exchanged.
 The common thread running through these different aspects of human communication is its inferential nature: what a speaker means -- verbal or otherwise -- is underdetermined by the parts that make up the utterance.
 It takes contextual social inferences to recover the intended meaning [@grice1991studies; @clark1996using; @sperber2001relevance; @levinson2000presumptive; @bohn2018common].
-These inferences are often referred to as *pragmatic* inferences [e.g., @bohn2019pervasive].
+These inferences are often referred to as *pragmatic* inferences.
 
@@
 A growing portion of this work is devoted to studying individual differences [@matthews2018individual; @wilson2021pragmatic].
-The motivation behind this is twofold: on the one hand, individual differences offer insights into the underlying psychological processes [@kidd2018individual; @matthews2018individual; @wilson2022novel].
+The motivation behind the move to study individual variation is twofold: on the one hand, individual differences offer insights into the underlying psychological processes.
+If two phenomena (e.g.
+pragmatic reasoning and executive functions) vary together this is consistent with shared cognitive processes [@kidd2018individual; @matthews2018individual; @wilson2022novel], though it is not definitive evidence for such a claim.
 On the other hand, deficits in pragmatic abilities have been linked to behavioral problems and forms of language impairment [@helland2014stable].
@@
 In their recent review, @matthews2018individual identified three issues that significantly limit what we can learn from individual differences research on pragmatic abilities.
-First, most studies have insufficient sample sizes so that small and medium sized correlations among pragmatics tasks and between pragmatics tasks and measures for other cognitive abilities cannot be reliably detected.
+First, most studies have insufficient sample sizes so that small and medium sized correlations among pragmatics tasks and between pragmatics tasks and measures for other cognitive abilities cannot be reliably detected [mirroring issues in estimating correlations across other fields, @schonbrodt2013sample].
 Second, the tasks used to assess pragmatic abilities often have poor or unknown psychometric properties.
-For example, many tasks only have a single trial and are therefore unable to capture variation between children.
-Reliability is not assessed, making it unclear if the task captures stable characteristics [see also @russell2008assessing].
+For example, many tasks only have a single trial and are therefore unable to capture variation between children [see also @enkavi2019large].
+Reliability is not assessed, making it unclear if the task captures stable characteristics [@russell2008assessing; @flake2020measurement].
 Third, the cognitive processes underlying pragmatic inferences in a particular task are underspecified.
-As a consequence, there is no clear rationale for why a task should correlate with another cognitive measure.
+As a consequence, there is often no clear rationale for why a particular target task should correlate with another cognitive measure.
 
-The studies presented here directly address the issues identified by Matthews and colleagues [@matthews2018individual].
+In search of a better understanding of individual variation in pragmatic ability, the studies presented here directly address these issues.
 We identified six pragmatic reasoning tasks in children between three and five years of age and investigated their psychometric properties, in particular their re-test reliability.
 Reliable tasks are a necessary precondition for meaningful individual differences research [@hedge2018reliability; @fried2018measurement].
-Next, we investigated the relations among different pragmatic reasoning tasks as well as between pragmatic reasoning and executive functions in a sample large enough to detect small to medium sized correlations.
+Next, we investigated the relations among different pragmatic reasoning tasks as well as between pragmatic reasoning and other cognitive abilities in a sample large enough to detect small to medium sized correlations.
+
  Finally, we introduced computational cognitive models of pragmatic reasoning to the study of individual differences.
-This allowed us to formalize the cognitive processes we think underlay pragmatic reasoning and thereby provide a substantive theoretical account for why certain pragmatic reasoning tasks are related to one another and why executive functions relate to them.
+Computational cognitive models formalize hypotheses about cognitive processes that could underlie pragmatic reasoning; thus, the use of these models provides a substantive theoretical account for why certain pragmatic reasoning tasks should be related to one another.
+Here, we use the formalism introduced by the Rational Speech Act (RSA) framework [@frank2012predicting; @goodman2016pragmatic].
+RSA models see pragmatic inferences as a special case of (Bayesian) social reasoning.
+A pragmatic listener interprets an utterance by assuming it was produced by a cooperative speaker.
+The speaker tries to be informative, that is, they provide messages that would increase the probability that the listener will recover their intended meaning.
+The informativeness of an utterance arises from a contrastive inference in which the effects of multiple – plausible – utterances are compared.
+We assume that this inference process is shared by some of the pragmatics tasks involved in this study and can thus be used to account for individual differences (see below).
 
@@
 They all share a common trial-by-trial structure in which the test event always involved an agent producing an ambiguous utterance that the child had to resolve using pragmatic reasoning.
-This allowed us to run multiple trials per task, and with that, to capture individual differences.
+This structure allowed us to run multiple trials per task, increasing reliability.
 We grouped the tasks into two broad categories (Figure \@ref(fig:fig1)).
-On the one hand, utterance-based tasks asked children to derive inferences from the words and gestures the speaker produced in context.
-On the other hand, common ground/discourse-based tasks asked children to derive inferences from the social interaction that preceded the utterance.
+On the one hand, *utterance-based tasks* asked children to derive inferences from the words and gestures the speaker produced in context.
+On the other hand, *common ground/discourse-based tasks* asked children to derive inferences from the social interaction that preceded the utterance.
 
-For the utterance-based category, we selected a mutual exclusivity, informativeness inference, and ad-hoc implicature task.
-Mutual exclusivity -- or principle of contrast -- describes the phenomenon that children tend to map a novel word to an unknown object [@markman1988children; @halberda2003development; @bion2013fast; @merriman1989mutual; @clark1988logic; @lewis2020role].
+For the utterance-based category, we selected mutual exclusivity, informativeness inference, and ad-hoc implicature tasks.
+"Mutual exclusivity"^[Following @lewis2020role, we use the term "mutual exclusivity" as a convenient term to denote a specific task.
+This term is also related to a particular theoretical account of the phenomenon [@markman1990constraints], but we do not presuppose that specific account.] describes the phenomenon that children tend to map a novel word to an unknown object [@markman1988children; @halberda2003development; @bion2013fast; @merriman1989mutual; @clark1988logic; @lewis2020role].
 Informativeness inferences describe situations in which children identify the referent of a novel word by assuming that the speaker is trying to be informative.
@@
 
-For the discourse-based category, we selected a speaker preference, discourse novelty and discourse continuity task.
+For the discourse-based category, we selected speaker preference, discourse novelty and discourse continuity tasks.
 In the speaker preference task, the child had to track the preference of a speaker in order to identify the referent of a novel word [@saylor2009preschoolers].
@@
 
-In addition to the pragmatics tasks, we also included tasks for executive functions [@zelazo2006dimensional] and of analogical reasoning [@christie2014language].
+In addition to the pragmatics tasks, we also included two additional cognitive tasks: one measuring executive functions [@zelazo2006dimensional] and the other analogical reasoning [@christie2014language].
 Executive functions refer to a family of top-down mental processes that enable us to inhibit automatic or intuitive responses and allow us to concentrate and focus attention on particulars [@diamond2013executive].
 A substantial body of research has investigated the link between executive functions and pragmatics -- with mixed results [@matthews2018individual; @nilsen2009relations].
-Analogical reasoning refers to the ability to reason about abstract relations between stimuli [@carstensen2021graded] -- an ability that has not been linked to pragmatics -- at least not to the same extent as executive functions.
+Analogical reasoning refers to the ability to reason about abstract relations between stimuli [@carstensen2021graded] -- an ability that, to our knowledge, has not been specifically linked to pragmatics -- at least not to the same extent as executive functions.
 
-After finding in Study 1 and 2 that most of the pragmatics tasks showed good to excellent re-test reliability, we studied a larger sample of children in Study 3 to investigate relations between the three utterance-based tasks.
-We focused on these tasks for theoretical reasons: we assume that -- computationally -- they share a common contrastive inference process according to which the listener compares the utterance the speaker made to alternative possible utterances.
-The listener expects the speaker to be helpful and informative, that is, to choose the utterance that best communicates the intended message.
+After finding in Study 1 and 2 that most of the pragmatics tasks showed relatively good re-test reliability, we studied a larger sample of children in Study 3 to investigate relations between the three utterance-based tasks.
+We focused on these tasks for theoretical reasons: as noted above, we assume that -- computationally -- they share a common contrastive inference process.
 We formalize these assumptions in a computational cognitive model which we then use to study individual differences in this alleged process.
@@
 Across analytical approaches, we found systematic relations among the pragmatics tasks as well as between pragmatics and executive functions, but not analogical reasoning.
+In the discussion, we use the structure of the cognitive model to speculate about the psychological processes shared between pragmatics and executive functions.
 
@@
 Study 1 focused on the psychometric properties of four pragmatics tasks, in particular, their re-test reliability.
-two of the tasks were from the utterance-based group and two from the common ground/discourse-based group.
+Two of the tasks were from the utterance-based group and two from the common ground/discourse-based group.
 As a fifth task, we included a measure of executive functions.
@@
 
-For Study 1, we collected data from `r dem%>%filter(study == "study1")%>%pull(n)` children ($m_{age}$ = `r dem%>%filter(study == "study1")%>%pull(mage)`, range$_{age}$: `r dem%>%filter(study == "study1")%>%pull(lrange)` - `r dem%>%filter(study == "study1")%>%pull(urange)`, `r dem%>%filter(study == "study1")%>%pull(female)` girls) of which `r dem%>%filter(study == "study1")%>%pull(reli_n)` were tested twice.
+For Study 1, we collected data from `r dem%>%filter(study == "study1")%>%pull(n)` children ($m_{age}$ = `r dem%>%filter(study == "study1")%>%pull(mage)`, range$_{age}$: `r dem%>%filter(study == "study1")%>%pull(lrange)` - `r dem%>%filter(study == "study1")%>%pull(urange)`, `r dem%>%filter(study == "study1")%>%pull(female)` girls), of whom `r dem%>%filter(study == "study1")%>%pull(reli_n)` were tested twice.
 For most children, the two test sessions were two days apart; the longest time difference was six days.
@@
 Yellow: Analogical reasoning.
+Bold numbers show the number of trials per task.
 
@@
 The task was adapted from @bohn_tessler_merrick_frank_2019.
-Th animal was standing between two trees with objects hanging in them.
+The animal was standing between two trees with objects hanging in them.
 In one tree, there were two objects (type A and B) and in the other tree there was only one (type B).
-The animal turned to the tree with the two objects and labelled one of the objects.
+The animal turned to the tree with the two objects and labeled one of the objects.
 It was unclear from the animal's utterance, which of the two objects they were referring to.
@@
 Next, the trees were replaced by new ones, one of which carried an object of type A and the other of type B.
-The animal then said that one of the trees had the same object as they labelled previously (using the same label) and asked the child to touch the tree.
+The animal then said that one of the trees had the same object as they labeled previously (using the same label) and asked the child to touch the tree.
 We coded as correct if the child selected the tree with the object of type A.
@@
 This task was modeled after @zelazo2006dimensional.
-The child saw to cards, a blue rabbit on the left and a red boat on the right.
+The child saw two cards, a blue rabbit on the left and a red boat on the right.
 The experimenter introduced the child to the color game they would be playing next.
-In this game, all blue cards (irrespective of object depicted) would go to the left card and all red cards to the right.
+In this game, all blue cards (irrespective of objects depicted) would go to the left card and all red cards to the right.
 Next, a third card appeared in the middle of the screen (red rabbit or blue boat) and the experimenter demonstrated the color sorting by moving the card to the one with the same color.
@@
 
-We analysed the data in three steps.
-First we investigated developmental effects in each task, then we assessed re-test reliability and finally, we looked at relations between the tasks.
-All analysis were run in `R` [@R-base] version 4.1.2.
+We analyzed the data in three steps.
+First we investigated developmental effects in each task, then we assessed re-test reliability, and finally, we looked at relations between the tasks.
+All analyses were run in `R` [@R-base] version 4.1.2.
 Regression models were fit as Bayesian generalized linear mixed models (GLMM) using the function `brm` from the package `brms` [@burkner2017brms].
@@
 
-To estimate developmental effects in each task, we fit a GLMM predicting correct responses (0/1) by age (centered at the mean) and trial number (also centered).
+To estimate developmental effects in each task, we fit a GLMM predicting correct responses (0/1) by age (in years, centered at the mean) and trial number (also centered).
 The model included random intercepts for each participant and random slopes for trial within participants (model notation in `R`: `correct ~ age + trial + (trial|id)` )^[We pre-registered the inclusion of random intercepts for item.
@@
 Second, we used a GLMM based approach suggested by @rouder2019psychometrics.
-Here, a GLMM was fitted to the trial-by-trial data for each task with a fixed effect of age, a random intercept for each participant and a random slope for test day (`correct ~ age + (0+test_day|id)`)^[The notation `0+test_day` yields a separate intercept estimate for each test day and subject instead of an intercept estimate for day 1 and a slope for the difference between day 1 and day 2.
+Here, a GLMM was fitted to the trial-by-trial data for each task with a fixed effect of age (in years, centered at the mean), a random intercept for each participant and a random slope for test day (`correct ~ age + (0+test_day|id)`)^[The notation `0+test_day` yields a separate intercept estimate for each test day and subject instead of an intercept estimate for day 1 and a slope for the difference between day 1 and day 2.
 As a consequence, the model estimates the correlation between the two test days instead of a correlation between an intercept and the slope for test day.].
@@
 This approach has several advantages.
-First, it uses the trial-by-trial data and avoids information loss that comes with data aggregation.
-Second, it uses hierarchical shrinkage to obtain better participant specific estimates.
+First, it uses trial-by-trial data and avoids information loss that comes with data aggregation.
+Second, it uses hierarchical shrinkage to obtain better participant-specific estimates.
 Finally, it allows us to get an age-independent estimate for reliability.
@@
 
-Finally, we used that aggregated data from both test days for each participant and task to compute Pearson correlations between the different tasks.
+Finally, we used aggregated data from both test days for each participant and task to compute Pearson correlations between the different tasks.
 Given the small sample size in Study 1, this part of the analysis was mostly exploratory.
@@
 Light shapes show the mean performance for each subject by study.
-Dotted line shows level of performance expected by chance.
+Dotted line shows the level of performance expected by chance.
 
@@
 In the mutual exclusivity task, performance was reliably above chance level and increased with age.
-For informative inference, the pattern was quite different: Performance was at chance level with only minor developmental gains.
+For informativeness inference, the pattern was quite different: Performance was at chance level with only minor developmental gains.
 In the speaker preference task, performance was again clearly above chance with developmental gains resulting in a ceiling effect for older children.
@@
 Re-test reliability was high for most tasks (see Figure \@ref(fig:fig4)).
-Raw correlation between the two test sessions was above .7 for mutual exclusivity, speaker preference and discourse novelty.
-With .62 it was slightly lower for card sorting.
+Raw correlation between the two test sessions was above .7 for mutual exclusivity, speaker preference and discourse novelty, though it was slightly lower for card sorting (.62).
 The model based -- age independent -- reliability estimates yielded similar results suggesting that the tasks did capture task specific individual differences.
@@
 Most correlations between the tasks were low and ranged between *r* = -0.2 and 0.2 (see Figure \@ref(fig:fig2)).
-A notable exception was the correlation between mutual exclusivity and card sorting with *r* = `r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(rho)` (95% CI[`r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(lci)` - `r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(uci)`]).
+A notable exception was the correlation between mutual exclusivity and card sorting (*r* = `r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(rho)`, 95% CI[`r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(lci)` - `r cors%>%filter(study == "study1", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(uci)`]).
 
-(ref:figlab3) Model estimates (with 95% CrI) for age based on GLMMs for each task and study.
+(ref:figlab3) Model estimates (with 95% CrI) for age (in years, centered at the mean) based on GLMMs for each task and study.
 
@@
 
-Study 1 showed that the different tasks were age appropriate and reliable.
+Study 1 showed that the different tasks were – for the most part – age appropriate and reliable.
 A notable exception was the informativeness inference task which generated no systematic variation in the age range we studied here.
-Correlations between the tasks were generally low, with the notable exception of the relation between mutual exclusivity and card sorting.
-Given the small sample size, we want to avoid overly strong claims, however, it was interesting to see that the relation between the two tasks tapping into discourse-based inferences (speaker preference and discourse novelty) were -- if anything -- negatively correlated.
+Correlations between the tasks were generally low, with the exception of the relation between mutual exclusivity and card sorting.
+Given the small sample size, we avoid overly strong claims, however, it was interesting to see that the relation between the two tasks tapping into discourse-based inferences (speaker preference and discourse novelty) were -- if anything -- negatively correlated.
 
@@
 
-Based on these results od Study 1, we compiled a new set of tasks for Study 2.
+Based on these results of Study 1, we compiled a new set of tasks for Study 2.
 We retained the mutual exclusivity and card sorting tasks because of the interesting relation between the two found in Study 2.
-We simplified the informativeness inference task to be more age appropriate with the hope to induce more variation in performance.
+We simplified the informativeness inference task to be more age appropriate with the hope of inducing more variation in performance.
 We removed the speaker preference and discourse novelty tasks -- despite their excellent re-test reliability -- because they seemed to be unrelated to one another and also unrelated to the other tasks.
-The new tasks focused on ad-hoc implicature and discourse continuity.
-As noted in the introduction, we had theoretical reasons to expected the ad-hoc implicature task to be related to the mutual exclusivity and informativeness inference tasks.
+We also added new tasks focused on ad-hoc implicature and discourse continuity.
+As noted in the introduction, we had theoretical reasons to expect the ad-hoc implicature task to be related to the mutual exclusivity and informativeness inference tasks.
 We had no such strong predictions for the discourse continuity task.
@@
 Participants for Study 2 were recruited from the same general population.
-We collected data from `r dem%>%filter(study == "study2")%>%pull(n)` children ($m_{age}$ = `r dem%>%filter(study == "study2")%>%pull(mage)`, range$_{age}$: `r dem%>%filter(study == "study2")%>%pull(lrange)` - `r dem%>%filter(study == "study2")%>%pull(urange)`, `r dem%>%filter(study == "study2")%>%pull(female)` girls) of which `r dem%>%filter(study == "study2")%>%pull(reli_n)` were tested twice.
+We collected data from `r dem%>%filter(study == "study2")%>%pull(n)` children ($m_{age}$ = `r dem%>%filter(study == "study2")%>%pull(mage)`, range$_{age}$: `r dem%>%filter(study == "study2")%>%pull(lrange)` - `r dem%>%filter(study == "study2")%>%pull(urange)`, `r dem%>%filter(study == "study2")%>%pull(female)` girls), of whom `r dem%>%filter(study == "study2")%>%pull(reli_n)` were tested twice.
 The two test sessions were again two days apart; the longest time difference was 14 days.
@@
 
-The general structure of the task was the same as in Study 1, however, we replaced the stimuli by the ones used by @frank2014inferring.
-We suspected that children did not treat the novel objects hanging in the tree as properties of the tree but the tree as a "container" for the novel objects.
+The general structure of the task was the same as in Study 1, however, we replaced the stimuli from @bohn_tessler_merrick_frank_2019 with those used originally by @frank2014inferring.
+We suspected that many children did not treat the novel objects hanging in the tree as properties of the tree but rather viewed the tree as a “container” for the novel objects.
 The alleged inference, however, relies on seeing the objects as properties of the referent.
@@
 The animal then asked which of these objects had the aforementioned property (e.g., which bear has a [non-word]).
-We coded as correct if the child selected the object with the property that was unique to the object during labeling.
+We coded responses as correct if the child selected the object with the property that was unique to the object during labeling.
 The first two trials were training trials, in which each object only had one property.
@@
 As properties we chose objects that were well known to children of that age range.
-One object had one property (A) and while the other had two (A and B).
-For example, objects were lunchboxes, one with an orange and the other with an orange and an apple.
+One object had one property (A), while the other had two (A and B).
+For example, objects were lunch boxes, one with an orange and the other with an orange and an apple.
 The animal then asked the child to hand them their object which was the one with the property that both objects shared (A).
@@
 There were five test trials, preceded by two training trials in which the objects did not share a common property.
-The positioning of the objects (left and right) was pseudo-randomized
+The positioning of the objects (left and right) was pseudo-randomized.
 
@@
 
-We used the same methods to analyse the data as in Study 1.
+We used the same methods to analyze the data as in Study 1.
 
@@
 The model-based reliability estimates were similar, with lower values for ad-hoc implicature and higher ones for discourse continuity.
-Notably, the informativeness inference task showed a much-improved re-test reliability compared to Study 1.
+Notably, the revised informativeness inference task showed a much-improved re-test reliability compared with the estimate from Study 1.
 
 Correlations between tasks were generally higher compared to Study 1.
-In fact, confidence intervals for correlation coefficients were not overlapping with 0 except for the correlation between the discourse continuity and informativeness inference tasks (Figure \@ref(fig:fig4).
+In fact, confidence intervals for correlation coefficients were not overlapping with 0 except for the correlation between the discourse continuity and informativeness inference tasks (Figures \@ref(fig:fig4).
 Once again, we found the strongest relation between card sorting and mutual exclusivity (*r* = `r cors%>%filter(study == "study2", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(rho)`, 95% CI[`r cors%>%filter(study == "study2", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(lci)` - `r cors%>%filter(study == "study2", task1 == "mutual_exclusivity", task2 == "card_sorting")%>%pull(uci)`]).
@@
 In Study 2 we found good results from a measurement perspective: all tasks had acceptable re-test reliability.
-This included the informativeness inference task which had deficits in that respect in Study 1.
-Higher average performance and increased variability suggest that our changes to the stimuli did make the task easier for children.
+This result extended to the informativeness inference task, which had very low reliability in Study 1.
+Higher average performance and increased variability both suggest that our changes to the stimuli made the task easier for children.
 
-Like in Study 1, we found a relatively strong correlation between the mutual exclusivity and card sorting tasks.
-This corroborates the idea that these tasks share common processes.
+As in Study 1, we found a relatively strong correlation between the mutual exclusivity and card sorting tasks.
+This finding supports the idea that these tasks share common processes.
 We also found substantial relations between the three utterance-based inference tasks (mutual exclusivity, ad-hoc implicature, informativeness inference).
-Furthermore, the correlations between tasks were lower when discourse continuity was involved -- though the numerical difference was minimal.
+The correlations between these tasks and the discourse continuity task were numerically lower.
 
@@
 In particular, we explored the idea that the three utterance-based inference tasks share common cognitive processes.
-Once again, we also included the card sorting task and added a new task of analogical reasoning for which we did not expect strong relations with the other tasks.
-To be able to test these predictions, we collected data from a comparatively larger sample of children.
+Once again, we also included the card sorting task and added a new task of analogical reasoning as a control for which we did not expect strong relations with the other tasks.
+To be able to test predictions about cross-task variation, we collected data from a comparatively larger sample of children.
 
@@
 
-From Study 2, we used the the mutual exclusivity, ad-hoc implicature, informativeness inference and card sorting tasks.
-We added the relational match-to-sample task, which we now describe in more detail.
+From Study 2, we used the mutual exclusivity, ad-hoc implicature, informativeness inference and card sorting tasks. We added the relational match-to-sample task, which we now describe in more detail.
 
@@
 
-The task was modeled after and used the original stimuli from @christie2014language.
+The task was modeled after (and used the original stimuli from) @christie2014language.
 The child saw three cards, one on top (the sample) and two at the bottom (the potential matches; see Figure \@ref(fig:fig1)).
@@
 We assumed that children would match the sample to the match that showed the same relation between shapes (sameness).
-Children received six test trial, preceded by two training trials in which one of the potential matches was identical to the sample.
+Children received six test trials, preceded by two training trials in which one of the potential matches was identical to the sample.
 The position of the same-match was pseudo randomized.
@@
 RSA models see pragmatic inferences as a form of Bayesian social reasoning where the listener tries to infer the speaker's meaning (here: the intended referent) by assuming that the speaker is helpful and informative.
-Being helpful and informative means that the speaker chooses a message based on the probability that it would help the listener to recover the speaker's intended meaning.
+Being helpful and informative means that the speaker chooses a message based on the probability that it would help the listener to recover the speaker's intended meaning (i.e., select the intended referent).
 Thus, RSA models have a recursive structure in which the the listener reasons about a speaker who is reasoning about the listener.
@@
 The studies from which we took the mutual exclusivity and informativeness inference tasks also formalized these tasks in an RSA-style model [@bohn_tessler_merrick_frank_2019; @bohn2021young].
-We refer to this earlier work for more details and a mathematical description of the models.
+We refer to this earlier work for a more detailed description of the models.
 For the present study, we formalized the ad-hoc implicature task within the same RSA framework.
-The three models share the same contrastive inference process according to which the listener compares the speaker's utterance to alternative, possible ones.
-The speaker then expects the listener to be informative (with degree $\alpha$), that is, choose the utterance that best communicates the intended message.
-In the mutual exclusivity task, the alternative utterance would be to use a familiar word.
-In the case of the informative inference task, the alternative was point to the object with only one property.
-For the ad-hoc implicature task it was to single out the property that was shared by both objects.
+The common model structure is formally defined as:
+
+$$P_{L_1}(r|u)\propto P_{S_1}(u|r) \cdot P(r)$$
+In the above equation, the listener ($P_{L_1}$) is trying to infer the speaker’s ($P_{S_1}$) intended referent r by imagining what a rational speaker would say, given the referent they are trying to communicate and combining it with the listener’s prior expectations about the referent $P(r)$^[We assumed a uniform prior distribution over potential referents.].
+The speaker is an approximately rational Bayesian actor (with degree of rationality $\alpha$) who produces utterances as a function of their informativity.
+
+$$P_{S_1}(u|r)\propto Informativity(u;r)^\alpha$$
+The informativity of an utterance for a referent is taken to be the probability with which a naive listener ($P_{L_0}$), who only interprets utterances according to their literal semantics, would select a particular referent given an utterance.
+
+$$Informativity(u; r) = P_{L_0}(r|u)$$
+
+The three models differ in the types of utterances that are being produced, however, they share the same contrastive inference process according to which the listener ($P_{L_1}$) compares the speaker’s ($P_{S_1}$) utterance to a set of alternative, possible utterances.
+As noted above, the listener expects the speaker to be informative (with degree $\alpha$) that is, choose the utterance that best communicates the intended message.
+In the mutual exclusivity task, the speaker produced an unfamiliar word; thus, the alternative utterance for the speaker would have been to use a familiar word.
+In the case of the informative inference task, the speaker pointed to the object with two properties; thus, the alternative would have been to point to the object with only one property.
+For the ad-hoc implicature task the speaker referred to the property shared by the two objects, which contrasts with referring to the property that was unique to one of the objects.
 In all cases, these alternative utterances would be better suited to communicate about the respective other referent.
 
-As noted above, all models shared one common parameter: the speaker informativeness parameter $\alpha$.
+As noted above, models for the different tasks shared one common parameter: the speaker informativeness parameter $\alpha$.
 This commonality offers a way of relating performance in the three tasks to one another by constraining the three models to use the same value for $\alpha$.
@@
 Given the developmental nature of our data, we defined $\alpha_j$ via a linear regression as a function of the child's age ($age_i$): $\alpha_j = \beta^\alpha_0 + age_i \cdot \beta^\alpha_1$.
-Thus, the participant specific value for $\alpha$ was not only constrained by the performance in the three tasks but also by the child's age.
+Thus, the participant-specific value for $\alpha$ was not only constrained by the performance in the three tasks but also by the child's age.
 
@@
 
-To validate this approach, we first applied this model to the data from Study 2 -- separate for each test session.
+To validate this approach, we first applied this model to the data from Study 2 separately for each test session.
 This allowed us to compute the re-test reliability of $\alpha$ and see if it captures individual differences equally well compared to the raw test scores.
-After finding excellent re-test reliability, we applied it to the data from Study 3 and correlated the results with the the card sorting and relational match-to sample tasks.
-For these correlational analysis, we converted the posterior distribution for each participant into a single value by taking the mode (and 95% highest density interval -- HDI).
-The cognitive models were implemented in `WebPPL` [@dippl] and the corresponding code, including information on prior distributions, can be found in the associated online repository.
+After finding excellent re-test reliability, we applied it to the data from Study 3 and correlated the results with the card sorting and relational match-to sample tasks.
+For this correlational analysis, we converted the posterior distribution for each participant into a single value by taking the mode (and 95% highest density interval -- HDI).
+The cognitive models were implemented in `WebPPL` [@dippl] and the corresponding code, including information on prior distributions (which we omit here for space), can be found in the associated online repository.
 
@@
 Overall, the correlations between the tasks were lower compared to Study 2.
-This was to some extent expected given that there were only half the number of trials per task in Study 3 and, with that, less room for capturing individual differences.
-Nevertheless, the overall pattern rsembles that found in Study 2 (Figure \@ref(fig:fig4)).
+This was to some extent expected given that there were only half the number of trials per task in Study 3 and, hence less "signal" (systematic, non-error variability) for capturing individual differences.
+Nevertheless, the overall pattern resembles that found in Study 2 (Figure \@ref(fig:fig4)).
 We saw the strongest bi-variate relation between the mutual exclusivity and the ad-hoc implicature task (*r* = `r cors%>%filter(study == "study3", task1 == "mutual_exclusivity", task2 == "ad_hoc_implicature")%>%pull(rho)`, 95% CI[`r cors%>%filter(study == "study3", task1 == "mutual_exclusivity", task2 == "ad_hoc_implicature")%>%pull(lci)` - `r cors%>%filter(study == "study3", task1 == "mutual_exclusivity", task2 == "ad_hoc_implicature")%>%pull(uci)`]) followed by ad-hoc implicature and card sorting (*r* = `r cors%>%filter(study == "study3", task1 == "card_sorting", task2 == "ad_hoc_implicature")%>%pull(rho)`, 95% CI[`r cors%>%filter(study == "study3", task1 == "card_sorting", task2 == "ad_hoc_implicature")%>%pull(lci)` - `r cors%>%filter(study == "study3", task1 == "card_sorting", task2 == "ad_hoc_implicature")%>%pull(uci)`]).
@@
 Our focal model -- including a latent factor for pragmatic reasoning -- fit the data well (PPP = `r round(model_fit%>%filter(index == "ppp", model == "fit1")%>%pull(value),3)`) and with a WAIC of `r round(model_comparison%>%filter(model == "fit1")%>%pull(waic),2)` (se = `r round(model_comparison%>%filter(model == "fit1")%>%pull(waic_se),2)`, weight = `r round(model_comparison%>%filter(model == "fit1")%>%pull(waic_weight),2)`) better compared to the two alternative models (individual factors model: PPP = `r round(model_fit%>%filter(index == "ppp", model == "fit3")%>%pull(value),3)`, WAIC = `r round(model_comparison%>%filter(model == "fit3")%>%pull(waic),2)`, se = `r round(model_comparison%>%filter(model == "fit3")%>%pull(waic_se),2)`, weight = `r round(model_comparison%>%filter(model == "fit3")%>%pull(waic_weight),2)`; one factor model: PPP = `r round(model_fit%>%filter(index == "ppp", model == "fit2")%>%pull(value),3)`, WAIC = `r round(model_comparison%>%filter(model == "fit2")%>%pull(waic),2)`, se = `r round(model_comparison%>%filter(model == "fit2")%>%pull(waic_se),2)`, weight = `r round(model_comparison%>%filter(model == "fit2")%>%pull(waic_weight),2)`).
-Figure \@ref(fig:fig5) shows that factor loadings for the individual tasks as well as their residual variance.
+
+Figure \@ref(fig:fig5) shows factor loadings for the individual tasks as well as their residual variance.
 The latent pragmatic reasoning factor best explained the mutual exclusivity task, followed by the ad-hoc implicature and the informativeness inference task.
@@
 Finally, we present the results of the cognitive modeling analysis.
-Using the data from Study 2, we could show that participant specific speaker informativeness parameters ($\alpha$) were highly reliable (Figure \@ref(fig:fig6)B).
+Using the data from Study 2, we saw that participant specific speaker informativeness parameters ($\alpha$) were highly reliable (Figure \@ref(fig:fig6)B).
 The scale parameter suggested that the mutual exclusivity task was easier and the informativeness inference task was harder compared to the ad-hoc implicature task (Figure \@ref(fig:fig6)C).
@@
 (ref:figlab6) Results of cognitive model analyses.
-A: Correlation between the speaker informativeness parameter $\alpha$ and the paerformance in the card sorting and relational match to sample tasks.
+A: Correlation between the speaker informativeness parameter $\alpha$ and the performance in the card sorting and relational match to sample tasks.
 Regression line (with 95% CI) is based on a linear model.
@@
 The latent factor explained substantial portions of the variance in each of the three tasks.
-The cognitive modelling approach provides an explicit theory of what the shared cognitive processes may look like: according to the model, the pragmatic inference in each task was driven by contrasting the utterance the speaker produced and alternative utterances.
+The cognitive modeling approach provides an explicit theory of what the shared cognitive processes may look like: according to the model, the pragmatic inference in each task was driven by contrasting the utterance the speaker produced and alternative utterances.
 Individual differences were thought to arise from differential expectations about how informative the speaker is.
@@
 We identified six tasks covering a broad range of pragmatic phenomena.
-We found them to have good psychometric properties, in particular good to excellent re-test reliability.
+We found them to have generally good re-test reliability.
 We then selected three utterance-based inference tasks for a well-powered study of relations among different types of pragmatic abilities and between pragmatics and other cognitive abilities.
-The results showed systematic relations between the tasks.
+The results showed systematic relations between the utterance-based tasks, consistent with a latent cognitive construct.
 We used a computational cognitive model of pragmatic reasoning to formalize the cognitive processes we believed the tasks to share.
-Finally, we found pragmatic abilities to be related to a task of executive functions.
+Finally, we found pragmatic abilities to be related to a task of executive functions
 
 One of the main contributions of this paper is that it presents six pragmatic inference tasks that are highly robust and reliable.
-Whenever we used a task in two studies (mutual exclusivity, informativeness inference, ad-hoc implicature), we found the developmental results to closely replicate.
-in Study 1 and 2, all tasks showed good re-test reliability -- even when corrected for age.
+Whenever we used a task in two studies (mutual exclusivity, informativeness inference, ad-hoc implicature), we found developmental results that replicated previous findings.
+In Study 1 and 2, all tasks showed good re-test reliability – even when corrected for age.
 A notable exception was the informativeness inference task in Study 1.
 However, after making some procedural changes, it turned out to be robust and reliable as well.
-Taken together, the tasks are highly suitable for individual differences research.
-The material is freely available via the associated online repository.
+Taken together, the tasks are suitable for individual differences research, advancing the agenda of @matthews2018individual.
+These materials are freely available via the associated online repository.
 
-We grouped the tasks into utterance-based and common ground/discourse based.
+We grouped our pragmatics tasks into utterance-based and common ground/discourse based.
 This grouping broadly captured the kind of information that we assumed to be relevant to compute the inference.
@@
 The shared structural features involve a recursive social inference process according to which the listener expects the speaker to select the most informative of a set of possible utterances.
-The individual difference parameter captured how informative the listener expected the speaker to be^[This interpretation follows from the conceptual role the parameter plays in the RSA framework.
-Technically, it acts as an amplifier of the basic inference].
-Previous accounts, in particular of mutual exclusivity [reviewed in @lewis2020role], would not have predicted such an overlap.
-The results of Study 3 (and also Study 2) supported our assumptions as we found systematic relations between the three tasks.
+The individual difference parameter captured how informative the listener expected the speaker to be.
+Previous accounts would not have predicted such an overlap.
+In particular, theoretical accounts of mutual exclusivity as arising from heuristics or principles unconnected with pragmatic reasoning [reviewed in @lewis2020role] do not make the prediction of correlations with other pragmatic tasks.
 
 Our formal model also allowed us to speculate about why we saw a systematic relation across the three studies between pragmatic inference and the card sorting task as a measure of executive functions.
-Before we do so, we want to emphasize that the model is first and foremost a computational description of the tasks an not a model of a psychological process [cf.
+Before we do so, we want to emphasize that the model is first and foremost a computational description of the tasks and not a model of a psychological process [cf.
 @goodman2016pragmatic].
-For the following, we assume more psychological realism than perhaps warranted.
-The card sorting task asks the child to switch between rules half way.
-This requires inhibiting a pre-potent response and attending to different features of the cards.
-The pragmatic inference in the model involves contrasting the observed utterance with alternative utterances.
-This could be described as requiring inhibiting available, plausible interpretations and contrasting different interpretations instead before making a response.
-The next step should be to jointly model card sorting and the pragmatics tasks to substantiate such a verbal analysis.
-The model we presented here lays the foundation for such a project.
+Here we speculate, assuming a bit more psychological realism in our interpretation of the RSA model than previous authors have.
+The card sorting task asks the child to switch between rules after having practiced the first rule over the course of several trials.
+This switch requires inhibiting a pre-potent response and attending to different features of the cards.
+Similarly, pragmatic inference in the RSA model involves contrasting the observed utterance with alternative plausible utterances.
+This process, too, could be described as requiring inhibiting available, plausible interpretations and contrasting different interpretations before making a response.
+To pursue this connection further, the next step should be to model card sorting and the pragmatics tasks jointly to substantiate such a verbal analysis.
 
@@
 The studies we presented here have important limitations.
-Our focus on the utterance-based pragmatic inference tasks meant that we did no study and analyse the common ground/discourse-based tasks with the same level of detail.
+Our focus on the utterance-based pragmatic inference tasks meant that we did not study or analyze the common ground/discourse-based tasks with the same level of detail.
 That is, we did not formalize them in a cognitive model and did not study relations between them in a larger sample.
 Future research should address these shortcomings.
-Nevertheless, the work presented here is an important first step because it showed that the tasks themselves have good psychometric properties and are therefore suitable for individual differences research.
+Nevertheless, the work presented here is an important first step because it showed that the common ground/discourse tasks themselves have good psychometric properties and are therefore suitable for individual differences research.
 
 We presented the tasks as interactive picture books on a tablet computer with animal characters as agents.
-This improved the quality of our measurement because it allowed us to experimentally isolate the different inferences and run multiple trials in each task.
-However, it also means that -- like most experimental work -- our tasks lack ecological validity.
+This methodological step improved the quality of our measurement because it allowed us to experimentally isolate the different inferences and run multiple trials in each task.
+However, it also means that – like most experimental work – our tasks lack ecological validity.
 In real-world conversations, multiple information sources are available to listeners to draw inferences from [@bohn2021young; @bohn_tessler_merrick_frank_2019].
-Furthermore, the setup prevented the use of strategies that are an integral part of real-world conversations, like asking questions or seeking clarification [@arkel2020simple; @clark1991grounding].
-However, we want to highlight that the tasks replicated many classical findings from interactive tasks [e.g., @markman1988children; @akhtar1996role; @saylor2009preschoolers; @frank2014inferring].
+Furthermore, by design our experimental paradigm prevented the use of strategies that are an integral part of real-world conversations, like asking questions or seeking clarification [@arkel2020simple; @clark1991grounding].
+However, we want to highlight that the results from our tasks replicated many findings from interactive versions of these tasks [@markman1988children; @akhtar1996role; @saylor2009preschoolers; @frank2014inferring].
 
@@
 
-The studies reported here addressed some fundamental challenges in the study of individual differences in pragmatic abilities [cf.
-@matthews2018individual].
+The studies reported here addressed some fundamental challenges in the study of individual differences in pragmatic abilities [@matthews2018individual].
 We developed and validated new methodological and theoretical tools that helped to study the relations between different types of pragmatic inferences as well as between pragmatics and other cognitive abilities in a more reliable and valid way.

### 2022-04-07 paper/manuscript.Rmd
prep submission

@@
   Pragmatic abilities are fundamental to successful language use and learning.
-Individual differences studies contribute to understanding the psychological processes involved in pragmatic reasoning as well as the link to other cognitive abilities.
+Individual differences studies contribute to understanding the psychological processes involved in pragmatic reasoning.
 Small sample sizes, insufficient measurement tools, and a lack of theoretical precision have hindered progress, however.
-Three studies addressed these challenges in a sample of three- to five-year-old German-speaking children (*N* = 228, 121 female).
+Three studies addressed these challenges in a sample of three- to five-year-old German-speaking children (N = 228, 121 female).
 Studies 1 and 2 assessed the psychometric properties of six pragmatics tasks.

### 2022-04-24 paper/manuscript.Rmd
add preprint link

@@
 Small sample sizes, insufficient measurement tools, and a lack of theoretical precision have hindered progress, however.
-Three studies addressed these challenges in a sample of three- to five-year-old German-speaking children (N = 228, 121 female).
+Three studies addressed these challenges in three- to five-year-old German-speaking children (N = 228, 121 female).
 Studies 1 and 2 assessed the psychometric properties of six pragmatics tasks.
 Study 3 investigated relations among pragmatics tasks and between pragmatics and other cognitive abilities.
-The shared cognitive processes were formalized in a computational cognitive model of pragmatic reasoning.
-The tasks were found to measure stable variation between individuals on a shared latent construct relating to pragmatic inference.
+The tasks were found to measure stable variation between individuals.
+Via a computational cognitive model, individual differences were traced back to a latent pragmatics construct.
+This presents the basis for understanding the relations between pragmatics and other cognitive abilities.
 
 keywords          : "Pragmatics, language development, individual differences, cognitive modeling"
-wordcount         : "8491"
+wordcount         : "8558"
 
@@
 classoption       : "man"
-output            : papaja::apa6_docx
+output            : papaja::apa6_pdf
 ---
@@
 The process of language learning recruits many of the social-cognitive processes that underlie pre-verbal communication [@bohn2019pervasive; @tomasello2009constructing; @clark2009first].
-Even for proficient language users, communication not reducible to the words being exchanged.
-The common thread running through these different aspects of human communication is its inferential nature: what a speaker means -- verbal or otherwise -- is underdetermined by the parts that make up the utterance.
-It takes contextual social inferences to recover the intended meaning [@grice1991studies; @clark1996using; @sperber2001relevance; @levinson2000presumptive; @bohn2018common].
-These inferences are often referred to as *pragmatic* inferences.
+Even for proficient language users, communication is not reducible to the words being exchanged.
+The common thread running through the different aspects of human communication is its inferential nature: what a speaker means -- verbal or otherwise -- is underdetermined by the parts that make up the utterance.
+It takes contextual social inferences, often referred to as *pragmatic* inferences, to recover the intended meaning [@grice1991studies; @clark1996using; @sperber2001relevance; @levinson2000presumptive; @bohn2018common].
 
@@
 A growing portion of this work is devoted to studying individual differences [@matthews2018individual; @wilson2021pragmatic].
-The motivation behind the move to study individual variation is twofold: on the one hand, individual differences offer insights into the underlying psychological processes.
+The motivation behind the move to study individual variation is twofold: first, individual differences offer insights into the underlying psychological processes.
 If two phenomena (e.g.
 pragmatic reasoning and executive functions) vary together this is consistent with shared cognitive processes [@kidd2018individual; @matthews2018individual; @wilson2022novel], though it is not definitive evidence for such a claim.
-On the other hand, deficits in pragmatic abilities have been linked to behavioral problems and forms of language impairment [@helland2014stable].
+Second, deficits in pragmatic abilities have been linked to maladaptive behavioral patterns and forms of language impairment [@helland2014stable].
 
@@
 For example, many tasks only have a single trial and are therefore unable to capture variation between children [see also @enkavi2019large].
-Reliability is not assessed, making it unclear if the task captures stable characteristics [@russell2008assessing; @flake2020measurement].
+Furthermore, reliability is not assessed, making it unclear if the task captures stable characteristics [@russell2008assessing; @flake2020measurement].
 Third, the cognitive processes underlying pragmatic inferences in a particular task are underspecified.
@@
 Next, we investigated the relations among different pragmatic reasoning tasks as well as between pragmatic reasoning and other cognitive abilities in a sample large enough to detect small to medium sized correlations.
-
- Finally, we introduced computational cognitive models of pragmatic reasoning to the study of individual differences.
-Computational cognitive models formalize hypotheses about cognitive processes that could underlie pragmatic reasoning; thus, the use of these models provides a substantive theoretical account for why certain pragmatic reasoning tasks should be related to one another.
+For this purpose, we introduced computational cognitive models of pragmatic reasoning to the study of individual differences.
+Computational cognitive models formalize hypotheses about cognitive processes that could underlie pragmatic reasoning; thus, the use of these models provides a substantive theoretical account of why certain pragmatic reasoning tasks should be related to one another.
 Here, we use the formalism introduced by the Rational Speech Act (RSA) framework [@frank2012predicting; @goodman2016pragmatic].
@@
 We grouped the tasks into two broad categories (Figure \@ref(fig:fig1)).
-On the one hand, *utterance-based tasks* asked children to derive inferences from the words and gestures the speaker produced in context.
-On the other hand, *common ground/discourse-based tasks* asked children to derive inferences from the social interaction that preceded the utterance.
+*Utterance-based tasks* asked children to derive inferences from the words and gestures the speaker produced in context.
+*Common ground/discourse-based tasks* asked children to derive inferences from the social interaction that preceded the utterance.
 
 For the utterance-based category, we selected mutual exclusivity, informativeness inference, and ad-hoc implicature tasks.
-"Mutual exclusivity"^[Following @lewis2020role, we use the term "mutual exclusivity" as a convenient term to denote a specific task.
-This term is also related to a particular theoretical account of the phenomenon [@markman1990constraints], but we do not presuppose that specific account.] describes the phenomenon that children tend to map a novel word to an unknown object [@markman1988children; @halberda2003development; @bion2013fast; @merriman1989mutual; @clark1988logic; @lewis2020role].
+"Mutual exclusivity" describes the phenomenon that children tend to map a novel word to an unknown object [@markman1988children; @halberda2003development; @bion2013fast; @merriman1989mutual; @clark1988logic; @lewis2020role].
+Following @lewis2020role, we use the term "mutual exclusivity" as a convenient term to denote a specific task.
+This term is also related to a particular theoretical account of the phenomenon [@markman1990constraints], but we do not presuppose that specific account.
 Informativeness inferences describe situations in which children identify the referent of a novel word by assuming that the speaker is trying to be informative.
-Being informative translates to using words that have smaller extensions in context [@frank2014inferring].
+Being informative translates to using words that reduce ambiguity and help the listener to recover the intended meaning [@frank2014inferring].
 Ad-hoc implicature describes inferences that ask the child to contrast an utterance with alternatives that the speaker could have used but did not [@stiller2015ad; @yoon2019role; @katsos2011pragmatic].
@@
 
-After finding in Study 1 and 2 that most of the pragmatics tasks showed relatively good re-test reliability, we studied a larger sample of children in Study 3 to investigate relations between the three utterance-based tasks.
+Study 1 and 2 explored the re-test reliability of the pragmatics tasks and found it to be  relatively good.
+Study 3 tested a larger sample of children to investigate relations between the three utterance-based tasks.
 We focused on these tasks for theoretical reasons: as noted above, we assume that -- computationally -- they share a common contrastive inference process.
@@
 
+Taken together, this study introduces a set of tasks that reliably measure individual differences in pragmatic abilities in the preschool years.
+In addition, it introduces a new (formal) theoretical framework that help us understand individual differences on a process level and, with that, suggests answers to why pragmatic abilities relate to other cognitive abilities.
+
 # Study 1
@@
 Study 1 focused on the psychometric properties of four pragmatics tasks, in particular, their re-test reliability.
+We chose our sample size so that we would detect medium to high re-test correlations with sufficient power.
 Two of the tasks were from the utterance-based group and two from the common ground/discourse-based group.
+This design allowed us to explore whether tasks within one group are more related to one another than between groups.
 As a fifth task, we included a measure of executive functions.
@@
 To estimate developmental effects in each task, we fit a GLMM predicting correct responses (0/1) by age (in years, centered at the mean) and trial number (also centered).
-The model included random intercepts for each participant and random slopes for trial within participants (model notation in `R`: `correct ~ age + trial + (trial|id)` )^[We pre-registered the inclusion of random intercepts for item.
-We deviate from this here because the order of items was fixed and the same for all participants so that trial and item were confounded.].
+The model included random intercepts for each participant and random slopes for trial within participants (model notation in `R`: `correct ~ age + trial + (trial|id)` ).
+We pre-registered the inclusion of random intercepts for item.
+We deviate from this here because the order of items was fixed and the same for all participants so that trial and item were confounded for each task.
 For each task, we inspected and visualized the posterior distribution (mean and 95% Credible Interval (CrI)) for the age estimate.
@@
 Second, we used a GLMM based approach suggested by @rouder2019psychometrics.
-Here, a GLMM was fitted to the trial-by-trial data for each task with a fixed effect of age (in years, centered at the mean), a random intercept for each participant and a random slope for test day (`correct ~ age + (0+test_day|id)`)^[The notation `0+test_day` yields a separate intercept estimate for each test day and subject instead of an intercept estimate for day 1 and a slope for the difference between day 1 and day 2.
-As a consequence, the model estimates the correlation between the two test days instead of a correlation between an intercept and the slope for test day.].
-The model yields a participant specific estimate for each test day and also estimates the correlation between the two.
-This correlation can be interpreted as the re-test reliability.
+Here, a GLMM was fitted to the trial-by-trial data for each task with a fixed effect of age (in years, centered at the mean), a random intercept for each participant and a random slope for test day (`correct ~ age + (0+test_day|id)`).
+The notation `0+test_day` yields a separate intercept estimate for each test day and subject instead of an intercept estimate for day 1 and a slope for the difference between day 1 and day 2.
+As a consequence, the model estimates the correlation between the two test days instead of a correlation between an intercept and the slope for test day.
+The correlation between test days can be interpreted as the re-test reliability.
 This approach has several advantages.
@@
 
-Based on these results of Study 1, we compiled a new set of tasks for Study 2.
+The goal of Study 2 was to assess the re-test reliability in a new set of tasks.
 We retained the mutual exclusivity and card sorting tasks because of the interesting relation between the two found in Study 2.
@@
 Because the highest plausible correlation between two tasks is the product of their reliabilities (higher correlations would mean that the task is more strongly related to a different task than to itself), the highest we could expect were correlations between two tasks around 0.7 * 0.7 = 0.49.
-We planned our sample so that we could detect correlations between two tasks of 0.3 with 95% power^[The first author drafted a pre-registration and shared it with the last author but forgot to register it at OSF.
-Thus, the study was not officially pre-registered.].
+We planned our sample so that we could detect correlations between two tasks of 0.3 with 95% power.
+The first author drafted a pre-registration and shared it with the last author but forgot to register it at OSF.
+Thus, the study was not officially pre-registered.
 Data, analysis scripts and experiment code can be found in the associated online repository.
@@
 $$P_{L_1}(r|u)\propto P_{S_1}(u|r) \cdot P(r)$$
-In the above equation, the listener ($P_{L_1}$) is trying to infer the speaker’s ($P_{S_1}$) intended referent r by imagining what a rational speaker would say, given the referent they are trying to communicate and combining it with the listener’s prior expectations about the referent $P(r)$^[We assumed a uniform prior distribution over potential referents.].
+In the above equation, the listener ($P_{L_1}$) is trying to infer the speaker’s ($P_{S_1}$) intended referent $r$ by imagining what a rational speaker would say, given the referent they are trying to communicate and the listener’s prior expectations about the referent $P(r)$ (which we assumed to be uniform over potential referents).
 The speaker is an approximately rational Bayesian actor (with degree of rationality $\alpha$) who produces utterances as a function of their informativity.
